### 2016-05-23 raspi_journal.tex
Initial commit. LaTeX template for the journal and related packages for compiling

%  LaTeX support: latex@mdpi.com
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.

%=================================================================
\documentclass[electronics,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}

%--------------------
% Class Options:
%--------------------
% journal
%----------
% Choose between the following MDPI journals:
% actuators, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, atmosphere, atoms, axioms, batteries, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, challenges, chemosensors, children, chromatography, climate, coatings, computation, computers, condensedmatter, cosmetics, cryptography, crystals, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, fishes, fluids, foods, forests, futureinternet, galaxies, games, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, inventions, jcdd, jcm, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, lubricants, machines, magnetochemistry, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nutrients, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, processes, proteomes, publications, recycling, religions, remotesensing, resources, risks, robotics, safety, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, sustainability, symmetry, systems, technologies, toxics, toxins, universe, urbansci, vaccines, vetsci, viruses, water
%---------
% article
%---------
% The default type of manuscript is article, but can be replaced by:
% addendum, article, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimage, letter, newbookreceived, opinion, obituary, projectreport, reply, retraction, review, sciprints, shortnote, supfile, technicalnote
% supfile = supplementary materials
%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g. the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\articlenumber{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2016}
\copyrightyear{2016}
\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed

%=================================================================
%% Please use the following mathematics environments:
 \theoremstyle{mdpi}
 \newcounter{thm}
 \setcounter{thm}{0}
 \newcounter{ex}
 \setcounter{ex}{0}
 \newcounter{re}
 \setcounter{re}{0}

 \newtheorem{Theorem}[thm]{Theorem}
 \newtheorem{Lemma}[thm]{Lemma}
 \newtheorem{Corollary}[thm]{Corollary}
 \newtheorem{Proposition}[thm]{Proposition}

 \theoremstyle{mdpidefinition}
 \newtheorem{Characterization}[thm]{Characterization}
 \newtheorem{Property}[thm]{Property}
 \newtheorem{Problem}[thm]{Problem}
 \newtheorem{Example}[ex]{Example}
 \newtheorem{ExamplesandDefinitions}[ex]{Examples and Definitions}
 \newtheorem{Remark}[re]{Remark}
 \newtheorem{Definition}[thm]{Definition}
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{The paper title}

% Authors, for the paper (add full first names)
\Author{N\'estor J. Hern\'andez Marcano $^{1,\dagger,\ddagger}$, Chres W. S{\o}rensen $^{1,\ddagger}$, Juan A. Cabrera G., Daniel E. Lucani and Frank H. P. Fitzek $^{2,}$*}
% Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Steinwuf ApS; nestor@steinwurf.com\\
$^{2}$ \quad Aalborg University, Department of Electronic Systems; nh@es.aau.dk}

% Contact information of the corresponding author
\corres{Correspondence: nh@es.aau.dk; Tel.: +45 51 20 03 49}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3}
\secondnote{These authors contributed equally to this work. Authors}

% Simple summary
%\simplesumm{}

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations. The abstract should be an objective representation of the article: it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3. List three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\S$ in the end of the title of this article.
%\conference{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:

%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Sections that are not mandatory are listed as such. The section titles given are for Articles. Review papers and other article types have a more flexible structure.

%% Only for the journal Gels: Please place the Experimental Section after the Conclusions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

The template details the sections that can be used in a manuscript. Sections that are not mandatory are listed as such. The section titles given are for Articles. Review papers and other article types have a more flexible structure. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications should be cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the main conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. And now citing a book reference \cite{ref-book}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}[leftmargin=*,labelsep=4mm]
\item	First bullet
\item	Second bullet
\item	Third bullet
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}[leftmargin=*,labelsep=3mm]
\item	First item
\item	Second item
\item	Third item
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure 1, Table 1, etc.

\begin{figure}[H]
\centering
%\includegraphics[width=3cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\small % Font size can be changed to match table content. Recommend 10 pt.
\centering
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
entry 1		& data			& data\\
entry 2		& data			& data\\
\bottomrule
\end{tabular}
\end{table}

\subsection{Formatting of Mathematical Components}

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}

%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}
The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

This section may be divided by subheadings. Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

This section should be divided by subheadings. Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{All sources of funding of the study should be disclosed. Please clearly indicate grants that you have received in support of your research work. Clearly state if you received funds for covering the costs to publish in open access.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``X.X. and Y.Y. conceived and designed the experiments; X.X. performed the experiments; X.X. and Y.Y. analyzed the data; W.W. contributed reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be limited to those who have contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictofinterests{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent MDPI: Multidisciplinary Digital Publishing Institute\\
DOAJ: Directory of open access journals\\
TLA: Three letter acronym\\
LD: linear dichroism}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\appendix
\section{}
The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathemtaical proofs of results not central to the paper can be added as an appendix.

\section{}
All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{mdpi}

%=====================================
% References, variant A: internal bibliography
%=====================================
\renewcommand\bibname{References}
\begin{thebibliography}{999}
% Reference 1
\bibitem{ref-journal}
Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
% Reference 2
\bibitem{ref-book}
Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
\end{thebibliography}

%=====================================
% References, variant B: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds ...... are available from the authors.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2016-05-26 raspi_journal.tex
Add paper structure. Remove redundancy. Add bibtex and acknowledgements

@@
 \copyrightyear{2016}
-\externaleditor{Academic Editor: name}
+\externaleditor{Academic Editor: Steven Johnston and Simon J. Cox}
 \history{Received: date; Accepted: date; Published: date}
@@
 % Full title of the paper (Capitalized)
-\Title{The paper title}
+\Title{As Easy as Pi: A Network Coding Raspberry Pi Testbed}
 
 % Authors, for the paper (add full first names)
-\Author{N\'estor J. Hern\'andez Marcano $^{1,\dagger,\ddagger}$, Chres W. S{\o}rensen $^{1,\ddagger}$, Juan A. Cabrera G., Daniel E. Lucani and Frank H. P. Fitzek $^{2,}$*}
+\Author{N\'estor J. Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W. S{\o}rensen $^{2,\dagger}$, Juan A. Cabrera G. $^{3}$, Daniel E. Lucani $^{2,\dagger}$ and Frank H. P. Fitzek $^{3}$}
 % Authors, for metadata in PDF
-\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
+\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Daniel Lucani and Frank Fitzek}
 
@@
 \address{%
-$^{1}$ \quad Steinwuf ApS; nestor@steinwurf.com\\
-$^{2}$ \quad Aalborg University, Department of Electronic Systems; nh@es.aau.dk}
+$^{1}$ \quad Steinwurf ApS; nestor@steinwurf.com\\
+$^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
+$^{3}$ \quad Technische Universi\"at Dresden, Deutsche Telekom Chair of Communications and Networks; \{juan.cabrera, frank.fitzek\}@tu-dresden.de}
 
 % Contact information of the corresponding author
-\corres{Correspondence: nh@es.aau.dk; Tel.: +45 51 20 03 49}
+\corres{Correspondence: nestor@steinwurf.com, nh@es.aau.dk; Tel.: +45 51 20 03 49}
 
 % Current address and/or shared authorship
-\firstnote{Current address: Affiliation 3}
-\secondnote{These authors contributed equally to this work. Authors}
+\firstnote{Fredrik Bajers Vej 7, Room: A3-111. Aalborg, Denmark}
 
@@
 % Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{A single paragraph of about 200 words maximum.
+\abstract{The abstract}
+
+% A single paragraph of about 200 words maximum.
 For research articles, abstracts should give a pertinent overview of the work.
 We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article: it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
+The abstract should be an objective representation of the article: it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.
 
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3. List three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.}
+\keyword{Network Coding; Raspberry Pi; Testbed; C++}
+
+% keyword 1; keyword 2; keyword 3. List three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\setcounter{section}{-1} %% Remove this when starting to work on the template.
-\section{How to Use this Template}
+% \setcounter{section}{-1} %% Remove this when starting to work on the template.
+% \section{How to Use this Template}
 
-The template details the sections that can be used in a manuscript.
+% The template details the sections that can be used in a manuscript.
 Sections that are not mandatory are listed as such.
@@
 
-The introduction should briefly place the study in a broad context and highlight why it is important.
+%The introduction should briefly place the study in a broad context and highlight why it is important.
 It should define the purpose of the work and its significance.
@@
 As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-And now citing a book reference \cite{ref-book}.
+
+Network Coding (NC) reference \cite{ahlswede2000network}.
+
+\section{Testbed Description}
+\subsection{System Overview}
+\subsection{Installation and Updating}
+\subsection{Platform Support: Architectures, OS, compilers and Cross-compilation}
+
+\section{Network Codes}
+\subsection{RLNC}
+\subsection{S-RLNC}
+\subsection{TSNC}
+
+\section{Topologies}
+\subsection{Unicast}
+\subsection{Broadcast}
+
+\section{Analyzed Metrics}
+\subsection{Encoding and Decoding Speeds}
+\subsection{Latency}
+\subsection{Energy}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Subsection}
-\subsubsection{Subsubsection}
+% \subsection{Subsection}
+% \subsubsection{Subsubsection}
 
-Bulleted lists look like this:
-\begin{itemize}[leftmargin=*,labelsep=4mm]
-\item	First bullet
-\item	Second bullet
-\item	Third bullet
-\end{itemize}
+% Bulleted lists look like this:
+% \begin{itemize}[leftmargin=*,labelsep=4mm]
+% \item	First bullet
+% \item	Second bullet
+% \item	Third bullet
+% \end{itemize}
 
-Numbered lists can be added as follows:
-\begin{enumerate}[leftmargin=*,labelsep=3mm]
-\item	First item
-\item	Second item
-\item	Third item
-\end{enumerate}
+% Numbered lists can be added as follows:
+% \begin{enumerate}[leftmargin=*,labelsep=3mm]
+% \item	First item
+% \item	Second item
+% \item	Third item
+% \end{enumerate}
 
-The text continues here.
+% The text continues here.
 
-\subsection{Figures, Tables and Schemes}
+% \subsection{Figures, Tables and Schemes}
 
-All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
+% All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
 
-\begin{figure}[H]
-\centering
-%\includegraphics[width=3cm]{logo-mdpi}
-\caption{This is a figure, Schemes follow the same formatting.
+% \begin{figure}[H]
+% \centering
+% %\includegraphics[width=3cm]{logo-mdpi}
+% \caption{This is a figure, Schemes follow the same formatting.
 If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
@@
 A caption on a single line should be centered.}
-\end{figure}
+% \end{figure}
 
-\begin{table}[H]
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-\small % Font size can be changed to match table content. Recommend 10 pt.
-\centering
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-entry 1		& data			& data\\
-entry 2		& data			& data\\
-\bottomrule
-\end{tabular}
-\end{table}
+% \begin{table}[H]
+% \caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
+% \small % Font size can be changed to match table content. Recommend 10 pt.
+% \centering
+% \begin{tabular}{ccc}
+% \toprule
+% \textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+% \midrule
+% entry 1		& data			& data\\
+% entry 2		& data			& data\\
+% \bottomrule
+% \end{tabular}
+% \end{table}
 
-\subsection{Formatting of Mathematical Components}
+% \subsection{Formatting of Mathematical Components}
 
-This is an example of an equation:
+% This is an example of an equation:
 
-\begin{equation}
-\mathbb{S}
-\end{equation}
+% \begin{equation}
+% \mathbb{S}
+% \end{equation}
 
@@
 The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
+% Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
 %% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-The text continues here. Proofs must be formatted as follows:
+% \begin{Theorem}
+% Example text of a theorem.
+% \end{Theorem}
+% The text continues here. Proofs must be formatted as follows:
 
 %% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
+% \begin{proof}[Proof of Theorem 1]
+% Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
+% \end{proof}
+% The text continues here.
+
+\section{Conclusion}
 
@@
 
-This section may be divided by subheadings.
+%This section may be divided by subheadings.
 Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
@@
 
-This section should be divided by subheadings.
+%This section should be divided by subheadings.
 Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
@@
 
-Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
+%Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
 If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
@@
 
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
 
@@
 %% optional
-\supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
+% \supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{All sources of funding of the study should be disclosed.
+\acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
+Curie project (317126) from the European Comission FP7 framework,
+the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
+and the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
+by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d).}
+
+%All sources of funding of the study should be disclosed.
 Please clearly indicate grants that you have received in support of your research work.
-Clearly state if you received funds for covering the costs to publish in open access.}
+Clearly state if you received funds for covering the costs to publish in open access.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
+% \authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
 The following statements should be used ``X.X.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictofinterests{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
+\conflictofinterests{The authors declare no conflict of interest.
+The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results.}
+
+%Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
 Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.}
+If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.
 
@@
 
-\noindent MDPI: Multidisciplinary Digital Publishing Institute\\
-DOAJ: Directory of open access journals\\
-TLA: Three letter acronym\\
-LD: linear dichroism}
+\noindent NC: Network Coding\\
+RLNC: Random Linear Network Coding\\}
 
@@
 %% optional
-\appendix
-\section{}
-The appendix is an optional section that can contain details and data supplemental to the main text.
+% \appendix
+% \section{}
+% The appendix is an optional section that can contain details and data supplemental to the main text.
 For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
@@
 
-\section{}
-All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
+% \section{}
+% All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
 
@@
 %=====================================
-\renewcommand\bibname{References}
-\begin{thebibliography}{999}
-% Reference 1
-\bibitem{ref-journal}
-Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
-% Reference 2
-\bibitem{ref-book}
-Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
-\end{thebibliography}
+% \renewcommand\bibname{References}
+% \begin{thebibliography}{999}
+% % Reference 1
+% \bibitem{ref-journal}
+% Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
+% % Reference 2
+% \bibitem{ref-book}
+% Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
+% \end{thebibliography}
 
@@
 %=====================================
-%\bibliography{your_external_BibTeX_file}
+\bibliography{raspi_journal}
 
@@
 %% optional
-\sampleavailability{Samples of the compounds ...... are available from the authors.}
+\sampleavailability{The testbed and measurements in this publication are both available from the authors.}
 

### 2016-05-27 raspi_journal.tex
Defining the sections. Use acronym file. Include cross-compiling description

@@
 % The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.
+
+% *** ACRONYM PACKAGE ***
+\usepackage[nolist]{acronym}
+\input{acronym} % Name of acronyms file
 
@@
 % Full title of the paper (Capitalized)
-\Title{As Easy as Pi: A Network Coding Raspberry Pi Testbed}
+\Title{Easy as Pi: A Network Coding Raspberry Pi Testbed}
 
@@
 % Current address and/or shared authorship
-\firstnote{Fredrik Bajers Vej 7, Room: A3-111. Aalborg, Denmark}
+\firstnote{Fredrik Bajers Vej 7, Room A3-111. Aalborg, Denmark}
 
@@
 % Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{The abstract}
+\abstract{Due to the recurrent nature }
 
@@
 
+At the beginning, there was darkness and then... bang! \ac{NC}
+\cite{ahlswede2000network} appeared to save us from the evilness
+of routing.
+
+General introduction. Introduction to topic addressed in the journal.
+Review of the State of the Art. Specify why our approach has benefits
+and which are they. Indicate contributions.
+
+Our work is organized as follows: Section \ref{sec:testbed} introduces
+the testbed system, its setup, connectivity, files configuration and
+compilation of the Kodo library. Section \ref{sec:schemes} defines the
+coding schemes employed in our study. Section \ref{sec:topologies} some
+configurable topologies in the tested. Later, in Section \ref{sec:metrics}
+we describe the considered metrics for performance comparison of the
+codes deployed in the Raspberry Pi. In Section \ref{sec:results}, we show
+the measurements in the Raspberry Pi of the mentioned metrics. Final
+conclusions and future work are reviewed in Section \ref{sec:conclusions}.
+
 %The introduction should briefly place the study in a broad context and highlight why it is important.
@@
 
-Network Coding (NC) reference \cite{ahlswede2000network}.
+\section{Testbed Description}
+\label{sec:testbed}
 
-\section{Testbed Description}
+We proceed to define the testbed environment by each of its conforming
+parts. We later indicate a procedure to set up the testbed. In this procedure,
+we summarize all the details regarding on setting the connectivity and
+system files for a set of Raspberry Pis in a centralized fashion.
+Afterwards, we indicate how to cross-compile the Kodo library in an
+easy way. Finally, we provide further information about Kodo itself in terms
+of testing, other platforms supported and source code documentation
+for further references.
+
 \subsection{System Overview}
 \subsection{Installation and Updating}
-\subsection{Platform Support: Architectures, OS, compilers and Cross-compilation}
+\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
 
-\section{Network Codes}
-\subsection{RLNC}
-\subsection{S-RLNC}
-\subsection{TSNC}
+Besides the previous description (\textbf{Include compiling Kodo from the
+RasPi from the scratch}), the testbed administrator can compile Kodo in its
+personal workstation and transfer the generated binaries directly to
+a path in the Raspberry Pi. To achieve this, we get a toolchain that
+contains the binaries for the \texttt{raspberry-gxx49-arm-g++} compiler
+for the Raspberry Pi. Therefore, we strongly recommend any testbed
+administrator to do the following procedure. In what follows, we provide
+the instructions considering that the NFS server uses the \texttt{\$HOME}
+directory as the working directory. However, the administrator may choose
+some other working directory of its preference if desired.
+
+\begin{enumerate}
+
+\item Download the Raspberry Pi toolchain for 64-bit Linux from: \\
+\texttt{http://buildbot.steinwurf.dk/toolchains/linux/} to your
+\texttt{\$HOME} directory. \\
+
+\item Extract the downloaded file locally in the NFS server. After
+this operation, there should be a new directory for the toolchain
+in the server. \\
+
+\item Add the \texttt{bin} folder of the toolchain to the \texttt{PATH}
+Linux environment variable of the server. This will help the server OS
+to recognize the location of the compiler command, which will be needed
+later. To do so, edit the \texttt{\$HOME/.profile} to add in a newline:
+\texttt{PATH="\$PATH:\$HOME/raspberry-gxx49-arm/bin"}. Save the
+\texttt{\$HOME/.profile}. \\
+
+\item Restart the server session in order for the changes made in the
+previous step take effect. To verify this, open a new terminal and type:
+\texttt{raspberry-gxx49-arm-g++ --version}. A correct binary installation
+should return an output similar to:
+
+\texttt{raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
+Copyright (C) 2014 Free Software Foundation, Inc.
+This is free software; see the source for copying conditions.  There is NO
+warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.} \\
+
+\item Clone the Kodo repository in the server by executing: \\
+\texttt{git clone git://github.com/steinwurf/kodo.git} in \texttt{\$HOME}. \\
+
+\item Navigate to the repository and configure \texttt{waf} by typing:
+\texttt{python config.py} and select the 16th ``make specification'' file
+for the Raspberry Pi which is option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
+presented by the file.
+
+This command configures \texttt{waf} to use the proper compiler and its
+required flags to generate the binaries for the Raspberry Pi. If the
+configuration was correct, the output will indicate:
+\texttt{'configure' finished successfully (X.XXXs)}, where \texttt{X.XXX}
+is total time in seconds for configuring the project in the server. \\
+
+\item Execute \texttt{python waf build}. If the build process was
+successful, the generated binaries for the Raspberry Pi should be located
+in \texttt{build/cxx\_raspberry\_gxx49\_arm} in the Kodo repository.
+\textbf{Indicate how the binary files should look like}.
+
+Once this procedure is made, the testbed administrator can relocate the
+generated binary files to Raspberry Pi's through the network as desired
+by using the \texttt{scp} command during the configuration step.
+
+\end{enumerate}
+
+\subsection{Kodo Builds, Platform Support and Documentation}
+Link to the buildbot and the relevant webpages providing a description
+of them.
+
+\section{Coding Schemes}
+\label{sec:schemes}
+
+In this section, we present a description of the considered coding schemes
+measured with our the Raspberry Pi testbed. We introduce a definition
+for the primitive coding operations, e.g. encoding, decoding and recoding
+(where applies) for each coding scheme. Later, we address particular schemes
+which are obtained by modifying the basic coding operations.
+
+\subsection{Random Linear Network Coding}
+
+\ac{RLNC} is an example of intra-session \ac{NC}. Here, data symbols from a
+single flow are combined with each other. In this type of network coding,
+all the original data packets $P_j, j \in [1,g]$, each of $B$ bits, are used
+to create coded packets. In the following subsections, we describe the
+basic functionalities of \ac{RLNC}. Later, we mention applications that could
+potentially benefit from including \ac{RLNC} as a coding scheme.
+
+\subsubsection{Encoding}
+With \ac{RLNC}, each coded packet is a random linear
+combination of the original set of packets. Hence,
+a \ac{l.i.} set of $g$ coded packets, $C_i,\ i \in [1,g]$
+is required in order to get the original information.
+Each original packet is considered as a concatenation of elements
+from a \ac{GF} of a given size $q$, which we denote
+$GF(q)$. To create a coded packet, a coding coefficient
+$v_{i,j}$, is chosen at random from $GF(q)$ for every
+packet $P_j$ and multiplied and added
+following the respective \ac{GF} arithmetics. In this way,
+a coded packet is:
+%
+\begin{align} \label{eq:coded_packet}
+C_i  &= \bigoplus_{j=1}^{g} v_{i,j} \otimes P_j ,\ \forall i \in [1,g]
+\end{align}
+
+To indicate which packets were used to generate a coded packet, one
+form is to append its coding coefficients. In this case, the overhead
+included for $C_i,\ \forall i \in [1,g]$ by the coding coefficients
+is given by:
+%
+\begin{align} \label{eq:coded_packet}
+|v_i| &= \sum_{j=1}^{g} |v_{i,j}| = g \times \lceil \log_{2} (q)
+\rceil ~ [\mathrm{bits}]
+\end{align}
+
+\subsubsection{Decoding}
+To perform decoding, we define $\textbf{C} = \left[C_1 \ldots C_g \right]^T$
+and $\textbf{P} = \left[P_1 \ldots P_g \right]^T$. Then, decoding
+reduces to solve the linear system $\textbf{C} = \textbf{V} \cdot \textbf{P}$
+using Gaussian elimination \cite{fragouli2006network}.
+Here, the coding matrix $\textbf{V}$ contains any set of $g$ linearly
+independent packets $C_i$ as rows as follows:
+%
+\begin{align} \label{eq:coding_matrix}
+\textbf{V} =
+\left[
+\begin{array}{c}
+        v_1    \\ \hline
+        \vdots \\ \hline
+        v_g    \\
+\end{array}
+\right]
+=
+\left[
+\begin{array}{ccc}
+        v_{1,1} & \ldots & v_{1,g} \\
+        \vdots  & \ddots & \vdots  \\
+        v_{g,1} & \ldots & v_{g,g} \\
+\end{array}
+\right]
+\end{align}
+%
+The decoder begins to compute and remove the contributions from each
+of the pivot elements, e.g. leftmost elements in the main diagonal of
+\eqref{eq:coding_matrix}, to reduce $\textbf{V}$ to reduced echelon
+form. In this way, it is possible to recover the original set of packets.
+
+\subsubsection{Recoding}
+Network coding allows intermediate nodes in a network to
+recombine (or recode) packets from their sources whether they are
+coded or not. In general, a recoded packet should be indistinguishable
+from a coded one. Thus, we define a recoded packet as
+$R_i$ and its corresponding encoding vector as
+$w_i$ with coding coefficients $ \left[w_{i,1} \ldots w_{i,g} \right]$,
+as follows:
+%
+\begin{align}
+\label{eq:recoded_packet}
+R_i = \bigoplus_{j=1}^{g} w_{i,j} \otimes C_j  ,\ \forall i \in [1,g]
+\end{align}
+
+In \eqref{eq:recoded_packet}, $w_{i,j}$ is the coding coefficient that
+multiplies $C_j$, uniformly and randomly chosen from $GF(q)$. Any
+decoder that collects $R_i, i \in [1,g]$ linearly independent coded packets,
+with their respective $w_i$, will be able to decode the data as mentioned
+before.
+
+\subsection{Sparse Random Linear Network Coding}
+
+In \ac{SRLNC}, instead of considering all the packets to create a coded
+packet like \ac{RLNC} does, here the encoder sets some coding coefficients to
+zero when creating a new coded packet. This permits to reduce the complexity
+of both the encoding and decoding operations since the encoder (or decoder)
+requires less operations to process the data. Therefore, a new code parameter
+to control the sparsity, the code density $d$, is included to vary the
+number of non-zero packet that are combined. Here are various approaches to
+set the density.
+
+A first method is to specify the number of zeros in a given
+generation size and later generate coded packets with this amount. For example:
+16 zeros in a coding vector of 64 packets where the position of zeros are
+modified at random for every coded packet generated. Another method is to
+define an average number of zeros in the coding vector. Therefore, more or
+less zeros are exactly generated for each coded packet in the process.
+However, if not carefully made, using a sparse coding scheme might increase
+the probability of generating \ac{l.d.} packets which incurs both overhead
+from redundant information and processing delay.
+
+\subsection{Tunable Sparse Network Coding}
 
 \section{Topologies}
+\label{sec:topologies}
 \subsection{Unicast}
@@
 \section{Analyzed Metrics}
+\label{sec:metrics}
 \subsection{Encoding and Decoding Speeds}
@@
 \section{Results}
+\label{sec:results}
 
@@
 \section{Conclusion}
+\label{sec:conclusions}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+%\section{Discussion}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
+%\section{Conclusions}
 

### 2016-05-29 raspi_journal.tex
Include buildbot and documentation descriptions and cite

@@
 \texttt{python config.py} and select the 16th ``make specification'' file
-for the Raspberry Pi which is option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
+for the Raspberry Pi, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
 presented by the file.
@@
 
-\subsection{Kodo Builds, Platform Support and Documentation}
-Link to the buildbot and the relevant webpages providing a description
-of them.
+\subsection{Kodo Builds for the Raspberry Pi, Platform Support and Documentation}
+
+You can check the build status of Kodo, Fifi and other relevant projects through
+their respective repository master branch on our buildbot page
+\cite{steinwurf2016buildbot}. Our buildbot displays the status of the builds for
+Raspbian 8 and GCC 4.9 for the ARM architecture which is the relevant one for the
+Raspberry Pi. At the link, you can check build status and build statistics. Also,
+documentation about Kodo basics with a tutorial is available at \cite{kododocs}.
 

### 2016-05-30 raspi_journal.tex
Wrote about TSNC

@@
 \documentclass[electronics,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
+\synctex=1
+\usepackage{fixme}
+
+\newcommand\floor[1]{\lfloor#1\rfloor}
 
@@
 %
-\begin{align} \label{eq:coded_packet}
+\begin{align} \label{eq:coded_packet_coef}
 |v_i| &= \sum_{j=1}^{g} |v_{i,j}| = g \times \lceil \log_{2} (q)
@@
 In \ac{SRLNC}, instead of considering all the packets to create a coded
-packet like \ac{RLNC} does, here the encoder sets some coding coefficients to
-zero when creating a new coded packet. This permits to reduce the complexity
-of both the encoding and decoding operations since the encoder (or decoder)
-requires less operations to process the data. Therefore, a new code parameter
-to control the sparsity, the code density $d$, is included to vary the
-number of non-zero packet that are combined. Here are various approaches to
-set the density.
+packet like \ac{RLNC} does, here the encoder sets more coding coefficients to
+zero when creating a new coded packet.
+In practice this can be implemented in
+a couple of ways.
+%One way to accomplish this is to add a Bernoulli random
+%variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:
+The simplest way to accomplish this is to add a Bernoulli random
+variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:
 
-A first method is to specify the number of zeros in a given
-generation size and later generate coded packets with this amount. For example:
-16 zeros in a coding vector of 64 packets where the position of zeros are
-modified at random for every coded packet generated. Another method is to
-define an average number of zeros in the coding vector. Therefore, more or
-less zeros are exactly generated for each coded packet in the process.
-However, if not carefully made, using a sparse coding scheme might increase
-the probability of generating \ac{l.d.} packets which incurs both overhead
-from redundant information and processing delay.
+\begin{align} \label{eq:sparse_coded_packet}
+    C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
+    v_{i,j} > 0,\
+    d \in
+    \begin{cases}
+        {]0,0.5]} & \text{for } q=2 \\
+        {]0,1]} & \text{for } q>2
+    \end{cases}
+\end{align}
+
+We call $d$ the coding density.
+Reducing $d$ enables the encoder to decrease the average number of packets that
+are mixed into each coded packet. Thereby reducing the complexity of the
+encoder that needs to mix less packets, but also on the decoder that in
+contrast needs to eliminate less nonzero coding coefficients. The catch of this
+approach is that coded packets produced by the encoder becomes more \ac{l.d.}
+on each other as the coding complexity is reduced. This incurs in additional
+channel overhead.
+
+Generating a coded packet does not imply that it contains any data at all. I.e.
+$ \left[ B(d)_{1}, \ldots, B(d)_{g} \right] = \mathbf{0}$.
+In that case, one would have to trash the coded packet and generate a new one.
+
+Most coded packets that are produced by the encoder are typically very sparse.
+We will therefore rely on a slightly different implementation in KODO
+\ref{eq:sparse_coded_packet2} that proved faster for low densities. It is best
+expressed as:
+
+\begin{align} \label{eq:sparse_coded_packet2}
+    C_i  &= \bigoplus_{j=1}^{\floor{\text{Binom}(g,d)}} v_{i,m} \otimes P_{m} ,\
+    %L \subseteq \{1,\dots,g\}: |L|=k ,\
+    \forall i \in [1,g] ,\
+    v_{i,j} > 0
+\end{align}
+where
+$m = \text{choice}(\{1,\dots,g\}, \text{size}=k, \text{replace}=\text{False})$.
+\fxnote{Can this be represented smarter?}
+
+%To solve this, one could trash the coded packet and generate a new coded
+%packet. This is not the most efficient because KODO needs to count the
+%the number of nonzero coding coefficients in each coded packets to eliminate
+%all zero packets.
+%
+%This is the most correct approach, but the most efficient approach although it is mathematically .
+
+It is often desired to express the coding density as $d=\frac{k}{g}$. We call
+this notation $k-sparse$ where $k$ is the average number of packets combined to
+produce a coded packet.
+
+%For low coding density, the encoder might generate a coded packet that consists
+%of no coded packets. I.e. the packet consists of all zeroes
+
+%In \ac{SRLNC}, instead of considering all the packets to create a coded
+%packet like \ac{RLNC} does, here the encoder sets some coding coefficients to
+%zero when creating a new coded packet. This permits to reduce the complexity
+%of both the encoding and decoding operations since the encoder (or decoder)
+%requires less operations to process the data. Therefore, a new code parameter
+%to control the sparsity, the code density $d$, is included to vary the
+%number of non-zero packet that are combined. Here are various approaches to
+%set the density.
+%
+%A first method is to specify the number of zeros in a given
+%generation size and later generate coded packets with this amount. For example:
+%16 zeros in a coding vector of 64 packets where the position of zeros are
+%modified at random for every coded packet generated. Another method is to
+%define an average number of zeros in the coding vector. Therefore, more or
+%less zeros are exactly generated for each coded packet in the process.
+%However, if not carefully made, using a sparse coding scheme might increase
+%the probability of generating \ac{l.d.} packets which incurs both overhead
+%from redundant information and processing delay.
 
 \subsection{Tunable Sparse Network Coding}
+
+\ac{TSNC} can be considered an extension to \ac{SRLNC}. The overall idea is
+not only for the encoder to generate sparse coded packets, but also to
+choose the sparsity of packets wiser. That is, as the decoder accomulates more
+coded packets it becomes more and more likely that the next received
+coded packet will be \ac{l.d.}.
+
+The idea of \ac{TSNC} is therefore to gradually increase the coding density
+as the decoderes \ac{DOF} increases. This enables TSNC to save a lot of
+complexity particulary in the beginning of transmissions, but also to
+tailor the coding delay. I.e. approximate the number of coded packets a
+decoder needs to receive to decode a generation of $g$ packets. We call
+this number the budget, $B$.
+
+Provided a desired budget, $B \geq g$, and the decoders \ac{DOF} it can be
+estimated how sparse the coded packets should be to finish a transmission in
+time.
+
+In our implementation, it is the encoders responsibility to estimate the coding
+density. We use feedback to provide the encoder a better estimate of the
+decoders \ac{DOF} at pre-defined points. Namely, when the decoder obtains the
+following \ac{DOF}'s:
+
+\begin{equation}\label{eq:feedback_dofs}
+    s(k) = g\cdot \frac{2^k -1}{2^k},  \; \text{for } k=0,1,2,\dots,k_t 
+\end{equation}
+where $k$ is the $k$-th feedback packet that is transmitted during a generation.
+
+The encoder considers the time between feedback packets as regions. It then
+estimates a fixed coding density for each region when a feedback packet is
+received.
+
+Before the coding density can be estimated it is essential that the encoder
+has a good estimate of the decoders \ac{DOF}, but also the remainder of the
+total budget. The feedback scheme \ref{eq:feedback_dofs} roughly splits the
+remaining \ac{DOF} in halves. This is also the case for the budget that is
+split equally among the two new regions. The very last region will be asigned
+the full remainder of the total budget.
 

### 2016-05-30 raspi_journal.tex
small chagne
Fixed Frank and Juan's affiliation

@@
 $^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
-$^{3}$ \quad Technische Universi\"at Dresden, Deutsche Telekom Chair of Communications and Networks; \{juan.cabrera, frank.fitzek\}@tu-dresden.de}
+$^{3}$ \quad Technische Universi\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, frank.fitzek\}@tu-dresden.de}
 
@@
 \begin{equation}\label{eq:feedback_dofs}
-    s(k) = g\cdot \frac{2^k -1}{2^k},  \; \text{for } k=0,1,2,\dots,k_t 
+    s(k) = g\cdot \frac{2^k -1}{2^k},  \; \text{for } k=0,1,2,\dots
 \end{equation}

### 2016-05-30 raspi_journal.tex
Added Simon Wunderlich as author

@@
 % Authors, for the paper (add full first names)
-\Author{N\'estor J. Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W. S{\o}rensen $^{2,\dagger}$, Juan A. Cabrera G. $^{3}$, Daniel E. Lucani $^{2,\dagger}$ and Frank H. P. Fitzek $^{3}$}
+\Author{N\'estor J.
+Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W.
+S{\o}rensen $^{2,\dagger}$, Juan A.
+Cabrera G.
+$^{3}$, Simon Wunderlich $^{3}$, Daniel E.
+Lucani $^{2,\dagger}$ and Frank H.
+P.
+Fitzek $^{3}$}
 % Authors, for metadata in PDF
@@
 $^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
-$^{3}$ \quad Technische Universi\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, frank.fitzek\}@tu-dresden.de}
+$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de}
 

### 2016-05-30 raspi_journal.tex
.
Breaking the main into pieces to allow parallel working

@@
 \section{Introduction}
-
-At the beginning, there was darkness and then... bang! \ac{NC}
-\cite{ahlswede2000network} appeared to save us from the evilness
-of routing.
-
-General introduction. Introduction to topic addressed in the journal.
-Review of the State of the Art. Specify why our approach has benefits
-and which are they. Indicate contributions.
-
-Our work is organized as follows: Section \ref{sec:testbed} introduces
-the testbed system, its setup, connectivity, files configuration and
-compilation of the Kodo library. Section \ref{sec:schemes} defines the
-coding schemes employed in our study. Section \ref{sec:topologies} some
-configurable topologies in the tested. Later, in Section \ref{sec:metrics}
-we describe the considered metrics for performance comparison of the
-codes deployed in the Raspberry Pi. In Section \ref{sec:results}, we show
-the measurements in the Raspberry Pi of the mentioned metrics. Final
-conclusions and future work are reviewed in Section \ref{sec:conclusions}.
-
-%The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications should be cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the main conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
+\input{introduction}
 
 \section{Testbed Description}
-\label{sec:testbed}
-
-We proceed to define the testbed environment by each of its conforming
-parts. We later indicate a procedure to set up the testbed. In this procedure,
-we summarize all the details regarding on setting the connectivity and
-system files for a set of Raspberry Pis in a centralized fashion.
-Afterwards, we indicate how to cross-compile the Kodo library in an
-easy way. Finally, we provide further information about Kodo itself in terms
-of testing, other platforms supported and source code documentation
-for further references.
-
-\subsection{System Overview}
-\subsection{Installation and Updating}
-\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
-
-Besides the previous description (\textbf{Include compiling Kodo from the
-RasPi from the scratch}), the testbed administrator can compile Kodo in its
-personal workstation and transfer the generated binaries directly to
-a path in the Raspberry Pi. To achieve this, we get a toolchain that
-contains the binaries for the \texttt{raspberry-gxx49-arm-g++} compiler
-for the Raspberry Pi. Therefore, we strongly recommend any testbed
-administrator to do the following procedure. In what follows, we provide
-the instructions considering that the NFS server uses the \texttt{\$HOME}
-directory as the working directory. However, the administrator may choose
-some other working directory of its preference if desired.
-
-\begin{enumerate}
-
-\item Download the Raspberry Pi toolchain for 64-bit Linux from: \\
-\texttt{http://buildbot.steinwurf.dk/toolchains/linux/} to your
-\texttt{\$HOME} directory. \\
-
-\item Extract the downloaded file locally in the NFS server. After
-this operation, there should be a new directory for the toolchain
-in the server. \\
-
-\item Add the \texttt{bin} folder of the toolchain to the \texttt{PATH}
-Linux environment variable of the server. This will help the server OS
-to recognize the location of the compiler command, which will be needed
-later. To do so, edit the \texttt{\$HOME/.profile} to add in a newline:
-\texttt{PATH="\$PATH:\$HOME/raspberry-gxx49-arm/bin"}. Save the
-\texttt{\$HOME/.profile}. \\
-
-\item Restart the server session in order for the changes made in the
-previous step take effect. To verify this, open a new terminal and type:
-\texttt{raspberry-gxx49-arm-g++ --version}. A correct binary installation
-should return an output similar to:
-
-\texttt{raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
-Copyright (C) 2014 Free Software Foundation, Inc.
-This is free software; see the source for copying conditions.  There is NO
-warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.} \\
-
-\item Clone the Kodo repository in the server by executing: \\
-\texttt{git clone git://github.com/steinwurf/kodo.git} in \texttt{\$HOME}. \\
-
-\item Navigate to the repository and configure \texttt{waf} by typing:
-\texttt{python config.py} and select the 16th ``make specification'' file
-for the Raspberry Pi, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
-presented by the file.
-
-This command configures \texttt{waf} to use the proper compiler and its
-required flags to generate the binaries for the Raspberry Pi. If the
-configuration was correct, the output will indicate:
-\texttt{'configure' finished successfully (X.XXXs)}, where \texttt{X.XXX}
-is total time in seconds for configuring the project in the server. \\
-
-\item Execute \texttt{python waf build}. If the build process was
-successful, the generated binaries for the Raspberry Pi should be located
-in \texttt{build/cxx\_raspberry\_gxx49\_arm} in the Kodo repository.
-\textbf{Indicate how the binary files should look like}.
-
-Once this procedure is made, the testbed administrator can relocate the
-generated binary files to Raspberry Pi's through the network as desired
-by using the \texttt{scp} command during the configuration step.
-
-\end{enumerate}
-
-\subsection{Kodo Builds for the Raspberry Pi, Platform Support and Documentation}
-
-You can check the build status of Kodo, Fifi and other relevant projects through
-their respective repository master branch on our buildbot page
-\cite{steinwurf2016buildbot}. Our buildbot displays the status of the builds for
-Raspbian 8 and GCC 4.9 for the ARM architecture which is the relevant one for the
-Raspberry Pi. At the link, you can check build status and build statistics. Also,
-documentation about Kodo basics with a tutorial is available at \cite{kododocs}.
+\input{testbed}
 
 \section{Coding Schemes}
-\label{sec:schemes}
-
-In this section, we present a description of the considered coding schemes
-measured with our the Raspberry Pi testbed. We introduce a definition
-for the primitive coding operations, e.g. encoding, decoding and recoding
-(where applies) for each coding scheme. Later, we address particular schemes
-which are obtained by modifying the basic coding operations.
-
-\subsection{Random Linear Network Coding}
-
-\ac{RLNC} is an example of intra-session \ac{NC}. Here, data symbols from a
-single flow are combined with each other. In this type of network coding,
-all the original data packets $P_j, j \in [1,g]$, each of $B$ bits, are used
-to create coded packets. In the following subsections, we describe the
-basic functionalities of \ac{RLNC}. Later, we mention applications that could
-potentially benefit from including \ac{RLNC} as a coding scheme.
-
-\subsubsection{Encoding}
-With \ac{RLNC}, each coded packet is a random linear
-combination of the original set of packets. Hence,
-a \ac{l.i.} set of $g$ coded packets, $C_i,\ i \in [1,g]$
-is required in order to get the original information.
-Each original packet is considered as a concatenation of elements
-from a \ac{GF} of a given size $q$, which we denote
-$GF(q)$. To create a coded packet, a coding coefficient
-$v_{i,j}$, is chosen at random from $GF(q)$ for every
-packet $P_j$ and multiplied and added
-following the respective \ac{GF} arithmetics. In this way,
-a coded packet is:
-%
-\begin{align} \label{eq:coded_packet}
-C_i  &= \bigoplus_{j=1}^{g} v_{i,j} \otimes P_j ,\ \forall i \in [1,g]
-\end{align}
-
-To indicate which packets were used to generate a coded packet, one
-form is to append its coding coefficients. In this case, the overhead
-included for $C_i,\ \forall i \in [1,g]$ by the coding coefficients
-is given by:
-%
-\begin{align} \label{eq:coded_packet_coef}
-|v_i| &= \sum_{j=1}^{g} |v_{i,j}| = g \times \lceil \log_{2} (q)
-\rceil ~ [\mathrm{bits}]
-\end{align}
-
-\subsubsection{Decoding}
-To perform decoding, we define $\textbf{C} = \left[C_1 \ldots C_g \right]^T$
-and $\textbf{P} = \left[P_1 \ldots P_g \right]^T$. Then, decoding
-reduces to solve the linear system $\textbf{C} = \textbf{V} \cdot \textbf{P}$
-using Gaussian elimination \cite{fragouli2006network}.
-Here, the coding matrix $\textbf{V}$ contains any set of $g$ linearly
-independent packets $C_i$ as rows as follows:
-%
-\begin{align} \label{eq:coding_matrix}
-\textbf{V} =
-\left[
-\begin{array}{c}
-        v_1    \\ \hline
-        \vdots \\ \hline
-        v_g    \\
-\end{array}
-\right]
-=
-\left[
-\begin{array}{ccc}
-        v_{1,1} & \ldots & v_{1,g} \\
-        \vdots  & \ddots & \vdots  \\
-        v_{g,1} & \ldots & v_{g,g} \\
-\end{array}
-\right]
-\end{align}
-%
-The decoder begins to compute and remove the contributions from each
-of the pivot elements, e.g. leftmost elements in the main diagonal of
-\eqref{eq:coding_matrix}, to reduce $\textbf{V}$ to reduced echelon
-form. In this way, it is possible to recover the original set of packets.
-
-\subsubsection{Recoding}
-Network coding allows intermediate nodes in a network to
-recombine (or recode) packets from their sources whether they are
-coded or not. In general, a recoded packet should be indistinguishable
-from a coded one. Thus, we define a recoded packet as
-$R_i$ and its corresponding encoding vector as
-$w_i$ with coding coefficients $ \left[w_{i,1} \ldots w_{i,g} \right]$,
-as follows:
-%
-\begin{align}
-\label{eq:recoded_packet}
-R_i = \bigoplus_{j=1}^{g} w_{i,j} \otimes C_j  ,\ \forall i \in [1,g]
-\end{align}
-
-In \eqref{eq:recoded_packet}, $w_{i,j}$ is the coding coefficient that
-multiplies $C_j$, uniformly and randomly chosen from $GF(q)$. Any
-decoder that collects $R_i, i \in [1,g]$ linearly independent coded packets,
-with their respective $w_i$, will be able to decode the data as mentioned
-before.
-
-\subsection{Sparse Random Linear Network Coding}
-
-In \ac{SRLNC}, instead of considering all the packets to create a coded
-packet like \ac{RLNC} does, here the encoder sets more coding coefficients to
-zero when creating a new coded packet.
-In practice this can be implemented in
-a couple of ways.
-%One way to accomplish this is to add a Bernoulli random
-%variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:
-The simplest way to accomplish this is to add a Bernoulli random
-variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:
-
-\begin{align} \label{eq:sparse_coded_packet}
-    C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
-    v_{i,j} > 0,\
-    d \in
-    \begin{cases}
-        {]0,0.5]} & \text{for } q=2 \\
-        {]0,1]} & \text{for } q>2
-    \end{cases}
-\end{align}
-
-We call $d$ the coding density.
-Reducing $d$ enables the encoder to decrease the average number of packets that
-are mixed into each coded packet. Thereby reducing the complexity of the
-encoder that needs to mix less packets, but also on the decoder that in
-contrast needs to eliminate less nonzero coding coefficients. The catch of this
-approach is that coded packets produced by the encoder becomes more \ac{l.d.}
-on each other as the coding complexity is reduced. This incurs in additional
-channel overhead.
-
-Generating a coded packet does not imply that it contains any data at all. I.e.
-$ \left[ B(d)_{1}, \ldots, B(d)_{g} \right] = \mathbf{0}$.
-In that case, one would have to trash the coded packet and generate a new one.
-
-Most coded packets that are produced by the encoder are typically very sparse.
-We will therefore rely on a slightly different implementation in KODO
-\ref{eq:sparse_coded_packet2} that proved faster for low densities. It is best
-expressed as:
-
-\begin{align} \label{eq:sparse_coded_packet2}
-    C_i  &= \bigoplus_{j=1}^{\floor{\text{Binom}(g,d)}} v_{i,m} \otimes P_{m} ,\
-    %L \subseteq \{1,\dots,g\}: |L|=k ,\
-    \forall i \in [1,g] ,\
-    v_{i,j} > 0
-\end{align}
-where
-$m = \text{choice}(\{1,\dots,g\}, \text{size}=k, \text{replace}=\text{False})$.
-\fxnote{Can this be represented smarter?}
-
-%To solve this, one could trash the coded packet and generate a new coded
-%packet. This is not the most efficient because KODO needs to count the
-%the number of nonzero coding coefficients in each coded packets to eliminate
-%all zero packets.
-%
-%This is the most correct approach, but the most efficient approach although it is mathematically .
-
-It is often desired to express the coding density as $d=\frac{k}{g}$. We call
-this notation $k-sparse$ where $k$ is the average number of packets combined to
-produce a coded packet.
-
-%For low coding density, the encoder might generate a coded packet that consists
-%of no coded packets. I.e. the packet consists of all zeroes
-
-%In \ac{SRLNC}, instead of considering all the packets to create a coded
-%packet like \ac{RLNC} does, here the encoder sets some coding coefficients to
-%zero when creating a new coded packet. This permits to reduce the complexity
-%of both the encoding and decoding operations since the encoder (or decoder)
-%requires less operations to process the data. Therefore, a new code parameter
-%to control the sparsity, the code density $d$, is included to vary the
-%number of non-zero packet that are combined. Here are various approaches to
-%set the density.
-%
-%A first method is to specify the number of zeros in a given
-%generation size and later generate coded packets with this amount. For example:
-%16 zeros in a coding vector of 64 packets where the position of zeros are
-%modified at random for every coded packet generated. Another method is to
-%define an average number of zeros in the coding vector. Therefore, more or
-%less zeros are exactly generated for each coded packet in the process.
-%However, if not carefully made, using a sparse coding scheme might increase
-%the probability of generating \ac{l.d.} packets which incurs both overhead
-%from redundant information and processing delay.
-
-\subsection{Tunable Sparse Network Coding}
-
-\ac{TSNC} can be considered an extension to \ac{SRLNC}. The overall idea is
-not only for the encoder to generate sparse coded packets, but also to
-choose the sparsity of packets wiser. That is, as the decoder accomulates more
-coded packets it becomes more and more likely that the next received
-coded packet will be \ac{l.d.}.
-
-The idea of \ac{TSNC} is therefore to gradually increase the coding density
-as the decoderes \ac{DOF} increases. This enables TSNC to save a lot of
-complexity particulary in the beginning of transmissions, but also to
-tailor the coding delay. I.e. approximate the number of coded packets a
-decoder needs to receive to decode a generation of $g$ packets. We call
-this number the budget, $B$.
-
-Provided a desired budget, $B \geq g$, and the decoders \ac{DOF} it can be
-estimated how sparse the coded packets should be to finish a transmission in
-time.
-
-In our implementation, it is the encoders responsibility to estimate the coding
-density. We use feedback to provide the encoder a better estimate of the
-decoders \ac{DOF} at pre-defined points. Namely, when the decoder obtains the
-following \ac{DOF}'s:
-
-\begin{equation}\label{eq:feedback_dofs}
-    s(k) = g\cdot \frac{2^k -1}{2^k},  \; \text{for } k=0,1,2,\dots
-\end{equation}
-where $k$ is the $k$-th feedback packet that is transmitted during a generation.
-
-The encoder considers the time between feedback packets as regions. It then
-estimates a fixed coding density for each region when a feedback packet is
-received.
-
-Before the coding density can be estimated it is essential that the encoder
-has a good estimate of the decoders \ac{DOF}, but also the remainder of the
-total budget. The feedback scheme \ref{eq:feedback_dofs} roughly splits the
-remaining \ac{DOF} in halves. This is also the case for the budget that is
-split equally among the two new regions. The very last region will be asigned
-the full remainder of the total budget.
+\input{schemes}
 
 \section{Topologies}
-\label{sec:topologies}
-\subsection{Unicast}
-\subsection{Broadcast}
+\input{topologies}
 
 \section{Analyzed Metrics}
-\label{sec:metrics}
-\subsection{Encoding and Decoding Speeds}
-\subsection{Latency}
-\subsection{Energy}
+\input{metrics}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
-
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+\section{Measurements}
+\input{measurements}
 

### 2016-05-30 schemes.tex
Breaking the main into pieces to allow parallel working

\label{sec:schemes}

In this section, we present a description of the considered coding schemes
measured with our the Raspberry Pi testbed. We introduce a definition
for the primitive coding operations, e.g. encoding, decoding and recoding
(where applies) for each coding scheme. Later, we address particular schemes
which are obtained by modifying the basic coding operations.

\subsection{Random Linear Network Coding}

\ac{RLNC} is an example of intra-session \ac{NC}. Here, data symbols from a
single flow are combined with each other. In this type of network coding,
all the original data packets $P_j, j \in [1,g]$, each of $B$ bits, are used
to create coded packets. In the following subsections, we describe the
basic functionalities of \ac{RLNC}. Later, we mention applications that could
potentially benefit from including \ac{RLNC} as a coding scheme.

\subsubsection{Encoding}
With \ac{RLNC}, each coded packet is a random linear
combination of the original set of packets. Hence,
a \ac{l.i.} set of $g$ coded packets, $C_i,\ i \in [1,g]$
is required in order to get the original information.
Each original packet is considered as a concatenation of elements
from a \ac{GF} of a given size $q$, which we denote
$GF(q)$. To create a coded packet, a coding coefficient
$v_{i,j}$, is chosen at random from $GF(q)$ for every
packet $P_j$ and multiplied and added
following the respective \ac{GF} arithmetics. In this way,
a coded packet is:
%
\begin{align} \label{eq:coded_packet}
C_i  &= \bigoplus_{j=1}^{g} v_{i,j} \otimes P_j ,\ \forall i \in [1,g]
\end{align}

To indicate which packets were used to generate a coded packet, one
form is to append its coding coefficients. In this case, the overhead
included for $C_i,\ \forall i \in [1,g]$ by the coding coefficients
is given by:
%
\begin{align} \label{eq:coded_packet_coef}
|v_i| &= \sum_{j=1}^{g} |v_{i,j}| = g \times \lceil \log_{2} (q)
\rceil ~ [\mathrm{bits}]
\end{align}

\subsubsection{Decoding}
To perform decoding, we define $\textbf{C} = \left[C_1 \ldots C_g \right]^T$
and $\textbf{P} = \left[P_1 \ldots P_g \right]^T$. Then, decoding
reduces to solve the linear system $\textbf{C} = \textbf{V} \cdot \textbf{P}$
using Gaussian elimination \cite{fragouli2006network}.
Here, the coding matrix $\textbf{V}$ contains any set of $g$ linearly
independent packets $C_i$ as rows as follows:
%
\begin{align} \label{eq:coding_matrix}
\textbf{V} =
\left[
\begin{array}{c}
        v_1    \\ \hline
        \vdots \\ \hline
        v_g    \\
\end{array}
\right]
=
\left[
\begin{array}{ccc}
        v_{1,1} & \ldots & v_{1,g} \\
        \vdots  & \ddots & \vdots  \\
        v_{g,1} & \ldots & v_{g,g} \\
\end{array}
\right]
\end{align}
%
The decoder begins to compute and remove the contributions from each
of the pivot elements, e.g. leftmost elements in the main diagonal of
\eqref{eq:coding_matrix}, to reduce $\textbf{V}$ to reduced echelon
form. In this way, it is possible to recover the original set of packets.

\subsubsection{Recoding}
Network coding allows intermediate nodes in a network to
recombine (or recode) packets from their sources whether they are
coded or not. In general, a recoded packet should be indistinguishable
from a coded one. Thus, we define a recoded packet as
$R_i$ and its corresponding encoding vector as
$w_i$ with coding coefficients $ \left[w_{i,1} \ldots w_{i,g} \right]$,
as follows:
%
\begin{align}
\label{eq:recoded_packet}
R_i = \bigoplus_{j=1}^{g} w_{i,j} \otimes C_j  ,\ \forall i \in [1,g]
\end{align}

In \eqref{eq:recoded_packet}, $w_{i,j}$ is the coding coefficient that
multiplies $C_j$, uniformly and randomly chosen from $GF(q)$. Any
decoder that collects $R_i, i \in [1,g]$ linearly independent coded packets,
with their respective $w_i$, will be able to decode the data as mentioned
before.

\subsection{Sparse Random Linear Network Coding}

In \ac{SRLNC}, instead of considering all the packets to create a coded
packet like \ac{RLNC} does, here the encoder sets more coding coefficients to
zero when creating a new coded packet.
In practice this can be implemented in
a couple of ways.
%One way to accomplish this is to add a Bernoulli random
%variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:
The simplest way to accomplish this is to add a Bernoulli random
variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:

\begin{align} \label{eq:sparse_coded_packet}
    %C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
    C_i  &= \bigoplus_{j=1}^{g} \text{B}(d) \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
    v_{i,j} > 0,\
    d \in
    \begin{cases}
        {(0,0.5]} & \text{for } q=2 \\
        {(0,1]} & \text{for } q>2
    \end{cases}
\end{align}

We call $d$ the coding density.
Reducing $d$ enables the encoder to decrease the average number of packets that
are mixed into each coded packet. Thereby reducing the complexity of the
encoder that needs to mix less packets, but also on the decoder that in
contrast needs to eliminate less nonzero coding coefficients. The catch of this
approach is that coded packets produced by the encoder becomes more \ac{l.d.}
on each other as the coding complexity is reduced. This incurs in additional
channel overhead.

Generating a coded packet does not imply that it contains any data at all. I.e.
$ \left[ B(d)_{1}, \ldots, B(d)_{g} \right] = \mathbf{0}$.
In that case, one would have to trash the coded packet and generate a new one.

Most coded packets that are produced by the encoder are typically very sparse.
We will therefore rely on a slightly different implementation in KODO
\ref{eq:sparse_coded_packet2} that proved faster for low densities. It is best
expressed as:

\begin{align} \label{eq:sparse_coded_packet2}
    C_i  &= \bigoplus_{j=1}^{\floor{\text{Binom}(g,d)}} v_{i,m} \otimes P_{m} ,\
    %L \subseteq \{1,\dots,g\}: |L|=k ,\
    \forall i \in [1,g] ,\
    v_{i,j} > 0
\end{align}
where
$m = \text{choice}(\{1,\dots,g\}, \text{size}=k, \text{replace}=\text{False})$.
\fxnote{Can this be represented smarter?}

%To solve this, one could trash the coded packet and generate a new coded
%packet. This is not the most efficient because KODO needs to count the
%the number of nonzero coding coefficients in each coded packets to eliminate
%all zero packets.
%
%This is the most correct approach, but the most efficient approach although it is mathematically .

It is often desired to express the coding density as $d=\frac{k}{g}$. We call
this notation $k-sparse$ where $k$ is the average number of packets combined to
produce a coded packet.

%For low coding density, the encoder might generate a coded packet that consists
%of no coded packets. I.e. the packet consists of all zeroes

%In \ac{SRLNC}, instead of considering all the packets to create a coded
%packet like \ac{RLNC} does, here the encoder sets some coding coefficients to
%zero when creating a new coded packet. This permits to reduce the complexity
%of both the encoding and decoding operations since the encoder (or decoder)
%requires less operations to process the data. Therefore, a new code parameter
%to control the sparsity, the code density $d$, is included to vary the
%number of non-zero packet that are combined. Here are various approaches to
%set the density.
%
%A first method is to specify the number of zeros in a given
%generation size and later generate coded packets with this amount. For example:
%16 zeros in a coding vector of 64 packets where the position of zeros are
%modified at random for every coded packet generated. Another method is to
%define an average number of zeros in the coding vector. Therefore, more or
%less zeros are exactly generated for each coded packet in the process.
%However, if not carefully made, using a sparse coding scheme might increase
%the probability of generating \ac{l.d.} packets which incurs both overhead
%from redundant information and processing delay.

\subsection{Tunable Sparse Network Coding}

\ac{TSNC} can be considered an extension to \ac{SRLNC}. The overall idea is
not only for the encoder to generate sparse coded packets, but also to
choose the sparsity of packets wiser. That is, as the decoder accomulates more
coded packets it becomes more and more likely that the next received
coded packet will be \ac{l.d.}.

The idea of \ac{TSNC} is therefore to gradually increase the coding density
as the decoderes \ac{DOF} increases. This enables TSNC to save a lot of
complexity particulary in the beginning of transmissions, but also to
tailor the coding delay. I.e. approximate the number of coded packets a
decoder needs to receive to decode a generation of $g$ packets. We call
this number the budget, $B$.

Provided a desired budget, $B \geq g$, and the decoders \ac{DOF} it can be
estimated how sparse the coded packets should be to finish a transmission in
time.

In our implementation, it is the encoders responsibility to estimate the coding
density. We use feedback to provide the encoder a better estimate of the
decoders \ac{DOF} at pre-defined points. Namely, when the decoder obtains the
following \ac{DOF}'s:

\begin{equation}\label{eq:feedback_dofs}
    s(k) = g\cdot \frac{2^k -1}{2^k},  \; \text{for } k=0,1,2,\dots
\end{equation}
where $k$ is the $k$-th feedback packet that is transmitted during a generation.

The encoder considers the time between feedback packets as regions. It then
estimates a fixed coding density for each region when a feedback packet is
received.

Before the coding density can be estimated it is essential that the encoder
has a good estimate of the decoders \ac{DOF}, but also the remainder of the
total budget. The feedback scheme \ref{eq:feedback_dofs} roughly splits the
remaining \ac{DOF} in halves. This is also the case for the budget that is
split equally among the two new regions. The very last region will be asigned
the full remainder of the total budget.

### 2016-05-30 raspi_journal.tex
Small contribution to multicore

--- 2016-05-30 raspi_journal.tex
@@
 complexity particulary in the beginning of transmissions, but also to
-tailor the coding delay. I.e. approximate the number of coded packets a
+tailor the coding delay. I.e., approximate the number of coded packets a
 decoder needs to receive to decode a generation of $g$ packets. We call
@@
 the full remainder of the total budget.
+
+\subsection{Network Coding Implementation for Multicore Architectures}
+\label{sub:implementation-multicore}
+
+The operations needed to encode and decode the data are, in general, similar. To
+encode packets, the encoder needs to perform the matrix multiplication
+$\textbf{C} = \textbf{V} \cdot \textbf{P}$. On the other hand, decoding the
+information requires the decoder to find $\textbf{V}^{-1}$ and to perform the
+matrix multiplication $\textbf{P} = \textbf{V}^{-1} \cdot \textbf{C}$. In both
+cases, a matrix multiplication is needed. Therefore, to make a practical
+implementation of network coding, it is valuable to find a way to optimize the
+matrix multiplications operations for multicore architectures.
+
+Some algorithms implement the decoding combining the matrix inversion and the
+matrix multiplication, e.g., performing the Gauss-Jordan algorithm over the
+coding matrix $\textbf{V}$ while performing, in parallel, row operations on the
+coded data $\textbf{C}$. The parallelization of such operations provide speeds
+up that are limited for small block sizes ($\leq 2048$ bytes). The reason is
+that to operate in a parallel fashion over the same coded packet $C_i$ requires
+strained synchronization.
 

### 2016-05-30 introduction.tex

--- 2016-05-30 raspi_journal.tex
@@
-%  LaTeX support: latex@mdpi.com
-%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+At the beginning, there was darkness and then... bang! \ac{NC}
+\cite{ahlswede2000network} appeared to save us from the evilness
+of routing.
 
-% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
+General introduction. Introduction to topic addressed in the journal.
+Review of the State of the Art. Specify why our approach has benefits
+and which are they. Indicate contributions.
 
-%=================================================================
-\documentclass[electronics,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
-\synctex=1
-\usepackage{fixme}
+Our work is organized as follows: Section \ref{sec:testbed} introduces
+the testbed system, its setup, connectivity, files configuration and
+compilation of the Kodo library. Section \ref{sec:schemes} defines the
+coding schemes employed in our study. Section \ref{sec:topologies} some
+configurable topologies in the tested. Later, in Section \ref{sec:metrics}
+we describe the considered metrics for performance comparison of the
+codes deployed in the Raspberry Pi. In Section \ref{sec:measurements}, we show
+the measurements in the Raspberry Pi of the mentioned metrics. Final
+conclusions and future work are reviewed in Section \ref{sec:conclusions}.
 
-\newcommand\floor[1]{\lfloor#1\rfloor}
-
-%--------------------
-% Class Options:
-%--------------------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% actuators, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, atmosphere, atoms, axioms, batteries, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, challenges, chemosensors, children, chromatography, climate, coatings, computation, computers, condensedmatter, cosmetics, cryptography, crystals, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, fishes, fluids, foods, forests, futureinternet, galaxies, games, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, inventions, jcdd, jcm, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, lubricants, machines, magnetochemistry, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nutrients, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, processes, proteomes, publications, recycling, religions, remotesensing, resources, risks, robotics, safety, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, sustainability, symmetry, systems, technologies, toxics, toxins, universe, urbansci, vaccines, vetsci, viruses, water
-%---------
-% article
-%---------
-% The default type of manuscript is article, but can be replaced by:
-% addendum, article, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimage, letter, newbookreceived, opinion, obituary, projectreport, reply, retraction, review, sciprints, shortnote, supfile, technicalnote
-% supfile = supplementary materials
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g.
-the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.
-
-% *** ACRONYM PACKAGE ***
-\usepackage[nolist]{acronym}
-\input{acronym} % Name of acronyms file
-
-%=================================================================
-\firstpage{1}
-\makeatletter
-\setcounter{page}{\@firstpage}
-\makeatother
-\articlenumber{x}
-\doinum{10.3390/------}
-\pubvolume{xx}
-\pubyear{2016}
-\copyrightyear{2016}
-\externaleditor{Academic Editor: Steven Johnston and Simon J. Cox}
-\history{Received: date; Accepted: date; Published: date}
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
-
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed
-
-%=================================================================
-%% Please use the following mathematics environments:
- \theoremstyle{mdpi}
- \newcounter{thm}
- \setcounter{thm}{0}
- \newcounter{ex}
- \setcounter{ex}{0}
- \newcounter{re}
- \setcounter{re}{0}
-
- \newtheorem{Theorem}[thm]{Theorem}
- \newtheorem{Lemma}[thm]{Lemma}
- \newtheorem{Corollary}[thm]{Corollary}
- \newtheorem{Proposition}[thm]{Proposition}
-
- \theoremstyle{mdpidefinition}
- \newtheorem{Characterization}[thm]{Characterization}
- \newtheorem{Property}[thm]{Property}
- \newtheorem{Problem}[thm]{Problem}
- \newtheorem{Example}[ex]{Example}
- \newtheorem{ExamplesandDefinitions}[ex]{Examples and Definitions}
- \newtheorem{Remark}[re]{Remark}
- \newtheorem{Definition}[thm]{Definition}
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
-
-%=================================================================
-% Full title of the paper (Capitalized)
-\Title{Easy as Pi: A Network Coding Raspberry Pi Testbed}
-
-% Authors, for the paper (add full first names)
-\Author{N\'estor J.
-Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W.
-S{\o}rensen $^{2,\dagger}$, Juan A.
-Cabrera G.
-$^{3}$, Simon Wunderlich $^{3}$, Daniel E.
-Lucani $^{2,\dagger}$ and Frank H.
-P.
-Fitzek $^{3}$}
-% Authors, for metadata in PDF
-\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Daniel Lucani and Frank Fitzek}
-
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad Steinwurf ApS; nestor@steinwurf.com\\
-$^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
-$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de}
-
-% Contact information of the corresponding author
-\corres{Correspondence: nestor@steinwurf.com, nh@es.aau.dk; Tel.: +45 51 20 03 49}
-
-% Current address and/or shared authorship
-\firstnote{Fredrik Bajers Vej 7, Room A3-111. Aalborg, Denmark}
-
-% Simple summary
-%\simplesumm{}
-
-% Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{Due to the recurrent nature }
-
-% A single paragraph of about 200 words maximum.
-For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article: it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.
-
-% Keywords
-\keyword{Network Coding; Raspberry Pi; Testbed; C++}
-
-% keyword 1; keyword 2; keyword 3. List three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.
-
-% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{J0101}
-%\MSC{}
-%\JEL{}
-
-% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\S$ in the end of the title of this article.
-%\conference{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data:
-
-%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
-If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
-In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
-
-%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Sections that are not mandatory are listed as such. The section titles given are for Articles. Review papers and other article types have a more flexible structure.
-
-%% Only for the journal Gels: Please place the Experimental Section after the Conclusions
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \setcounter{section}{-1} %% Remove this when starting to work on the template.
-% \section{How to Use this Template}
-
-% The template details the sections that can be used in a manuscript.
-Sections that are not mandatory are listed as such.
-The section titles given are for Articles.
-Review papers and other article types have a more flexible structure.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.
-
-\section{Introduction}
-\input{introduction}
-
-\section{Testbed Description}
-\input{testbed}
-
-\section{Coding Schemes}
-\input{schemes}
-
-\section{Topologies}
-\input{topologies}
-
-\section{Analyzed Metrics}
-\input{metrics}
-
-\section{Measurements}
-\input{measurements}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Subsection}
-% \subsubsection{Subsubsection}
-
-% Bulleted lists look like this:
-% \begin{itemize}[leftmargin=*,labelsep=4mm]
-% \item	First bullet
-% \item	Second bullet
-% \item	Third bullet
-% \end{itemize}
-
-% Numbered lists can be added as follows:
-% \begin{enumerate}[leftmargin=*,labelsep=3mm]
-% \item	First item
-% \item	Second item
-% \item	Third item
-% \end{enumerate}
-
-% The text continues here.
-
-% \subsection{Figures, Tables and Schemes}
-
-% All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
-
-% \begin{figure}[H]
-% \centering
-% %\includegraphics[width=3cm]{logo-mdpi}
-% \caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-% \end{figure}
-
-% \begin{table}[H]
-% \caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-% \small % Font size can be changed to match table content. Recommend 10 pt.
-% \centering
-% \begin{tabular}{ccc}
-% \toprule
-% \textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-% \midrule
-% entry 1		& data			& data\\
-% entry 2		& data			& data\\
-% \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \subsection{Formatting of Mathematical Components}
-
-% This is an example of an equation:
-
-% \begin{equation}
-% \mathbb{S}
-% \end{equation}
-
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-% Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-% \begin{Theorem}
-% Example text of a theorem.
-% \end{Theorem}
-% The text continues here. Proofs must be formatted as follows:
-
-%% Example of a proof:
-% \begin{proof}[Proof of Theorem 1]
-% Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-% \end{proof}
-% The text continues here.
-
-\section{Conclusion}
-\label{sec:conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Discussion}
-
-%This section may be divided by subheadings.
-Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
-
-%This section should be divided by subheadings.
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
-
-%Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Conclusions}
-
-%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-% \supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
-Curie project (317126) from the European Comission FP7 framework,
-the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
-and the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
-by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d).}
-
-%All sources of funding of the study should be disclosed.
-Please clearly indicate grants that you have received in support of your research work.
-Clearly state if you received funds for covering the costs to publish in open access.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``X.X.
-and Y.Y.
-conceived and designed the experiments; X.X.
-performed the experiments; X.X.
-and Y.Y.
-analyzed the data; W.W.
-contributed reagents/materials/analysis tools; Y.Y.
-wrote the paper.'' Authorship must be limited to those who have contributed substantially to the work reported.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictofinterests{The authors declare no conflict of interest.
-The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results.}
-
-%Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\abbreviations{The following abbreviations are used in this manuscript:\\
-
-\noindent NC: Network Coding\\
-RLNC: Random Linear Network Coding\\}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-% \appendix
-% \section{}
-% The appendix is an optional section that can contain details and data supplemental to the main text.
-For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
-Mathemtaical proofs of results not central to the paper can be added as an appendix.
-
-% \section{}
-% All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{mdpi}
-
-%=====================================
-% References, variant A: internal bibliography
-%=====================================
-% \renewcommand\bibname{References}
-% \begin{thebibliography}{999}
-% % Reference 1
-% \bibitem{ref-journal}
-% Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
-% % Reference 2
-% \bibitem{ref-book}
-% Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
-% \end{thebibliography}
-
-%=====================================
-% References, variant B: external bibliography
-%=====================================
-\bibliography{raspi_journal}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\sampleavailability{The testbed and measurements in this publication are both available from the authors.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{document}
+%The introduction should briefly place the study in a broad context and highlight why it is important.
+It should define the purpose of the work and its significance.
+The current state of the research field should be reviewed carefully and key publications should be cited.
+Please highlight controversial and diverging hypotheses when necessary.
+Finally, briefly mention the main aim of the work and highlight the main conclusions.
+As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.

### 2016-05-30 measurements.tex

--- 2016-05-30 raspi_journal.tex
@@
-%  LaTeX support: latex@mdpi.com
-%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+\label{sec:measurements}
 
-% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
-
-%=================================================================
-\documentclass[electronics,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
-\synctex=1
-\usepackage{fixme}
-
-\newcommand\floor[1]{\lfloor#1\rfloor}
-
-%--------------------
-% Class Options:
-%--------------------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% actuators, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, atmosphere, atoms, axioms, batteries, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, challenges, chemosensors, children, chromatography, climate, coatings, computation, computers, condensedmatter, cosmetics, cryptography, crystals, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, fishes, fluids, foods, forests, futureinternet, galaxies, games, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, inventions, jcdd, jcm, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, lubricants, machines, magnetochemistry, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nutrients, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, processes, proteomes, publications, recycling, religions, remotesensing, resources, risks, robotics, safety, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, sustainability, symmetry, systems, technologies, toxics, toxins, universe, urbansci, vaccines, vetsci, viruses, water
-%---------
-% article
-%---------
-% The default type of manuscript is article, but can be replaced by:
-% addendum, article, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimage, letter, newbookreceived, opinion, obituary, projectreport, reply, retraction, review, sciprints, shortnote, supfile, technicalnote
-% supfile = supplementary materials
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g.
-the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.
-
-% *** ACRONYM PACKAGE ***
-\usepackage[nolist]{acronym}
-\input{acronym} % Name of acronyms file
-
-%=================================================================
-\firstpage{1}
-\makeatletter
-\setcounter{page}{\@firstpage}
-\makeatother
-\articlenumber{x}
-\doinum{10.3390/------}
-\pubvolume{xx}
-\pubyear{2016}
-\copyrightyear{2016}
-\externaleditor{Academic Editor: Steven Johnston and Simon J. Cox}
-\history{Received: date; Accepted: date; Published: date}
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
-
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed
-
-%=================================================================
-%% Please use the following mathematics environments:
- \theoremstyle{mdpi}
- \newcounter{thm}
- \setcounter{thm}{0}
- \newcounter{ex}
- \setcounter{ex}{0}
- \newcounter{re}
- \setcounter{re}{0}
-
- \newtheorem{Theorem}[thm]{Theorem}
- \newtheorem{Lemma}[thm]{Lemma}
- \newtheorem{Corollary}[thm]{Corollary}
- \newtheorem{Proposition}[thm]{Proposition}
-
- \theoremstyle{mdpidefinition}
- \newtheorem{Characterization}[thm]{Characterization}
- \newtheorem{Property}[thm]{Property}
- \newtheorem{Problem}[thm]{Problem}
- \newtheorem{Example}[ex]{Example}
- \newtheorem{ExamplesandDefinitions}[ex]{Examples and Definitions}
- \newtheorem{Remark}[re]{Remark}
- \newtheorem{Definition}[thm]{Definition}
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
-
-%=================================================================
-% Full title of the paper (Capitalized)
-\Title{Easy as Pi: A Network Coding Raspberry Pi Testbed}
-
-% Authors, for the paper (add full first names)
-\Author{N\'estor J.
-Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W.
-S{\o}rensen $^{2,\dagger}$, Juan A.
-Cabrera G.
-$^{3}$, Simon Wunderlich $^{3}$, Daniel E.
-Lucani $^{2,\dagger}$ and Frank H.
-P.
-Fitzek $^{3}$}
-% Authors, for metadata in PDF
-\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Daniel Lucani and Frank Fitzek}
-
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad Steinwurf ApS; nestor@steinwurf.com\\
-$^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
-$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de}
-
-% Contact information of the corresponding author
-\corres{Correspondence: nestor@steinwurf.com, nh@es.aau.dk; Tel.: +45 51 20 03 49}
-
-% Current address and/or shared authorship
-\firstnote{Fredrik Bajers Vej 7, Room A3-111. Aalborg, Denmark}
-
-% Simple summary
-%\simplesumm{}
-
-% Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{Due to the recurrent nature }
-
-% A single paragraph of about 200 words maximum.
-For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article: it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.
-
-% Keywords
-\keyword{Network Coding; Raspberry Pi; Testbed; C++}
-
-% keyword 1; keyword 2; keyword 3. List three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.
-
-% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{J0101}
-%\MSC{}
-%\JEL{}
-
-% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\S$ in the end of the title of this article.
-%\conference{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data:
-
-%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
-If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
-In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
-
-%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Sections that are not mandatory are listed as such. The section titles given are for Articles. Review papers and other article types have a more flexible structure.
-
-%% Only for the journal Gels: Please place the Experimental Section after the Conclusions
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \setcounter{section}{-1} %% Remove this when starting to work on the template.
-% \section{How to Use this Template}
-
-% The template details the sections that can be used in a manuscript.
-Sections that are not mandatory are listed as such.
-The section titles given are for Articles.
-Review papers and other article types have a more flexible structure.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.
-
-\section{Introduction}
-\input{introduction}
-
-\section{Testbed Description}
-\input{testbed}
-
-\section{Coding Schemes}
-\input{schemes}
-
-\section{Topologies}
-\input{topologies}
-
-\section{Analyzed Metrics}
-\input{metrics}
-
-\section{Measurements}
-\input{measurements}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Subsection}
-% \subsubsection{Subsubsection}
-
-% Bulleted lists look like this:
-% \begin{itemize}[leftmargin=*,labelsep=4mm]
-% \item	First bullet
-% \item	Second bullet
-% \item	Third bullet
-% \end{itemize}
-
-% Numbered lists can be added as follows:
-% \begin{enumerate}[leftmargin=*,labelsep=3mm]
-% \item	First item
-% \item	Second item
-% \item	Third item
-% \end{enumerate}
-
-% The text continues here.
-
-% \subsection{Figures, Tables and Schemes}
-
-% All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
-
-% \begin{figure}[H]
-% \centering
-% %\includegraphics[width=3cm]{logo-mdpi}
-% \caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-% \end{figure}
-
-% \begin{table}[H]
-% \caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-% \small % Font size can be changed to match table content. Recommend 10 pt.
-% \centering
-% \begin{tabular}{ccc}
-% \toprule
-% \textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-% \midrule
-% entry 1		& data			& data\\
-% entry 2		& data			& data\\
-% \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \subsection{Formatting of Mathematical Components}
-
-% This is an example of an equation:
-
-% \begin{equation}
-% \mathbb{S}
-% \end{equation}
-
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-% Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-% \begin{Theorem}
-% Example text of a theorem.
-% \end{Theorem}
-% The text continues here. Proofs must be formatted as follows:
-
-%% Example of a proof:
-% \begin{proof}[Proof of Theorem 1]
-% Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-% \end{proof}
-% The text continues here.
-
-\section{Conclusion}
-\label{sec:conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Discussion}
-
-%This section may be divided by subheadings.
-Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
-
-%This section should be divided by subheadings.
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
-
-%Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Conclusions}
-
-%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-% \supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
-Curie project (317126) from the European Comission FP7 framework,
-the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
-and the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
-by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d).}
-
-%All sources of funding of the study should be disclosed.
-Please clearly indicate grants that you have received in support of your research work.
-Clearly state if you received funds for covering the costs to publish in open access.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``X.X.
-and Y.Y.
-conceived and designed the experiments; X.X.
-performed the experiments; X.X.
-and Y.Y.
-analyzed the data; W.W.
-contributed reagents/materials/analysis tools; Y.Y.
-wrote the paper.'' Authorship must be limited to those who have contributed substantially to the work reported.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictofinterests{The authors declare no conflict of interest.
-The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results.}
-
-%Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\abbreviations{The following abbreviations are used in this manuscript:\\
-
-\noindent NC: Network Coding\\
-RLNC: Random Linear Network Coding\\}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-% \appendix
-% \section{}
-% The appendix is an optional section that can contain details and data supplemental to the main text.
-For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
-Mathemtaical proofs of results not central to the paper can be added as an appendix.
-
-% \section{}
-% All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{mdpi}
-
-%=====================================
-% References, variant A: internal bibliography
-%=====================================
-% \renewcommand\bibname{References}
-% \begin{thebibliography}{999}
-% % Reference 1
-% \bibitem{ref-journal}
-% Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
-% % Reference 2
-% \bibitem{ref-book}
-% Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
-% \end{thebibliography}
-
-%=====================================
-% References, variant B: external bibliography
-%=====================================
-\bibliography{raspi_journal}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\sampleavailability{The testbed and measurements in this publication are both available from the authors.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{document}
+This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.

### 2016-05-30 schemes.tex

@@
 the full remainder of the total budget.
+
+\subsection{Network Coding Implementation for Multicore Architectures}
+\label{sub:implementation-multicore}
+
+The operations needed to encode and decode the data are, in general, similar. To
+encode packets, the encoder needs to perform the matrix multiplication
+$\textbf{C} = \textbf{V} \cdot \textbf{P}$. On the other hand, decoding the
+information requires the decoder to find $\textbf{V}^{-1}$ and to perform the
+matrix multiplication $\textbf{P} = \textbf{V}^{-1} \cdot \textbf{C}$. In both
+cases, a matrix multiplication is needed. Therefore, to make a practical
+implementation of network coding, it is valuable to find a way to optimize the
+matrix multiplications operations for multicore architectures.
+
+Some algorithms implement the decoding combining the matrix inversion and the
+matrix multiplication, e.g., performing the Gauss-Jordan algorithm over the
+coding matrix $\textbf{V}$ while performing, in parallel, row operations on the
+coded data $\textbf{C}$. The parallelization of such operations provide speeds
+up that are limited for small block sizes ($\leq 2048$ bytes). The reason is
+that to operate in a parallel fashion over the same coded packet $C_i$ requires
+strained synchronization.

### 2016-05-30 testbed.tex

--- 2016-05-30 raspi_journal.tex
@@
-%  LaTeX support: latex@mdpi.com
-%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+\label{sec:testbed}
 
-% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
+We proceed to define the testbed environment by each of its conforming
+parts. We later indicate a procedure to set up the testbed. In this procedure,
+we summarize all the details regarding on setting the connectivity and
+system files for a set of Raspberry Pis in a centralized fashion.
+Afterwards, we indicate how to cross-compile the Kodo library in an
+easy way. Finally, we provide further information about Kodo itself in terms
+of testing, other platforms supported and source code documentation
+for further references.
 
-%=================================================================
-\documentclass[electronics,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
-\synctex=1
-\usepackage{fixme}
+\subsection{System Overview}
+\subsection{Installation and Updating}
+\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
 
-\newcommand\floor[1]{\lfloor#1\rfloor}
+Besides the previous description (\textbf{Include compiling Kodo from the
+RasPi from the scratch}), the testbed administrator can compile Kodo in its
+personal workstation and transfer the generated binaries directly to
+a path in the Raspberry Pi. To achieve this, we get a toolchain that
+contains the binaries for the \texttt{raspberry-gxx49-arm-g++} compiler
+for the Raspberry Pi. Therefore, we strongly recommend any testbed
+administrator to do the following procedure. In what follows, we provide
+the instructions considering that the NFS server uses the \texttt{\$HOME}
+directory as the working directory. However, the administrator may choose
+some other working directory of its preference if desired.
 
-%--------------------
-% Class Options:
-%--------------------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% actuators, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, atmosphere, atoms, axioms, batteries, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, challenges, chemosensors, children, chromatography, climate, coatings, computation, computers, condensedmatter, cosmetics, cryptography, crystals, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, fishes, fluids, foods, forests, futureinternet, galaxies, games, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, inventions, jcdd, jcm, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, lubricants, machines, magnetochemistry, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nutrients, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, processes, proteomes, publications, recycling, religions, remotesensing, resources, risks, robotics, safety, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, sustainability, symmetry, systems, technologies, toxics, toxins, universe, urbansci, vaccines, vetsci, viruses, water
-%---------
-% article
-%---------
-% The default type of manuscript is article, but can be replaced by:
-% addendum, article, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimage, letter, newbookreceived, opinion, obituary, projectreport, reply, retraction, review, sciprints, shortnote, supfile, technicalnote
-% supfile = supplementary materials
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g.
-the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.
+\begin{enumerate}
 
-% *** ACRONYM PACKAGE ***
-\usepackage[nolist]{acronym}
-\input{acronym} % Name of acronyms file
+\item Download the Raspberry Pi toolchain for 64-bit Linux from: \\
+\texttt{http://buildbot.steinwurf.dk/toolchains/linux/} to your
+\texttt{\$HOME} directory. \\
 
-%=================================================================
-\firstpage{1}
-\makeatletter
-\setcounter{page}{\@firstpage}
-\makeatother
-\articlenumber{x}
-\doinum{10.3390/------}
-\pubvolume{xx}
-\pubyear{2016}
-\copyrightyear{2016}
-\externaleditor{Academic Editor: Steven Johnston and Simon J. Cox}
-\history{Received: date; Accepted: date; Published: date}
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
+\item Extract the downloaded file locally in the NFS server. After
+this operation, there should be a new directory for the toolchain
+in the server. \\
 
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed
+\item Add the \texttt{bin} folder of the toolchain to the \texttt{PATH}
+Linux environment variable of the server. This will help the server OS
+to recognize the location of the compiler command, which will be needed
+later. To do so, edit the \texttt{\$HOME/.profile} to add in a newline:
+\texttt{PATH="\$PATH:\$HOME/raspberry-gxx49-arm/bin"}. Save the
+\texttt{\$HOME/.profile}. \\
 
-%=================================================================
-%% Please use the following mathematics environments:
- \theoremstyle{mdpi}
- \newcounter{thm}
- \setcounter{thm}{0}
- \newcounter{ex}
- \setcounter{ex}{0}
- \newcounter{re}
- \setcounter{re}{0}
+\item Restart the server session in order for the changes made in the
+previous step take effect. To verify this, open a new terminal and type:
+\texttt{raspberry-gxx49-arm-g++ --version}. A correct binary installation
+should return an output similar to:
 
- \newtheorem{Theorem}[thm]{Theorem}
- \newtheorem{Lemma}[thm]{Lemma}
- \newtheorem{Corollary}[thm]{Corollary}
- \newtheorem{Proposition}[thm]{Proposition}
+\texttt{raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
+Copyright (C) 2014 Free Software Foundation, Inc.
+This is free software; see the source for copying conditions.  There is NO
+warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.} \\
 
- \theoremstyle{mdpidefinition}
- \newtheorem{Characterization}[thm]{Characterization}
- \newtheorem{Property}[thm]{Property}
- \newtheorem{Problem}[thm]{Problem}
- \newtheorem{Example}[ex]{Example}
- \newtheorem{ExamplesandDefinitions}[ex]{Examples and Definitions}
- \newtheorem{Remark}[re]{Remark}
- \newtheorem{Definition}[thm]{Definition}
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+\item Clone the Kodo repository in the server by executing: \\
+\texttt{git clone git://github.com/steinwurf/kodo.git} in \texttt{\$HOME}. \\
 
-%=================================================================
-% Full title of the paper (Capitalized)
-\Title{Easy as Pi: A Network Coding Raspberry Pi Testbed}
+\item Navigate to the repository and configure \texttt{waf} by typing:
+\texttt{python config.py} and select the 16th ``make specification'' file
+for the Raspberry Pi, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
+presented by the file.
 
-% Authors, for the paper (add full first names)
-\Author{N\'estor J.
-Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W.
-S{\o}rensen $^{2,\dagger}$, Juan A.
-Cabrera G.
-$^{3}$, Simon Wunderlich $^{3}$, Daniel E.
-Lucani $^{2,\dagger}$ and Frank H.
-P.
-Fitzek $^{3}$}
-% Authors, for metadata in PDF
-\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Daniel Lucani and Frank Fitzek}
+This command configures \texttt{waf} to use the proper compiler and its
+required flags to generate the binaries for the Raspberry Pi. If the
+configuration was correct, the output will indicate:
+\texttt{'configure' finished successfully (X.XXXs)}, where \texttt{X.XXX}
+is total time in seconds for configuring the project in the server. \\
 
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad Steinwurf ApS; nestor@steinwurf.com\\
-$^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
-$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de}
+\item Execute \texttt{python waf build}. If the build process was
+successful, the generated binaries for the Raspberry Pi should be located
+in \texttt{build/cxx\_raspberry\_gxx49\_arm} in the Kodo repository.
+\textbf{Indicate how the binary files should look like}.
 
-% Contact information of the corresponding author
-\corres{Correspondence: nestor@steinwurf.com, nh@es.aau.dk; Tel.: +45 51 20 03 49}
+Once this procedure is made, the testbed administrator can relocate the
+generated binary files to Raspberry Pi's through the network as desired
+by using the \texttt{scp} command during the configuration step.
 
-% Current address and/or shared authorship
-\firstnote{Fredrik Bajers Vej 7, Room A3-111. Aalborg, Denmark}
+\end{enumerate}
 
-% Simple summary
-%\simplesumm{}
+\subsection{Kodo Builds for the Raspberry Pi, Platform Support and Documentation}
 
-% Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{Due to the recurrent nature }
-
-% A single paragraph of about 200 words maximum.
-For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article: it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.
-
-% Keywords
-\keyword{Network Coding; Raspberry Pi; Testbed; C++}
-
-% keyword 1; keyword 2; keyword 3. List three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.
-
-% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{J0101}
-%\MSC{}
-%\JEL{}
-
-% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\S$ in the end of the title of this article.
-%\conference{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data:
-
-%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
-If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
-In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
-
-%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Sections that are not mandatory are listed as such. The section titles given are for Articles. Review papers and other article types have a more flexible structure.
-
-%% Only for the journal Gels: Please place the Experimental Section after the Conclusions
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \setcounter{section}{-1} %% Remove this when starting to work on the template.
-% \section{How to Use this Template}
-
-% The template details the sections that can be used in a manuscript.
-Sections that are not mandatory are listed as such.
-The section titles given are for Articles.
-Review papers and other article types have a more flexible structure.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.
-
-\section{Introduction}
-\input{introduction}
-
-\section{Testbed Description}
-\input{testbed}
-
-\section{Coding Schemes}
-\input{schemes}
-
-\section{Topologies}
-\input{topologies}
-
-\section{Analyzed Metrics}
-\input{metrics}
-
-\section{Measurements}
-\input{measurements}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Subsection}
-% \subsubsection{Subsubsection}
-
-% Bulleted lists look like this:
-% \begin{itemize}[leftmargin=*,labelsep=4mm]
-% \item	First bullet
-% \item	Second bullet
-% \item	Third bullet
-% \end{itemize}
-
-% Numbered lists can be added as follows:
-% \begin{enumerate}[leftmargin=*,labelsep=3mm]
-% \item	First item
-% \item	Second item
-% \item	Third item
-% \end{enumerate}
-
-% The text continues here.
-
-% \subsection{Figures, Tables and Schemes}
-
-% All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
-
-% \begin{figure}[H]
-% \centering
-% %\includegraphics[width=3cm]{logo-mdpi}
-% \caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-% \end{figure}
-
-% \begin{table}[H]
-% \caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-% \small % Font size can be changed to match table content. Recommend 10 pt.
-% \centering
-% \begin{tabular}{ccc}
-% \toprule
-% \textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-% \midrule
-% entry 1		& data			& data\\
-% entry 2		& data			& data\\
-% \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \subsection{Formatting of Mathematical Components}
-
-% This is an example of an equation:
-
-% \begin{equation}
-% \mathbb{S}
-% \end{equation}
-
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-% Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-% \begin{Theorem}
-% Example text of a theorem.
-% \end{Theorem}
-% The text continues here. Proofs must be formatted as follows:
-
-%% Example of a proof:
-% \begin{proof}[Proof of Theorem 1]
-% Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-% \end{proof}
-% The text continues here.
-
-\section{Conclusion}
-\label{sec:conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Discussion}
-
-%This section may be divided by subheadings.
-Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
-
-%This section should be divided by subheadings.
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
-
-%Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Conclusions}
-
-%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-% \supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
-Curie project (317126) from the European Comission FP7 framework,
-the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
-and the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
-by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d).}
-
-%All sources of funding of the study should be disclosed.
-Please clearly indicate grants that you have received in support of your research work.
-Clearly state if you received funds for covering the costs to publish in open access.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``X.X.
-and Y.Y.
-conceived and designed the experiments; X.X.
-performed the experiments; X.X.
-and Y.Y.
-analyzed the data; W.W.
-contributed reagents/materials/analysis tools; Y.Y.
-wrote the paper.'' Authorship must be limited to those who have contributed substantially to the work reported.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictofinterests{The authors declare no conflict of interest.
-The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results.}
-
-%Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\abbreviations{The following abbreviations are used in this manuscript:\\
-
-\noindent NC: Network Coding\\
-RLNC: Random Linear Network Coding\\}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-% \appendix
-% \section{}
-% The appendix is an optional section that can contain details and data supplemental to the main text.
-For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
-Mathemtaical proofs of results not central to the paper can be added as an appendix.
-
-% \section{}
-% All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{mdpi}
-
-%=====================================
-% References, variant A: internal bibliography
-%=====================================
-% \renewcommand\bibname{References}
-% \begin{thebibliography}{999}
-% % Reference 1
-% \bibitem{ref-journal}
-% Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
-% % Reference 2
-% \bibitem{ref-book}
-% Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
-% \end{thebibliography}
-
-%=====================================
-% References, variant B: external bibliography
-%=====================================
-\bibliography{raspi_journal}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\sampleavailability{The testbed and measurements in this publication are both available from the authors.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{document}
+You can check the build status of Kodo, Fifi and other relevant projects through
+their respective repository master branch on our buildbot page
+\cite{steinwurf2016buildbot}. Our buildbot displays the status of the builds for
+Raspbian 8 and GCC 4.9 for the ARM architecture which is the relevant one for the
+Raspberry Pi. At the link, you can check build status and build statistics. Also,
+documentation about Kodo basics with a tutorial is available at \cite{kododocs}.

### 2016-05-30 schemes.tex
Attempt to merge

--- 2016-05-30 schemes.tex
@@
 to create coded packets. In the following subsections, we describe the
-basic functionalities of \ac{RLNC}. Later, we mention applications that could
-potentially benefit from including \ac{RLNC} as a coding scheme.
+basic functionalities of \ac{RLNC}.
 
 \subsubsection{Encoding}
-With \ac{RLNC}, each coded packet is a random linear
-combination of the original set of packets. Hence,
-a \ac{l.i.} set of $g$ coded packets, $C_i,\ i \in [1,g]$
-is required in order to get the original information.
-Each original packet is considered as a concatenation of elements
-from a \ac{GF} of a given size $q$, which we denote
-$GF(q)$. To create a coded packet, a coding coefficient
-$v_{i,j}$, is chosen at random from $GF(q)$ for every
-packet $P_j$ and multiplied and added
-following the respective \ac{GF} arithmetics. In this way,
-a coded packet is:
+In \ac{RLNC}, any coded packet is a linear combination from all
+the original packets. For the coding scheme, packets are seen as
+algebraic entities formed as a sequence of elements from $GF(q)$,
+which is a \ac{GF} of size $q$. Later, each original packet is
+multiplied by a coding coefficient from $GF(q)$. The coding coefficients
+are picked uniformly at random by the encoder. To perform the
+multiplication of a packet by a coding coefficient, the coefficient is
+multiplied for each of the elements in the concatenation that composes
+an original packet, preserving the concatenation. Later, all resulting
+packets are added within the \ac{GF} arithmetics together to generate
+a coded packet. Thus, a coded packet can be written as:
 %
 \begin{align} \label{eq:coded_packet}
-C_i  &= \bigoplus_{j=1}^{g} v_{i,j} \otimes P_j ,\ \forall i \in [1,g]
+C_i  &= \bigoplus_{j=1}^{g} v_{i,j} \otimes P_j ,\ \forall i \in [1,\ldots)
 \end{align}
 
-To indicate which packets were used to generate a coded packet, one
-form is to append its coding coefficients. In this case, the overhead
-included for $C_i,\ \forall i \in [1,g]$ by the coding coefficients
-is given by:
+In \eqref{eq:coded_packet}, $C_i$ is the generic coded packet. In principle,
+the encoder may
+
+For signaling a receiver which of the original packets were utilized to
+create a coded packet, a simple choice is to append its coding coefficients
+as a header of the coded packet. Hence, an amount of overhead is included
+since every coded packet given that we need to provide some signalling.
+The coding coefficients overhead can be quantied as:
 %
@@
 \subsubsection{Decoding}
-To perform decoding, we define $\textbf{C} = \left[C_1 \ldots C_g \right]^T$
-and $\textbf{P} = \left[P_1 \ldots P_g \right]^T$. Then, decoding
-reduces to solve the linear system $\textbf{C} = \textbf{V} \cdot \textbf{P}$
-using Gaussian elimination \cite{fragouli2006network}.
-Here, the coding matrix $\textbf{V}$ contains any set of $g$ linearly
-independent packets $C_i$ as rows as follows:
+To be able to decode a batch of $g$ packets, a \ac{l.i.} set of $g$
+coded packets, $C_i,\ i \in [1,g]$ is required in order to get the
+original information. Once this set has been collected for any receiver,
+the original packets can be found by computing the solution of a system
+of linear equation using \ac{GF} aritmethics. Thus, we define
+$\textbf{C} = \left[C_1 \ldots C_g \right]^T$ and
+$\textbf{P} = \left[P_1 \ldots P_g \right]^T$. Algebraically, decoding
+simplifies to finding the inverse of $\textbf{V}$ in the linear system
+$\textbf{C} = \textbf{V} \cdot \textbf{P}$, which can achieved using
+Gaussian elimination techniques \cite{fragouli2006network} that can
+be efficient. For decoding to be possible, the (coding) matrix $\textbf{V}$
+must contain any set of $g$ linearly independent packets $C_i$ in order
+to reduce to row-echelon form. The coding matrix is represented as follows:
 %

### 2016-05-30 schemes.tex
Editing RLNC

@@
 multiplied by a coding coefficient from $GF(q)$. The coding coefficients
-are picked uniformly at random by the encoder. To perform the
-multiplication of a packet by a coding coefficient, the coefficient is
-multiplied for each of the elements in the concatenation that composes
-an original packet, preserving the concatenation. Later, all resulting
-packets are added within the \ac{GF} arithmetics together to generate
-a coded packet. Thus, a coded packet can be written as:
+are picked uniformly at random from the \ac{GF} by the encoder. To
+perform the multiplication of a packet by a coding coefficient, the
+coefficient is multiplied for each of the elements in the
+concatenation that composes an original packet, preserving the
+concatenation. Later, all resulting packets are added within the
+\ac{GF} arithmetics together to generate a coded packet. Thus, a
+coded packet can be written as:
 %
@@
 In \eqref{eq:coded_packet}, $C_i$ is the generic coded packet. In principle,
-the encoder may
+the encoder may produce any number of coded packets, but a finite
+number is produced in practice given that a decoder needs only
+$g$ \ac{l.i.} coded packets to decode the batch. Also, in
+\eqref{eq:coded_packet}, $v_{i,j}$ is the coding coefficient used in the
+$i$-th coded packet and assigned to multiply the $j$-th original packet.
 
-For signaling a receiver which of the original packets were utilized to
-create a coded packet, a simple choice is to append its coding coefficients
-as a header of the coded packet. Hence, an amount of overhead is included
-since every coded packet given that we need to provide some signalling.
-The coding coefficients overhead can be quantied as:
+For indicating a receiver which of the original packets were utilized
+to create a coded packet, a simple and useful choice is to append
+its coding coefficients as a header of the coded packet. Hence, an
+amount of overhead is included in every coded packet given that we
+need to provide some signalling needed for decoding. The coding
+coefficients overhead amount for packet $i$, $|v_i|$, can be quantified
+as:
 %

### 2016-05-31 schemes.tex
Editing RLNC decoding. Need to finish the recoding part

@@
 
-For indicating a receiver which of the original packets were utilized
-to create a coded packet, a simple and useful choice is to append
+For indicating a receiver which packets were utilized
+to create a coded one, a simple yet versatile choice is to append
 its coding coefficients as a header of the coded packet. Hence, an
@@
 To be able to decode a batch of $g$ packets, a \ac{l.i.} set of $g$
-coded packets, $C_i,\ i \in [1,g]$ is required in order to get the
-original information. Once this set has been collected for any receiver,
+coded packets, $C_i,\ i \in [1,g]$ is required at a decoder.
+Once this set has been collected for a decoder,
 the original packets can be found by computing the solution of a system
-of linear equation using \ac{GF} aritmethics. Thus, we define
+of linear equations using \ac{GF} aritmethics. Thus, we define
 $\textbf{C} = \left[C_1 \ldots C_g \right]^T$ and
@@
 $\textbf{C} = \textbf{V} \cdot \textbf{P}$, which can achieved using
-Gaussian elimination techniques \cite{fragouli2006network} that can
-be efficient. For decoding to be possible, the (coding) matrix $\textbf{V}$
-must contain any set of $g$ linearly independent packets $C_i$ in order
-to reduce to row-echelon form. The coding matrix is represented as follows:
+efficient Gaussian elimination techniques \cite{fragouli2006network}.
+On real applications, decoding is performed on-the-fly, e.g. the pivots are
+computed as packets are progressively received, in order to minimize the computation
+delay for each step. The coding matrix is represented as follows:
 %
@@
 %
-The decoder begins to compute and remove the contributions from each
+A decoder starts to calculate and substract contributions from each
 of the pivot elements, e.g. leftmost elements in the main diagonal of
-\eqref{eq:coding_matrix}, to reduce $\textbf{V}$ to reduced echelon
-form. In this way, it is possible to recover the original set of packets.
+\eqref{eq:coding_matrix}, from top to bottom. The purpose is to obtain 
+the equivalence  $\textbf{V}$ in its reduced echelon form. The steps
+for reducing the matrix by elementary row operations are carried each
+a \ac{l.i.} packet is received. Once in reduced echelon form, packets
+can be retrieved by doing a substitution starting from the lastest
+coded packet. In this way, the amount of elementary operations at the end
+is diminished.
 
 \subsubsection{Recoding}
-Network coding allows intermediate nodes in a network to
-recombine (or recode) packets from their sources whether they are
-coded or not. In general, a recoded packet should be indistinguishable
+An inherent property of \ac{NC} is the possibility for intermediate nodes
+in a network between a source and a destination, to create coded packets
+even from coded packets sent from the source. In general, a recoded packet should be indistinguishable
 from a coded one. Thus, we define a recoded packet as
@@
 \label{eq:recoded_packet}
-R_i = \bigoplus_{j=1}^{g} w_{i,j} \otimes C_j  ,\ \forall i \in [1,g]
+R_i = \bigoplus_{j=1}^{g} w_{i,j} \otimes C_j  ,\ \forall i \in [1,\ldots)
 \end{align}
@@
     \begin{cases}
-        {(0,0.5]} & \text{for } q=2 \\
-        {(0,1]} & \text{for } q>2
+        {(0,0.5]} & \text{for} q = 2 \\
+        {(0,1]} & \text{for} q > 2
     \end{cases}

### 2016-05-31 metrics.tex
multicore information added

--- 2016-05-30 raspi_journal.tex
@@
-%  LaTeX support: latex@mdpi.com
-%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+\label{sec:metrics}
+\subsection{Encoding and Decoding Speeds}
 
-% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
+\subsubsection{Multicore Network Coding}
+\label{subs:multicore-network-coding}
 
-%=================================================================
-\documentclass[electronics,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
-\synctex=1
-\usepackage{fixme}
-
-\newcommand\floor[1]{\lfloor#1\rfloor}
-
-%--------------------
-% Class Options:
-%--------------------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% actuators, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, atmosphere, atoms, axioms, batteries, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, challenges, chemosensors, children, chromatography, climate, coatings, computation, computers, condensedmatter, cosmetics, cryptography, crystals, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, fishes, fluids, foods, forests, futureinternet, galaxies, games, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, inventions, jcdd, jcm, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, lubricants, machines, magnetochemistry, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nutrients, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, processes, proteomes, publications, recycling, religions, remotesensing, resources, risks, robotics, safety, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, sustainability, symmetry, systems, technologies, toxics, toxins, universe, urbansci, vaccines, vetsci, viruses, water
-%---------
-% article
-%---------
-% The default type of manuscript is article, but can be replaced by:
-% addendum, article, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimage, letter, newbookreceived, opinion, obituary, projectreport, reply, retraction, review, sciprints, shortnote, supfile, technicalnote
-% supfile = supplementary materials
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g.
-the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.
-
-% *** ACRONYM PACKAGE ***
-\usepackage[nolist]{acronym}
-\input{acronym} % Name of acronyms file
-
-%=================================================================
-\firstpage{1}
-\makeatletter
-\setcounter{page}{\@firstpage}
-\makeatother
-\articlenumber{x}
-\doinum{10.3390/------}
-\pubvolume{xx}
-\pubyear{2016}
-\copyrightyear{2016}
-\externaleditor{Academic Editor: Steven Johnston and Simon J. Cox}
-\history{Received: date; Accepted: date; Published: date}
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
-
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed
-
-%=================================================================
-%% Please use the following mathematics environments:
- \theoremstyle{mdpi}
- \newcounter{thm}
- \setcounter{thm}{0}
- \newcounter{ex}
- \setcounter{ex}{0}
- \newcounter{re}
- \setcounter{re}{0}
-
- \newtheorem{Theorem}[thm]{Theorem}
- \newtheorem{Lemma}[thm]{Lemma}
- \newtheorem{Corollary}[thm]{Corollary}
- \newtheorem{Proposition}[thm]{Proposition}
-
- \theoremstyle{mdpidefinition}
- \newtheorem{Characterization}[thm]{Characterization}
- \newtheorem{Property}[thm]{Property}
- \newtheorem{Problem}[thm]{Problem}
- \newtheorem{Example}[ex]{Example}
- \newtheorem{ExamplesandDefinitions}[ex]{Examples and Definitions}
- \newtheorem{Remark}[re]{Remark}
- \newtheorem{Definition}[thm]{Definition}
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
-
-%=================================================================
-% Full title of the paper (Capitalized)
-\Title{Easy as Pi: A Network Coding Raspberry Pi Testbed}
-
-% Authors, for the paper (add full first names)
-\Author{N\'estor J.
-Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W.
-S{\o}rensen $^{2,\dagger}$, Juan A.
-Cabrera G.
-$^{3}$, Simon Wunderlich $^{3}$, Daniel E.
-Lucani $^{2,\dagger}$ and Frank H.
-P.
-Fitzek $^{3}$}
-% Authors, for metadata in PDF
-\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Daniel Lucani and Frank Fitzek}
-
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad Steinwurf ApS; nestor@steinwurf.com\\
-$^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
-$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de}
-
-% Contact information of the corresponding author
-\corres{Correspondence: nestor@steinwurf.com, nh@es.aau.dk; Tel.: +45 51 20 03 49}
-
-% Current address and/or shared authorship
-\firstnote{Fredrik Bajers Vej 7, Room A3-111. Aalborg, Denmark}
-
-% Simple summary
-%\simplesumm{}
-
-% Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{Due to the recurrent nature }
-
-% A single paragraph of about 200 words maximum.
-For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article: it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.
-
-% Keywords
-\keyword{Network Coding; Raspberry Pi; Testbed; C++}
-
-% keyword 1; keyword 2; keyword 3. List three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.
-
-% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{J0101}
-%\MSC{}
-%\JEL{}
-
-% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\S$ in the end of the title of this article.
-%\conference{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data:
-
-%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
-If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
-In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
-
-%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Sections that are not mandatory are listed as such. The section titles given are for Articles. Review papers and other article types have a more flexible structure.
-
-%% Only for the journal Gels: Please place the Experimental Section after the Conclusions
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \setcounter{section}{-1} %% Remove this when starting to work on the template.
-% \section{How to Use this Template}
-
-% The template details the sections that can be used in a manuscript.
-Sections that are not mandatory are listed as such.
-The section titles given are for Articles.
-Review papers and other article types have a more flexible structure.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.
-
-\section{Introduction}
-\input{introduction}
-
-\section{Testbed Description}
-\input{testbed}
-
-\section{Coding Schemes}
-\input{schemes}
-
-\section{Topologies}
-\input{topologies}
-
-\section{Analyzed Metrics}
-\input{metrics}
-
-\section{Measurements}
-\input{measurements}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Subsection}
-% \subsubsection{Subsubsection}
-
-% Bulleted lists look like this:
-% \begin{itemize}[leftmargin=*,labelsep=4mm]
-% \item	First bullet
-% \item	Second bullet
-% \item	Third bullet
-% \end{itemize}
-
-% Numbered lists can be added as follows:
-% \begin{enumerate}[leftmargin=*,labelsep=3mm]
-% \item	First item
-% \item	Second item
-% \item	Third item
-% \end{enumerate}
-
-% The text continues here.
-
-% \subsection{Figures, Tables and Schemes}
-
-% All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
-
-% \begin{figure}[H]
-% \centering
-% %\includegraphics[width=3cm]{logo-mdpi}
-% \caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-% \end{figure}
-
-% \begin{table}[H]
-% \caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-% \small % Font size can be changed to match table content. Recommend 10 pt.
-% \centering
-% \begin{tabular}{ccc}
-% \toprule
-% \textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-% \midrule
-% entry 1		& data			& data\\
-% entry 2		& data			& data\\
-% \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \subsection{Formatting of Mathematical Components}
-
-% This is an example of an equation:
-
-% \begin{equation}
-% \mathbb{S}
-% \end{equation}
-
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-% Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-% \begin{Theorem}
-% Example text of a theorem.
-% \end{Theorem}
-% The text continues here. Proofs must be formatted as follows:
-
-%% Example of a proof:
-% \begin{proof}[Proof of Theorem 1]
-% Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-% \end{proof}
-% The text continues here.
-
-\section{Conclusion}
-\label{sec:conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Discussion}
-
-%This section may be divided by subheadings.
-Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
-
-%This section should be divided by subheadings.
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
-
-%Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Conclusions}
-
-%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-% \supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
-Curie project (317126) from the European Comission FP7 framework,
-the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
-and the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
-by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d).}
-
-%All sources of funding of the study should be disclosed.
-Please clearly indicate grants that you have received in support of your research work.
-Clearly state if you received funds for covering the costs to publish in open access.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``X.X.
-and Y.Y.
-conceived and designed the experiments; X.X.
-performed the experiments; X.X.
-and Y.Y.
-analyzed the data; W.W.
-contributed reagents/materials/analysis tools; Y.Y.
-wrote the paper.'' Authorship must be limited to those who have contributed substantially to the work reported.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictofinterests{The authors declare no conflict of interest.
-The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results.}
-
-%Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\abbreviations{The following abbreviations are used in this manuscript:\\
-
-\noindent NC: Network Coding\\
-RLNC: Random Linear Network Coding\\}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-% \appendix
-% \section{}
-% The appendix is an optional section that can contain details and data supplemental to the main text.
-For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
-Mathemtaical proofs of results not central to the paper can be added as an appendix.
-
-% \section{}
-% All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{mdpi}
-
-%=====================================
-% References, variant A: internal bibliography
-%=====================================
-% \renewcommand\bibname{References}
-% \begin{thebibliography}{999}
-% % Reference 1
-% \bibitem{ref-journal}
-% Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
-% % Reference 2
-% \bibitem{ref-book}
-% Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
-% \end{thebibliography}
-
-%=====================================
-% References, variant B: external bibliography
-%=====================================
-\bibliography{raspi_journal}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\sampleavailability{The testbed and measurements in this publication are both available from the authors.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{document}
+\subsection{Latency}
+\subsection{Energy}

### 2016-05-31 schemes.tex
multicore information added

--- 2016-05-30 schemes.tex
@@
+%!TEX root = raspi_journal.tex
 \label{sec:schemes}
@@
 remaining \ac{DOF} in halves. This is also the case for the budget that is
-split equally among the two new regions. The very last region will be asigned
+split equally among the two new regions. The very last region will be assigned
 the full remainder of the total budget.
@@
 
-Some algorithms implement the decoding combining the matrix inversion and the
+When designing multithreaded algorithms for network coding operations, it is
+possible to implement the decoding by combining the matrix inversion and the
 matrix multiplication, e.g., performing the Gauss-Jordan algorithm over the
 coding matrix $\textbf{V}$ while performing, in parallel, row operations on the
-coded data $\textbf{C}$. The parallelization of such operations provide speeds
-up that are limited for small block sizes ($\leq 2048$ bytes). The reason is
-that to operate in a parallel fashion over the same coded packet $C_i$ requires
-strained synchronization.
+coded data $\textbf{C}$. However, the parallelization of such operations provide
+speeds up that are limited for small block sizes ($\leq 2048$ bytes). The reason
+is that to operate in a parallel fashion over the same coded packet $C_i$
+requires strained synchronization. In~\cite{5061951} and~\cite{4262451} the
+parallelization of the row operations are optimized for \ac{GPU} and \ac{SMP}
+systems respectively.
+
+Therefore, to overcome the constraints of a tight synchronization, it is
+preferable to explicitly invert the matrix $\textbf{V}$, and then take advantage
+of optimizations for matrix multiplications. The authors implemented
+in~\cite{wunderlich2015network} an algorithm that adopts the ideas of efficient
+\ac{BLAS} operations~\cite{lawson1979basic} reimplementing them for finite
+fields operations. The implemented algorithm tries to be cache efficient
+maximizing the number of operations performed over a block of fetched data. This
+is done by operating on square sub-blocks of the matrices, which exploits the
+spatial locality of the data, at least for $\mathcal{O}(n^3)$
+algorithms~\cite{golub2012matrix}. The optimal size of the block is
+architecture-dependent. The ideal block has a number of operands that fit into
+L1 cache, and it is a multiple of the \ac{SIMD} operations size.
+
+The main idea of the implemented algorithm is to represent each one of the sub-
+block matrix operations as a base, \textit{kernel}, operation that can be
+optimized, e.g., using \ac{SIMD} operations. Each of these kernels, at the same
+time, can be represented as a task with inputs and outputs in memory. If the
+algorithm is formulated conventionally, and the data operations on the sub-
+blocks are reordered, then it is possible to resolve data dependencies with a
+\ac{DAG}. For the algorithm, a dependency means, for example, that a sub-block
+of the matrix in memory cannot be read unless a previous writing operation was
+performed there. When the \ac{DAG} is determined, then, a scheduler assigns to
+the available cores the individual kernel operations that have their
+dependencies fulfilled. The benefit of this algorithm is that the
+synchronization relies only on data dependencies, and it does not requires the
+insertion of artificial synchronization points. Using this technique, the matrix
+inversion is performed using an algorithm based on LU
+factorization~\cite{Dongarra:2011:HPM:2132876.2132885}, and the matrix
+multiplication is performed by making the various matrix-matrix multiplications
+of the sub-blocks.

### 2016-05-31 measurements.tex
Started writing on multicore results

@@
+%!TEX root = raspi_journal.tex
 \label{sec:measurements}
 
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+This section may be divided by subheadings. It should provide a concise and
+precise description of the experimental results, their interpretation as well as
+the experimental conclusions that can be drawn.
+
+\subsubsection{Multicore Network Coding}
+\label{subs:multicore-network-coding}
+
+The authors implemented the algorithm described in
+Section~\ref{sub:implementation-multicore} on the Raspberry Pi 2 Model B, which
+features four ARM Cortex-A7 cores in a Broadcom BCM2836 \ac{SOC} with a 900 MHz
+clock. Each core has a 32 KiB L1 data cache and 32 KiB L1 instruction cache. The
+cores share a 512 KiB L2 cache. All the measured results, including the baseline
+results, were obtained with NEON-enabled code adopted from the FIFI/KODO library
+\cite{kodo2011pedersen}. The NEON extension provides an 128-bit \ac{SIMD}
+instruction set to the Raspberry Pi 2. Figures~\ref{enc_dec1024},
+\ref{enc_dec128} and \ref{enc_dec16} show the encoding and decoding throughput
+in MiB per second for different generation sizes ($g$ = 1024, 128, and 16
+respectively). The throughput is the rate of generating $g$ coded packets,
+divided by the time the encoder took to perform the task. The size of each coded
+packet was fixed to $1536$~bytes since that is the typical size of an Ethernet
+frame. The blocked operations were performed dividing the matrices in sub-blocks
+of 16,32,64,...,1024 elements, and the figures only show the best results (usually obtained with a block size of 16 or 32 since with bigger block sizes, the operands do not fit in L1 cache).
+
+The following test cases were considered:
+
+\paragraph{Baseline encoding results} The baseline results involve no recording
+of the \ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder
+uses only one thread. And the difference between the non-blocked and blocked
+encoding is that in the blocked scheme, the matrix multiplications are performed
+dividing the matrices in sub-blocks in order to make the algorithm cache
+efficient as described in Section~\ref{sub:implementation-multicore}.
+
+\paragraph{Encoding results} The encoding results were performed using the
+method described in Section~\ref{sub:implementation-multicore}. The time
+recorded includes the dependencies resolving, creation of the \ac{DAG}, and the
+task scheduling. In practice, it would suffice to calculate and store this
+information only once per generation size.
+
+\paragraph{Decoding results} The differences between encoding and decoding, is
+that the decoding task also involves the matrix inversion. Similarly as with the
+encoding results, the time recorded includes the dependencies resolving, the
+creation of the \ac{DAG} and the task scheduling. However, to decode, these
+calculations are also made for inverting the matrix of coding coefficients.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=\columnwidth]{images/2015-04-18_encoding_decoding_1024.eps}
+\caption{Encoding and Decoding performance for g = 1024}
+\label{enc_dec1024}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=\columnwidth]{images/2015-04-18_encoding_decoding_128.eps}
+\caption{Encoding and Decoding performance for g = 128}
+\label{enc_dec128}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=\columnwidth]{images/2015-04-18_encoding_decoding_16.eps}
+\caption{Encoding and Decoding performance for g = 16}
+\label{enc_dec16}
+\end{figure}
+
+\paragraph{Comparison of the load of matrix multiplications and inversions}
+
+\begin{table}[H]
+\center
+\caption{Multiplication and inversion run-times for different generation sizes with 1 thread}
+\begin{tabular}{|r|r|r|r|}
+\hline
+g & multiplication (ms) & inversion (ms) & ratio \\
+\hline
+\hline
+
+	16 & 1.703  & 0.345 & 4.9 \\
+\hline
+	32 & 6.573  & 0.914 & 7.2 \\
+\hline
+	64 & 21.341  & 3.479 & 6.1 \\
+\hline
+	128 & 82.326  & 17.411 & 4.7 \\
+\hline
+	256 & 336.398  & 106.861 & 3.1 \\
+\hline
+	512 & 1548.750  & 659.469 & 2.3 \\
+\hline
+	1024 & 6730.380  & 5166.920 & 1.3 \\
+\hline
+\end{tabular}
+\vspace{0.2cm}
+\label{runtimes}
+\end{table}

### 2016-05-31 raspi_journal.tex
Started writing on multicore results

--- 2016-05-30 raspi_journal.tex
@@
 Cabrera G.
-$^{3}$, Simon Wunderlich $^{3}$, Daniel E.
+$^{3,4}$, Simon Wunderlich $^{3}$, Daniel E.
 Lucani $^{2,\dagger}$ and Frank H.
@@
 % Authors, for metadata in PDF
-\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Daniel Lucani and Frank Fitzek}
+\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Simon Wunderlich, Daniel Lucani and Frank Fitzek}
 
@@
 $^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
-$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de}
+$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de\\
+$^{4}$ \quad SFB 912 -- HAEC}
 

### 2016-05-31 measurements.tex
added haec ack

@@
 
-\paragraph{Baseline encoding results} The baseline results involve no recording
+\paragraph{Baseline encoding} The baseline results involve no recording
 of the \ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder
@@
 
-\paragraph{Encoding results} The encoding results were performed using the
+\paragraph{Encoding blocked} The encoding results were performed using the
 method described in Section~\ref{sub:implementation-multicore}. The time
@@
 
-\paragraph{Decoding results} The differences between encoding and decoding, is
+\paragraph{Decoding blocked} The differences between encoding and decoding, is
 that the decoding task also involves the matrix inversion. Similarly as with the

### 2016-05-31 raspi_journal.tex
added haec ack

@@
 the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
-and the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
-by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d).}
+, the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
+by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d),
+and by the German Research Foundation (DFG) within the Collaborative Research Center SFB 912 – HAEC.}
 

### 2016-05-31 measurements.tex
expanded results multicore

@@
 frame. The blocked operations were performed dividing the matrices in sub-blocks
-of 16,32,64,...,1024 elements, and the figures only show the best results (usually obtained with a block size of 16 or 32 since with bigger block sizes, the operands do not fit in L1 cache).
+of 16,32,64,...,1024 symbols, and the figures only show the best results
+(usually block sizes of 16 or 32 symbols since with bigger block sizes, the
+operands do not fit in L1 cache).
 
@@
 
-\begin{figure}[ht!]
+\begin{figure}[h!]
 \centering
-\includegraphics[width=\columnwidth]{images/2015-04-18_encoding_decoding_1024.eps}
+\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_1024.eps}
 \caption{Encoding and Decoding performance for g = 1024}
@@
 
-\begin{figure}[ht!]
+For $g=$ 1024, the blocked baseline measurements outperforms the non blocked
+variant. This means that making the matrix multiplication algorithm cache
+efficient brings an increase in throughput by a factor of 2.83. When using the
+algorithm described in Section~\ref{sub:implementation-multicore}, encoding with
+four cores is on average 3.7 times faster than with one core. Similarly,
+decoding with four codes is 3.05 times faster, on average, than decoding with a
+single core. Figure~\ref{enc_dec1024} shows that the implemented algorithm, by
+exploiting cache efficiency and only three extra cores provides a gain of 10
+folds compared with traditional non-blocked algorithms. With $g$ = 1024, the
+matrix inversion becomes more expensive than at smaller generations sizes.
+Therefore, the decoding throughput is 46\% of the encoding throughput.
+
+\begin{figure}[h!]
 \centering
-\includegraphics[width=\columnwidth]{images/2015-04-18_encoding_decoding_128.eps}
+\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_128.eps}
 \caption{Encoding and Decoding performance for g = 128}
@@
 
-\begin{figure}[ht!]
+For $g$ = 128, the differences between the baselines operations show that a
+blocked algorithm is 15\% faster than the non-blocked variant. Encoding with
+four cores is 2.82 times faster than with a single core. Due to the smaller
+matrix sizes, the gain by using blocked operations in the baselines is not that
+big compared with $g$ = 1024. For the same reason, the matrix inversion is less
+expensive. As a consequence, the decoding throughput is 71\% of the encoding
+throughput.
+
+\begin{figure}[h!]
 \centering
-\includegraphics[width=\columnwidth]{images/2015-04-18_encoding_decoding_16.eps}
+\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_16.eps}
 \caption{Encoding and Decoding performance for g = 16}
@@
 
+When $g$ = 16, the gains of blocked operations are negligible compared with the
+non-blocked ones. The reason behind this behavior is that all the data fits in
+the L1 cache. For the scheduled version, since the problem to solve is so small,
+the gain of using four cores is a factor of 1.68 compared with a single core,
+and 1.01 compared with two cores. Therefore, there are no practical benefits in
+using four cores instead of two.
+
+The differences in throughput, for all generation sizes, between the blocked
+baseline and the scheduled measurements are due the time spent resolving the
+dependencies and the scheduling overhead. These effects are negligible for big
+generation sizes, while considerable for small matrices.
+
+% \begin{figure}
+% \centering
+% \begin{subfigure}[b]{0.3\textwidth}
+% \includegraphics[width=\textwidth]{images/2015-04-18_encoding_decoding_1024.eps}
+% \caption{Encoding and Decoding performance for g = 1024}
+% \label{enc_dec1024}
+% \end{subfigure}
+%
+% \begin{subfigure}[b]{0.3\textwidth}
+% \includegraphics[width=\textwidth]{images/2015-04-18_encoding_decoding_128.eps}
+% \caption{Encoding and Decoding performance for g = 128}
+% \label{enc_dec128}
+% \end{subfigure}
+%
+% \begin{subfigure}[b]{0.3\textwidth}
+% \includegraphics[width=\textwidth]{images/2015-04-18_encoding_decoding_16.eps}
+% \caption{Encoding and Decoding performance for g = 16}
+% \label{enc_dec16}
+% \end{subfigure}
+% \end{figure}
+
 \paragraph{Comparison of the load of matrix multiplications and inversions}
+
+To compare how much slower is the matrix multiplication with the matrix
+inversion for different generation sizes, we ran a set of tests. We used a
+single core to perform the operations. We changed the generation sizes,
+performed matrices multiplications and matrix inversions, and measured the spent
+time doing so. We then calculated the ratio $ratio = \frac{T_{mult}}{T_{inv}}$.
+Table~\ref{runtimes} summarizes the results. The bigger the matrix size, the
+smaller is the calculated ratio. This means that when the problems are bigger,
+the decoding throughput decreases compared with the encoding throughput.
 

### 2016-05-31 schemes.tex
Edit RLNC. Update on decoding

@@
 (where applies) for each coding scheme. Later, we address particular schemes
-which are obtained by modifying the basic coding operations.
+which are obtained by modifying the basic coding operations that provide
+better processing speeds, particularly relevant for the Raspberry Pi.
 
@@
 \subsubsection{Decoding}
+\label{sssec:decoding}
 To be able to decode a batch of $g$ packets, a \ac{l.i.} set of $g$
@@
 of linear equations using \ac{GF} aritmethics. Thus, we define
-$\textbf{C} = \left[C_1 \ldots C_g \right]^T$ and
-$\textbf{P} = \left[P_1 \ldots P_g \right]^T$. Algebraically, decoding
-simplifies to finding the inverse of $\textbf{V}$ in the linear system
-$\textbf{C} = \textbf{V} \cdot \textbf{P}$, which can achieved using
-efficient Gaussian elimination techniques \cite{fragouli2006network}.
-On real applications, decoding is performed on-the-fly, e.g. the pivots are
-computed as packets are progressively received, in order to minimize the computation
-delay for each step. The coding matrix is represented as follows:
+$\textbf{C} = \left[C_1 \ldots C_g \right]^T$,
+$\textbf{P} = \left[P_1 \ldots P_g \right]^T$ and the coding matrix
+$\textbf{V}$ that collects the coding coefficients for each of the $g$
+coded packets, as follows:
 %
@@
 %
+Algebraically, decoding simplifies to finding the inverse of
+$\textbf{V}$ in the linear system
+$\textbf{C} = \textbf{V} \textbf{P}$, which can achieved using
+efficient Gaussian elimination techniques \cite{fragouli2006network}.
+On real applications, decoding is performed on-the-fly, e.g. the pivots are
+computed as packets are progressively received, in order to minimize the
+computation delay for each step.
+
 A decoder starts to calculate and substract contributions from each
@@
 the equivalence  $\textbf{V}$ in its reduced echelon form. The steps
-for reducing the matrix by elementary row operations are carried each
+for reducing the matrix by elementary row operations are carried each time
 a \ac{l.i.} packet is received. Once in reduced echelon form, packets
-can be retrieved by doing a substitution starting from the lastest
+can be retrieved by doing a substitution starting from the latest
 coded packet. In this way, the amount of elementary operations at the end
-is diminished.
+of the decoding process is diminished.
 
 \subsubsection{Recoding}
-An inherent property of \ac{NC} is the possibility for intermediate nodes
-in a network between a source and a destination, to create coded packets
-even from coded packets sent from the source. In general, a recoded packet should be indistinguishable
-from a coded one. Thus, we define a recoded packet as
-$R_i$ and its corresponding encoding vector as
-$w_i$ with coding coefficients $ \left[w_{i,1} \ldots w_{i,g} \right]$,
-as follows:
+As an inherent property of \ac{RLNC}, an intermediate node in the network
+is able to create new coded packets without needing to decode previously
+received ones from an encoding source. Therefore, \ac{RLNC} is an end-to-end
+coding scheme that permits to \textit{recode} former coded packets at any
+point in the network without inquiring in local decoding processing. In
+principle, a recoded packet should be indistinguishable from a coded one.
+Thus, we define a recoded packet as $R_i$ and consider the coding
+coefficients $ \left[w_{i,1} \ldots w_{i,g} \right]$, as the used ones to
+create $R_i$. Later, a recoded packet can be written as:
 %
@@
 
-In \eqref{eq:recoded_packet}, $w_{i,j}$ is the coding coefficient that
-multiplies $C_j$, uniformly and randomly chosen from $GF(q)$. Any
-decoder that collects $R_i, i \in [1,g]$ linearly independent coded packets,
-with their respective $w_i$, will be able to decode the data as mentioned
-before.
+In \eqref{eq:recoded_packet}, $w_{i,j}$ is the coding coefficient used
+in the $i$-th recoded packet and assigned to multiply a previously coded
+packet $C_j$. These coding coefficients are again uniformly and randomly chosen
+from $GF(q)$. Still, each of the $w_{i,j}$ are not the appended recoding
+coefficients for signalling since the they will only retrieve previously
+coded packets. The analytical expression for the appended recoding
+coefficients is obtained by calculating recoded packets as function of the
+original packets. Therefore, we define the local coding matrix $\textbf{W}$
+in the same way as it was made for $\textbf{V}$. Thus, the local coding matrix
+can be written as:
+%
+\begin{align} \label{eq:local_coding_matrix}
+\textbf{W} =
+\left[
+\begin{array}{c}
+        w_1    \\ \hline
+        \vdots \\ \hline
+        w_g    \\
+\end{array}
+\right]
+=
+\left[
+\begin{array}{ccc}
+        w_{1,1} & \ldots & w_{1,g} \\
+        \vdots  & \ddots & \vdots  \\
+        w_{g,1} & \ldots & w_{g,g} \\
+\end{array}
+\right]
+\end{align}
+%
+With the definitions from \eqref{eq:coding_matrix} and
+\eqref{eq:local_coding_matrix}, the recoded packets
+$\textbf{R} = \left[R_1 \ldots R_g \right]^T$ are written as
+$\textbf{R} = (\textbf{W} \textbf{V}) \textbf{P}$
+
+Similarly as with encoding, any decoder that collects a set
+of $g$ \ac{l.i.} recoded packets with their respective $w_i$, will be able to
+decode the data as mentioned before in Section \ref{sssec:decoding}. Finally,
+the appended coding coefficients for decoding
 
@@
 packet like \ac{RLNC} does, here the encoder sets more coding coefficients to
-zero when creating a new coded packet.
-In practice this can be implemented in
+zero when creating a new coded packet. In practice this can be implemented in
 a couple of ways.
+
 %One way to accomplish this is to add a Bernoulli random
@@
     \begin{cases}
-        {(0,0.5]} & \text{for} q = 2 \\
-        {(0,1]} & \text{for} q > 2
+        {(0,0.5]} & \text{for } q = 2 \\
+        {(0,1]} & \text{for } q > 2
     \end{cases}

### 2016-05-31 schemes.tex
Remove raw kodo and include kodo-rlnc or kodo-cpp. Editing recoding in RLNC

@@
 $\textbf{R} = \left[R_1 \ldots R_g \right]^T$ are written as
-$\textbf{R} = (\textbf{W} \textbf{V}) \textbf{P}$
+$\textbf{R} = (\textbf{W} \textbf{V}) \textbf{P}$. Here, we recognize
+the relationship between original and recoded packets. The resulting
+coding matrix is simply the multiplication of matrices $\textbf{W}$ and
+$\textbf{V}$. Denoting ${(\textbf{W} \textbf{V})}_{i,j}$ as the element
+in the $i$-th row and $j$-th column of $(\textbf{W} \textbf{V})$, this
+term is the resulting coding coefficient used to create $R_i$ after
+encoding the original packet $P_j$ recoding it locally in an intermediate
+node. In this case, we have assumed that recoding has taken place at the
+closesBy doing some algebra, these terms can be verified to be computed
+as:
+
+\begin{align}
+\label{eq:appended_coded_coefficients}
+{(\textbf{W} \textbf{V})}_{i,j} = \sum_{k=1}^{g} w_{i,k} v_{k,j}\ ,\ \forall i,j \in [1,g] \times [1,g]
+\end{align}
 

### 2016-05-31 schemes.tex
Change double subscript notation

@@
 \begin{align} \label{eq:coded_packet}
-C_i  &= \bigoplus_{j=1}^{g} v_{i,j} \otimes P_j ,\ \forall i \in [1,\ldots)
+C_i  &= \bigoplus_{j=1}^{g} v_{ij} \otimes P_j ,\ \forall i \in [1,\ldots)
 \end{align}
@@
 $g$ \ac{l.i.} coded packets to decode the batch. Also, in
-\eqref{eq:coded_packet}, $v_{i,j}$ is the coding coefficient used in the
+\eqref{eq:coded_packet}, $v_{ij}$ is the coding coefficient used in the
 $i$-th coded packet and assigned to multiply the $j$-th original packet.
@@
 \begin{align} \label{eq:coded_packet_coef}
-|v_i| &= \sum_{j=1}^{g} |v_{i,j}| = g \times \lceil \log_{2} (q)
+|v_i| &= \sum_{j=1}^{g} |v_{ij}| = g \times \lceil \log_{2} (q)
 \rceil ~ [\mathrm{bits}]
@@
 \begin{array}{ccc}
-        v_{1,1} & \ldots & v_{1,g} \\
+        v_{11} & \ldots & v_{1g} \\
         \vdots  & \ddots & \vdots  \\
-        v_{g,1} & \ldots & v_{g,g} \\
+        v_{g1} & \ldots & v_{gg} \\
 \end{array}
@@
 Thus, we define a recoded packet as $R_i$ and consider the coding
-coefficients $ \left[w_{i,1} \ldots w_{i,g} \right]$, as the used ones to
+coefficients $w_{i1}, \ldots, w_{ig}$ as the used ones to
 create $R_i$. Later, a recoded packet can be written as:
@@
 \label{eq:recoded_packet}
-R_i = \bigoplus_{j=1}^{g} w_{i,j} \otimes C_j  ,\ \forall i \in [1,\ldots)
+R_i = \bigoplus_{j=1}^{g} w_{ij} \otimes C_j  ,\ \forall i \in [1,\ldots)
 \end{align}
 
-In \eqref{eq:recoded_packet}, $w_{i,j}$ is the coding coefficient used
+In \eqref{eq:recoded_packet}, $w_{ij}$ is the coding coefficient used
 in the $i$-th recoded packet and assigned to multiply a previously coded
 packet $C_j$. These coding coefficients are again uniformly and randomly chosen
-from $GF(q)$. Still, each of the $w_{i,j}$ are not the appended recoding
+from $GF(q)$. Still, each of the $w_{ij}$ are not the appended recoding
 coefficients for signalling since the they will only retrieve previously
@@
 \begin{array}{ccc}
-        w_{1,1} & \ldots & w_{1,g} \\
+        w_{11} & \ldots & w_{1g} \\
         \vdots  & \ddots & \vdots  \\
-        w_{g,1} & \ldots & w_{g,g} \\
+        w_{g1} & \ldots & w_{gg} \\
 \end{array}
@@
 coding matrix is simply the multiplication of matrices $\textbf{W}$ and
-$\textbf{V}$. Denoting ${(\textbf{W} \textbf{V})}_{i,j}$ as the element
+$\textbf{V}$. Denoting ${(\textbf{W} \textbf{V})}_{ij}$ as the element
 in the $i$-th row and $j$-th column of $(\textbf{W} \textbf{V})$, this
@@
 as:
-
+%
 \begin{align}
 \label{eq:appended_coded_coefficients}
-{(\textbf{W} \textbf{V})}_{i,j} = \sum_{k=1}^{g} w_{i,k} v_{k,j}\ ,\ \forall i,j \in [1,g] \times [1,g]
+{(\textbf{W} \textbf{V})}_{ij} = \sum_{k=1}^{g} w_{ik} v_{kj}\ ,\ \forall i,j \in [1,g] \times [1,g]
 \end{align}
-
+%
 Similarly as with encoding, any decoder that collects a set
@@
 \begin{align} \label{eq:sparse_coded_packet}
-    %C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
-    C_i  &= \bigoplus_{j=1}^{g} \text{B}(d) \, v_{i,j} \otimes P_j ,\ \forall i \in [1,g] ,\
-    v_{i,j} > 0,\
+    %C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{ij} \otimes P_j ,\ \forall i \in [1,g] ,\
+    C_i  &= \bigoplus_{j=1}^{g} \text{B}(d) \, v_{ij} \otimes P_j ,\ \forall i \in [1,g] ,\
+    v_{ij} > 0,\
     d \in
@@
 \begin{align} \label{eq:sparse_coded_packet2}
-    C_i  &= \bigoplus_{j=1}^{\floor{\text{Binom}(g,d)}} v_{i,m} \otimes P_{m} ,\
+    C_i  &= \bigoplus_{j=1}^{\floor{\text{Binom}(g,d)}} v_{im} \otimes P_{m} ,\
     %L \subseteq \{1,\dots,g\}: |L|=k ,\
     \forall i \in [1,g] ,\
-    v_{i,j} > 0
+    v_{ij} > 0
 \end{align}

### 2016-05-31 schemes.tex
Finished RLNC ...for now

@@
 coefficients for signalling since the they will only retrieve previously
-coded packets. The analytical expression for the appended recoding
-coefficients is obtained by calculating recoded packets as function of the
+coded packets. The analytical expression for the appended coefficients
+after recoding is obtained by calculating recoded packets as function of the
 original packets. Therefore, we define the local coding matrix $\textbf{W}$
@@
 encoding the original packet $P_j$ recoding it locally in an intermediate
-node. In this case, we have assumed that recoding has taken place at the
-closesBy doing some algebra, these terms can be verified to be computed
-as:
+node. Finally, the appended coefficients for $R_i$ are
+${(\textbf{W} \textbf{V})}_{ik}$ with $k \in [1,g]$. By doing some
+algebra, each ${(\textbf{W} \textbf{V})}_{ij}$ term can be verified to be
+computed as:
 %
@@
 %
-Similarly as with encoding, any decoder that collects a set
-of $g$ \ac{l.i.} recoded packets with their respective $w_i$, will be able to
-decode the data as mentioned before in Section \ref{sssec:decoding}. Finally,
-the appended coding coefficients for decoding
+This procedure is carried by all the recoders in a given network, therefore
+keeping the structure of the recoded packets for any decoder to compute
+the Gaussian elimination. Similarly as with encoding, any decoder that
+collects a set of $g$ \ac{l.i.} recoded packets with their respective
+${(\textbf{W} \textbf{V})}_{ij}$, will be able to decode the data as mentioned before in Section \ref{sssec:decoding}.
 

### 2016-06-01 schemes.tex
SRLNC almost done

@@
 \subsection{Random Linear Network Coding}
+\label{ssec:RLNC}
 
@@
 This procedure is carried by all the recoders in a given network, therefore
-keeping the structure of the recoded packets for any decoder to compute
-the Gaussian elimination. Similarly as with encoding, any decoder that
-collects a set of $g$ \ac{l.i.} recoded packets with their respective
-${(\textbf{W} \textbf{V})}_{ij}$, will be able to decode the data as mentioned before in Section \ref{sssec:decoding}.
+allowing any decoder to compute the original data after Gaussian elimination,
+regardless of the amount of times where recoding was performed. Similarly as
+with the encoding operation, any decoder that collects a set of $g$ \ac{l.i.} recoded
+packets with their respective coefficients, will be able to decode the data
+as mentioned before in Section \ref{sssec:decoding}.
 
@@
 In \ac{SRLNC}, instead of considering all the packets to create a coded
-packet like \ac{RLNC} does, here the encoder sets more coding coefficients to
-zero when creating a new coded packet. In practice this can be implemented in
-a couple of ways.
+packet as in \ac{RLNC}, for this coding scheme an encoder sets more
+coding coefficients to zero when generating a coded packet. A way to
+accomplish this, is to set a fixed ratio of non-zero coefficients
+in the encoding vector of size $g$. We refer to this fixed ratio as the
+average coding density $d$. Thus, for any coded packet $C_i$ with coding
+coefficients $v_{ij},\ j \in [1,g]$, its coding density is defined as follows:
+%
+\begin{align}
+\label{eq:coding_density}
+d = \frac{\sum_{j=1}^{g} f(v_{ij})}{g},\ \
+    f(v_{ij}) =
+    \begin{cases}
+        0 & \text{for } v_{ij} = 0 \\
+        1 & \text{for } v_{ij} \neq 0
+    \end{cases}
+\end{align}
+%
+From the density definition in \eqref{eq:coding_density}, it can be observed that
+$0 \leq d \leq 1$. As $g$ increased, we obtain more granularity in the density.
+Notice that the special case $d = 0$ has no practical purpose since it
+implies just zero padded data. So, a practical range for the density excludes
+the zero case, $0 < d \leq 1$. Moreover, it can be also observed that the
+case of $d = 1$ reduces to the \ac{RLNC} coding scheme described in Section
+\ref{ssec:RLNC}.
 
+To achieve a desired average coding density in the coefficients, for each
+of them, we utilize a set of Bernoulli random variables all with parameter $d$, i.e.
+$\mathbb{B}_j \sim Bernoulli(d)\ ,\ \forall j \in [1,g]$. In this way, we
+can represent a coded packet in \ac{SRLNC} as:
 %One way to accomplish this is to add a Bernoulli random
 %variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:
-The simplest way to accomplish this is to add a Bernoulli random
-variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:
-
 \begin{align} \label{eq:sparse_coded_packet}
     %C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{ij} \otimes P_j ,\ \forall i \in [1,g] ,\
-    C_i  &= \bigoplus_{j=1}^{g} \text{B}(d) \, v_{ij} \otimes P_j ,\ \forall i \in [1,g] ,\
-    v_{ij} > 0,\
+    C_i  &= \bigoplus_{j=1}^{g} \mathbb{B}_j v_{ij} \otimes P_j ,\ \forall i \in [1,g] ,\ \
     d \in
@@
 \end{align}
+%
+In \eqref{eq:sparse_coded_packet}, we have specified a dependency on the field size
+for practical density values. In case of employing $GF(2)$, the maximum plausible
+density is restricted up to 0.5 since higher values incur in more frequent \ac{l.d.}
+coded packets \textbf{Include reference here}. Reducing $d$ enables the encoder to
+decrease the average number of packets manipulated to make a coded packet. This
+reduces the complexity of the encoder since it needs to mix less packets. Moreover,
+it also simplifies the decoder processing given that less nonzero coding coefficients
+required to be operated on during the Gaussian elimination stage.
 
-We call $d$ the coding density.
-Reducing $d$ enables the encoder to decrease the average number of packets that
-are mixed into each coded packet. Thereby reducing the complexity of the
-encoder that needs to mix less packets, but also on the decoder that in
-contrast needs to eliminate less nonzero coding coefficients. The catch of this
-approach is that coded packets produced by the encoder becomes more \ac{l.d.}
-on each other as the coding complexity is reduced. This incurs in additional
-channel overhead.
+The drawback of this scheme is that coded packets from the encoder become more \ac{l.d.}
+on each other as the density is reduced. This incurs in transmission overhead
+since more coded packets are required to be sent to overcome the reception of redundant
+packets. Also, particularly with this method, generating a coded packet may imply
+that it could not contain any data at all. For example, we might find the case
+where $\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] = \mathbf{0}$. In that case,
+the encoder discards the coded packet and tries to generate a new one, though this is
+unlikely to occur in general.
 
-Generating a coded packet does not imply that it contains any data at all. I.e.
-$ \left[ B(d)_{1}, \ldots, B(d)_{g} \right] = \mathbf{0}$.
-In that case, one would have to trash the coded packet and generate a new one.
+Under the current method for setting the density, most coded packets that
+are produced by the encoder are typically very sparse.
+The reason being that here we control the \textit{average} amount
+of nonzero coefficients, but not the exact value for each coded packet. Therefore,
+we may have some cases where we have more or less packets combined. A second
+implementation in Kodo considers doing something more clever.
 
-Most coded packets that are produced by the encoder are typically very sparse.
-We will therefore rely on a slightly different implementation in KODO
-\ref{eq:sparse_coded_packet2} that proved faster for low densities. It is best
-expressed as:
-
+As is shown in \eqref{eq:sparse_coded_packet2}, that implementation
+proved faster for low densities \textbf{reference?}. It is best expressed as:
+%
 \begin{align} \label{eq:sparse_coded_packet2}
@@
 \fxnote{Can this be represented smarter?}
-
-%To solve this, one could trash the coded packet and generate a new coded
-%packet. This is not the most efficient because KODO needs to count the
-%the number of nonzero coding coefficients in each coded packets to eliminate
-%all zero packets.
-%
-%This is the most correct approach, but the most efficient approach although it is mathematically .
 

### 2016-06-01 schemes.tex
Reviewing description of SRLNC

@@
 %
-From the density definition in \eqref{eq:coding_density}, it can be observed that
-$0 \leq d \leq 1$. As $g$ increased, we obtain more granularity in the density.
-Notice that the special case $d = 0$ has no practical purpose since it
-implies just zero padded data. So, a practical range for the density excludes
-the zero case, $0 < d \leq 1$. Moreover, it can be also observed that the
-case of $d = 1$ reduces to the \ac{RLNC} coding scheme described in Section
-\ref{ssec:RLNC}.
+From the density definition in \eqref{eq:coding_density}, it can be
+observed that $0 \leq d \leq 1$. As $g$ increased, we obtain more
+granularity in the density. Notice that the special case $d = 0$ has no
+practical purpose since it implies just zero padded data. So, a practical
+range for the density excludes the zero case, $0 < d \leq 1$. Moreover,
+it can be also observed that the case of $d = 1$ reduces to the \ac{RLNC}
+coding scheme described in Section \ref{ssec:RLNC}.
 
 To achieve a desired average coding density in the coefficients, for each
-of them, we utilize a set of Bernoulli random variables all with parameter $d$, i.e.
-$\mathbb{B}_j \sim Bernoulli(d)\ ,\ \forall j \in [1,g]$. In this way, we
-can represent a coded packet in \ac{SRLNC} as:
-%One way to accomplish this is to add a Bernoulli random
-%variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:
+of them, we utilize a set of Bernoulli random variables all with parameter
+$d$ as it success probability, i.e. $\mathbb{B}_j \sim Bernoulli(d)\ ,\ \forall
+j \in [1,g]$. In this way, we can represent a coded packet in \ac{SRLNC} as:
+%
 \begin{align} \label{eq:sparse_coded_packet}
-    %C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{ij} \otimes P_j ,\ \forall i \in [1,g] ,\
-    C_i  &= \bigoplus_{j=1}^{g} \mathbb{B}_j v_{ij} \otimes P_j ,\ \forall i \in [1,g] ,\ \
+    C_i  &= \bigoplus_{j=1}^{g} \mathbb{B}_j v_{ij} \otimes P_j ,\ v_{ij}
+    \neq 0\
+    \forall i \in [1,\ldots) ,\ \
     d \in
@@
 %
-In \eqref{eq:sparse_coded_packet}, we have specified a dependency on the field size
-for practical density values. In case of employing $GF(2)$, the maximum plausible
-density is restricted up to 0.5 since higher values incur in more frequent \ac{l.d.}
-coded packets \textbf{Include reference here}. Reducing $d$ enables the encoder to
-decrease the average number of packets manipulated to make a coded packet. This
-reduces the complexity of the encoder since it needs to mix less packets. Moreover,
-it also simplifies the decoder processing given that less nonzero coding coefficients
-required to be operated on during the Gaussian elimination stage.
+In \eqref{eq:sparse_coded_packet}, we have the requirement for the coding
+coefficient to not be zero, since we want to ensure a coding coefficient
+is generate for any random trial where $\mathbb{B}_j = 1$. Therefore, in our
+implementation of \ac{SRLNC} we exclude the zero element and then pick
+uniformly distributed random elements from $GF(q)-\{ 0 \}$. Also, we have
+specified a dependency on the field size for practical
+density values. In case of employing $GF(2)$, the
+maximum plausible density is restricted up to 0.5 since higher values incur
+in more frequent \ac{l.d.} coded packets \textbf{Include reference here}.
 
-The drawback of this scheme is that coded packets from the encoder become more \ac{l.d.}
-on each other as the density is reduced. This incurs in transmission overhead
-since more coded packets are required to be sent to overcome the reception of redundant
-packets. Also, particularly with this method, generating a coded packet may imply
-that it could not contain any data at all. For example, we might find the case
-where $\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] = \mathbf{0}$. In that case,
-the encoder discards the coded packet and tries to generate a new one, though this is
-unlikely to occur in general.
+Reducing $d$ enables the encoder to decrease the average number of packets
+manipulated to make a coded one. This reduces the complexity of the encoder
+since it needs to mix less packets. Moreover, it also simplifies the decoder
+processing given that less nonzero coding coefficients are required to be
+operated during the Gaussian elimination stage.
+
+The drawback of this scheme is that coded packets from the encoder
+become more \ac{l.d.} on each other as the density is reduced.
+This leads to transmission overhead since another coded packet
+is required to be sent for every reception of a redundant packet.
+Also, particularly with this method, generating a coded packet may imply
+that it could not contain any data at all. For example, we might find
+the case where $\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] =
+\mathbf{0}$. In that case, the encoder discards the coded packet
+and tries to generate a new one. This situation occurs more frequently
+as the density is reduced.
 

### 2016-06-01 schemes.tex
Expanded multicore description. 2 more citations added

@@
 
-The operations needed to encode and decode the data are, in general, similar. To
+The operations needed to encode and decode data are, in general, similar. To
 encode packets, the encoder needs to perform the matrix multiplication
@@
 coding matrix $\textbf{V}$ while performing, in parallel, row operations on the
-coded data $\textbf{C}$. However, the parallelization of such operations provide
-speeds up that are limited for small block sizes ($\leq 2048$ bytes). The reason
-is that to operate in a parallel fashion over the same coded packet $C_i$
-requires strained synchronization. In~\cite{5061951} and~\cite{4262451} the
+coded data $\textbf{C}$. For example, in~\cite{5061951} and~\cite{4262451} the
 parallelization of the row operations are optimized for \ac{GPU} and \ac{SMP}
-systems respectively.
+systems respectively. However, the parallelization of such operations provide
+limited speeds up for small block sizes ($\leq 2048$ bytes). The reason is that
+to operate in a parallel fashion over the same coded packet $C_i$ requires
+strained synchronization.
 
@@
 preferable to explicitly invert the matrix $\textbf{V}$, and then take advantage
-of optimizations for matrix multiplications. The authors implemented
-in~\cite{wunderlich2015network} an algorithm that adopts the ideas of efficient
-\ac{BLAS} operations~\cite{lawson1979basic} reimplementing them for finite
-fields operations. The implemented algorithm tries to be cache efficient
+of optimizations for matrix multiplications, both at encoding and decoding time.
+With that purpose, the authors implemented in~\cite{wunderlich2015network} an
+algorithm that adopts the ideas of efficient \ac{BLAS}
+operations~\cite{lawson1979basic} reimplementing them for finite fields
+operations. Although there are already certain libraries available such as
+~\cite{dumas2008dense} and \cite{dumas2002linbox} that allows the usage of the
+highly optimize \ac{BLAS} implementations for some finite fields, they work
+converting the GF elements into floating point numbers and back. Even though
+that approach is efficient for large matrix sizes, the overhead imposed by the
+conversions is not suitable for the the matrix sizes of typical network coding
+implementations. The implemented algorithm aims to be cache efficient by
 maximizing the number of operations performed over a block of fetched data. This
-is done by operating on square sub-blocks of the matrices, which exploits the
-spatial locality of the data, at least for $\mathcal{O}(n^3)$
-algorithms~\cite{golub2012matrix}. The optimal size of the block is
-architecture-dependent. The ideal block has a number of operands that fit into
-L1 cache, and it is a multiple of the \ac{SIMD} operations size.
+is done by dividing the matrices in square sub-blocks and operating with them.
+As a consequence, this technique exploits the spatial locality of the data, at
+least for $\mathcal{O}(n^3)$ algorithms~\cite{golub2012matrix}. The optimal size
+of the block is architecture-dependent. The ideal block has a number of operands
+that fit into L1 cache, and it is a multiple of the \ac{SIMD} operations size.
 
 The main idea of the implemented algorithm is to represent each one of the sub-
-block matrix operations as a base, \textit{kernel}, operation that can be
-optimized, e.g., using \ac{SIMD} operations. Each of these kernels, at the same
-time, can be represented as a task with inputs and outputs in memory. If the
-algorithm is formulated conventionally, and the data operations on the sub-
-blocks are reordered, then it is possible to resolve data dependencies with a
-\ac{DAG}. For the algorithm, a dependency means, for example, that a sub-block
-of the matrix in memory cannot be read unless a previous writing operation was
-performed there. When the \ac{DAG} is determined, then, a scheduler assigns to
-the available cores the individual kernel operations that have their
-dependencies fulfilled. The benefit of this algorithm is that the
-synchronization relies only on data dependencies, and it does not requires the
-insertion of artificial synchronization points. Using this technique, the matrix
-inversion is performed using an algorithm based on LU
+block matrix operations (matrix-matrix multiplication, matrix-triangle matrix
+multiplication, triangle-matrix system solving, etc) as a base, \textit{kernel},
+operation that can be optimized individually, e.g., using \ac{SIMD} operations.
+Each of these kernel operations, at the same time, can be represented as a task
+with inputs and outputs in memory. If any algorithm is formulated
+conventionally, and the data operations on the sub-blocks are reordered, then it
+is possible to resolve data dependencies with a \ac{DAG}. For the algorithm, a
+dependency means, for example, that a sub-block of the matrix in memory cannot
+be read unless a previous writing operation was performed there. When the
+\ac{DAG} is determined, then, a scheduler assigns to the available cores the
+execution of the individual kernel operations that have their dependencies
+satisfied. The benefit of this method is that the synchronization relies only on
+data dependencies, and it does not requires the insertion of artificial
+synchronization points. Using this technique, the matrix inversion is performed
+using an algorithm based on LU
 factorization~\cite{Dongarra:2011:HPM:2132876.2132885}, and the matrix
 multiplication is performed by making the various matrix-matrix multiplications
-of the sub-blocks.
+on the sub-blocks.

### 2016-06-01 schemes.tex
Detailing SRLNC

--- 2016-06-01 schemes.tex
@@
 allowing any decoder to compute the original data after Gaussian elimination,
-regardless of the amount of times where recoding was performed. Similarly as
-with the encoding operation, any decoder that collects a set of $g$ \ac{l.i.} recoded
-packets with their respective coefficients, will be able to decode the data
-as mentioned before in Section \ref{sssec:decoding}.
+regardless of the amount of times where recoding was performed. Similarly
+as with the encoding operation, any decoder that collects a set of
+$g$ \ac{l.i.} recoded packets with their respective coefficients, will
+be able to decode the data as mentioned before in Section \ref{sssec:decoding}.
 
@@
 packet as in \ac{RLNC}, for this coding scheme an encoder sets more
-coding coefficients to zero when generating a coded packet. A way to
-accomplish this, is to set a fixed ratio of non-zero coefficients
-in the encoding vector of size $g$. We refer to this fixed ratio as the
-average coding density $d$. Thus, for any coded packet $C_i$ with coding
-coefficients $v_{ij},\ j \in [1,g]$, its coding density is defined as follows:
+coding coefficients to zero when generating a coded packet with the purpose
+of reducing the overall processing in both encoding and decoding. In what
+follows, we describe the coding scheme with a basic method to produce sparse
+coded packets and later we indicate a second one, giving reference to their
+implementation performance.
+
+\subsubsection{Method 1: Fixing the Coding Density}
+A way to control the amount of non-zero coding coefficients, is to set a
+fixed ratio of non-zero coefficients in the encoding vector of size $g$. We
+refer to this fixed ratio as the average coding density $d$. Thus, for any
+coded packet $C_i$ with coding coefficients $v_{ij},\ j \in [1,g]$, its
+coding density is defined as follows:
 %
@@
 is required to be sent for every reception of a redundant packet.
-Also, particularly with this method, generating a coded packet may imply
-that it could not contain any data at all. For example, we might find
+Also, particularly with this method, we may still generate a coded packet
+which does not contain any data at all. For example, we might find
 the case where $\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] =
@@
 
-Under the current method for setting the density, most coded packets that
-are produced by the encoder are typically very sparse.
-The reason being that here we control the \textit{average} amount
-of nonzero coefficients, but not the exact value for each coded packet. Therefore,
-we may have some cases where we have more or less packets combined. A second
-implementation in Kodo considers doing something more clever.
+\subsubsection{Method 2: Sampling the Amount of Packets to Combine}
+The method described from \eqref{eq:sparse_coded_packet} permits
+to obtain a fast implementation in terms of execution time for
+$d \geq 0.3$ \textbf{Include reference here}. Nevertheless, for $d < 0.3$
+the implementation becomes slow given that more Bernoulli trials are
+required in total for all random variables to generate a coded packet.
+Thus, we introduce a second method that permits a fast implementation
+for low coding densities  \textbf{Same reference here}.
+
+For this method, we first calculate the amount of coding coefficients
+that we will use to combine.
+
+The second method
+% The reason being that here we control the \textit{average} amount
+% of nonzero coefficients, but not the exact value for each coded packet. Therefore,
+% we may have some cases where we have more or less packets combined. A second
+% implementation in Kodo considers doing something more clever.
 

### 2016-06-01 schemes.tex
Explaining SRLNC

@@
 For this method, we first calculate the amount of coding coefficients
-that we will use to combine.
+that we will use to combine. To do it so, a random number $\mathbb{N}$
+of the original packets is used to produce a coded packet. For our case,
+$\mathbb{N}$ is binomially distributed with parameters $g$ for the number
+of trials and $d$ for its success probability, e.g. $\mathbb{N} \sim
+Binomial(g,d)$. However, when sampling from this distribution, the case
+$\mathbb{N} = 0$ occurs with a non-zero probability. In order to handle
+this special case, our implementation considers
+$\mathbb{K} = \max(1,\mathbb{N})$ as the final amount of packets to be
+mixed together. In this way, we always ensure that at least one packet is
+encoded.
 
-The second method
-% The reason being that here we control the \textit{average} amount
-% of nonzero coefficients, but not the exact value for each coded packet. Therefore,
-% we may have some cases where we have more or less packets combined. A second
-% implementation in Kodo considers doing something more clever.
+The only caveat is that the case of $\mathbb{K} = 1$ occurs slightly
+more often than in the original distribution, but for the
+considered density range in this method it is depreciable
+\textbf{Same reference here}. Then, once the distribution number of packets
+to mix as been defined, we create a subset $\mathcal{C}$ of size $k$
 
-As is shown in \eqref{eq:sparse_coded_packet2}, that implementation
+a coded packetas is shown in
+\eqref{eq:sparse_coded_packet2}, that implementation
 proved faster for low densities \textbf{reference?}. It is best expressed as:

### 2016-06-01 measurements.tex
added caption to figures

@@
 packet was fixed to $1536$~bytes since that is the typical size of an Ethernet
-frame. The blocked operations were performed dividing the matrices in sub-blocks
-of 16,32,64,...,1024 symbols, and the figures only show the best results
-(usually block sizes of 16 or 32 symbols since with bigger block sizes, the
-operands do not fit in L1 cache).
+frame. The blocked operations were performed dividing the matrices in squared
+sub-blocks of 16,32,64,...,1024 operands (words in the finite field) in height
+and width, and the figures only show the best results (usually block sizes of
+16x16 or 32x32 operands since with bigger block sizes, the operands do not fit
+in L1 cache).
 
@@
 
-\paragraph{Baseline encoding} The baseline results involve no recording
-of the \ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder
-uses only one thread. And the difference between the non-blocked and blocked
-encoding is that in the blocked scheme, the matrix multiplications are performed
+\paragraph{Baseline encoding} The baseline results involve no recording of the
+\ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder uses
+only one thread. And the difference between the non-blocked and blocked encoding
+schemes is that in the blocked scheme, the matrix multiplications are performed
 dividing the matrices in sub-blocks in order to make the algorithm cache
@@
 \includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_1024.eps}
-\caption{Encoding and Decoding performance for g = 1024}
+\caption{Encoding and Decoding performance for g = 1024 \cite{wunderlich2015network}}
 \label{enc_dec1024}
@@
 \includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_128.eps}
-\caption{Encoding and Decoding performance for g = 128}
+\caption{Encoding and Decoding performance for g = 128 \cite{wunderlich2015network}}
 \label{enc_dec128}
@@
 four cores is 2.82 times faster than with a single core. Due to the smaller
-matrix sizes, the gain by using blocked operations in the baselines is not that
-big compared with $g$ = 1024. For the same reason, the matrix inversion is less
-expensive. As a consequence, the decoding throughput is 71\% of the encoding
-throughput.
+matrix sizes, the gain when using blocked operations in the baselines is not
+that significant when compared with $g$ = 1024. For the same reason, the matrix
+inversion is less expensive. As a consequence, the decoding throughput is 71\%
+of the encoding throughput.
 
@@
 \includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_16.eps}
-\caption{Encoding and Decoding performance for g = 16}
+\caption{Encoding and Decoding performance for g = 16 \cite{wunderlich2015network}}
 \label{enc_dec16}
@@
 the L1 cache. For the scheduled version, since the problem to solve is so small,
-the gain of using four cores is a factor of 1.68 compared with a single core,
+the gain when using four cores is a factor of 1.68 compared with a single core,
 and 1.01 compared with two cores. Therefore, there are no practical benefits in
@@
 The differences in throughput, for all generation sizes, between the blocked
-baseline and the scheduled measurements are due the time spent resolving the
-dependencies and the scheduling overhead. These effects are negligible for big
-generation sizes, while considerable for small matrices.
+baseline and the single threaded scheduled measurements are due the time spent
+resolving the dependencies and the scheduling overhead. These effects are
+negligible for big generation sizes, while considerable for small matrices.
 
@@
 
-To compare how much slower is the matrix multiplication with the matrix
-inversion for different generation sizes, we ran a set of tests. We used a
-single core to perform the operations. We changed the generation sizes,
-performed matrices multiplications and matrix inversions, and measured the spent
-time doing so. We then calculated the ratio $ratio = \frac{T_{mult}}{T_{inv}}$.
-Table~\ref{runtimes} summarizes the results. The bigger the matrix size, the
-smaller is the calculated ratio. This means that when the problems are bigger,
-the decoding throughput decreases compared with the encoding throughput.
+To compare how much slower is the matrix multiplication with respect to the
+matrix inversion for different generation sizes, we ran a set of tests. We used
+a single core to perform the operations. We changed the generation sizes,
+performed matrices multiplications and matrix inversions, and measured the time
+spent doing so. We then calculated the ratio between these two measured times
+times $ratio = \frac{T_{mult}}{T_{inv}}$. Table~\ref{runtimes} summarizes the
+results. The bigger the matrix size, the smaller is the calculated ratio. This
+means that when the problems are bigger, the decoding throughput decreases
+compared with the encoding throughput.
 

### 2016-06-01 testbed.tex
Remove raw kodo and include kodo-rlnc or kodo-cpp. Editing recoding in RLNC

@@
 \subsection{System Overview}
+
+This section will be used to present our Raspberry Pi testbed, but also how
+it is set up and configured.
+
+The testbed is depicted in \ref{fig:testbed_setup}. It consists of twenty
+Raspberry Pi 1 model B rev 2 (Rasp\_01 to Rasp\_20) and 
+ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).
+The Raspberry Pis are each equipped with an ethernet interface (eth0) that are
+assigned the \ac{IP} addresses listed in the figure.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.6\textwidth]{images/testbed_setup.eps}
+\caption{Testbed setup}
+\label{fig:testbed_setup}
+\end{figure}
+
+\subsubsection{Installing Raspbian}
+
+- 
+- Download image (wget)
+- Update/Modify image (chroot)
+- Burn image
+- Bang! linux is running
+-
+
+We have installed the official Raspbian linux \ac{OS} on all the devices.
+
 \subsection{Installation and Updating}
@@
 \item Clone the Kodo repository in the server by executing: \\
-\texttt{git clone git://github.com/steinwurf/kodo.git} in \texttt{\$HOME}. \\
+\texttt{git clone git://github.com/steinwurf/kodo.git} in \texttt{\$HOME}. \textbf{Change the repo to kodo-rlnc or kodo-cpp since just raw kodo is going to be depreceated soon} \\
 

### 2016-06-01 raspi_journal.tex
expanded results multicore
Finished SRLNC for now..

@@
 \usepackage{fixme}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 \input{acronym} % Name of acronyms file
+
+\usepackage[]{algorithm2e}
 
@@
 \address{%
-$^{1}$ \quad Steinwurf ApS; nestor@steinwurf.com\\
-$^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
-$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de\\
-$^{4}$ \quad SFB 912 -- HAEC}
+$^{1}$ \quad Steinwurf ApS. Aalborg, Denmark; nestor@steinwurf.com\\
+$^{2}$ \quad Aalborg University, Department of Electronic Systems. Aalborg, Denmark; \{nh, cws, del\}@es.aau.dk\\
+$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks. Dresden, Germany; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de\\
+$^{4}$ \quad SFB 912 -- Collaborative Research Center HAEC. Dresden, Germany}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
-Curie project (317126) from the European Comission FP7 framework,
-the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
-, the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
-by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d),
-and by the German Research Foundation (DFG) within the Collaborative Research Center SFB 912 – HAEC.}
+\acknowledgments{This research has been partially financed by the
+Marie Curie Initial Training Network (ITN) CROSSFIRE project
+(Grant No. EU - FP7 - CROSSFIRE - 317126) from the European Comission FP7
+framework, the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B),
+the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted by the
+Danish Council for Independent Research (Det Frie Forskningsr\r{a}d), and
+by the German Research Foundation (DFG) within the Collaborative Research
+Center SFB 912 – HAEC.}
 

### 2016-06-01 schemes.tex
Finished SRLNC for now..

@@
 
-For this method, we first calculate the amount of coding coefficients
-that we will use to combine. To do it so, a random number $\mathbb{N}$
-of the original packets is used to produce a coded packet. For our case,
-$\mathbb{N}$ is binomially distributed with parameters $g$ for the number
-of trials and $d$ for its success probability, e.g. $\mathbb{N} \sim
-Binomial(g,d)$. However, when sampling from this distribution, the case
+For this method, we first obtain the amount of packets
+that we will combine to create a coded packet. To do it so, a random
+number $\mathbb{N}$ of the original packets is used to produce a
+coded packet. For our case, $\mathbb{N}$ is binomially distributed
+with parameters $g$ for the number of trials and $d$ for its success
+probability, e.g. $\mathbb{N} \sim Binomial(g,d)$. However,
+when sampling from this distribution, the case
 $\mathbb{N} = 0$ occurs with a non-zero probability. In order to handle
@@
 The only caveat is that the case of $\mathbb{K} = 1$ occurs slightly
-more often than in the original distribution, but for the
-considered density range in this method it is depreciable
-\textbf{Same reference here}. Then, once the distribution number of packets
-to mix as been defined, we create a subset $\mathcal{C}$ of size $k$
-
-a coded packetas is shown in
-\eqref{eq:sparse_coded_packet2}, that implementation
-proved faster for low densities \textbf{reference?}. It is best expressed as:
+more often than $\mathbb{N} = 1$ in the original distribution, but for
+the considered density range in this method, this is not a significant
+modification \textbf{Same reference here}. Then, once the distribution for the
+number of packets to mix has been defined, we sample a value $n$ from
+$\mathbb{N}$ and compute $k = \max(1,n)$. Later, we create a create a
+set $\mathcal{K}$ with cardinality $k$, e.g. $|\mathcal{K}| = k$,
+where the elements in $\mathcal{K}$ are the indexes of the packets that are
+going to be considered for making a coded packet. To compute the indexes
+of the set $\mathcal{K}$, we do the following algorithm in pseudo-code: \\
+\ \\
+\begin{algorithm}[H]
+ \label{alg:k_set}
+ \KwData{$k$: Size of $\mathcal{K}$. $g$: Generation Size}
+ \KwResult{$\mathcal{K}$: The set of non-repeated indexes}
+ $\mathcal{K}$ = \{ \}\;
+ \While{$|\mathcal{K}| \neq k$ }{
+  $i$ = Sample from $\mathbb{U}(1,g)$\;
+  \If{$i \notin \mathcal{K}$}{
+   Insert $i$ in $\mathcal{K}$\;
+   }
+ }
+ \caption{Computation of the set of indexes for packet combination in SRLNC.}
+\end{algorithm}
+\ \\
+Where in Algorithm~\ref{alg:k_set}, the notation $\mathbb{U}(1,g)$ stands
+for a uniform discrete random variable with limits $1$ and $g$. The
+pseudo-code in Algorithm~\ref{alg:k_set} indicates that the set $\mathbb{K}$
+is filled with non-repeated elements taken uniformly at random from
+$[1,\ldots,g]$. Finally, once the set of indexes has been defined, a coded
+packet using \ac{SRLNC} can be written as shown in
+\eqref{eq:sparse_coded_packet2}:
 %
 \begin{align} \label{eq:sparse_coded_packet2}
-    C_i  &= \bigoplus_{j=1}^{\floor{\text{Binom}(g,d)}} v_{im} \otimes P_{m} ,\
+    C_i  &= \bigoplus_{m \in \mathcal{K}} v_{im} \otimes P_{m},\ v_{im} \neq 0,\ \forall i \in [1,\ldots)
     %L \subseteq \{1,\dots,g\}: |L|=k ,\
-    \forall i \in [1,g] ,\
-    v_{ij} > 0
 \end{align}
-where
-$m = \text{choice}(\{1,\dots,g\}, \text{size}=k, \text{replace}=\text{False})$.
-\fxnote{Can this be represented smarter?}
 
-It is often desired to express the coding density as $d=\frac{k}{g}$. We call
-this notation $k-sparse$ where $k$ is the average number of packets combined to
-produce a coded packet.
+% It is often desired to express the coding density as $d=\frac{k}{g}$. We call
+% this notation $k-sparse$ where $k$ is the average number of packets combined to
+% produce a coded packet.
 

### 2016-06-01 testbed.tex

@@
 
-This section will be used to present our Raspberry Pi testbed, but also how
-it is set up and configured.
+This section will be used to present a Raspberry Pi testbed and the steps to
+install and configure the individual devices.
 
-The testbed is depicted in \ref{fig:testbed_setup}. It consists of twenty
+The testbed is depicted in figure~\ref{fig:testbed_setup}. It consists of twenty
 Raspberry Pi 1 model B rev 2 (Rasp\_01 to Rasp\_20) and 
 ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).
-The Raspberry Pis are each equipped with an ethernet interface (eth0) that are
-assigned the \ac{IP} addresses listed in the figure.
+
+The goal is to configure all the devices identically with the same software
+and configurations. There are however a few differences between them that we
+need to take into account. E.g. hostname and network addresses.
+
+The testbed will be used by students that might need to change how the
+devices are work either temporary or permanently. We will illustrate how this
+can be accomplished using an overlaying filesystem.
+
+Finally, it should be possible to store data that are generated from
+simulations on the memory cards that are in the individual Raspberry Pi.
+%We using a overlaying filesystem that 
+%We will illustrate
+%how that can be done. In the case of temporary changes, it is important that
+%all changes can be easily reverted. We put a \ac{RAM} filesystem on top of
+%the the root filesystem to .
+%the configure the
+%devices to behave according to their test specifications. We
+%will also present how that might be done.
+
+%their linkings. That could be to change network config
+
+%The goal is to configure all the devices to be as identical as possible. This
+%means that it is desired to have the same software on every device, but
+
+The Raspberry Pis are all equipped with an ethernet interface (eth0) and
+connected by wire to the university's \ac{LAN}. The university network
+administration was provided
+the \ac{MAC} addresses of the ethernet interfaces to automatically assign
+the devices the desired \ac{IP} addresses as shown in the figure. In a personal
+\ac{LAN}, another option could be to manually provide the devices with static
+\ac{IP}s.
+%that are
+%assigned the \ac{IP} addresses in the figure and connected wired to the
+%university's \ac{LAN}.
 
@@
 
+We use standard usb power adapters to power the Raspberry Pis.
+
 \subsubsection{Installing Raspbian}
+
+To get started, we first need to install an \ac{OS} on the
+Raspberry Pis. We have decided to create a common image of Raspbian Linux
+for all devices. After the image has been configured it can be written to
+a memory card and used in any of the Raspberry Pis. This means that each
+device needs a memory card, but it does not matter which card is put into
+which device.
+
+It can then be written to a memory card and used in one device
+after it has been completely configured
+
+that
+can be written to a memory card and
+
+We have decided to go with Raspbian linux~\cite{raspbian} and
+to install it on memory cards.
+
+%There exists a number of ways to setup a testbed in a centralized manner.
+%E.g. using e.g. \ac{NFS}.
+
+There exists a number of ways to setup a testbed
+
+with multiple devices. We
+have decided on a very simple approach of simply instal
 

### 2016-06-01 schemes.tex
Minor changes in SRLNC theory

@@
 coding coefficients to zero when generating a coded packet with the purpose
-of reducing the overall processing in both encoding and decoding. In what
-follows, we describe the coding scheme with a basic method to produce sparse
-coded packets and later we indicate a second one, giving reference to their
+of reducing the overall processing. Decoding is the same as in \ac{RLNC}, but
+given that the coding matrices are now sparse, we will have less operations
+performed in the decoding process. Recoding, although theoreticaly possible,
+is omitted in practical systems since it is too complex to keep packets sparse
+after recoding [\textbf{reference}]. In what follows, we
+describe the coding scheme with a basic method to produce sparse coded
+packets and later we indicate a second one, giving reference to their
 implementation performance.

### 2016-06-01 raspi_journal.tex
Added lstlisting style

--- 2016-05-31 raspi_journal.tex
@@
 \usepackage{fixme}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{listings}             % Include the listings-package
+\usepackage{placeins}
 
@@
 \begin{document}
+\definecolor{mygreen}{rgb}{0,0.6,0}
+\definecolor{mygray}{rgb}{0.5,0.5,0.5}
+\definecolor{mymauve}{rgb}{0.58,0,0.82}
+\lstset{ %
+  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
+  basicstyle=\footnotesize\ttfamily,
+  breaklines=true,        % the size of the fonts that are used for the code
+  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
+  breaklines=true,                 % sets automatic line breaking
+  captionpos=b,                    % sets the caption-position to bottom
+  commentstyle=\color{mygreen},    % comment style
+  deletekeywords={...},            % if you want to delete keywords from the given language
+  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
+  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
+  frame=single,	                   % adds a frame around the code
+  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
+  keywordstyle=\color{blue},       % keyword style
+  language=Bash,                 % the language of the code
+  otherkeywords={*,...},           % if you want to add more keywords to the set
+  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
+  numbersep=5pt,                   % how far the line-numbers are from the code
+  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
+  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
+  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
+  showstringspaces=false,          % underline spaces within strings only
+  showtabs=false,                  % show tabs within strings adding particular underscores
+  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
+  stringstyle=\color{mymauve},     % string literal style
+  tabsize=2,	                   % sets default tabsize to 2 spaces
+  title=\lstname,                  % show the filename of files included with \lstinputlisting; also try caption instead of title
+  xleftmargin=5mm,
+  xrightmargin=5mm,
+  columns=flexible
+}
 
@@
 \acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
-Curie project (317126) from the European Comission FP7 framework,
-the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
-, the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
-by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d),
-and by the German Research Foundation (DFG) within the Collaborative Research Center SFB 912 – HAEC.}
+Curie project (317126) from the European Comission FP7 framework, the Green
+Mobile Cloud project (Grant No. DFF - 0602 - 01372B) , the TuneSCode project
+(Grant No. DFF - 1335 - 00125) both granted by the Danish Council for
+Independent Research (Det Frie Forskningsr\r{a}d), and by the German Research
+Foundation (DFG) within the Collaborative Research Center SFB 912 – HAEC.}
 

### 2016-06-01 testbed.tex
Added lstlisting style

@@
 To get started, we first need to install an \ac{OS} on the
-Raspberry Pis. We have decided to create a common image of Raspbian Linux
-for all devices. After the image has been configured it can be written to
-a memory card and used in any of the Raspberry Pis. This means that each
-device needs a memory card, but it does not matter which card is put into
-which device.
+Raspberry Pis. We will use Raspbian linux~\cite{raspbian}
 
-It can then be written to a memory card and used in one device
-after it has been completely configured
+We will use a desktop that has linux installed to download,
+configure, and write the image to the memory cards.
+%We have decided to use a linux desktop machine to create a
+%common image of Raspbian Linux that can be used in any of the Raspberry Pis.
 
-that
-can be written to a memory card and
+%for all devices. After the image has been configured it can be written to
+%a memory card and used in any of the Raspberry Pis. This means that each
+%device needs a memory card, but it does not matter which card is put into
+%which device.
 
@@
 -
+
+\begin{lstlisting}[frame=single]  % Start your code-block
+IMAGE="raspbian_lite-2016-05-31/2016-05-27-raspbian-jessie-lite"
+WORKDIR="${HOME}/Raspbian"
+cd ${WORKDIR}
+wget http://downloads.raspberrypi.org/raspbian_lite/images/${IMAGE}.zip
+unzip ${IMAGE}
+\end{lstlisting}
+\FloatBarrier
 

### 2016-06-01 raspi_journal.tex
changed lstlisting style

--- 2016-05-31 raspi_journal.tex
@@
 \begin{document}
+\definecolor{mygreen}{rgb}{0,0.6,0}
+\definecolor{mygray}{rgb}{0.5,0.5,0.5}
+\definecolor{mymauve}{rgb}{0.58,0,0.82}
+\lstset{ %
+  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
+  basicstyle=\footnotesize\ttfamily,
+  breaklines=true,        % the size of the fonts that are used for the code
+  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
+  breaklines=true,                 % sets automatic line breaking
+  captionpos=b,                    % sets the caption-position to bottom
+  commentstyle=\color{mygreen},    % comment style
+  deletekeywords={...},            % if you want to delete keywords from the given language
+  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
+  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
+  frame=single,	                   % adds a frame around the code
+  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
+  %keywordstyle=\color{blue},       % keyword style
+  language=Bash,                 % the language of the code
+  otherkeywords={*,...},           % if you want to add more keywords to the set
+  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
+  numbersep=5pt,                   % how far the line-numbers are from the code
+  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
+  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
+  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
+  showstringspaces=false,          % underline spaces within strings only
+  showtabs=false,                  % show tabs within strings adding particular underscores
+  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
+  %stringstyle=\color{mymauve},     % string literal style
+  tabsize=2,	                   % sets default tabsize to 2 spaces
+  title=\lstname,                  % show the filename of files included with \lstinputlisting; also try caption instead of title
+  xleftmargin=5mm,
+  xrightmargin=5mm,
+  columns=flexible
+}
 

### 2016-06-01 raspi_journal.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
-Curie project (317126) from the European Comission FP7 framework, the Green
-Mobile Cloud project (Grant No. DFF - 0602 - 01372B) , the TuneSCode project
-(Grant No. DFF - 1335 - 00125) both granted by the Danish Council for
-Independent Research (Det Frie Forskningsr\r{a}d), and by the German Research
-Foundation (DFG) within the Collaborative Research Center SFB 912 – HAEC.}
+\acknowledgments{This research has been partially financed by the
+Marie Curie Initial Training Network (ITN) CROSSFIRE project
+(Grant No. EU - FP7 - CROSSFIRE - 317126) from the European Comission FP7
+framework, the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B),
+the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted by the
+Danish Council for Independent Research (Det Frie Forskningsr\r{a}d), and
+by the German Research Foundation (DFG) within the Collaborative Research
+Center SFB 912 – HAEC.}
 

### 2016-06-01 schemes.tex
Changes in TSNC

@@
 
-\ac{TSNC} can be considered an extension to \ac{SRLNC}. The overall idea is
+\ac{TSNC} can be considered an extension to \ac{SRLNC}. The key idea is
 not only for the encoder to generate sparse coded packets, but also to
-choose the sparsity of packets wiser. That is, as the decoder accomulates more
-coded packets it becomes more and more likely that the next received
-coded packet will be \ac{l.d.}.
+modify the code density of the packets progressively as required. As a
+decoder accomulates more coded packets, the probability that the next
+received coded packet will be \ac{l.d.} increases.
 
-The idea of \ac{TSNC} is therefore to gradually increase the coding density
-as the decoderes \ac{DOF} increases. This enables TSNC to save a lot of
+Therefore, in \ac{TSNC}, a simple procedure for controlling this probability
+is to gradually increase the coding density as the \ac{DOF} increases. This enables TSNC to save a lot of
 complexity particulary in the beginning of transmissions, but also to

### 2016-06-01 raspi_journal.tex
TSNC editing and removing unnecesary sections
Wrote on testbed

@@
   basicstyle=\footnotesize\ttfamily,
-  breaklines=true,        % the size of the fonts that are used for the code
   breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
@@
   captionpos=b,                    % sets the caption-position to bottom
-  commentstyle=\color{mygreen},    % comment style
+  %commentstyle=\color{mygreen},    % comment style
   deletekeywords={...},            % if you want to delete keywords from the given language
@@
   %keywordstyle=\color{blue},       % keyword style
-  language=Bash,                 % the language of the code
+  %language=Bash,                 % the language of the code
   otherkeywords={*,...},           % if you want to add more keywords to the set

### 2016-06-01 testbed.tex
Wrote on testbed

@@
 
-\begin{lstlisting}[frame=single]  % Start your code-block
-IMAGE="raspbian_lite-2016-05-31/2016-05-27-raspbian-jessie-lite"
-WORKDIR="${HOME}/Raspbian"
-cd ${WORKDIR}
-wget http://downloads.raspberrypi.org/raspbian_lite/images/${IMAGE}.zip
-unzip ${IMAGE}
+Open a terminal, and then...
+
+hashmark (#) means to perform operation as root, dollar (\$) means to perform operation as user
+
+%\begin{lstlisting}[caption=Define variable]  % Start your code-block
+\begin{lstlisting}[]  % Start your code-block
+
+$ export IMAGE="2016-05-27-raspbian-jessie-lite"
+$ export WORKDIR="${HOME}/Raspbian"
+\end{lstlisting}
+\FloatBarrier
+
+%\begin{lstlisting}[caption=Download and unpack image]  % Start your code-block
+\begin{lstlisting}[]  % Start your code-block
+
+$ mkdir -p ${WORKDIR}
+$ cd ${WORKDIR}
+$ wget http://downloads.raspberrypi.org/raspbian_lite/images/raspbian_lite-2016-05-31/${IMAGE}.zip
+$ unzip ${IMAGE}.zip
+\end{lstlisting}
+\FloatBarrier
+
+%\begin{lstlisting}[caption="Check out the image"]  % Start your code-block
+\begin{lstlisting}[]  % Start your code-block
+
+$ fdisk -lu ${IMAGE}.img
+Disk 2016-05-27-raspbian-jessie-lite.img: 1.3 GiB, 1387266048 bytes, 2709504 sectors
+Units: sectors of 1 * 512 = 512 bytes
+Sector size (logical/physical): 512 bytes / 512 bytes
+I/O size (minimum/optimal): 512 bytes / 512 bytes
+Disklabel type: dos
+Disk identifier: 0x6fcf21f3
+
+Device                               Boot  Start     End Sectors  Size Id Type
+2016-05-27-raspbian-jessie-lite.img1        8192  137215  129024   63M  c W95 FAT32 (LBA)
+2016-05-27-raspbian-jessie-lite.img2      137216 2709503 2572288  1.2G 83 Linux
+\end{lstlisting}
+\FloatBarrier
+
+We see that the boot and root partitions starts at sector 8192 and 137216 respectivly.
+We also notice that each sector is 512 bytes.
+
+Mount root partition:
+%\begin{lstlisting}[caption="Mount the root partition"]  % Start your code-block
+\begin{lstlisting}[]  % Start your code-block
+
+$ export ROOTDIR="${WORKDIR}/root"
+$ mkdir -p ${ROOTDIR}
+# mount -o loop,offset=$((137216*512)) ${IMAGE}.img ${ROOTDIR}
+\end{lstlisting}
+\FloatBarrier
+
+Mount boot partition:
+%\begin{lstlisting}[caption="Mount boot partition"]  % Start your code-block
+\begin{lstlisting}[]  % Start your code-block
+
+# mount -o loop,offset=$((8192*512)) ${IMAGE}.img ${ROOTDIR}/boot
 \end{lstlisting}

### 2016-06-01 schemes.tex

@@
 Therefore, in \ac{TSNC}, a simple procedure for controlling this probability
-is to gradually increase the coding density as the \ac{DOF} increases. This enables TSNC to save a lot of
-complexity particulary in the beginning of transmissions, but also to
-tailor the coding delay. I.e. approximate the number of coded packets a
+is to gradually increase the coding density as the \ac{dof}\footnote{We refer
+as degrees of freedom to the dimension of the linear span from the coded
+packets that a decoder has at a given point} increases, e.g. as the
+cardinality of the set of \ac{l.i.} coded packets increases. This enables
+\ac{TSNC} to significantly reduce the complexity particulary in the
+beginning of the transmission process and also to control the decoding
+delay. For \ac{TNSC}, we define the number of coded packets a
 decoder needs to receive to decode a generation of $g$ packets. We call
@@
 
-Provided a desired budget, $B \geq g$, and the decoders \ac{DOF} it can be
+Provided a desired budget, $B \geq g$, and the decoders \ac{dof} it can be
 estimated how sparse the coded packets should be to finish a transmission in
@@
 density. We use feedback to provide the encoder a better estimate of the
-decoders \ac{DOF} at pre-defined points. Namely, when the decoder obtains the
-following \ac{DOF}'s:
+decoders \ac{dof} at pre-defined points. Namely, when the decoder obtains the
+following \ac{dof}'s:
 
@@
 Before the coding density can be estimated it is essential that the encoder
-has a good estimate of the decoders \ac{DOF}, but also the remainder of the
+has a good estimate of the decoders \ac{dof}, but also the remainder of the
 total budget. The feedback scheme \ref{eq:feedback_dofs} roughly splits the
-remaining \ac{DOF} in halves. This is also the case for the budget that is
+remaining \ac{dof} in halves. This is also the case for the budget that is
 split equally among the two new regions. The very last region will be assigned

### 2016-06-01 schemes.tex
Some edits

@@
 cardinality of the set of \ac{l.i.} coded packets increases. This enables
-\ac{TSNC} to significantly reduce the complexity particulary in the
+\ac{TSNC} to significantly reduce the complexity, particularly in the
 beginning of the transmission process and also to control the decoding
-delay. For \ac{TNSC}, we define the number of coded packets a
-decoder needs to receive to decode a generation of $g$ packets. We call
-this number the budget, $B$.
+delay. For \ac{TSNC}, we define the budget, $B \geq g$, to be a target
+number of coded packets a transmitter wants to send to a receiver
+for decoding a generation of $g$ packets.
 
-Provided a desired budget, $B \geq g$, and the decoders \ac{dof} it can be
-estimated how sparse the coded packets should be to finish a transmission in
+Provided a desired budget $B$ and the \ac{dof}s of the
+decoder, an encoder can estimate the required coding density to not exceed
+the required y the budget. ow sparse the coded packets should be to finish a transmission in
 time.

### 2016-06-01 testbed.tex
fixed warning

@@
 
-hashmark (#) means to perform operation as root, dollar (\$) means to perform operation as user
+hashmark (\#) means to perform operation as root, dollar (\$) means to perform operation as user
 
@@
 Mount root partition:
-%\begin{lstlisting}[caption="Mount the root partition"]  % Start your code-block
+%Mount the root partition
 \begin{lstlisting}[]  % Start your code-block
@@
 Mount boot partition:
-%\begin{lstlisting}[caption="Mount boot partition"]  % Start your code-block
+%Mount boot partition
 \begin{lstlisting}[]  % Start your code-block
@@
 
-We have installed the official Raspbian linux \ac{OS} on all the devices.
+We can now change all the files in the disk image.
+
+\subsection{Configuring OS files and scripts}
+
+% Set hostname
+\begin{lstlisting}[]  % Start your code-block
+
+# echo "MrAwesome script" >> ${ROOTDIR}/etc/init.d/hostname.sh
+\end{lstlisting}
+\FloatBarrier
 
 \subsection{Installation and Updating}
+
+% CHROOT to OS image
+\begin{lstlisting}[]  % Start your code-block
+
+# mount ...
+# chroot ${ROOTDIR}
+\end{lstlisting}
+\FloatBarrier
+
 \subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}

### 2016-06-02 schemes.tex
Theory done for now

@@
 better processing speeds, particularly relevant for the Raspberry Pi.
+Finally, we include a review of the
 
@@
     \begin{cases}
-        0 & \text{for } v_{ij} = 0 \\
-        1 & \text{for } v_{ij} \neq 0
+        0 &,\ v_{ij} = 0 \\
+        1 &,\ v_{ij} \neq 0
     \end{cases}
@@
     \begin{cases}
-        {(0,0.5]} & \text{for } q = 2 \\
-        {(0,1]} & \text{for } q > 2
+        {(0,0.5]} & ,\ q = 2 \\
+        {(0,1]}   & ,\ q > 2
     \end{cases}
@@
 
-Provided a desired budget $B$ and the \ac{dof}s of the
-decoder, an encoder can estimate the required coding density to not exceed
-the required y the budget. ow sparse the coded packets should be to finish a transmission in
-time.
+Provided a desired budget $B$ and the \ac{dof} of the decoder, an encoder
+can estimate the required coding density for the packets to not exceed the
+budget. In our implementation, we use feedback packets to provide the
+encoder an estimate of the decoder \ac{dof} at pre-defined points of the
+transmission process. The points in the process occur when a decoder
+obtains a given amount of \ac{dof}. In our implementation, we define $r(k),\
+k \in [1, \ldots)$ as the rank $r$ of the decoder\footnote{The rank of
+a decoder is the rank of its coding matrix at a given point in the
+transmissions process.} where a decoder has to send the $k$-th feedback in
+\eqref{eq:feedback_dofs}.
+%
+\begin{equation}\label{eq:feedback_dofs}
+    r(k) = \floor{g\cdot \left[\frac{2^k -1}{2^k}\right]},\ k \in [1,\ldots)
+\end{equation}
+%
+At the beginning of the transmission process, we assume that the encoder
+starts with an initial coding density that has been calculated depending to
+the budget. According to \eqref{eq:feedback_dofs}, a decoder sends feedback
+once it has obtained (rounded down) $g/2,\ 3g/4,\ 7g/8,\ \ldots$  degrees of
+freedom. The total amount of feedback for this scheme will depend on the
+generation size. Still, we have an implementation that limits the amount of
+feedback to be sent from the decoder in [\textbf{reference}].
 
-In our implementation, it is the encoders responsibility to estimate the coding
-density. We use feedback to provide the encoder a better estimate of the
-decoders \ac{dof} at pre-defined points. Namely, when the decoder obtains the
-following \ac{dof}'s:
+The transmissions made between feedback packets are called the density
+regions since the same estimated density is used for encoding sparse
+packets. Once new feedback is received, an encoder recalculates the coding
+density for the new region until the next feedback packet is received.
+Before the coding density can be estimated, it is essential that the
+encoder has a good estimate of the decoder \ac{dof}, but also the remainder
+of the total budget. The feedback scheme based on the rank reports of
+\eqref{eq:feedback_dofs} roughly splits the remaining coding regions in
+two halves in every. In other words, the first half is the region where
+the encoder currently operates. Once an encoder finishes with this region,
+it proceeds with second half where again it splits this into to two region
+and so on until it finishes on transmitting the whole generation. This is
+also the case for the budget that is split equally among the two new
+regions. The very last region will be assigned the full remainder of
+the total budget and the coding density will not vary.
 
-\begin{equation}\label{eq:feedback_dofs}
-    s(k) = g\cdot \frac{2^k -1}{2^k},  \; \text{for } k=0,1,2,\dots
-\end{equation}
-where $k$ is the $k$-th feedback packet that is transmitted during a generation.
-
-The encoder considers the time between feedback packets as regions. It then
-estimates a fixed coding density for each region when a feedback packet is
-received.
-
-Before the coding density can be estimated it is essential that the encoder
-has a good estimate of the decoders \ac{dof}, but also the remainder of the
-total budget. The feedback scheme \ref{eq:feedback_dofs} roughly splits the
-remaining \ac{dof} in halves. This is also the case for the budget that is
-split equally among the two new regions. The very last region will be assigned
-the full remainder of the total budget.
-
-\subsection{Network Coding Implementation for Multicore Architectures}
+\subsection{Network Coding Implementation for Multicore Architectures with
+the Raspberry Pi}
 \label{sub:implementation-multicore}
 
-The operations needed to encode and decode data are, in general, similar. To
-encode packets, the encoder needs to perform the matrix multiplication
-$\textbf{C} = \textbf{V} \cdot \textbf{P}$. On the other hand, decoding the
-information requires the decoder to find $\textbf{V}^{-1}$ and to perform the
-matrix multiplication $\textbf{P} = \textbf{V}^{-1} \cdot \textbf{C}$. In both
-cases, a matrix multiplication is needed. Therefore, to make a practical
-implementation of network coding, it is valuable to find a way to optimize the
-matrix multiplications operations for multicore architectures.
+The arithmetic operations needed to encode and decode data are,
+in general, similar. To encode packets, the encoder needs to perform the
+matrix multiplication $\textbf{C} = \textbf{V} \textbf{P}$. On the other
+hand, decoding the information requires the decoder to find
+$\textbf{V}^{-1}$ and to perform the matrix multiplication
+$\textbf{P} = \textbf{V}^{-1} \textbf{C}$. In both cases, a matrix
+multiplication is needed. Therefore, to make a practical implementation of
+network coding, it is valuable to find a way to optimize the matrix
+multiplications operations for multicore architectures.
 
-When designing multithreaded algorithms for network coding operations, it is
+When designing multi-threaded algorithms for network coding operations, it is
 possible to implement the decoding by combining the matrix inversion and the
-matrix multiplication, e.g., performing the Gauss-Jordan algorithm over the
+matrix multiplication, e.g. performing the Gauss-Jordan algorithm over the
 coding matrix $\textbf{V}$ while performing, in parallel, row operations on the
@@
 
-Therefore, to overcome the constraints of a tight synchronization, it is
-preferable to explicitly invert the matrix $\textbf{V}$, and then take advantage
-of optimizations for matrix multiplications, both at encoding and decoding time.
-With that purpose, the authors implemented in~\cite{wunderlich2015network} an
-algorithm that adopts the ideas of efficient \ac{BLAS}
-operations~\cite{lawson1979basic} reimplementing them for finite fields
-operations. Although there are already certain libraries available such as
-~\cite{dumas2008dense} and \cite{dumas2002linbox} that allows the usage of the
-highly optimize \ac{BLAS} implementations for some finite fields, they work
-converting the GF elements into floating point numbers and back. Even though
-that approach is efficient for large matrix sizes, the overhead imposed by the
-conversions is not suitable for the the matrix sizes of typical network coding
-implementations. The implemented algorithm aims to be cache efficient by
-maximizing the number of operations performed over a block of fetched data. This
-is done by dividing the matrices in square sub-blocks and operating with them.
-As a consequence, this technique exploits the spatial locality of the data, at
-least for $\mathcal{O}(n^3)$ algorithms~\cite{golub2012matrix}. The optimal size
-of the block is architecture-dependent. The ideal block has a number of operands
-that fit into L1 cache, and it is a multiple of the \ac{SIMD} operations size.
+Therefore, to overcome the constraints of tight synchronization, a
+preferable option is to explicitly invert the matrix $\textbf{V}$, and then
+take advantage of optimizations for matrix multiplications, both at
+encoding and decoding time. With that purpose, authors
+in~\cite{wunderlich2015network} implemented an algorithm that adopts
+the ideas of efficient \ac{BLAS}~\cite{lawson1979basic} operations
+reimplementing them for finite fields operations. Although there are
+libraries such as \cite{dumas2008dense} and \cite{dumas2002linbox} that allow
+highly optimized finite field \ac{BLAS} implementations, they work on
+converting the \ac{GF} elements into floating point numbers and back.
+Even though the approach is efficient for large matrix sizes, the
+numerical type conversion overhead is not suitable for matrix sizes of
+network coding implementations.
 
-The main idea of the implemented algorithm is to represent each one of the sub-
-block matrix operations (matrix-matrix multiplication, matrix-triangle matrix
-multiplication, triangle-matrix system solving, etc) as a base, \textit{kernel},
-operation that can be optimized individually, e.g., using \ac{SIMD} operations.
-Each of these kernel operations, at the same time, can be represented as a task
-with inputs and outputs in memory. If any algorithm is formulated
-conventionally, and the data operations on the sub-blocks are reordered, then it
-is possible to resolve data dependencies with a \ac{DAG}. For the algorithm, a
-dependency means, for example, that a sub-block of the matrix in memory cannot
-be read unless a previous writing operation was performed there. When the
-\ac{DAG} is determined, then, a scheduler assigns to the available cores the
-execution of the individual kernel operations that have their dependencies
-satisfied. The benefit of this method is that the synchronization relies only on
-data dependencies, and it does not requires the insertion of artificial
-synchronization points. Using this technique, the matrix inversion is performed
-using an algorithm based on LU
-factorization~\cite{Dongarra:2011:HPM:2132876.2132885}, and the matrix
-multiplication is performed by making the various matrix-matrix multiplications
-on the sub-blocks.
+The implemented algorithm in~\cite{wunderlich2015network} aims to be
+cache-efficient by maximizing the number of operations performed over a
+fetched data block. Here, the matrices are divided in square sub-blocks
+where we can operate each of them. As a consequence, this technique
+exploits the spatial locality of the data, at least for
+$\mathcal{O}(n^3)$ algorithms~\cite{golub2012matrix}. The optimal block
+size is architecture-dependent. The ideal block has a number of operands
+that fit into the system L1 cache, and it is a multiple of the \ac{SIMD}
+operations size.
+
+The idea of the implemented algorithm is to represent each one of the
+sub-block matrix operations: matrix-matrix multiplication,
+matrix-triangle matrix multiplication, triangle-matrix system solving,
+etc; as a base or \textit{kernel} operation that can be optimized
+individually using \ac{SIMD} operations. Each kernel operation, at the
+same time, can be represented as a task with inputs and outputs in memory.
+If an algorithm is formulated conventionally and the data operations on the
+sub-blocks are reordered, then it is possible to resolve data
+dependencies with a \ac{DAG}. For the algorithm, as an example, a dependency
+could be that a sub-block of the matrix in memory cannot be read unless
+a previous writing operation was performed there. When the
+\ac{DAG} is determined, then a scheduler assigns to the available cores the
+execution of the kernel operations that have their dependencies satisfied.
+The benefit of this method is that the synchronization relies only on
+data dependencies and it does not require the insertion of artificial
+synchronization points. Using this technique, the matrix inversion is
+performed using an algorithm based on LU factorization
+\cite{Dongarra:2011:HPM:2132876.2132885}, and the matrix multiplication is
+performed by making the various matrix-matrix multiplications on the
+sub-blocks.

### 2016-06-02 measurements.tex
Starting with the results

@@
 
-\subsubsection{Multicore Network Coding}
+\subsection{Multicore Network Coding}
 \label{subs:multicore-network-coding}
@@
 The authors implemented the algorithm described in
-Section~\ref{sub:implementation-multicore} on the Raspberry Pi 2 Model B, which
-features four ARM Cortex-A7 cores in a Broadcom BCM2836 \ac{SOC} with a 900 MHz
-clock. Each core has a 32 KiB L1 data cache and 32 KiB L1 instruction cache. The
-cores share a 512 KiB L2 cache. All the measured results, including the baseline
-results, were obtained with NEON-enabled code adopted from the FIFI/KODO library
-\cite{kodo2011pedersen}. The NEON extension provides an 128-bit \ac{SIMD}
-instruction set to the Raspberry Pi 2. Figures~\ref{enc_dec1024},
-\ref{enc_dec128} and \ref{enc_dec16} show the encoding and decoding throughput
-in MiB per second for different generation sizes ($g$ = 1024, 128, and 16
+Section~\ref{sub:implementation-multicore} on the Raspberry Pi 2 Model B,
+which features four ARM Cortex-A7 cores in a Broadcom BCM2836 \ac{SOC}
+with a 900 MHz clock. Each core has a 32 KiB L1 data cache and 32 KiB
+L1 instruction cache. The cores share a 512 KiB L2 cache. All the
+measured results, including the baseline results, were obtained with
+NEON-enabled code adopted from the Fifi library [\textbf{Fifi reference}].
+The NEON extension provides an 128-bit \ac{SIMD} instruction set to the
+Raspberry Pi 2. Figures~\ref{enc_dec1024}, \ref{enc_dec128} and
+\ref{enc_dec16} show the encoding and decoding throughput in MiB per
+second for different generation sizes ($g$ = 1024, 128, and 16
 respectively). The throughput is the rate of generating $g$ coded packets,
-divided by the time the encoder took to perform the task. The size of each coded
-packet was fixed to $1536$~bytes since that is the typical size of an Ethernet
-frame. The blocked operations were performed dividing the matrices in squared
-sub-blocks of 16,32,64,...,1024 operands (words in the finite field) in height
-and width, and the figures only show the best results (usually block sizes of
-16x16 or 32x32 operands since with bigger block sizes, the operands do not fit
-in L1 cache).
+divided by the time the encoder took to perform the task. The size of
+each coded packet was fixed to $1536$~bytes since that is the typical
+size of an Ethernet frame. The blocked operations were performed dividing
+the matrices in squared sub-blocks of $16,\ 32\ ,\ 64,\ldots,\ 1024$ operands
+(words in the finite field) in height and width. The figures show only
+block sizes of $16 \times 16$ or $32 \times 32$ operands since with bigger
+block sizes, the operands do not fit in L1 cache.
 
@@
 
-\paragraph{Baseline encoding} The baseline results involve no recording of the
+\subsubsection{Baseline encoding}
+The baseline results involve no recording of the
 \ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder uses
-only one thread. And the difference between the non-blocked and blocked encoding
-schemes is that in the blocked scheme, the matrix multiplications are performed
-dividing the matrices in sub-blocks in order to make the algorithm cache
-efficient as described in Section~\ref{sub:implementation-multicore}.
+only one thread. And the difference between the non-blocked and blocked
+encoding schemes is that in the blocked scheme, the matrix multiplications are
+performed dividing the matrices in sub-blocks in order to make the algorithm
+cache efficient as described in Section~\ref{sub:implementation-multicore}.
 
-\paragraph{Encoding blocked} The encoding results were performed using the
+\subsubsection{Encoding blocked}
+The encoding results were performed using the
 method described in Section~\ref{sub:implementation-multicore}. The time
-recorded includes the dependencies resolving, creation of the \ac{DAG}, and the
-task scheduling. In practice, it would suffice to calculate and store this
+recorded includes the dependencies resolving, creation of the \ac{DAG}, and
+the task scheduling. In practice, it would suffice to calculate and store this
 information only once per generation size.
 
-\paragraph{Decoding blocked} The differences between encoding and decoding, is
-that the decoding task also involves the matrix inversion. Similarly as with the
-encoding results, the time recorded includes the dependencies resolving, the
-creation of the \ac{DAG} and the task scheduling. However, to decode, these
-calculations are also made for inverting the matrix of coding coefficients.
+\subsubsection{Decoding blocked}
+The differences between encoding and decoding, is that the decoding task also
+involves the matrix inversion. Similarly as with the encoding results, the
+time recorded includes the dependencies resolving, the creation of the
+\ac{DAG} and the task scheduling. However, to decode, these calculations are also made for inverting the matrix of coding coefficients.
 
-\begin{figure}[h!]
+\begin{figure}[ht!]
 \centering
@@
 
-\begin{figure}[h!]
+\begin{figure}[ht!]
 \centering
@@
 
-\paragraph{Comparison of the load of matrix multiplications and inversions}
+\subsubsection{Comparison of the load of matrix multiplications and inversions}
 

### 2016-06-02 raspi_journal.tex
Theory done for now
suppress/reactivate linenumbers in lstlistings

@@
 \usepackage{placeins}
+\usepackage{xcolor}
+\usepackage{caption}
 
-\newcommand\floor[1]{\lfloor#1\rfloor}
+\newcommand\floor[1]{\left\lfloor#1\right\rfloor}
 
@@
   deletekeywords={...},            % if you want to delete keywords from the given language
-  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
+  %escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
+  escapeinside={<@}{@>}
   extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
@@
   columns=flexible
+}
+
+% Used to suppress line numbers in lstlistings
+\let\origthelstnumber\thelstnumber
+\makeatletter
+\newcommand*\Suppressnumber{%
+  \lst@AddToHook{OnNewLine}{%
+    \let\thelstnumber\relax%
+     \advance\c@lstnumber-\@ne\relax%
+    }%
+}
+
+% Used to reactivate line numbers in lstlistrings
+\newcommand*\Reactivatenumber{%
+  \lst@AddToHook{OnNewLine}{%
+   \let\thelstnumber\origthelstnumber%
+   \advance\c@lstnumber\@ne\relax}%
 }
@@
 
-\section{Topologies}
-\input{topologies}
+% \section{Topologies}
+% \input{topologies}
 

### 2016-06-03 rasp_config/set_hostname.sh
worked more on testbed

@@ -1,0 +1,11 @@
+#!/bin/bash
+
+mac=$(cat /sys/class/net/eth0/address)
+hostname=$(grep $mac nodes.csv | cut -f2 -d' ')
+
+# Assign hostname found in nodes.csv
+if [ ! -z $hostname ]; then
+    echo $hostname > /etc/hostname
+    hostname $hostname
+fi
+

### 2016-06-03 upload_rasp_config.sh

@@ -1,0 +1,5 @@
+#!/usr/bin/env bash
+
+zip -r rasp_config rasp_config
+scp rasp_config.zip js3:/afs/ies.auc.dk/project/TuneSCode/public_html/
+rm rasp_config.zip

### 2016-06-03 metrics.tex
Started writing on multicore results
TSNC editing and removing unnecesary sections
More on the measurements

@@
 \label{sec:metrics}
-\subsection{Encoding and Decoding Speeds}
 
-\subsubsection{Multicore Network Coding}
-\label{subs:multicore-network-coding}
+Once we have defined the coding schemes behavior in terms of encoding
+and decoding, we proceed to describe the metrics considered in our study.
+We review the energy consumption of the Raspberry Pi since this platform
+is deployed at a large scale in scenarios where (i) energy is
+constrained to the lifetime of the device battery and (ii) the devices
+could be established in locations that are unavailable for regular
+maintenance. Typical use cases of this type of scenarios are sensor
+applications where devices are positioned for measurement retrieval
+without any supervision for large periods fo time. In this type of
+settings, both overall and per-bit energy consumption of the devices
+during the encoding and decoding process are relevant parameters that
+impact in the network performance for a given coding scheme. Also,
+Raspberry Pi processors are based in the \ac{ARM} architecture which
+is the same as in mobile devices like smartphones or tables.
+Therefore, the Raspberry Pi could be used to get an estimate of
+computing capabilities of a mobile device that is much more easy-deployable
+and at a lower overall cost.
 
-\subsection{Latency}
-\subsection{Energy}
+To complement our study, we consider the goodput defined as the ratio
+of the useful delivered information at the application layer and the total
+delivery time. We focus on the goodput considering only the coding process,
+i.e. we assume that the application data has been properly
+generated before encoding and also correctly post-processed after decoding.
+The goodput is a measure for the effective processing speed since it
+excludes protocol overhead but considers process
+
+\subsection{Energy Costs}
+\subsubsection{Average Consumption}
+\subsubsection{Per-Bit Consumption}
+
+\subsection{Goodput}
+\subsubsection{Encoding}
+\subsubsection{Decoding}

### 2016-06-03 raspi_journal.tex

@@
 \usepackage{caption}
+\usepackage{textcomp}  % To get the correct quotes in lstlistings (')
 
@@
   xrightmargin=5mm,
-  columns=flexible
+  columns=flexible,
+  upquote=true
 }

### 2016-06-03 testbed.tex
more testbed

--- 2016-06-01 testbed.tex
@@
 
-\begin{lstlisting}[frame=single]  % Start your code-block
-IMAGE="raspbian_lite-2016-05-31/2016-05-27-raspbian-jessie-lite"
-WORKDIR="${HOME}/Raspbian"
-cd ${WORKDIR}
-wget http://downloads.raspberrypi.org/raspbian_lite/images/${IMAGE}.zip
-unzip ${IMAGE}
+Open a terminal, and then...
+
+hashmark (\#) means to perform operation as root, dollar (\$) means to perform operation as user
+
+% Define variable]
+\begin{lstlisting}[] 
+$ export IMAGE="2016-05-27-raspbian-jessie-lite"
+$ export WORKDIR="${HOME}/Raspbian"
 \end{lstlisting}
@@
 
-We have installed the official Raspbian linux \ac{OS} on all the devices.
+% Download and unpack image
+\begin{lstlisting}[] 
+$ mkdir -p ${WORKDIR}
+$ cd ${WORKDIR}
+$ wget http://downloads.raspberrypi.org/raspbian_lite/images/raspbian_lite-2016-05-31/${IMAGE}.zip
+$ unzip ${IMAGE}.zip
+\end{lstlisting}
+\FloatBarrier
+
+% Check out the image   % The dollar hack was to fix vim syntax
+\begin{lstlisting}[literate={DOLLAR}{\$}1]
+DOLLAR fdisk -lu ${IMAGE}.img
+Disk 2016-05-27-raspbian-jessie-lite.img: 1.3 GiB, 1387266048 bytes, 2709504 sectors
+Units: sectors of 1 * 512 = 512 bytes
+Sector size (logical/physical): 512 bytes / 512 bytes
+I/O size (minimum/optimal): 512 bytes / 512 bytes
+Disklabel type: dos
+Disk identifier: 0x6fcf21f3
+
+Device                               Boot  Start     End Sectors  Size Id Type
+2016-05-27-raspbian-jessie-lite.img1        8192  137215  129024   63M  c W95 FAT32 (LBA)
+2016-05-27-raspbian-jessie-lite.img2      137216 2709503 2572288  1.2G 83 Linux
+\end{lstlisting}
+\FloatBarrier
+
+We see that the boot and root partitions starts at sector 8192 and 137216 respectivly.
+We also notice that each sector is 512 bytes.
+
+On newer systems, we can mount the device easier using "losetup --show -f -P IMAGE"
+
+Mount root partition:
+
+\begin{lstlisting}[]
+$ export ROOTDIR="${WORKDIR}/root"
+$ mkdir -p ${ROOTDIR}
+# mount -o loop,offset=$((137216*512)) ${IMAGE}.img ${ROOTDIR}
+\end{lstlisting}
+\FloatBarrier
+
+Mount boot partition:
+\begin{lstlisting}[]
+# mount -o loop,offset=$((8192*512)) ${IMAGE}.img ${ROOTDIR}/boot
+\end{lstlisting}
+\FloatBarrier
+
+We can now change all the files in the disk image.
+
+\subsection{Configuring OS files and scripts}
+
+% MAC and Hostname file
+\Suppressnumber\begin{lstlisting}[]
+<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/.rasp\_config/nodes.csv}@>
+<@\textcolor{gray}{
+---------------------------------------------------------------}
+\Reactivatenumber @>
+# Ethernet MAC    Hostname
+b8:27:eb:5b:da:20 rasp_00
+b8:27:eb:7b:c3:91 rasp_01
+b8:27:eb:54:9c:64 rasp_02
+b8:27:eb:95:bd:11 rasp_03
+\end{lstlisting}
+\FloatBarrier
+
+% Set hostname
+\Suppressnumber\begin{lstlisting}[]
+<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/.rasp\_config/set\_hostname}@>
+<@\textcolor{gray}{
+---------------------------------------------------------------}
+\Reactivatenumber @>
+#!/usr/bin/env bash
+mac=$(cat /sys/class/net/eth0/address)
+hostname=$(grep $mac nodes.csv | cut -f2 -d' ')
+
+# Assign hostname found in nodes.csv
+if [ ! -z $hostname ]; then
+    echo $hostname > /etc/hostname
+    hostname $hostname
+fi
+\end{lstlisting}
+\FloatBarVrier
+
+% Get the files
+\begin{lstlisting}[]
+wget http://kom.aau.dk/project/TuneSCode/rasp_config.zip
+unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
+\end{lstlisting}
+\FloatBarrier
+
+Call set\_hostname script at startup. We insert a line of code to call script in rc.local just after the initial comments (i.e. lines starting with \#).
+\begin{lstlisting}[]
+line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
+sed -i "${line_number}c bash /home/pi/.rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
+\end{lstlisting}
+\FloatBarrier
+%$ line="bash /home/pi/.rasp_config/set_hostname"
+%# awk -v text="$line" '!/^#/ && !p {print text; p=1} 1' ${ROOTDIR}/etc/rc.local > <@ \Suppressnumber @>
+%    ${ROOTDIR}/etc/rc.local <@ \Reactivatenumber @>
+
+All other files could be updated.
 
 \subsection{Installation and Updating}
+
+It may be desired to pre-install some programs in the image before it is
+written to all the memory cards that goes into the Raspberry pis.
+This can be done using QEMU Chroot (change root).
+\url{https://wiki.archlinux.org/index.php/Raspberry_Pi}
+
+\fxnote{Lets use RPi for Raspberry Pis throughout the paper!}
+\fxnote{Which packages is required for this on debian/ubuntu?}
+
+% CHROOT to OS image
+\begin{lstlisting}[]
+# apt-get install binfmt-support qemu qemu-user-static
+# update-binfmts --importdir /var/lib/binfmts/ --import
+# update-binfmts --display qemu-arm
+# update-binfmts --enable qemu-arm
+\end{lstlisting}
+\FloatBarrier
+
+% CHROOT to OS image
+\begin{lstlisting}[]
+# cd $ROOTDIR
+# cp /etc/resolv.conf etc/resolv.conf
+# cp /usr/bin/qemu-arm-static usr/bin
+# mount -t proc proc proc/
+# mount --rbind /sys sys/
+# mount --rbind /dev dev/
+# mount --rbind /run run/
+# chroot ${ROOTDIR} /usr/bin/qemu-arm-static /bin/bash
+
+ALTERNATIVE:
+# proot -q qemu-arm-static -S ${ROOTDIR}
+\end{lstlisting}
+\FloatBarrier
+
+% Update system
+\begin{lstlisting}[]
+# apt-get update
+# apt-get upgrade
+\end{lstlisting}
+\FloatBarrier
+
+Lets install some programs
+% Install packages
+\begin{lstlisting}[]
+# apt-get install vim git
+\end{lstlisting}
+\FloatBarrier
+
+\subsection{Installation an overlaying filesystem}
+
+We use the code provided by
+
+Assumuing that we are still chrooted to the RPi image and the boot partition is mounted to /boot
+
+% Get files
+\begin{lstlisting}[]
+# OVERLAYROOTDIR="/tmp/overlayroot"
+# git clone https://github.com/chesty/overlayroot.git $OVERLAYROOTDIR
+\end{lstlisting}
+\FloatBarrier
+
+% Install required packages
+\begin{lstlisting}[]
+# apt-get install busybox
+\end{lstlisting}
+\FloatBarrier
+
+% Tell uboot to load initramfs
+\begin{lstlisting}[]
+# echo "initramfs init.gz" > /boot/config.txt
+\end{lstlisting}
+\FloatBarrier
+
+% Setup initramfs
+\begin{lstlisting}[]
+# echo "overlay" > /etc/initramfs-tools/modules
+# cp ${OVERLAYROOTDIR}/hooks-overlay /etc/initramfs-tools/hooks/
+# cp ${OVERLAYROOTDIR}/init-bottom-overlay /etc/initramfs-tools/scripts/init-bottom/
+\end{lstlisting}
+\FloatBarrier
+
+% Create an initramfs
+\begin{lstlisting}[]
+# mkinitramfs -o /boot/init.gz
+\end{lstlisting}
+\FloatBarrier
+
 \subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}

### 2016-06-03 testbed.tex
more testbed

@@
 \end{lstlisting}
-\FloatBarVrier
+\FloatBarrier
 
@@
 \begin{lstlisting}[]
-wget http://kom.aau.dk/project/TuneSCode/rasp_config.zip
-unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
+$ wget http://kom.aau.dk/project/TuneSCode/rasp_config.zip
+# unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
-sed -i "${line_number}c bash /home/pi/.rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
+# line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
+# sed -i "${line_number}c bash /home/pi/.rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
 \end{lstlisting}
@@
 
-\subsection{Installation and Updating}
+\subsection{Installation and Updating the image}
 

### 2016-06-03 testbed.tex
testbed

@@
 \Suppressnumber\begin{lstlisting}[]
-<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/.rasp\_config/nodes.csv}@>
+<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/rasp\_config/nodes.csv}@>
 <@\textcolor{gray}{
@@
 \Suppressnumber\begin{lstlisting}[]
-<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/.rasp\_config/set\_hostname}@>
+<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/rasp\_config/set\_hostname}@>
 <@\textcolor{gray}{
@@
 # line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
-# sed -i "${line_number}c bash /home/pi/.rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
+# sed -i "${line_number}c bash /home/pi/rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
 \end{lstlisting}
@@
 # mount --rbind /dev dev/
-# mount --rbind /run run/
-# chroot ${ROOTDIR} /usr/bin/qemu-arm-static /bin/bash
+# proot -q qemu-arm-static -S ${ROOTDIR}
 
 ALTERNATIVE:
-# proot -q qemu-arm-static -S ${ROOTDIR}
+# chroot ${ROOTDIR} /usr/bin/qemu-arm-static /bin/bash
+\end{lstlisting}
+\FloatBarrier
+
+% Optionally, we may create a unique prompt to indicate we have changed root
+\begin{lstlisting}[]
+# export PS1="(chroot) $PS1"
 \end{lstlisting}
@@
 
+% Setup initramfs
+\begin{lstlisting}[]
+# cp ${OVERLAYROOTDIR}/hooks-overlay /etc/initramfs-tools/hooks/
+# cp ${OVERLAYROOTDIR}/init-bottom-overlay /etc/initramfs-tools/scripts/init-bottom/
+# echo "overlay" > /etc/initramfs-tools/modules
+\end{lstlisting}
+\FloatBarrier
+
 % Tell uboot to load initramfs
@@
 
-% Setup initramfs
+% Create an initramfs
 \begin{lstlisting}[]
-# echo "overlay" > /etc/initramfs-tools/modules
-# cp ${OVERLAYROOTDIR}/hooks-overlay /etc/initramfs-tools/hooks/
-# cp ${OVERLAYROOTDIR}/init-bottom-overlay /etc/initramfs-tools/scripts/init-bottom/
+# mkinitramfs -o /boot/init.gz
+# mkinitramfs -o /boot/init.gz -k 4.4.11+
 \end{lstlisting}
@@
 
-% Create an initramfs
+\subsection{Write image}
+
+% Exit chroot, umount, and write to memory card
 \begin{lstlisting}[]
-# mkinitramfs -o /boot/init.gz
+# exit
+# cd ..
+# umount --recursive ${ROOTDIR}
+# losetup -d WHICH_NUMBE.img of=/dev/mmcblk0 bs=4MR
+# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M
 \end{lstlisting}

### 2016-06-03 upload_rasp_config.sh

@@ -1,5 +1,7 @@
 #!/usr/bin/env bash
 
-zip -r rasp_config rasp_config
-scp rasp_config.zip js3:/afs/ies.auc.dk/project/TuneSCode/public_html/
-rm rasp_config.zip
+cd rasp_config
+zip -r rasp_config *
+#zip -r rasp_config rasp_config
+#scp rasp_config.zip js3:/afs/ies.auc.dk/project/TuneSCode/public_html/
+#rm rasp_config.zip

### 2016-06-03 metrics.tex
Editing metrics

@@
 The goodput is a measure for the effective processing speed since it
-excludes protocol overhead but considers process
+excludes protocol overhead but considers all delays related with
+algorithmic procedures, field operations, hardware processing,
+multicore coordination (where it applies), etc. Moreover, encoding
+and decoding goodput permits to observe if coding is a system-block
+that limits the end-to-end performance. For example, a low goodput
+would affect the \ac{QoE} of delay-densitive applications for the
+end user. Use cases of the
 
-\subsection{Energy Costs}
-\subsubsection{Average Consumption}
-\subsubsection{Per-Bit Consumption}
+\subsection{Energy Consumption}
+\subsubsection{Average }
+\subsubsection{Per-Bit}
 

### 2016-06-03 metrics.tex
Metrics intro done

@@
 
-Once we have defined the coding schemes behavior in terms of encoding
+Once defined the coding schemes behavior in terms of encoding
 and decoding, we proceed to describe the metrics considered in our study.
-We review the energy consumption of the Raspberry Pi since this platform
-is deployed at a large scale in scenarios where (i) energy is
-constrained to the lifetime of the device battery and (ii) the devices
-could be established in locations that are unavailable for regular
-maintenance. Typical use cases of this type of scenarios are sensor
-applications where devices are positioned for measurement retrieval
-without any supervision for large periods fo time. In this type of
-settings, both overall and per-bit energy consumption of the devices
-during the encoding and decoding process are relevant parameters that
-impact in the network performance for a given coding scheme. Also,
-Raspberry Pi processors are based in the \ac{ARM} architecture which
-is the same as in mobile devices like smartphones or tables.
-Therefore, the Raspberry Pi could be used to get an estimate of
-computing capabilities of a mobile device that is much more easy-deployable
-and at a lower overall cost.
+We consider the goodput defined as the ratio of the useful delivered
+information at the application layer and the total delivery time. We focus
+on the goodput considering only the coding process, i.e. we assume that
+the application data has been properly generated before encoding and
+also correctly post-processed after decoding. The goodput is a measure
+for the effective processing speed since it excludes protocol overhead
+but considers all delays related with algorithmic procedures, field
+operations, hardware processing, multicore coordination (where it applies),
+etc. Moreover, encoding and decoding goodput permits to observe if coding is
+a system-block that limits the end-to-end performance. As a reference, a low
+goodput would affect the \ac{QoE} of delay-intolerant applications for the
+end user. For example, Raspberry Pi processors are based in the \ac{ARM}
+architecture which is the same as in mobile devices such as smartphones or
+tables. Mobile user applications are typically delay-intolerant.
+Therefore, the Raspberry Pi might be used as an experiemental tool to
+get an estimate of computing capabilities of a mobile device that is
+much more easy-deployable and at a lower overall cost.
 
-To complement our study, we consider the goodput defined as the ratio
-of the useful delivered information at the application layer and the total
-delivery time. We focus on the goodput considering only the coding process,
-i.e. we assume that the application data has been properly
-generated before encoding and also correctly post-processed after decoding.
-The goodput is a measure for the effective processing speed since it
-excludes protocol overhead but considers all delays related with
-algorithmic procedures, field operations, hardware processing,
-multicore coordination (where it applies), etc. Moreover, encoding
-and decoding goodput permits to observe if coding is a system-block
-that limits the end-to-end performance. For example, a low goodput
-would affect the \ac{QoE} of delay-densitive applications for the
-end user. Use cases of the
+To complement our study, we review the energy consumption of the Raspberry
+Pi since this platform is deployed at a large scale in scenarios where (i)
+energy is constrained to the lifetime of the device battery and (ii) the
+devices could be established in locations that are unavailable for
+regular maintenance. Typical use cases of this type of scenarios are
+sensor applications where devices are positioned for measurement retrieval
+without any supervision for large periods fo time. In this type of settings,
+both overall and per-bit energy consumption of the devices during the
+encoding and decoding process are relevant parameters that impact in the
+network performance for a given coding scheme.
+
+\subsection{Goodput}
+\subsubsection{Encoding}
+\subsubsection{Decoding}
 
@@
 \subsubsection{Per-Bit}
-
-\subsection{Goodput}
-\subsubsection{Encoding}
-\subsubsection{Decoding}

### 2016-06-03 metrics.tex
Including benchmark description

@@
 and decoding, we proceed to describe the metrics considered in our study.
-We consider the goodput defined as the ratio of the useful delivered
-information at the application layer and the total delivery time. We focus
-on the goodput considering only the coding process, i.e. we assume that
-the application data has been properly generated before encoding and
-also correctly post-processed after decoding. The goodput is a measure
-for the effective processing speed since it excludes protocol overhead
-but considers all delays related with algorithmic procedures, field
-operations, hardware processing, multicore coordination (where it applies),
-etc. Moreover, encoding and decoding goodput permits to observe if coding is
-a system-block that limits the end-to-end performance. As a reference, a low
-goodput would affect the \ac{QoE} of delay-intolerant applications for the
-end user. For example, Raspberry Pi processors are based in the \ac{ARM}
-architecture which is the same as in mobile devices such as smartphones or
-tables. Mobile user applications are typically delay-intolerant.
-Therefore, the Raspberry Pi might be used as an experiemental tool to
-get an estimate of computing capabilities of a mobile device that is
-much more easy-deployable and at a lower overall cost.
+The goodput is a measure for the effective processing speed since it
+excludes protocol overhead but considers all delays related with
+algorithmic procedures, field operations, hardware processing, multicore
+coordination (where it applies), etc. Moreover, encoding and decoding
+goodput permits to observe if coding is a system-block that limits the
+end-to-end performance. If a system presents a low goodput, this will
+affect the \ac{QoE} of delay-intolerant applications for the end user.
+For example, mobile user applications are typically delay-intolerant.
+Furthermore, Raspberry Pi processors are based in the \ac{ARM} architecture
+which is the same as in mobile devices such as smartphones or tables.
+Thus, the Raspberry Pi might be used as an experimental tool to get an
+estimate of a mobile device processing capability which is easy-deployable
+and at a much lower cost than a smartphone.
 
@@
 sensor applications where devices are positioned for measurement retrieval
-without any supervision for large periods fo time. In this type of settings,
+without any supervision for large periods fo time.
+
+\subsection{Goodput}
+We consider the goodput defined as the ratio of the useful delivered
+information at the application layer and the total delivery time. We focus
+on the goodput considering only the coding process, i.e. we assume that
+the application data has been properly generated before encoding and
+also correctly post-processed after decoding. In this way, the goodput
+
+\subsubsection{Encoding}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.6\textwidth]{images/.............}
+\caption{Encoding goodput benchmark}
+\label{fig:enc_goodput_benchmark}
+\end{figure}
+
+\subsubsection{Decoding}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.6\textwidth]{images/.............}
+\caption{Decoding goodput benchmark}
+\label{fig:dec_goodput_benchmark}
+\end{figure}
+
+\subsection{Energy Consumption}
+In large-scale networks where several Raspberry Pis might be deployed,
 both overall and per-bit energy consumption of the devices during the
 encoding and decoding process are relevant parameters that impact in the
-network performance for a given coding scheme.
+network performance for a given coding scheme. To compute the
 
-\subsection{Goodput}
-\subsubsection{Encoding}
-\subsubsection{Decoding}
-
-\subsection{Energy Consumption}
-\subsubsection{Average }
+\subsubsection{Average}
 \subsubsection{Per-Bit}

### 2016-06-03 testbed.tex
changed scripts
added current measurements

@@
 
-This section will be used to present a Raspberry Pi testbed and the steps to
-install and configure the individual devices.
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.6\textwidth]{images/testbed_setup2.eps}
+\caption{Testbed setup}
+\label{fig:testbed_setup}
+\end{figure}
+
+This section will present a testbed of thirty \ac{Raspi}s.
+%Twenty \ac{Raspi} 1 model B revision 2 and ten \ac{Raspi} 2 model B V1.1.
+They are all equipped with a memory card and are connected to the
+university network by wire using their ethernet interface (eth0).
+
+To easily discover the \ac{Raspi}s within the university network, they have all
+been assigned a unique name under a common domain.
+This eliminates the need to remember their individual \ac{IP}s.
+
+A sketch of the testbed is depicted in figure~\ref{fig:testbed_setup}.
+We have two types of \ac{Raspi}s in our setup.
+Table \ref{tab:rasp_naming} shows the naming convention.
+
+\begin{table}[ht!]
+  \centering
+  \begin{tabular}{|c|c|}
+    \hline
+      \textbf{Hostname} & \textbf{Model} \\ \hline
+    Rasp00 - Rasp19 & Raspberry Pi 1 model B rev. 2 \\ \hline
+    Rasp100 - Rasp109 & Rasperry Pi 2 model B V1.1 \\ \hline
+  \end{tabular}
+  \caption{Raspberry Pi naming convention}
+  \label{tab:rasp_naming}
+\end{table}
+
+Accessing them is easily done using \ac{SSH}.
+To address them within the university network, 
+The \ac{Raspi}s
+
+The Raspberry Pis are all equipped with an ethernet interface (eth0) and
+connected by wire to the university's \ac{LAN}. The university network
+administration was provided
+the \ac{MAC} addresses of the ethernet interfaces to automatically assign
+the devices the desired \ac{IP} addresses as shown in the figure. In a personal
+\ac{LAN}, another option could be to manually provide the devices with static
+\ac{IP}s.
+
+This section will be used to present a \ac{Raspi} testbed and the steps to
+install and configure its devices.
 
 The testbed is depicted in figure~\ref{fig:testbed_setup}. It consists of twenty
-Raspberry Pi 1 model B rev 2 (Rasp\_01 to Rasp\_20) and 
+Raspberry Pi 1 model B rev 2 (Rasp01 to Rasp20) and 
 ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).
 
-The goal is to configure all the devices identically with the same software
+The goal is to configure all the \ac{Raspi}s identically with the same software
 and configurations. There are however a few differences between them that we
@@
 %university's \ac{LAN}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.6\textwidth]{images/testbed_setup.eps}
-\caption{Testbed setup}
-\label{fig:testbed_setup}
-\end{figure}
 
@@
 
+\subsection{Download image}
+
 % Define variable]
@@
 \FloatBarrier
+
+\subsection{Mount image}
 
@@
 # Ethernet MAC    Hostname
-b8:27:eb:5b:da:20 rasp_00
-b8:27:eb:7b:c3:91 rasp_01
-b8:27:eb:54:9c:64 rasp_02
-b8:27:eb:95:bd:11 rasp_03
+b8:27:eb:5b:da:20 rasp00
+b8:27:eb:7b:c3:91 rasp01
+b8:27:eb:54:9c:64 rasp02
+b8:27:eb:95:bd:11 rasp03
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# mkinitramfs -o /boot/init.gz
+# How to i know the kernel version /lib/modules/
 # mkinitramfs -o /boot/init.gz -k 4.4.11+
@@
 # umount --recursive ${ROOTDIR}
-# losetup -d WHICH_NUMBE.img of=/dev/mmcblk0 bs=4MR
+# losetup -d WHICH_NUMBE.img
 # dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M
@@
 \FloatBarrier
+
+How about kodo python?
 

### 2016-06-03 metrics.tex
some more changes

@@
 the application data has been properly generated before encoding and
-also correctly post-processed after decoding. In this way, the goodput
+also correctly post-processed after decoding. In this way, we define
+the goodput for either an encoder or a decoder as follows:
+%
+\begin{align} \label{eq:goodput}
+Goodput = \frac{gB}{T_{proc}} ~ [\mathrm{Bytes/s}]
+\end{align}
+%
+In \eqref{eq:goodput}, $B$ and $g$ are the packet and generation size
+as defined previously and both represented the data to be processed. For
+goodput measurements, we are concerned in quantifying the processing time
+for either encoding or decoding $g$ \ac{l.i.} packets. Thus, $T_{proc}$ is
+the processing time required for this processing. In the next subsections, we
+define two time bechmarks available in [\textbf{Chres repos here}].
+The purpose of the benchmarks is to quantify the processing time for
+any of the coding scheme considered in Section \ref{sec:schemes}.
 
-\subsubsection{Encoding}
+\subsubsection{Encoding Benchmark}
+Fig. \ref{fig:enc_goodput_benchmark} refers to the benchmark setup
+made for measuring the encoding processing time. The time benchmark
+is divided in two parts. In the first part, called a \textit{pre-run},
+we quantify the amount of \textit{transmitted} coded packets from an
+encoder (named 1 in Fig. \ref{fig:enc_goodput_benchmark}) required for
+decoding in a single encoder-decoder link with no packet erasures
+for a defined configuration of coding scheme, coding parameters and
+amount of feedback. In the case of \ac{TSNC}, we also record the
+points where a feedback was received from the decoder. The purpose of
+the pre-run is to predict how an encoder should behave with a given
+seed within its random number generator. This part of the benchmark is
+not regarded as a measurement.
+
+In the second part which is the actual \textit{simulation}, a reseted
+encoder (2 in Fig. \ref{fig:enc_goodput_benchmark}) is given the same
+seed as in the pre-run and then we measure the time from which the
+process start until we reach the amount of transmitted packets in the
+pre-run. Then, this measurement is stored as the encoder $T_{proc}$
+for this generic configuration.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{images/.............}
+\includegraphics[width=0.6\textwidth]{images/measure_encoder.eps}
 \caption{Encoding goodput benchmark}
@@
 
-\subsubsection{Decoding}
+\subsubsection{Decoding Benchmark}
+Fig. \ref{fig:dec_goodput_benchmark} shows the benchmark setup
+for measuring the decoding processing time. The time benchmark
+is divided in two parts as its encoding counterpart, e.g. a pre-run
+and the actual simulation. However, some differences occur.
+
+In the pre-run, we still quantify the amount of transmitted coded
+packets from encoder 1. Notice that we include the feedback case because
+it is necesary for the \ac{TSNC} scheme. However, now we store
+the \textit{transmitted packets} instead. The reason being
+that we want to feed the decoder with the same packets in the same
+order. Later, in the actual simulation, an encoder (2 in Fig.
+\ref{fig:dec_goodput_benchmark}) is given the same packets in the same
+order from the pre-run and then we measure the time from which the
+process start until the decoder finishes to retrieve the original
+packets. Finally, this measurement is saved as the decoder $T_{proc}$
+for this general configuration.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{images/.............}
+\includegraphics[width=0.6\textwidth]{images/measure_decoder.eps}
 \caption{Decoding goodput benchmark}

### 2016-06-03 schemes.tex
Some changes

@@
 single flow are combined with each other. In this type of network coding,
-all the original data packets $P_j, j \in [1,g]$, each of $B$ bits, are used
+all the original data packets $P_j, j \in [1,g]$, each of $B$ bytes, are used
 to create coded packets. In the following subsections, we describe the
@@
 
-\subsection{Network Coding Implementation for Multicore Architectures with
-the Raspberry Pi}
+\subsection{Implementation for the Raspberry Pi Multicore Architecture}
 \label{sub:implementation-multicore}

### 2016-06-04 measurements.tex
Preparing for energy and power section

@@
 This section may be divided by subheadings. It should provide a concise and
-precise description of the experimental results, their interpretation as well as
-the experimental conclusions that can be drawn.
+precise description of the experimental results, their interpretation as well
+as the experimental conclusions that can be drawn.
 
@@
 method described in Section~\ref{sub:implementation-multicore}. The time
-recorded includes the dependencies resolving, creation of the \ac{DAG}, and
-the task scheduling. In practice, it would suffice to calculate and store this
-information only once per generation size.
+recorded includes the dependencies resolving, creation of the \ac{DAG},
+and the task scheduling. In practice, it would suffice to calculate and
+store this information only once per generation size.
 
 \subsubsection{Decoding blocked}
-The differences between encoding and decoding, is that the decoding task also
-involves the matrix inversion. Similarly as with the encoding results, the
-time recorded includes the dependencies resolving, the creation of the
+The differences between encoding and decoding, is that the decoding task
+also involves the matrix inversion. Similarly as with the encoding results,
+the time recorded includes the dependencies resolving, the creation of the
 \ac{DAG} and the task scheduling. However, to decode, these calculations are also made for inverting the matrix of coding coefficients.
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_1024.eps}
+\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_1024.pdf}
 \caption{Encoding and Decoding performance for g = 1024 \cite{wunderlich2015network}}
@@
 efficient brings an increase in throughput by a factor of 2.83. When using the
-algorithm described in Section~\ref{sub:implementation-multicore}, encoding with
-four cores is on average 3.7 times faster than with one core. Similarly,
-decoding with four codes is 3.05 times faster, on average, than decoding with a
-single core. Figure~\ref{enc_dec1024} shows that the implemented algorithm, by
-exploiting cache efficiency and only three extra cores provides a gain of 10
-folds compared with traditional non-blocked algorithms. With $g$ = 1024, the
-matrix inversion becomes more expensive than at smaller generations sizes.
-Therefore, the decoding throughput is 46\% of the encoding throughput.
+algorithm described in Section~\ref{sub:implementation-multicore},
+encoding with four cores is on average 3.7 times faster than with one core.
+Similarly, decoding with four codes is 3.05 times faster, on average, than
+decoding with a single core. Figure~\ref{enc_dec1024} shows that the
+implemented algorithm, by exploiting cache efficiency and only three extra
+cores provides a gain of 10 folds compared with traditional non-blocked
+algorithms. With $g$ = 1024, the matrix inversion becomes more expensive
+than at smaller generations sizes. Therefore, the decoding throughput
+is 46\% of the encoding throughput.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_128.eps}
+\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_128.pdf}
 \caption{Encoding and Decoding performance for g = 128 \cite{wunderlich2015network}}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_16.eps}
+\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_16.pdf}
 \caption{Encoding and Decoding performance for g = 16 \cite{wunderlich2015network}}
@@
 
-When $g$ = 16, the gains of blocked operations are negligible compared with the
-non-blocked ones. The reason behind this behavior is that all the data fits in
-the L1 cache. For the scheduled version, since the problem to solve is so small,
-the gain when using four cores is a factor of 1.68 compared with a single core,
-and 1.01 compared with two cores. Therefore, there are no practical benefits in
-using four cores instead of two.
+When $g$ = 16, the gains of blocked operations are negligible compared with
+the non-blocked ones. The reason behind this behavior is that all the data
+fits in the L1 cache. For the scheduled version, since the problem to solve
+is so small, the gain when using four cores is a factor of 1.68 compared
+with a single core, and 1.01 compared with two cores. Therefore, there
+are no practical benefits in using four cores instead of two.
 
-The differences in throughput, for all generation sizes, between the blocked
-baseline and the single threaded scheduled measurements are due the time spent
-resolving the dependencies and the scheduling overhead. These effects are
-negligible for big generation sizes, while considerable for small matrices.
-
-% \begin{figure}
-% \centering
-% \begin{subfigure}[b]{0.3\textwidth}
-% \includegraphics[width=\textwidth]{images/2015-04-18_encoding_decoding_1024.eps}
-% \caption{Encoding and Decoding performance for g = 1024}
-% \label{enc_dec1024}
-% \end{subfigure}
-%
-% \begin{subfigure}[b]{0.3\textwidth}
-% \includegraphics[width=\textwidth]{images/2015-04-18_encoding_decoding_128.eps}
-% \caption{Encoding and Decoding performance for g = 128}
-% \label{enc_dec128}
-% \end{subfigure}
-%
-% \begin{subfigure}[b]{0.3\textwidth}
-% \includegraphics[width=\textwidth]{images/2015-04-18_encoding_decoding_16.eps}
-% \caption{Encoding and Decoding performance for g = 16}
-% \label{enc_dec16}
-% \end{subfigure}
-% \end{figure}
+The differences in throughput, for all generation sizes, between the
+blocked baseline and the single threaded scheduled measurements are due the
+time spent resolving the dependencies and the scheduling overhead. These
+effects are negligible for big generation sizes, while considerable for
+small matrices.
 
@@
 performed matrices multiplications and matrix inversions, and measured the time
-spent doing so. We then calculated the ratio between these two measured times
-times $ratio = \frac{T_{mult}}{T_{inv}}$. Table~\ref{runtimes} summarizes the
-results. The bigger the matrix size, the smaller is the calculated ratio. This
-means that when the problems are bigger, the decoding throughput decreases
-compared with the encoding throughput.
+spent doing so which we name $T_{mult}$ and $T_{inv}$. We calculate the ratio
+between these two measured times defined as $r = \frac{T_{mult}}{T_{inv}}$.
+Table~\ref{runtimes} summarizes the results. The bigger the matrix size, the
+smaller is the calculated ratio. This means that when the problems are bigger,
+the decoding throughput decreases compared with the encoding throughput.
 
@@
 \begin{tabular}{|r|r|r|r|}
+
 \hline
-g & multiplication (ms) & inversion (ms) & ratio \\
+$g$ & $T_{mult}$ (ms) & $T_{inv}$ (ms) &$r$ \\
 \hline

### 2016-06-04 metrics.tex
Preparing for energy and power section

@@
 
-\subsection{Energy Consumption}
+\subsection{Power and Energy Consumption}
 In large-scale networks where several Raspberry Pis might be deployed,
@@
 
-\subsubsection{Average}
-\subsubsection{Per-Bit}
+\subsubsection{Average Power}
+\subsubsection{Energy Consumption}

### 2016-06-04 metrics.tex
start to use Raspi in Nestor docs

@@
 For example, mobile user applications are typically delay-intolerant.
-Furthermore, Raspberry Pi processors are based in the \ac{ARM} architecture
+Furthermore, \ac{Raspi} processors are based in the \ac{ARM} architecture
 which is the same as in mobile devices such as smartphones or tables.
-Thus, the Raspberry Pi might be used as an experimental tool to get an
+Thus, the \ac{Raspi} might be used as an experimental tool to get an
 estimate of a mobile device processing capability which is easy-deployable
@@
 \subsection{Power and Energy Consumption}
-In large-scale networks where several Raspberry Pis might be deployed,
-both overall and per-bit energy consumption of the devices during the
-encoding and decoding process are relevant parameters that impact in the
-network performance for a given coding scheme. To compute the
+In large-scale networks where several \ac{Raspi}s might be deployed,
+both average power and energy per bit consumption of the devices are
+relevant parameters that impact in the network performance for a given
+coding scheme. The average power specifies the rate at which energy
+consumed in the \ac{Raspi}, thus it provides information about the autonomy
 
 \subsubsection{Average Power}
-\subsubsection{Energy Consumption}
+\subsubsection{Energy per Bit Consumption}

### 2016-06-04 testbed.tex

@@
 
+\subsection{fabric}
+
+% Exit chroot, umount, and write to memory card
+\begin{lstlisting}[]
+from fabric.api import run, env, task
+# Python Fabric script to run commands on multiple hosts through ssh
+#
+# Run script as 'fab <task>', where <task> is one of the scripts functions
+# marked as a tesk. The task marked as 'default' will be run if <task> is not
+# specified
+
+env.hosts = ['rasp00.domain.com','rasp01.domain.com','rasp02.domain.com']
+env.user = 'root'
+env.password = 'sdn'
+
+@task
+def install(program):
+    """
+    Install a program
+    program: program name
+    """
+    result = run('apt-get install -y {}'.format(program), quiet=True)
+
+@task
+def open(program, args):
+    """
+    Open af program
+    program: program name
+    args: program arguments
+    """
+    # Set environment variable DISPLAY=:0 and run commands
+    with shell_env(DISPLAY=':0'):
+        # Wake monitor
+        run('xset dpms force on', quiet=True)
+
+        # Run program
+        run('{}'.format(program, " ".join(args)), quit=True)
+
+\end{lstlisting}
+\FloatBarrier
+
+execute a script function by calling "fab install:feh"
+
 \subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}

### 2016-06-04 introduction.tex
Starting with the results
Update Raspi acronym

@@
 compilation of the Kodo library. Section \ref{sec:schemes} defines the
-coding schemes employed in our study. Section \ref{sec:topologies} some
-configurable topologies in the tested. Later, in Section \ref{sec:metrics}
+coding schemes employed in our study. Later, in Section \ref{sec:metrics}
 we describe the considered metrics for performance comparison of the
-codes deployed in the Raspberry Pi. In Section \ref{sec:measurements}, we show
-the measurements in the Raspberry Pi of the mentioned metrics. Final
+codes deployed in the \ac{Raspi}. In Section \ref{sec:measurements}, we show
+the measurements in the \ac{Raspi} of the mentioned metrics. Final
 conclusions and future work are reviewed in Section \ref{sec:conclusions}.

### 2016-06-04 metrics.tex
Update Raspi acronym

@@
 
-To complement our study, we review the energy consumption of the Raspberry
-Pi since this platform is deployed at a large scale in scenarios where (i)
+To complement our study, we review the energy consumption of the \ac{Raspi}
+since this platform is deployed at a large scale in scenarios where (i)
 energy is constrained to the lifetime of the device battery and (ii) the
@@
 We consider the goodput defined as the ratio of the useful delivered
-information at the application layer and the total delivery time. We focus
+information at the application layer and the total processing time. We focus
 on the goodput considering only the coding process, i.e. we assume that
@@
 The purpose of the benchmarks is to quantify the processing time for
-any of the coding scheme considered in Section \ref{sec:schemes}.
+any of the coding schemes considered in Section \ref{sec:schemes}.
 

### 2016-06-04 schemes.tex
Update Raspi acronym

@@
 In this section, we present a description of the considered coding schemes
-measured with our the Raspberry Pi testbed. We introduce a definition
+measured with our the \ac{Raspi} testbed. We introduce a definition
 for the primitive coding operations, e.g. encoding, decoding and recoding
@@
 which are obtained by modifying the basic coding operations that provide
-better processing speeds, particularly relevant for the Raspberry Pi.
+better processing speeds, particularly relevant for the \ac{Raspi}.
 Finally, we include a review of the

### 2016-06-04 testbed.tex
Update Raspi acronym

@@
 we summarize all the details regarding on setting the connectivity and
-system files for a set of Raspberry Pis in a centralized fashion.
+system files for a set of \ac{Raspi}s in a centralized fashion.
 Afterwards, we indicate how to cross-compile the Kodo library in an
@@
 
-The Raspberry Pis are all equipped with an ethernet interface (eth0) and
+The \ac{Raspi}s are all equipped with an ethernet interface (eth0) and
 connected by wire to the university's \ac{LAN}. The university network
@@
 Finally, it should be possible to store data that are generated from
-simulations on the memory cards that are in the individual Raspberry Pi.
+simulations on the memory cards that are in the individual \ac{Raspi}.
 %We using a overlaying filesystem that
@@
 
-We use standard usb power adapters to power the Raspberry Pis.
+We use standard usb power adapters to power the \ac{Raspi}s.
 
@@
 personal workstation and transfer the generated binaries directly to
-a path in the Raspberry Pi. To achieve this, we get a toolchain that
+a path in the \ac{Raspi}. To achieve this, we get a toolchain that
 contains the binaries for the \texttt{raspberry-gxx49-arm-g++} compiler
-for the Raspberry Pi. Therefore, we strongly recommend any testbed
+for the \ac{Raspi}. Therefore, we strongly recommend any testbed
 administrator to do the following procedure. In what follows, we provide
@@
 
-\item Download the Raspberry Pi toolchain for 64-bit Linux from: \\
+\item Download the \ac{Raspi} toolchain for 64-bit Linux from: \\
 \texttt{http://buildbot.steinwurf.dk/toolchains/linux/} to your
@@
 \item Clone the Kodo repository in the server by executing: \\
-\texttt{git clone git://github.com/steinwurf/kodo.git} in \texttt{\$HOME}. \textbf{Change the repo to kodo-rlnc or kodo-cpp since just raw kodo is going to be depreceated soon} \\
+\texttt{git clone git://github.com/steinwurf/kodo.git} in \texttt{\$HOME}.
+\textbf{Change the repo to kodo-rlnc or kodo-cpp since just raw kodo is going
+to be depreceated soon} \\
 
@@
 \texttt{python config.py} and select the 16th ``make specification'' file
-for the Raspberry Pi, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
+for the \ac{Raspi}, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
 presented by the file.
@@
 This command configures \texttt{waf} to use the proper compiler and its
-required flags to generate the binaries for the Raspberry Pi. If the
+required flags to generate the binaries for the \ac{Raspi}. If the
 configuration was correct, the output will indicate:
@@
 \item Execute \texttt{python waf build}. If the build process was
-successful, the generated binaries for the Raspberry Pi should be located
+successful, the generated binaries for the \ac{Raspi} should be located
 in \texttt{build/cxx\_raspberry\_gxx49\_arm} in the Kodo repository.
@@
 Once this procedure is made, the testbed administrator can relocate the
-generated binary files to Raspberry Pi's through the network as desired
+generated binary files to the \ac{Raspi}s through the network as desired
 by using the \texttt{scp} command during the configuration step.
@@
 
-\subsection{Kodo Builds for the Raspberry Pi, Platform Support and Documentation}
+\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation}
 
-You can check the build status of Kodo, Fifi and other relevant projects through
-their respective repository master branch on our buildbot page
-\cite{steinwurf2016buildbot}. Our buildbot displays the status of the builds for
-Raspbian 8 and GCC 4.9 for the ARM architecture which is the relevant one for the
-Raspberry Pi. At the link, you can check build status and build statistics. Also,
-documentation about Kodo basics with a tutorial is available at \cite{kododocs}.
+You can check the build status of Kodo, Fifi and other relevant projects
+through their respective repository master branch on our buildbot page
+\cite{steinwurf2016buildbot}. Our buildbot displays the status of the builds
+for Raspbian 8 and GCC 4.9 for the ARM architecture which is the relevant one
+for the \ac{Raspi}. At the link, you can check build status and build
+statistics. Also, documentation about Kodo basics with a tutorial is available
+at \cite{kododocs}.

### 2016-06-04 metrics.tex
Ready for now..

@@
 \begin{align} \label{eq:goodput}
-Goodput = \frac{gB}{T_{proc}} ~ [\mathrm{Bytes/s}]
+R_{proc} = \frac{gB}{T_{proc}} ~ [\mathrm{Bytes/s}]
 \end{align}
@@
 
-\subsection{Power and Energy Consumption}
+\subsection{Energetic Expenditure}
 In large-scale networks where several \ac{Raspi}s might be deployed,
@@
 relevant parameters that impact in the network performance for a given
-coding scheme. The average power specifies the rate at which energy
-consumed in the \ac{Raspi}, thus it provides information about the autonomy
+coding scheme. Hence, we consider a study of these energy expenditure
+parameters for the encoding and decoding. We define these metrics
+and propose a setup to measure them.
 
-\subsubsection{Average Power}
+The average power specifies the rate at which energy is
+consumed in the \ac{Raspi}. Thus, for a given energy value in the device
+battery without any external supplies, this metric permits to infer the amount
+of time for which the \ac{Raspi} can operate autonomously before draining
+out its battery. For the energy per bit consumption, it indicates how
+much energy is expended to effectively transmit or receive 1 bit of bit
+considering the encoding or decoding respectively. This energy is computed
+
+For our energy measurement campaign, we automate the setup presented
+in Fig. \ref{fig:measurement_setup} to sequentially run a series of
+simulations for a given configuration of coding scheme and parameters,
+to estimate the energy consumption in both of our \ac{Raspi}
+models. A representative sketch of the setup is shown in the
+computer monitor in Fig. \ref{fig:measurement_setup}. The figure presents
+a \ac{Raspi} device whose power supply is an Agilent 66319D \ac{DC} source,
+instead of its conventional chorded supply. The output of the measurements
+are later sent to a workstation where the raw measurement data is processed.
+The measured variable was the current consumed by the device for a fixed
+5V supply from the source. To identify each experiment, we classified the
+electrical current samples into two groups based on the magnitude. In our
+measurements, the groups to be reported are the idle current $I_{idle}$
+and the processing current $I_{proc}$. The former is the current the
+\ac{Raspi} requires while in idle state, meaning that no processing
+is being carried. The latter stands for the current needed during
+the encoding or decoding processing of the packets. The measurements
+where $I_{proc}$ is observed are made for a given configuration of
+coding scheme with its parameters. Finally, each simulation was enumerated
+to map the coding speed measurements with the corresponding energy
+consumption.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.7\textwidth]{images/measurement_setup.eps}
+\caption{Energy measurement setup}
+\label{fig:measurement_setup}
+\end{figure}
+
+\subsubsection{Average Power Expenditure}
+To extract the energy consumption of network coding, we subtracted the
+idle energy consumption from the energy consumption used during simulations.
+
+%
+\begin{align} \label{eq:avg_current}
+I_{avg} = \frac{1}{N_s}\sum_{k=1}^{N_s} I_{k}  ~[\mathrm{Amperes}]
+\end{align}
+%
+
+%
+\begin{align} \label{eq:avg_power}
+P_{avg} = V_{supply}(I_{proc,avg} - I_{idle,avg}) ~[\mathrm{Watts}]
+\end{align}
+%
 \subsubsection{Energy per Bit Consumption}
+%
+\begin{align} \label{eq:goodput}
+E_b = P_{avg} T_{proc} = P_{avg} \times \frac{gB}{R_{proc}} ~[\mathrm{Joules/bit}]
+\end{align}
+%

### 2016-06-04 testbed.tex
worked on testbred

@@
 
-\subsection{Download image}
+The first thing we need to do is to download the linux installation file.
+For Raspbian, this is available at \url{http://downloads.raspberrypi.org}.
+
+Raspbian is made available in two bundles. Raspbian and Raspbian lite.
+The difference between the two is that Raspbian contains a pre-installed desktop
+environment, and Raspbian lite is by default only accessable through a shell. 
+They will both also be remotely accessible using \ac{SSH}.
+
+Our testbed does not have monitors so we will install Raspbian lite.
+A desktop environment can always be installed manually in case that will be
+desired sometime in the future.
+
+Below is a procedure of how we setup the \ac{Raspi}s in our testbed. We
+have decided a simple setup where each \ac{Raspi} is equipped with a
+memory card that contains a slightly customized Raspbian lite image with
+identical settings.
+
+The reason this can be done easily is because the official Raspbian lite image
+that we will download simply conntains a complete linux installation that are
+packaged in an image rather than written to a harddrive, memory card, or usb
+pen.
+
+The overall steps to customize the official Raspbian lite image are listed below:
+\begin{enumerate}
+    \item Download Raspbian lite
+    \item Alter Raspbian lite. E.g. browse, modify, add, and delete files
+        in the official Raspbian lite image
+    \item Change root. I.e. change root filesystem into the Raspbian lite
+        image to update and install software packages
+    \item Write image to memory cards
+\end{enumerate}
+
+\subsection{Download Raspbian lite}
 

### 2016-06-04 testbed.tex
testbed

@@
 
+To download the latest Raspbian lite, we go to the url
+\url{http://downloads.raspberrypi.org/raspbian_lite/images/}.
+At the time of this writing, the latest bundle was
+2016-05-27-raspbian-jessie-lite.zip.
+
+We want to proceed downloading the image with a shell instead of the browser.
+To do this, first open a command window on a linux machine. This guide is
+assuming a debian based distribution, but there should only be minor differences
+if you have another package manager. I.e. the application that is used to
+download and install software packages in linux.
+
+After the terminal has been opened, we first declare a few variables to reduce
+redundant typing. The first variables we declare is the Raspbian image name.
+Notice that the extension has been omitted. This is because the image has been
+packed into a zip file.
+The other variable we declare is a working directory. This is where we will
+download the image to and work on it. In other words, it will be stored in
+/home/<username>/Raspbian
+
+%To download Raspbian lite, we go to the \url{http://downloads.raspberrypi.org}.
+%There should be a folder called raspbian\lite and
+%to find the download page at which Raspbian lite should be located. Instead of
+%downloading with the browser, we just extract the download url to the latest
+%image. At the time of this writing, that was
+
 % Define variable]
@@
 \FloatBarrier
+
+A final thing to notice is the way \$ and \# are used in the code blocks. \$
+means that the command can be run as a normal user where \# indicates that the
+command should be run with root permissions.
+Running a command with root permissions can on most systems be done by putting
+the command "sudo" in front of each line. This is illustrated in the code below
+with the command "whoami" that prints the username of the caller. Lines without
+leading \$ or \# is the terminal output.
+
+% Root example
+\begin{lstlisting}[]
+$ whoami
+chres
+$ sudo whoami
+root
+\end{lstlisting}
+\FloatBarrier
+
+Next, we make the working directory and change directory (cd) into the working
+directory. We can then use wget to download Raspbian lite. Unpack the image
+when the download is complete.
 

### 2016-06-04 testbed.tex
testbed

@@
 
+After Raspbian lite has been unpacked, there should be an .img file in the directory.
+"fdisk" can be used to display what is inside. Pass the arguments "-u sectors" to
+display the sizes in sectors and "-l" to display partitions and exit.
+
 % Check out the image   % The dollar hack was to fix vim syntax
 \begin{lstlisting}[literate={DOLLAR}{\$}1]
-DOLLAR fdisk -lu ${IMAGE}.img
+DOLLAR fdisk -u sectors -l ${IMAGE}.img
 Disk 2016-05-27-raspbian-jessie-lite.img: 1.3 GiB, 1387266048 bytes, 2709504 sectors
@@
 
-We see that the boot and root partitions starts at sector 8192 and 137216 respectivly.
-We also notice that each sector is 512 bytes.
+The image contains two partitions. The first one of starting at sector 8192 and
+the other partition starting at sector 137216. The partitions is of type FAT32
+and Linux and have sizes 63M and 1.2G. This indicates that the first partition
+is most likely a boot partition and the second partition is a traditional file
+system. Actually, it is a linux root filesystem (i.e. /).
 
-On newer systems, we can mount the device easier using "losetup --show -f -P IMAGE"
+%We see that the boot and root partitions starts at sector 8192 and 137216 respectivly.
+%We also notice that each sector is 512 bytes.
 
-Mount root partition:
+%On newer systems, we can mount the device easier using "losetup --show -f -P IMAGE"
+
+%Mount root partition:
+
+To browser and alter the files in the image, it is possible to mount the partitions.
+
+Lets first mount the root partition. This is done by first creating a new folder
+that we will call root which will be located in our working directory. After this,
+we mount the partition starting at sector 137216. To provide this offset information
+to mount, we need to find the offset in bytes. From the fdisk command we could also
+see that each sector is 512 bytes. Thus, we multiply the sector size and the sector
+start to get the offset in bytes.
 
@@
 \FloatBarrier
+
+After this, we can also mount the boot partition inside the newly mounted
+root filesystem. This is useful because that partition will be mounted
+this exact place when a \ac{Raspi} starts up with a memory card containing
+this image. It is therefore the natural place to mount it for later purposes.
 
@@
 @task
-def open(program, args):
-    """
-    Open af program
-    program: program name
-    args: program arguments
-    """
-    # Set environment variable DISPLAY=:0 and run commands
-    with shell_env(DISPLAY=':0'):
-        # Wake monitor
-        run('xset dpms force on', quiet=True)
-
-        # Run program
-        run('{}'.format(program, " ".join(args)), quit=True)
+def copy_to_rasp(filename):
+    put(...)
 

### 2016-06-04 testbed.tex
more testbed

@@
 
-We can now change all the files in the disk image.
+We can now change all the files in the disk image as desired.
 
 \subsection{Configuring OS files and scripts}
+
+The \ac{Raspi}s should be setup to be as similar as possible. One of those
+things that is prefered to be different on the devices is their hostname.
+This helps distinguish them from each other. One solution to this in our
+approach would be to uniquely change the hostname in each memory card.
+This is however not desired because that would either require modifying
+the the customized Raspbian lite image before writing the content to the
+memory card or to manually change it in the \ac{Raspi}s after the image has
+been written to a meomory card.
+Instead, we decided to register the ethernet MAC addresses of all the \ac{Raspi}s
+in our testbed. Those had to be used to put them in a domain name anyway.
+
+Below is a part of the file where we keep track of the MAC addresses and assign
+hostnames. This file will be available online and copied to the Raspbian lite
+image in a later step under the listed filename. For different \ac{Raspi}s
+the MAC addresses has to be changed. The MAC address of a network card can be found
+using the command "ifconfig" or "ip addr".
 
@@
 
+Provided that each \ac{Raspi} will have knowledge of all other \ac{Raspi}s in
+the testbed, it still needs to know which name to give itself.
+We do this using a small Bash script:
+
 % Set hostname
@@
 #!/usr/bin/env bash
+
+script_path="$(dirname $(realpath $0))"
 mac=$(cat /sys/class/net/eth0/address)
-hostname=$(grep $mac nodes.csv | cut -f2 -d' ')
+hostname=$(grep $mac ${script_path}/nodes.csv | cut -f2 -d' ')
 
@@
 \FloatBarrier
+
+Line 1 tells the system to interpret the script using Bash. Line 3 gets the
+path of the script itself. Line 4 gets the MAC address. This script will be
+located in a \ac{Raspi} and thus return the MAC address of itself when called.
+Line 4 searches line by line for this mac address.
+Line 8-11 assigns the hostname found in "nodes.csv". If the MAC did not exists,
+then it will keep the default hostname of the system.
 
@@
 \fxnote{Which packages is required for this on debian/ubuntu?}
+
+See the following link for information on this procedure:
+\url{https://wiki.archlinux.org/index.php/Raspberry_Pi}
 
@@
 \subsection{Installation an overlaying filesystem}
+
+See this link:
+\url{https://github.com/chesty/overlayroot}
 

### 2016-06-04 testbed.tex
more testbed

@@
 
+We have packed the files and uploaded them to a webserver. These can be
+retrieved with wget and unziped into the Raspbian lite image that
+we are customizing:
+
 % Get the files
@@
 
-Call set\_hostname script at startup. We insert a line of code to call script in rc.local just after the initial comments (i.e. lines starting with \#).
+"nodes.csv" can be changed using a text editor. For vim, this could be done
+the following way:
 \begin{lstlisting}[]
-# line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
-# sed -i "${line_number}c bash /home/pi/rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
+# vim ${ROOTDIR}/home/pi/rasp_config/nodes.csv
 \end{lstlisting}
 \FloatBarrier
+
+Finally, to actually make the \ac{Raspi}s change hostname, we have to make
+each \ac{Raspi} call the above script when it starts up.
+Do this by inserting the line below in "\$\{ROOTDIR\}/etc/rc.local".
+The file
+can be opened with your favorite text editor.
+
+\begin{lstlisting}[]
+bash /home/pi/rasp_config/set_hostname"
+\end{lstlisting}
+\FloatBarrier
+
+%This can be done by inserting a call to the script
+%set\_hostname in rc.local before it exits.
+%
+%Call set\_hostname script at startup. We insert a line of code to call script in rc.local just after the initial comments (i.e. lines starting with \#).
+%\begin{lstlisting}[]
+%# line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
+%# sed -i "${line_number}c bash /home/pi/rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
+%\end{lstlisting}
+%\FloatBarrier
 %$ line="bash /home/pi/.rasp_config/set_hostname"
@@
 
-All other files could be updated.
+All other files could be updated as well.
 
@@
 It may be desired to pre-install some programs in the image before it is
-written to all the memory cards that goes into the Raspberry pis.
+written to all the memory cards that goes into the \ac{Raspi}s.
 This can be done using QEMU Chroot (change root).
@@
 
-\fxnote{Lets use RPi for Raspberry Pis throughout the paper!}
 \fxnote{Which packages is required for this on debian/ubuntu?}

### 2016-06-04 testbed.tex
more testbed

@@
 written to all the memory cards that goes into the \ac{Raspi}s.
-This can be done using QEMU Chroot (change root).
-\url{https://wiki.archlinux.org/index.php/Raspberry_Pi}
+This can be done from any linux x86 machine using QEMU Chroot (change root).
+\url{https://wiki.debian.org/QemuUserEmulation}
+%\url{https://wiki.archlinux.org/index.php/Raspberry_Pi}
 
-\fxnote{Which packages is required for this on debian/ubuntu?}
-
-See the following link for information on this procedure:
-\url{https://wiki.archlinux.org/index.php/Raspberry_Pi}
+Due to the \ac{ARM} processor that \ac{Raspi}s are using, it is required to
+install some additional software:
+%Because \ac{Raspi}s are eqipped with an \ac{ARM} processor 
+%%it is not as
+%straightforward as performing the task for two linux systems of the same
+%architecture.
 
@@
 # apt-get install binfmt-support qemu qemu-user-static
-# update-binfmts --importdir /var/lib/binfmts/ --import
 # update-binfmts --display qemu-arm
+qemu-arm (enabled):
+     package = qemu-user-static
+        type = magic
+      offset = 0
+       magic = \x7fELF\x01\x01\x01\x00\x00\x00\x00\x00\x00\x00\x00\x00\x02\x00\x28\x00
+        mask = \xff\xff\xff\xff\xff\xff\xff\x00\xff\xff\xff\xff\xff\xff\xff\xff\xfe\xff\xff\xff
+ interpreter = /usr/bin/qemu-arm-static
+    detector = 
+\end{lstlisting}
+\FloatBarrier
+% This was neccessary on arch
+%# update-binfmts --importdir /var/lib/binfmts/ --import
+
+Make sure the second command writes "enabled" as the output above. If that 
+is not the case, then try enabling it:
+
+\begin{lstlisting}[]
 # update-binfmts --enable qemu-arm
@@
 \FloatBarrier
+
+Provided that qemu-arm is enabled, we should now be able to change root (chroot)
+into our Raspbian lite image. Change root is a method i linux that enables
+the root (/) to be changed. Thus, enabling a linux installation within a
+linux installation.
+
+There are a few commands to be performed before we can change root.
+First, to get internet access from within the Raspbian lite image it is needed
+to copy our resolv.conf into the filesystem. Line 1 steps into Raspbian lite's
+root filesystem. Then line 2 copies resolv.conf.
 
@@
 # cp /etc/resolv.conf etc/resolv.conf
+\end{lstlisting}
+\FloatBarrier
+
+Now, because of the ARM architecture, it is also required to copy
+/usr/bin/qemu-arm-static into the image before we can continue:
+
+% CHROOT to OS image
+\begin{lstlisting}[]
 # cp /usr/bin/qemu-arm-static usr/bin
+\end{lstlisting}
+\FloatBarrier
+
+The final preparation before chaning root is to populate the directories proc,
+sys, and dev:
+
+% CHROOT to OS image
+\begin{lstlisting}[]
 # mount -t proc proc proc/
@@
 # mount --rbind /dev dev/
-# proot -q qemu-arm-static -S ${ROOTDIR}
-
-ALTERNATIVE:
-# chroot ${ROOTDIR} /usr/bin/qemu-arm-static /bin/bash
 \end{lstlisting}
 \FloatBarrier
+
+Finally, the filesystem is ready for us to change root. This can be done with
+"proot". It may be required to install proot:
+
+% CHROOT to OS image
+\begin{lstlisting}[]
+# proot -q qemu-arm-static -S ${ROOTDIR}
+\end{lstlisting}
+\FloatBarrier
+
+Most available online material uses the more known chroot command as written in
+the code block below. This did not work correctly in our machines, but we show
+it as an alternative in case proot may not work on other systems.
+
+% CHROOT to OS image
+\begin{lstlisting}[]
+# chroot ${ROOTDIR} /usr/bin/qemu-arm-static /bin/bash    (ALTERNATIVE TO proot)
+\end{lstlisting}
+\FloatBarrier
+
+If everything went well, we should now be standing in the Raspbian lite filesystem
+under its root. Optionally, we can change the prompt title to indicate that we
+are chrooted:
 
@@
 \FloatBarrier
+
+The Raspbian lite system should now be possible to use as if it had been booted
+in a \ac{Raspi}. The only difference is that the laptop that we are using is
+significantly faster than a \ac{Raspi}. Thus enabling us to for example update,
+upgrade, and install software packages:
 
@@
 
-Lets install some programs
+Lets install some useful applications:
 % Install packages
@@
 \FloatBarrier
+
+All the changes that are made here will exists in all \ac{Raspi}s when the
+image is written to a memory card.
 

### 2016-06-04 testbed.tex
more testbed

@@
 
-See this link:
-\url{https://github.com/chesty/overlayroot}
+Our goal was to enable the users of the testbed to change however the
+\ac{Raspi} are configured while still being able to revert those changes easily.
 
-We use the code provided by
+We do this by storing a users work in the \ac{Raspi}s in \ac{RAM}. Thus a
+\ac{Raspi}, when a \ac{Raspi} is rebooted, it will forget all changes.
 
-Assumuing that we are still chrooted to the RPi image and the boot partition is mounted to /boot
+A way to do this is using stacked filesystem. Stacking filesystem enables
+a filesystem to overlay another filesystem. Whenever a file is accessed,
+the upper filesystem will forward the request to the lower filesystem in
+case it does not have it itself. If it has it, it will simpy return the file.
+
+This idea can be used in our setup to mount the root filesystem (i.e. Raspbian
+lite) in the \ac{Raspi}s duing startup as read-only. Thus, the files will not
+be changable. Some programs needs to change files and the testbed admin might
+want to change configurations. To enable this, it is possible to
+overlay a filesystem that is mounted in \ac{RAM} as read/writable on top of
+the regular root. Thus, reading a file may return a file from the lower filesytem,
+but if it is stored, it will be saved in the upper filesystem. Accessing this file
+again will return the stored file from the upper layer.
+
+%We do this using an overlay filesystem. The idea is to let the \ac{Raspi}s
+%mount their root filesystem as 
+%
+%We do this using an overlay filesystem (overlayfs).
+%Overlayfs enables a filesystem to be stacked on top of another filesystem. Thus,
+%if the \ac{Raspi}s mount their root filesystem (/) as read-onlyif we mount our root (/) filesystem as 
+%
+%
+%Overlayfs enables filesystems
+%to be stacked on top of each other. We will be using this to make a lower
+%filesystem and an upper filesystem. The lower filesystem will be our
+%traditional filesystem and the upper filesystem will be mounted in tmpfs
+%(i.e. mounted in \ac{RAM}).
+%
+%Thus, when a file is requsted from stacked filesystem, it will first attempt
+%to fetch the file in the upper filesystem if it does not exists there, it will
+%request it from the lower filessytem.
+
+Assuming that you are still chrooted into the Raspbian lite filesystem, we
+can setup the overlay filesystem (overlayfs).
+
+There already exists implementations overlaying the root filesystem. We will
+use an existing implementation
+available at github: \url{https://github.com/chesty/overlayroot}.
 

### 2016-06-04 testbed.tex
testbed needs some more work

@@
 
+We installed git in a previous step, so lets clone the repository. The below
+code stores it in /tmp which is really mounted in \ac{RAM}. Thus, the files
+will disappear when the machine is rebooted.
+
 % Get files
@@
 
+To enable the overlaying filesystem it is required to generate an initial \ac{RAM}
+file system (initramfs). Initramfs is an initial filesystem that gets loaded into
+\ac{RAM} during the startup process of a linux machine to prepare the real
+filesystem.
+
+For this purpose, we need BuxyBox:
+
 % Install required packages
@@
 \FloatBarrier
+
+Add and activate the overlaying filesystem, we need to add the scripts and tell initramfs
+to load the overlaying filesytem:
 
@@
 
+Raspbian lite uses a "u-boot" to boot, so it should be made aware of the
+initramfs that we will generate.
+
 % Tell uboot to load initramfs
@@
 
+Finally, lets generate the image. This is done using "mkinitramfs", that will
+by default look for the kernel modules of the current system. Remember we are
+chrooted, so we need to specify the correct kernel modules to look for. These
+can be found in "/lib/modules".
+
 % Create an initramfs
 \begin{lstlisting}[]
-# How to i know the kernel version /lib/modules/
+# ls /lib/modules/
+\end{lstlisting}
+\FloatBarrier
+
+For \ac{Raspi} 1, our kernel modules was "4.4.11+". The other modules in /lib/modules
+is for \ac{Raspi} 2.
+
+Thus, to run mkinitramfs, type in the correct kernel version:
+
+% Create an initramfs
+\begin{lstlisting}[]
 # mkinitramfs -o /boot/init.gz -k 4.4.11+
@@
 
+This should generate a new initial \ac{RAM} filesystem that will overlay a \ac{RAM} filesystem.
+
 \subsection{Write image}
+
+The final step is to write the image to all the memory cards before they can
+be plugged in the \ac{Raspi}s. This is done by first leaving the chrooted filesystem
+and unmounting all the directories we mounted:
 
@@
 # losetup -d WHICH_NUMBE.img
+\end{lstlisting}
+\FloatBarrier
+
+If successfully unmounted, you can insert a memory card in your machine. In our
+system, this memory card was available under /dev/mmcblk0, but this may be
+different on different machines. For internal memory card readers, it will
+probably be named /dev/mmcblkX where X is some number and if the memory card
+reader is connected through \ac{USB}, then it is likely called /dev/sdX.
+Make sure to write to the correct device as everything will be overwritten!
+
+Below is a few commands that may help you to deduce which device is correct:
+
+\begin{lstlisting}[]
+# lsblk
+# df -h
+\end{lstlisting}
+\FloatBarrier
+
+For us, the device was /dev/mmcblk0, so we write the image to that device:
+\begin{lstlisting}[]
 # dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M
@@
 
-How about kodo python?
+\subsection{Kodo python}
 

### 2016-06-04 metrics.tex
Metrics and Methodology done

@@
 \begin{align} \label{eq:goodput}
-R_{proc} = \frac{gB}{T_{proc}} ~ [\mathrm{Bytes/s}]
+R_{proc} = \frac{gB}{T_{proc}} ~ [\mathrm{Bytes/second}]
 \end{align}
@@
 much energy is expended to effectively transmit or receive 1 bit of bit
-considering the encoding or decoding respectively. This energy is computed
+considering the encoding or decoding respectively.
 
 For our energy measurement campaign, we automate the setup presented
-in Fig. \ref{fig:measurement_setup} to sequentially run a series of
-simulations for a given configuration of coding scheme and parameters,
-to estimate the energy consumption in both of our \ac{Raspi}
-models. A representative sketch of the setup is shown in the
-computer monitor in Fig. \ref{fig:measurement_setup}. The figure presents
-a \ac{Raspi} device whose power supply is an Agilent 66319D \ac{DC} source,
-instead of its conventional chorded supply. The output of the measurements
+in Fig.~\ref{fig:measurement_setup} to sequentially run a series of
+simulations for a given configuration of a coding scheme and its parameters,
+to estimate the energic expenditure in both of our \ac{Raspi}
+models. The energy measurement setup goal is to quantify the power
+consumption of the \ac{Raspi} over long periods of processing time to
+obtain accurate results. A representative sketch of the setup is shown
+in the computer monitor in Fig.~\ref{fig:measurement_setup}.
+
+The energy measurement setup presents a \ac{Raspi} device whose power
+supply is an Agilent 66319D \ac{DC} source, instead of a conventional
+power chord supply.   To compute the power, we just need to measure
+the current since the \ac{Raspi} feeds from a fixed input voltage of $5V$
+set by the Agilent device, but its current consumption is variable.
+Hence, the measured variable is the current consumed by the device for
+this fixed input voltage. The output of the measurements
 are later sent to a workstation where the raw measurement data is processed.
-The measured variable was the current consumed by the device for a fixed
-5V supply from the source. To identify each experiment, we classified the
-electrical current samples into two groups based on the magnitude. In our
-measurements, the groups to be reported are the idle current $I_{idle}$
-and the processing current $I_{proc}$. The former is the current the
-\ac{Raspi} requires while in idle state, meaning that no processing
-is being carried. The latter stands for the current needed during
-the encoding or decoding processing of the packets. The measurements
-where $I_{proc}$ is observed are made for a given configuration of
-coding scheme with its parameters. Finally, each simulation was enumerated
-to map the coding speed measurements with the corresponding energy
-consumption.
 
@@
 
+To identify each experiment, we classified the electrical current samples
+into two groups based on the magnitude. In our measurements, the groups to
+be reported are the idle current $I_{idle}$ and the processing current
+$I_{proc}$. The former is the current the \ac{Raspi} requires while in idle
+state, meaning that no processing is being carried. The latter stands for
+the current needed during the encoding or decoding processing of the packets.
+Measurements are taken either when $I_{idle}$ or $I_{proc}$ are observed.
+For the processing currents, its current measurements are made while the
+goodput benchmarks are running for a given configuration of a coding scheme
+with its parameters. For each configuration, $10^3$ simulations from the
+goodput benchmarks are carried during the period of time where $I_{proc}$
+occurs. We remark that a simulation is the conveying of $g$ \ac{l.i.} coded
+packets. Finally, for each configuration, each set of current measurements is
+enumerated to map it with its average power value and the corresponding goodput
+measurements. At post-processing, from the average power expenditure and the
+results from the goodput measurements it is possible to extract the energy
+per bit consumption. We elaborate further on this post-processing in the
+next subsections.
+
 \subsubsection{Average Power Expenditure}
-To extract the energy consumption of network coding, we subtracted the
-idle energy consumption from the energy consumption used during simulations.
-
+To extract the average power for a given configuration in our setup, we
+first calculate the average current in each the idle state $I_{idle,avg}$
+and the processing state $I_{idle,avg}$ for all the available sample for
+the given configuration. Regardless of the current type, the average value
+of the sample set of a given number of samples $N_s$ is:
 %
@@
 %
-
+With the average current from \eqref{eq:avg_current}, we compute the average
+current used for processing with respect to the idle state, by substracting
+$I_{idle,avg}$ from $I_{proc,avg}$. Then, the result is multiplied by the
+supply voltage to obtain the average power during the considered configuration,
+given as:
 %
@@
 \subsubsection{Energy per Bit Consumption}
+To get this metric for a given configuration, we simply express the energy
+as the product of the average power by the processing time $T_{proc}$ obtained
+from the goodput measurement for the same configuration. In this way, we can
+relate the processing time by the goodput, the packet and the generation size
+as shown:
 %
 \begin{align} \label{eq:goodput}
-E_b = P_{avg} T_{proc} = P_{avg} \times \frac{gB}{R_{proc}} ~[\mathrm{Joules/bit}]
+E_b = P_{avg} T_{proc} = P_{avg} \times \frac{g(B/8)}{R_{proc}} ~[\mathrm{Joules/bit}]
 \end{align}

### 2016-06-04 measurements.tex
Update Raspi acronym
Extracting the figures from the pdf does not look good

@@
 
-This section may be divided by subheadings. It should provide a concise and
-precise description of the experimental results, their interpretation as well
-as the experimental conclusions that can be drawn.
+With the testbed and setups from the previous sections, we
+proceed to obtain the measurements.
+
+\subsection{Goodput}
+Short intro
+
+\subsubsection{Encoding}
+\includepdf[pages={31-32,38,40}]{images/raspberry.pdf}
+
+\subsubsection{Decoding}
+\includepdf[pages={29-30,34,36}]{images/raspberry.pdf}
+
+\subsection{Average Power}
+Short section intro
+
+Raspberry One
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.7\textwidth]{images/current_vs_sec_raspberry_change_gen_from_-10sec_to_500sec.eps}
+\caption{Current measurements for the \ac{Raspi} 1}
+\label{current_rasp2}
+\end{figure}
+
+Raspberry Two
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.7\textwidth]{images/current_vs_sec_raspberry2_change_gen_from_-10sec_to_500sec.eps}
+\caption{Current measurements for the \ac{Raspi} 2}
+\label{current_rasp2}
+\end{figure}
+
+\subsection{Energy per bit}
 
@@
 The NEON extension provides an 128-bit \ac{SIMD} instruction set to the
-Raspberry Pi 2. Figures~\ref{enc_dec1024}, \ref{enc_dec128} and
+\ac{Raspi} 2. Figures~\ref{enc_dec1024}, \ref{enc_dec128} and
 \ref{enc_dec16} show the encoding and decoding throughput in MiB per
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_1024.pdf}
+\includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_1024.pdf}
 \caption{Encoding and Decoding performance for g = 1024 \cite{wunderlich2015network}}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_128.pdf}
+\includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_128.pdf}
 \caption{Encoding and Decoding performance for g = 128 \cite{wunderlich2015network}}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_16.pdf}
+\includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_16.pdf}
 \caption{Encoding and Decoding performance for g = 16 \cite{wunderlich2015network}}

### 2016-06-05 measurements.tex
Extract some figures for the results

@@
 \subsubsection{Encoding}
-\includepdf[pages={31-32,38,40}]{images/raspberry.pdf}
+%\includepdf[pages={31-32,38,40}]{images/raspberry.pdf}
+
+% \begin{figure}[ht!]
+% \centering
+% \includegraphics[width=0.7\textwidth]{}
+% \caption{Gooput measurements for the \ac{Raspi} 1. $q = 2$}
+% \label{goodput_enc_rasp1}
+% \end{figure}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.475\textwidth}
+        \centering
+        \includegraphics[width=1.3\textwidth]{images/rasp1_good_vs_g_enc_gf2.pdf}
+        \caption[]%
+        {{\small $q = 2$}}    
+        \label{fig:mean and std of net14}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.475\textwidth}  
+        \centering 
+        \includegraphics[width=\textwidth]{images/rasp1_good_vs_g_enc_gf256.pdf}
+        \caption[]%
+        {{\small $q = 2^8$}}    
+        \label{fig:mean and std of net24}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=\textwidth]{images/rasp1_good_vs_B_enc_gf2.pdf}
+        \caption[]%
+        {{\small $q = 2$}}    
+        \label{fig:mean and std of net34}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=\textwidth]{images/rasp1_good_vs_B_enc_gf256.pdf}
+        \caption[]%
+        {{\small $q = 2^8$}}    
+        \label{fig:mean and std of net44}
+    \end{subfigure}
+    \caption[ The average and standard deviation of critical parameters ]
+    {\small The average and standard deviation of critical parameters: Region R4} 
+    \label{fig:mean and std of nets}
+\end{figure*}
 
 \subsubsection{Decoding}
-\includepdf[pages={29-30,34,36}]{images/raspberry.pdf}
+%\includepdf[pages={29-30,34,36}]{images/raspberry.pdf}
 

### 2016-06-05 metrics.tex
Extract some figures for the results

@@
 from the goodput measurement for the same configuration. In this way, we can
-relate the processing time by the goodput, the packet and the generation size
+relate the processing time with the goodput, the packet and the generation size
 as shown:
@@
 \begin{align} \label{eq:goodput}
-E_b = P_{avg} T_{proc} = P_{avg} \times \frac{g(B/8)}{R_{proc}} ~[\mathrm{Joules/bit}]
+E_b = P_{avg} T_{proc} = P_{avg} \times \frac{g(8B)}{R_{proc}} ~[\mathrm{Joules}]
 \end{align}

### 2016-06-05 measurements.tex
Some updates

@@
         \centering
-        \includegraphics[width=1.3\textwidth]{images/rasp1_good_vs_g_enc_gf2.pdf}
+        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf2.pdf}
         \caption[]%
@@
         \centering 
-        \includegraphics[width=\textwidth]{images/rasp1_good_vs_g_enc_gf256.pdf}
+        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf256.pdf}
         \caption[]%
@@
         \centering 
-        \includegraphics[width=\textwidth]{images/rasp1_good_vs_B_enc_gf2.pdf}
+        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf2.pdf}
         \caption[]%
@@
         \centering 
-        \includegraphics[width=\textwidth]{images/rasp1_good_vs_B_enc_gf256.pdf}
+        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf256.pdf}
         \caption[]%
@@
     \caption[ The average and standard deviation of critical parameters ]
-    {\small The average and standard deviation of critical parameters: Region R4} 
+    {\small Encoder goodput measurements for the \ac{Raspi} 1} 
     \label{fig:mean and std of nets}

### 2016-06-05 testbed.tex
Updating cross compiling

@@
 \begin{lstlisting}[]
-$ wget http://kom.aau.dk/project/TuneSCode/rasp_config.zip
+$ wget http://kom.aau.dk/project/TuneSCode/raspi/rasp_config.zip
 # unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
@@
 
-\item Download the \ac{Raspi} toolchain for 64-bit Linux from: \\
-\texttt{http://buildbot.steinwurf.dk/toolchains/linux/} to your
-\texttt{\$HOME} directory. \\
+\item Create toolchain directory:
+\begin{lstlisting}[]
+$ TOOLCHAINDIR="${HOME}/toolchains"
+$ mkdir -p $TOOLCHAINDIR
+$ cd $TOOLCHAINDIR
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
 
-\item Extract the downloaded file locally in the NFS server. After
-this operation, there should be a new directory for the toolchain
-in the server. \\
+\item Download the \ac{Raspi} toolchain for 64-bit Linux from.
+A more recent \ac{Raspi} toolchain may be available at
+\texttt{http://buildbot.steinwurf.dk/toolchains/linux/}:
 
-\item Add the \texttt{bin} folder of the toolchain to the \texttt{PATH}
-Linux environment variable of the server. This will help the server OS
-to recognize the location of the compiler command, which will be needed
-later. To do so, edit the \texttt{\$HOME/.profile} to add in a newline:
-\texttt{PATH="\$PATH:\$HOME/raspberry-gxx49-arm/bin"}. Save the
-\texttt{\$HOME/.profile}. \\
+\begin{lstlisting}[]
+$ TOOLCHAIN="raspberry-gxx49-arm"
+$ wget http://kom.aau.dk/project/TuneSCode/raspi/${TOOLCHAIN}.zip
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
 
-\item Restart the server session in order for the changes made in the
-previous step take effect. To verify this, open a new terminal and type:
-\texttt{raspberry-gxx49-arm-g++ --version}. A correct binary installation
-should return an output similar to:
+\item Extract the downloaded file:
+%locally in the NFS server. After
+%this operation, there should be a new directory for the toolchain
+%in the server. \\
+\begin{lstlisting}[]
+$ unzip ${TOOLCHAIN}.zip
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
 
-\texttt{raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
+\item (Optional) Delete zip file:
+%locally in the NFS server. After
+%this operation, there should be a new directory for the toolchain
+%in the server. \\
+\begin{lstlisting}[]
+$ rm ${TOOLCHAIN}.zip
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\item We can now verify that the ARM cross compiler is working:
+
+\begin{lstlisting}[]
+$ ${TOOLCHAINDIR}/${TOOLCHAIN}/bin/${TOOLCHAIN}-g++ --version
+raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
 Copyright (C) 2014 Free Software Foundation, Inc.
 This is free software; see the source for copying conditions.  There is NO
-warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.} \\
+warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+%\begin{lstlisting}[]
+%$ echo "${TOOLCHAINDIR}/${TOOLCHAIN}/bin/${TOOLCHAIN}-g++"
+%/home/<USER>/toolchains/raspberry-gxx49-arm/bin/raspberry-gxx49-arm-g++
+%\end{lstlisting}
+%\FloatBarrier
+%\vspace{-5mm}
+
+%    The ARM cross compilers should now be located in
+
+\item Make toolchain binaries available systemwide. Instead of calling
+the ARM cross compiler using its full path, we can make it accessible
+from the command shell systemwide. One way to do this is by adding the 
+toolchain binaries directory to the Linux environment variable \texttt{PATH}
+when the \ac{OS} starts up:
+
+%\item Add toolchain binaries to \texttt{PATH}. Instead specifying the full
+%path to the toolchain binaries we can instead tell the operation system
+%where to search for it. This makes the toolchain binaries available
+%systemwide.
+
+\begin{lstlisting}[]
+$ echo PATH=\"\$PATH:${TOOLCHAINDIR}/${TOOLCHAIN}/bin\" >> ${HOME}/.profile
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+%$ printf 'PATH="%s/%s/bin"\n' "${TOOLCHAINDIR}" "${TOOLCHAIN}" >> ${HOME}/.profile
+
+%\item Add the \texttt{bin} folder of the toolchain to the \texttt{PATH}
+%Linux environment variable of the server. This will help the server OS
+%to recognize the location of the compiler command, which will be needed
+%later. To do so, edit the \texttt{\$HOME/.profile} to add in a newline:
+%\texttt{PATH="\$PATH:\$HOME/raspberry-gxx49-arm/bin"}. Save the
+%\texttt{\$HOME/.profile}. \\
+
+\texttt{~/.profile} should now contain the line we inserted. There may be more
+code in you file.
+% MAC and Hostname file
+\Suppressnumber\begin{lstlisting}[]
+<@\textcolor{gray}{\$HOME/.profile}@>
+<@\textcolor{gray}{
+---------------------------------------------------------------}
+\Reactivatenumber @>
+PATH="$PATH:/home/<USERNAME>/toolchains/raspberry-gxx49-arm/bin"
+\end{lstlisting}
+\FloatBarrier
+
+\item Update \texttt{PATH}. Source \texttt{~/.profile} to make the changes
+take effect in your system:
+\begin{lstlisting}[]
+$ source ${HOME}/.profile
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\item ARM cross compiler should now be available systemwide:
+
+\begin{lstlisting}[]
+$ raspberry-gxx49-arm-g++ --version
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+%\item Restart the server session in order for the changes made in the
+%previous step take effect. To verify this, open a new terminal and type:
+%\texttt{raspberry-gxx49-arm-g++ --version}. A correct binary installation
+%should return an output similar to:
+%
+%\texttt{raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
+%Copyright (C) 2014 Free Software Foundation, Inc.
+%This is free software; see the source for copying conditions.  There is NO
+%warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.} \\
 

### 2016-06-05 upload_rasp_config.sh

@@ -1,5 +1,5 @@
 #!/usr/bin/env bash
 
 zip -r rasp_config rasp_config
-scp rasp_config.zip js3:/afs/ies.auc.dk/project/TuneSCode/public_html/
+scp rasp_config.zip js3:/afs/ies.auc.dk/project/TuneSCode/public_html/raspi/
 rm rasp_config.zip

### 2016-06-05 testbed.tex
worked on testbed

@@
 \begin{lstlisting}[]
-# apt-get install vim git
+# apt-get install vim git screen
 \end{lstlisting}
@@
 
-\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
+\section{Cross-compilation: From PC to Raspberry Pi}
+
+%\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
+
+\subsection{Install toolchain on PC}
 
@@
 
-\texttt{~/.profile} should now contain the line we inserted. There may be more
+\texttt{.profile} should now contain the line we inserted. There may be more
 code in you file.
@@
 
-\item Update \texttt{PATH}. Source \texttt{~/.profile} to make the changes
+\item Update \texttt{PATH}. Source \texttt{.profile} to make the changes
 take effect in your system:
@@
 %warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.} \\
+
+\end{enumerate}
+
+\subsection{Cross compile example}
+
+Create a directory to hold our code:
+\begin{lstlisting}[]
+$ CODEDIR="${HOME}/code"
+$ mkdir -p ${CODEDIR}
+$ cd ${CODEDIR}
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Create a \texttt{hello\_world.cpp} using your favorite text editor:
+
+\Suppressnumber\begin{lstlisting}[]
+<@\textcolor{gray}{\${CODEDIR}/hello\_world.cpp}@>
+<@\textcolor{gray}{
+---------------------------------------------------------------}
+\Reactivatenumber @>
+#include <iostream>
+
+int main()
+{
+    std::cout << "Hello World!" << std::endl;
+    return 0;
+}
+\end{lstlisting}
+\FloatBarrier
+
+Save \texttt{hello\_world.cpp} and compile it for \ac{Raspi}:
+
+\begin{lstlisting}[]
+$ raspberry-gxx49-arm-g++ hello_world.cpp -o hello_world
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Lets copy the executable file to a \ac{Raspi} and test it. We will use \ac{SCP}
+to copy the executable to one of the \ac{Raspi}s.
+
+Default username is "pi" and password is "raspberry"
+
+\begin{lstlisting}[]
+$ scp main pi:<RASP_IP>:~/
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+If you do not know the \ac{IP} address of a \ac{Raspi} in your network, you can
+connect a monitor to it and run the following command after you have logged in:
+\begin{lstlisting}[]
+pi@rasp01:~ $ ifconfig
+eth0      Link encap:Ethernet  HWaddr b8:27:eb:72:77:54  
+          inet addr:192.168.87.107  Bcast:192.168.87.255  Mask:255.255.255.0
+          inet6 addr: fe80::e0a5:38f3:6f82:bc79/64 Scope:Link
+          UP BROADCAST RUNNING MULTICAST  MTU:1500  Metric:1
+          RX packets:1537 errors:0 dropped:0 overruns:0 frame:0
+          TX packets:445 errors:0 dropped:0 overruns:0 carrier:0
+          collisions:0 txqueuelen:1000 
+          RX bytes:259117 (253.0 KiB)  TX bytes:52551 (51.3 KiB)
+
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+After the executable has been copied to a \ac{Raspi}. Then, \ac{SSH} to it:
+
+\begin{lstlisting}[]
+$ ssh pi:<RASP_IP>
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+We can list the directory content after we have logged into the \ac{Raspi} and
+see that \texttt{hello\_world} is there:
+
+\begin{lstlisting}[]
+pi@rasp07:~ $ ls
+hello_world  rasp_config
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Now, simply execute the \texttt{hello\_world}:
+
+\begin{lstlisting}[]
+pi@rasp07:~ $ ./hello_world
+Hello World!
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\subsection{Long running jobs over SSH (PUT THIS SECTION SOMEWHERE ELSE)}
+
+Problem when you logout, then applications will terminate. SCREEN is the answer.
+
+EXAMPLE
+
+\texttt{hello\_world} returns immediately. This is not always the case.
+Sometimes it is desired to run simulations that should run for days. 
+A software package called \texttt{screen} can be used for this purpose.
+Simply run ...
+
+\subsection{Cross compile Kodo}
+
+\begin{enumerate}
 

### 2016-06-05 measurements.tex
Details about measurements setup

@@
 
-With the testbed and setups from the previous sections, we
-proceed to obtain the measurements.
+With the testbed, methodology and setups from the previous sections, we
+proceed to obtain the measurements for the \ac{Raspi} 1 and 2 platforms.
+We consider the following set of parameters for our study:
+For all the codes, we use $g = [16,\ 32,\ 64,\ 128,\ 256,\ 512]$
+and $q = [2,\ 2^8]$. For the non-optimized multicore implementations
+and cases when the generation size is varied $B = 1600\ bytes$.
+We consider a setup where we only vary the packet size,
+$B = [64,\ 128,\ 256,\ 512,\ 1024,\ 2048,\ 4096,\ 8192,\ 16384,\ 32768
+,\ 65536,\ 131072]\ bytes$ with a generation size fixed on $g = [16,\ 128]$
+to see computing load that the \ac{Raspi} present in the low and high
+packet size regimes. We considered $B = 1536\ bytes$ for the optimized
+multicore implementation. For \ac{SRLNC}, we considered
+$d = [0.02,\ 0.1]$. For \ac{TSNC}, we considered excess packets,
+$e = [8,\ 16]$, so that the budget is simply $b = g + e$. In all our
+measurement reports, to simplify their review, we first presents the
+results for the \ac{Raspi} 1 and later continue with the \ac{Raspi} 2.
 
 \subsection{Goodput}
-Short intro
+For the goodput, we separate the results according to their time benchmarks
+as we did in Section \ref{sec:metrics} sicne their consider different
+methodologies. We proceed first with the measurements related to the encoder
+and later review the case of the decoder.
 
 \subsubsection{Encoding}
-%\includepdf[pages={31-32,38,40}]{images/raspberry.pdf}
-
-% \begin{figure}[ht!]
-% \centering
-% \includegraphics[width=0.7\textwidth]{}
-% \caption{Gooput measurements for the \ac{Raspi} 1. $q = 2$}
-% \label{goodput_enc_rasp1}
-% \end{figure}
+Figs. \ref{fig:}
 
@@
         \caption[]%
-        {{\small $q = 2$}}    
+        {{\small Goodput vs. Generation size for $GF(2)$}}    
         \label{fig:mean and std of net14}
@@
         \caption[]%
-        {{\small $q = 2^8$}}    
+        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
         \label{fig:mean and std of net24}
@@
         \caption[]%
-        {{\small $q = 2$}}    
+        {{\small Goodput vs. Packet size for $GF(2)$}}    
         \label{fig:mean and std of net34}
@@
         \caption[]%
-        {{\small $q = 2^8$}}    
+        {{\small Goodput vs. Packet size for $GF(2^8)$}}    
         \label{fig:mean and std of net44}
     \end{subfigure}
-    \caption[ The average and standard deviation of critical parameters ]
+    \caption[]
     {\small Encoder goodput measurements for the \ac{Raspi} 1} 
-    \label{fig:mean and std of nets}
+    \label{fig:enc_good_rasp1}
 \end{figure*}
@@
 \subsubsection{Decoding}
-%\includepdf[pages={29-30,34,36}]{images/raspberry.pdf}
 

### 2016-06-05 introduction.tex
wrote introduction. Added \newcommand TODO to the main.tex

@@
-At the beginning, there was darkness and then... bang! \ac{NC}
-\cite{ahlswede2000network} appeared to save us from the evilness
-of routing.
+%!TEX root = raspi_journal.tex
+% At the beginning, there was darkness and then... bang! \ac{NC}
+% \cite{ahlswede2000network} appeared to save us from the evilness
+% of routing.
+%
+% General introduction. Introduction to topic addressed in the journal.
+% Review of the State of the Art. Specify why our approach has benefits
+% and which are they. Indicate contributions.
 
-General introduction. Introduction to topic addressed in the journal.
-Review of the State of the Art. Specify why our approach has benefits
-and which are they. Indicate contributions.
+% INTRODUCTION TO NETWORK CODING
+Network coding is a novel and disruptive technology introduced in the year
+2000~\cite{ahlswede2000network}. It has imposed a change of paradigm in the way
+how researchers and industry alike interpret networks and, more specifically,
+the role of intermediate relays in the process of transmission of information.
+The key element is that it allows relays to be part of the coding process
+enabling the recoding (i.e., to produce linear combinations without a previous
+decoding process) of the received packets. The recoding process disrupts with
+the traditional routing (store and forward) strategies in today's networks,
+including the Internet \todot{a citation here?}. Network coding allows the
+increase of throughput, reliability, security and delay performance of the
+networks. In its initial conception, the relays would combine and transfer
+packets of different flows, while in later applications of the technology, both
+the sources and the relays would form linear combinations of packets within the
+same information flow.
 
-Our work is organized as follows: Section \ref{sec:testbed} introduces
-the testbed system, its setup, connectivity, files configuration and
-compilation of the Kodo library. Section \ref{sec:schemes} defines the
-coding schemes employed in our study. Later, in Section \ref{sec:metrics}
-we describe the considered metrics for performance comparison of the
-codes deployed in the \ac{Raspi}. In Section \ref{sec:measurements}, we show
-the measurements in the \ac{Raspi} of the mentioned metrics. Final
-conclusions and future work are reviewed in Section \ref{sec:conclusions}.
+Differently from other broadly used coding schemes (e.g., Gallager's
+codes~\cite{gallager1962low}, Reed-Solomon codes~\cite{reed1960polynomial}),
+network coding is a technology that has been implemented in real systems since
+the early years of its conception. Only six years later, in 2006, Katabi et
+al.~\cite{katabi2006practical} published the results of the performance of their
+protocol COPE when implemented in a real wireless system\todot{is there any
+previous implementation?}. Similarly, in 2008, Pedersen et
+al.~\cite{pedersen2008implementation} used commercially available Symbian OS
+enabled mobile phones to implement network coding in a \ac{D2D} cooperation
+application. In 2011, researchers at Aalborg University in Denmark developed
+KODO~\cite{kodo2011pedersen}, a C++ network coding library with open source code
+for researchers intended to make network coding implementations easily available
+for both, the research community and commercial entities.
+CATWOMAN~\cite{hundeboll2012catwoman} is a protocol implemented in 2012 on IEEE
+802.11 based multi-hop meshed networks. It uses network coding to improve the
+throughput of meshed networks established using the
+B.A.T.M.A.N.~\cite{johnson2008simple} routing protocol. It is currently
+available as open source code and part of the Linux kernel. Also in 2012,
+Pahlevani et al. implemented PlayNCool~\cite{pahlevani2013playncool} as an
+opportunistic protocol that increases the throughput of a wireless mesh network
+by using network coding and local optimization. Similarly, many other
+implementations have been tested on real world systems~
+\cite{katti2008xors,krigslund2013core,paramanathan2013leanandmean}.
+
+It is then undeniable that network coding theory has always been hand to hand
+with practical implementations. However, each one of the previously tested
+protocols has been implemented in a separate, somehow hard to reproduce,
+testbed. Given the previous importance of practical testbeds for this particular
+technology, the needs for reproducibility of past and future results among
+researchers, and the needs of low-cost and easy-to-deploy testbeds, this paper
+aims to solve those needs. In this work, the authors contribute to the research
+community by providing detailed instructions on how to set up a low-cost,
+heterogeneous and scalable testbed consisting of Raspberry Pis (Raspis), and by
+providing detailed measurements of goodput and energy consumption of such
+testbed when performing network coding operations with different codecs (such as
+full RLNC, multicore-enabled RLNC, sparse RLNC and tunable sparse RLNC). The
+goals are \textbf{i)} to provide information on how to easily build and deploy a
+low-cost testbed for researchers and industry alike in order to test and
+implement their network coding related protocols; and \textbf{ii)} to provide
+information on the expected performance in terms of energy and goodput of such
+testbed while covering a wide range of codecs.
+
+The heterogeneity of the testbed comes from the fact that old, single core,
+Raspis (i.e., Raspberry Pi 1 model B) are integrated seamlessly in the described
+testbed together with newer, multicore versions (i.e., Raspberry Pi 2 model B).
+The testbed is scalable because tenths or hundreds of Raspis can be connected
+together with the described method. And it is low-cost because Raspis represent
+a low fraction of the cost of laptops, desktop computers or other similar
+devices. \todot{is all of this true"?}
+
+Our work is organized as follows: Section~\ref{sec:testbed} introduces the
+testbed system, its setup, connectivity, files configuration and compilation of
+the Kodo library. Section~\ref{sec:schemes} defines the coding schemes employed
+in our study. Later, in Section~\ref{sec:metrics} we describe the considered
+metrics for performance comparison of the codes deployed in the \ac{Raspi}. In
+Section~\ref{sec:measurements}, we show the measurements in the \ac{Raspi} of
+the mentioned metrics. Final conclusions and future work are reviewed in
+Section~\ref{sec:conclusions}.
 

### 2016-06-05 measurements.tex
Use the ideal plots

@@
 \subsubsection{Encoding}
-Figs. \ref{fig:}
+
+Fig. \ref{fig:enc_good_rasp1} shows the results of the encoder goodput measurements
+for the \ac{Raspi} 1.
 
@@
         \centering
-        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf2.pdf}
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_encoder_Binary_1600.eps}
         \caption[]%
         {{\small Goodput vs. Generation size for $GF(2)$}}    
-        \label{fig:mean and std of net14}
+        \label{fig:enc_good_rasp1_gen_gf2}
     \end{subfigure}
@@
         \centering 
-        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf256.pdf}
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_encoder_Binary8_1600.eps}
         \caption[]%
         {{\small Goodput vs. Generation size for $GF(2^8)$}}    
-        \label{fig:mean and std of net24}
+        \label{fig:enc_good_rasp1_gen_gf256}
     \end{subfigure}
@@
         \centering 
-        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf2.pdf}
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_encoder_Binary_16.eps}
         \caption[]%
         {{\small Goodput vs. Packet size for $GF(2)$}}    
-        \label{fig:mean and std of net34}
+        \label{fig:enc_good_rasp1_packet_gf2}
     \end{subfigure}
@@
         \centering 
-        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf256.pdf}
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_encoder_Binary8_16.eps}
         \caption[]%
         {{\small Goodput vs. Packet size for $GF(2^8)$}}    
-        \label{fig:mean and std of net44}
+        \label{fig:enc_good_rasp1_packet_gf2}
     \end{subfigure}

### 2016-06-05 testbed.tex

@@
 
+WRITE SOMETHING ABOUT THIS AND MENTION HOW TO REQUEST A KODO LICENSE
+
 \begin{enumerate}
 
-\item Clone the Kodo repository in the server by executing: \\
-\texttt{git clone git://github.com/steinwurf/kodo.git} in \texttt{\$HOME}.
-\textbf{Change the repo to kodo-rlnc or kodo-cpp since just raw kodo is going
-to be depreceated soon} \\
+\item Create a directory to hold our code:
+\begin{lstlisting}[]
+$ CODEDIR="${HOME}/code"
+$ mkdir -p ${CODEDIR}
+$ cd ${CODEDIR}
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\item Clone the Kodo repository and change directory into the repository: \\
+\begin{lstlisting}[]
+$ git clone https://github.com/steinwurf/kodo-cpp.git
+$ cd kodo-cpp
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\item Configure Kodo to build executables for the \ac{ARM} architecture using our toolchain:
+\begin{lstlisting}[]
+$ python waf configure --cxx_mkspec=cxx_raspberry_gxx49_arm
+...
+'configure' finished successfully (0.620s)
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\item Build executables:
+\begin{lstlisting}[]
+$ python waf build
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
 

### 2016-06-05 testbed.tex
more testbed

@@
 
-\subsection{Kodo python}
-
-\subsection{fabric}
-
-% Exit chroot, umount, and write to memory card
-\begin{lstlisting}[]
-from fabric.api import run, env, task
-# Python Fabric script to run commands on multiple hosts through ssh
-#
-# Run script as 'fab <task>', where <task> is one of the scripts functions
-# marked as a tesk. The task marked as 'default' will be run if <task> is not
-# specified
-
-env.hosts = ['rasp00.domain.com','rasp01.domain.com','rasp02.domain.com']
-env.user = 'root'
-env.password = 'sdn'
-
-@task
-def install(program):
-    """
-    Install a program
-    program: program name
-    """
-    result = run('apt-get install -y {}'.format(program), quiet=True)
-
-@task
-def copy_to_rasp(filename):
-    put(...)
-
-\end{lstlisting}
-\FloatBarrier
-
-execute a script function by calling "fab install:feh"
-
 \section{Cross-compilation: From PC to Raspberry Pi}
@@
 
-\subsection{Long running jobs over SSH (PUT THIS SECTION SOMEWHERE ELSE)}
-
-Problem when you logout, then applications will terminate. SCREEN is the answer.
-
-EXAMPLE
-
-\texttt{hello\_world} returns immediately. This is not always the case.
-Sometimes it is desired to run simulations that should run for days. 
-A software package called \texttt{screen} can be used for this purpose.
-Simply run ...
-
 \subsection{Cross compile Kodo}
 
-WRITE SOMETHING ABOUT THIS AND MENTION HOW TO REQUEST A KODO LICENSE
+WRITE SOME SMALL INTRO AND MENTION HOW TO REQUEST A KODO LICENSE
 
@@
 $ python waf build
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-\item Navigate to the repository and configure \texttt{waf} by typing:
-\texttt{python config.py} and select the 16th ``make specification'' file
-for the \ac{Raspi}, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
-presented by the file.
-
-This command configures \texttt{waf} to use the proper compiler and its
-required flags to generate the binaries for the \ac{Raspi}. If the
-configuration was correct, the output will indicate:
-\texttt{'configure' finished successfully (X.XXXs)}, where \texttt{X.XXX}
-is total time in seconds for configuring the project in the server. \\
-
-\item Execute \texttt{python waf build}. If the build process was
-successful, the generated binaries for the \ac{Raspi} should be located
-in \texttt{build/cxx\_raspberry\_gxx49\_arm} in the Kodo repository.
-\textbf{Indicate how the binary files should look like}.
-
-Once this procedure is made, the testbed administrator can relocate the
-generated binary files to the \ac{Raspi}s through the network as desired
-by using the \texttt{scp} command during the configuration step.
+...
+'build' finished successfully (2m22.918s)
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\item SHARED and/or STATIC libraries
+\item COPY TO RASPI
+\item RUN EXECUTABLE encode\_decode\_simple
+
+%\item Navigate to the repository and configure \texttt{waf} by typing:
+%\texttt{python config.py} and select the 16th ``make specification'' file
+%for the \ac{Raspi}, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
+%presented by the file.
+%
+%This command configures \texttt{waf} to use the proper compiler and its
+%required flags to generate the binaries for the \ac{Raspi}. If the
+%configuration was correct, the output will indicate:
+%\texttt{'configure' finished successfully (X.XXXs)}, where \texttt{X.XXX}
+%is total time in seconds for configuring the project in the server. \\
+%
+%\item Execute \texttt{python waf build}. If the build process was
+%successful, the generated binaries for the \ac{Raspi} should be located
+%in \texttt{build/cxx\_raspberry\_gxx49\_arm} in the Kodo repository.
+%\textbf{Indicate how the binary files should look like}.
+%
+%Once this procedure is made, the testbed administrator can relocate the
+%generated binary files to the \ac{Raspi}s through the network as desired
+%by using the \texttt{scp} command during the configuration step.
 
@@
 at \cite{kododocs}.
+
+\subsection{Long running jobs over SSH (PUT THIS SECTION SOMEWHERE ELSE)}
+
+Problem when you logout, then applications will terminate. SCREEN is the answer.
+
+EXAMPLE
+
+\texttt{hello\_world} returns immediately. This is not always the case.
+Sometimes it is desired to run simulations that should run for days. 
+A software package called \texttt{screen} can be used for this purpose.
+Simply run ...
+
+\subsection{Kodo python}
+
+WRITE HOW TO RUN A KODO PYTHON SCRIPT IN THE RASPIS
+
+\subsection{fabric}
+
+SHORT INTRO. EXPLAIN A FEW USECASES FOR FABRIC. E.G. REBOOT, INSTALL PACKAGE, RUN SCRIPT ON MULTIPLE RASPIS. COPY FILES TO/FROM PC AND MULTIPLE RASPIS
+
+% Exit chroot, umount, and write to memory card
+\begin{lstlisting}[]
+from fabric.api import run, env, task
+# Python Fabric script to run commands on multiple hosts through ssh
+#
+# Run script as 'fab <task>', where <task> is one of the scripts functions
+# marked as a tesk. The task marked as 'default' will be run if <task> is not
+# specified
+
+env.hosts = ['rasp00.domain.com','rasp01.domain.com','rasp02.domain.com']
+env.user = 'root'
+env.password = 'sdn'
+
+@task
+def install(program):
+    """
+    Install a program
+    program: program name
+    """
+    result = run('apt-get install -y {}'.format(program), quiet=True)
+
+@task
+def copy_to_rasp(filename):
+    put(...)
+
+\end{lstlisting}
+\FloatBarrier
+
+execute a script function by calling "fab install:feh"

### 2016-06-05 measurements.tex
Setting goodput plots

@@
 and $q = [2,\ 2^8]$. For the non-optimized multicore implementations
-and cases when the generation size is varied $B = 1600\ bytes$.
+and cases when the generation size is varied $B = 1600$ bytes.
 We consider a setup where we only vary the packet size,
 $B = [64,\ 128,\ 256,\ 512,\ 1024,\ 2048,\ 4096,\ 8192,\ 16384,\ 32768
-,\ 65536,\ 131072]\ bytes$ with a generation size fixed on $g = [16,\ 128]$
+,\ 65536,\ 131072]$ bytes with a generation size fixed on $g = [16,\ 128]$
 to see computing load that the \ac{Raspi} present in the low and high
-packet size regimes. We considered $B = 1536\ bytes$ for the optimized
+packet size regimes. We considered $B = 1536$ bytes for the optimized
 multicore implementation. For \ac{SRLNC}, we considered
@@
 
-Fig. \ref{fig:enc_good_rasp1} shows the results of the encoder goodput measurements
-for the \ac{Raspi} 1.
+Fig. \ref{fig:enc_good_rasp1} shows the results of the encoder goodput
+measurements for the \ac{Raspi} 1. Figs. \ref{fig:enc_good_rasp1_gen_gf2}
+and \ref{fig:enc_good_rasp1_gen_gf256} present goodput as function of the
+generation size for $GF(2)$ and $GF(2^8)$ respectively for a packet size
+of $B = 1600$ bytes. Figs. \ref{fig:enc_good_rasp1_packet_gf2} and 
+\ref{fig:enc_good_rasp1_packet_gf256} present the same metric but now as
+function of the packet size for $GF(2)$ and $GF(2^8)$ respectively. In this
+case the gneation size was set to $g = 16$ packets.
 
@@
         \caption[]%
-        {{\small Goodput vs. Packet size for $GF(2)$}}    
+        {{\small Goodput vs. Packet size for $GF(2)$ and $g=16$}}    
         \label{fig:enc_good_rasp1_packet_gf2}
@@
         \caption[]%
-        {{\small Goodput vs. Packet size for $GF(2^8)$}}    
-        \label{fig:enc_good_rasp1_packet_gf2}
+        {{\small Goodput vs. Packet size for $GF(2^8)$ and $g=16$}}    
+        \label{fig:enc_good_rasp1_packet_gf256}
     \end{subfigure}
@@
 
+Similarly, Fig. \ref{fig:enc_good_rasp2} shows the same set of
+measurements for the \ac{Raspi} 2. Hence, Figs. \ref{fig:enc_good_rasp2_gen_gf2}
+and \ref{fig:enc_good_rasp2_gen_gf256} present goodput as function of the
+generation size  and Figs. \ref{fig:enc_good_rasp2_packet_gf2} and 
+\ref{fig:enc_good_rasp2_packet_gf256} as a function of the packet size for the
+same cases mentioned previously.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.475\textwidth}
+        \centering
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary_1600.eps}
+        \caption[]%
+        {{\small Goodput vs. Generation size for $GF(2)$}}    
+        \label{fig:enc_good_rasp2_gen_gf2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.475\textwidth}  
+        \centering 
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary8_1600.eps}
+        \caption[]%
+        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
+        \label{fig:enc_good_rasp2_gen_gf256}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary_16.eps}
+        \caption[]%
+        {{\small Goodput vs. Packet size for $GF(2)$ and $g=16$}}    
+        \label{fig:enc_good_rasp2_packet_gf2}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary8_16.eps}
+        \caption[]%
+        {{\small Goodput vs. Packet size for $GF(2^8)$ and $g=16$}}    
+        \label{fig:enc_good_rasp2_packet_gf256}
+    \end{subfigure}
+    \caption[]
+    {\small Encoder goodput measurements for the \ac{Raspi} 2} 
+    \label{fig:enc_good_rasp2}
+\end{figure*}
+
+Figures description
+
 \subsubsection{Decoding}
+
+We perform the same evaluation as before but now we focus on the decoder.
+Fig. \ref{fig:dec_good_rasp1} shows the results of the decoder goodput
+measurements for the \ac{Raspi} 1. and \ref{fig:dec_good_rasp2} does
+the proper for \ac{Raspi} 2.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.475\textwidth}
+        \centering
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_decoder_Binary_1600.eps}
+        \caption[]%
+        {{\small Goodput vs. Generation size for $GF(2)$}}    
+        \label{fig:dec_good_rasp1_gen_gf2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.475\textwidth}  
+        \centering 
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_decoder_Binary8_1600.eps}
+        \caption[]%
+        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
+        \label{fig:dec_good_rasp1_gen_gf256}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_decoder_Binary_16.eps}
+        \caption[]%
+        {{\small Goodput vs. Packet size for $GF(2)$ and $g=16$}}    
+        \label{fig:dec_good_rasp1_packet_gf2}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_decoder_Binary8_16.eps}
+        \caption[]%
+        {{\small Goodput vs. Packet size for $GF(2^8)$ and $g=16$}}    
+        \label{fig:dec_good_rasp1_packet_gf256}
+    \end{subfigure}
+    \caption[]
+    {\small Encoder goodput measurements for the \ac{Raspi} 1} 
+    \label{fig:dec_good_rasp1}
+\end{figure*}
+
+Description
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.475\textwidth}
+        \centering
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_decoder_Binary_1600.eps}
+        \caption[]%
+        {{\small Goodput vs. Generation size for $GF(2)$}}    
+        \label{fig:dec_good_rasp2_gen_gf2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.475\textwidth}  
+        \centering 
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_decoder_Binary8_1600.eps}
+        \caption[]%
+        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
+        \label{fig:dec_good_rasp2_gen_gf256}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_decoder_Binary_16.eps}
+        \caption[]%
+        {{\small Goodput vs. Packet size for $GF(2)$ and $g=16$}}    
+        \label{fig:dec_good_rasp2_packet_gf2}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_decoder_Binary8_16.eps}
+        \caption[]%
+        {{\small Goodput vs. Packet size for $GF(2^8)$ and $g=16$}}    
+        \label{fig:dec_good_rasp2_packet_gf256}
+    \end{subfigure}
+    \caption[]
+    {\small Encoder goodput measurements for the \ac{Raspi} 2} 
+    \label{fig:dec_good_rasp2}
+\end{figure*}
+
+Description
 

### 2016-06-05 cross_compilation.tex

--- 2016-06-05 testbed.tex
@@
-\label{sec:testbed}
+%\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
 
-We proceed to define the testbed environment by each of its conforming
-parts. We later indicate a procedure to set up the testbed. In this procedure,
-we summarize all the details regarding on setting the connectivity and
-system files for a set of \ac{Raspi}s in a centralized fashion.
-Afterwards, we indicate how to cross-compile the Kodo library in an
-easy way. Finally, we provide further information about Kodo itself in terms
-of testing, other platforms supported and source code documentation
-for further references.
-
-\subsection{System Overview}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.6\textwidth]{images/testbed_setup2.eps}
-\caption{Testbed setup}
-\label{fig:testbed_setup}
-\end{figure}
-
-This section will present a testbed of thirty \ac{Raspi}s.
-%Twenty \ac{Raspi} 1 model B revision 2 and ten \ac{Raspi} 2 model B V1.1.
-They are all equipped with a memory card and are connected to the
-university network by wire using their ethernet interface (eth0).
-
-To easily discover the \ac{Raspi}s within the university network, they have all
-been assigned a unique name under a common domain.
-This eliminates the need to remember their individual \ac{IP}s.
-
-A sketch of the testbed is depicted in figure~\ref{fig:testbed_setup}.
-We have two types of \ac{Raspi}s in our setup.
-Table \ref{tab:rasp_naming} shows the naming convention.
-
-\begin{table}[ht!]
-  \centering
-  \begin{tabular}{|c|c|}
-    \hline
-      \textbf{Hostname} & \textbf{Model} \\ \hline
-    Rasp00 - Rasp19 & Raspberry Pi 1 model B rev. 2 \\ \hline
-    Rasp100 - Rasp109 & Rasperry Pi 2 model B V1.1 \\ \hline
-  \end{tabular}
-  \caption{Raspberry Pi naming convention}
-  \label{tab:rasp_naming}
-\end{table}
-
-Accessing them is easily done using \ac{SSH}.
-To address them within the university network,
-The \ac{Raspi}s
-
-The \ac{Raspi}s are all equipped with an ethernet interface (eth0) and
-connected by wire to the university's \ac{LAN}. The university network
-administration was provided
-the \ac{MAC} addresses of the ethernet interfaces to automatically assign
-the devices the desired \ac{IP} addresses as shown in the figure. In a personal
-\ac{LAN}, another option could be to manually provide the devices with static
-\ac{IP}s.
-
-This section will be used to present a \ac{Raspi} testbed and the steps to
-install and configure its devices.
-
-The testbed is depicted in figure~\ref{fig:testbed_setup}. It consists of twenty
-Raspberry Pi 1 model B rev 2 (Rasp01 to Rasp20) and
-ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).
-
-The goal is to configure all the \ac{Raspi}s identically with the same software
-and configurations. There are however a few differences between them that we
-need to take into account. E.g. hostname and network addresses.
-
-The testbed will be used by students that might need to change how the
-devices are work either temporary or permanently. We will illustrate how this
-can be accomplished using an overlaying filesystem.
-
-Finally, it should be possible to store data that are generated from
-simulations on the memory cards that are in the individual \ac{Raspi}.
-%We using a overlaying filesystem that
-%We will illustrate
-%how that can be done. In the case of temporary changes, it is important that
-%all changes can be easily reverted. We put a \ac{RAM} filesystem on top of
-%the the root filesystem to .
-%the configure the
-%devices to behave according to their test specifications. We
-%will also present how that might be done.
-
-%their linkings. That could be to change network config
-
-%The goal is to configure all the devices to be as identical as possible. This
-%means that it is desired to have the same software on every device, but
-
-The \ac{Raspi}s are all equipped with an ethernet interface (eth0) and
-connected by wire to the university's \ac{LAN}. The university network
-administration was provided
-the \ac{MAC} addresses of the ethernet interfaces to automatically assign
-the devices the desired \ac{IP} addresses as shown in the figure. In a personal
-\ac{LAN}, another option could be to manually provide the devices with static
-\ac{IP}s.
-%that are
-%assigned the \ac{IP} addresses in the figure and connected wired to the
-%university's \ac{LAN}.
-
-We use standard usb power adapters to power the \ac{Raspi}s.
-
-\subsubsection{Installing Raspbian}
-
-To get started, we first need to install an \ac{OS} on the
-Raspberry Pis. We will use Raspbian linux~\cite{raspbian}
-
-We will use a desktop that has linux installed to download,
-configure, and write the image to the memory cards.
-%We have decided to use a linux desktop machine to create a
-%common image of Raspbian Linux that can be used in any of the Raspberry Pis.
-
-%for all devices. After the image has been configured it can be written to
-%a memory card and used in any of the Raspberry Pis. This means that each
-%device needs a memory card, but it does not matter which card is put into
-%which device.
-
-We have decided to go with Raspbian linux~\cite{raspbian} and
-to install it on memory cards.
-
-%There exists a number of ways to setup a testbed in a centralized manner.
-%E.g. using e.g. \ac{NFS}.
-
-There exists a number of ways to setup a testbed
-
-with multiple devices. We
-have decided on a very simple approach of simply instal
-
--
-- Download image (wget)
-- Update/Modify image (chroot)
-- Burn image
-- Bang! linux is running
--
-
-Open a terminal, and then...
-
-hashmark (\#) means to perform operation as root, dollar (\$) means to perform operation as user
-
-The first thing we need to do is to download the linux installation file.
-For Raspbian, this is available at \url{http://downloads.raspberrypi.org}.
-
-Raspbian is made available in two bundles. Raspbian and Raspbian lite.
-The difference between the two is that Raspbian contains a pre-installed desktop
-environment, and Raspbian lite is by default only accessable through a shell. 
-They will both also be remotely accessible using \ac{SSH}.
-
-Our testbed does not have monitors so we will install Raspbian lite.
-A desktop environment can always be installed manually in case that will be
-desired sometime in the future.
-
-Below is a procedure of how we setup the \ac{Raspi}s in our testbed. We
-have decided a simple setup where each \ac{Raspi} is equipped with a
-memory card that contains a slightly customized Raspbian lite image with
-identical settings.
-
-The reason this can be done easily is because the official Raspbian lite image
-that we will download simply conntains a complete linux installation that are
-packaged in an image rather than written to a harddrive, memory card, or usb
-pen.
-
-The overall steps to customize the official Raspbian lite image are listed below:
-\begin{enumerate}
-    \item Download Raspbian lite
-    \item Alter Raspbian lite. E.g. browse, modify, add, and delete files
-        in the official Raspbian lite image
-    \item Change root. I.e. change root filesystem into the Raspbian lite
-        image to update and install software packages
-    \item Write image to memory cards
-\end{enumerate}
-
-\subsection{Download Raspbian lite}
-
-To download the latest Raspbian lite, we go to the url
-\url{http://downloads.raspberrypi.org/raspbian_lite/images/}.
-At the time of this writing, the latest bundle was
-2016-05-27-raspbian-jessie-lite.zip.
-
-We want to proceed downloading the image with a shell instead of the browser.
-To do this, first open a command window on a linux machine. This guide is
-assuming a debian based distribution, but there should only be minor differences
-if you have another package manager. I.e. the application that is used to
-download and install software packages in linux.
-
-After the terminal has been opened, we first declare a few variables to reduce
-redundant typing. The first variables we declare is the Raspbian image name.
-Notice that the extension has been omitted. This is because the image has been
-packed into a zip file.
-The other variable we declare is a working directory. This is where we will
-download the image to and work on it. In other words, it will be stored in
-/home/<username>/Raspbian
-
-%To download Raspbian lite, we go to the \url{http://downloads.raspberrypi.org}.
-%There should be a folder called raspbian\lite and
-%to find the download page at which Raspbian lite should be located. Instead of
-%downloading with the browser, we just extract the download url to the latest
-%image. At the time of this writing, that was
-
-% Define variable]
-\begin{lstlisting}[]
-$ export IMAGE="2016-05-27-raspbian-jessie-lite"
-$ export WORKDIR="${HOME}/Raspbian"
-\end{lstlisting}
-\FloatBarrier
-
-A final thing to notice is the way \$ and \# are used in the code blocks. \$
-means that the command can be run as a normal user where \# indicates that the
-command should be run with root permissions.
-Running a command with root permissions can on most systems be done by putting
-the command "sudo" in front of each line. This is illustrated in the code below
-with the command "whoami" that prints the username of the caller. Lines without
-leading \$ or \# is the terminal output.
-
-% Root example
-\begin{lstlisting}[]
-$ whoami
-chres
-$ sudo whoami
-root
-\end{lstlisting}
-\FloatBarrier
-
-Next, we make the working directory and change directory (cd) into the working
-directory. We can then use wget to download Raspbian lite. Unpack the image
-when the download is complete.
-
-% Download and unpack image
-\begin{lstlisting}[]
-$ mkdir -p ${WORKDIR}
-$ cd ${WORKDIR}
-$ wget http://downloads.raspberrypi.org/raspbian_lite/images/raspbian_lite-2016-05-31/${IMAGE}.zip
-$ unzip ${IMAGE}.zip
-\end{lstlisting}
-\FloatBarrier
-
-\subsection{Mount image}
-
-After Raspbian lite has been unpacked, there should be an .img file in the directory.
-"fdisk" can be used to display what is inside. Pass the arguments "-u sectors" to
-display the sizes in sectors and "-l" to display partitions and exit.
-
-% Check out the image   % The dollar hack was to fix vim syntax
-\begin{lstlisting}[literate={DOLLAR}{\$}1]
-DOLLAR fdisk -u sectors -l ${IMAGE}.img
-Disk 2016-05-27-raspbian-jessie-lite.img: 1.3 GiB, 1387266048 bytes, 2709504 sectors
-Units: sectors of 1 * 512 = 512 bytes
-Sector size (logical/physical): 512 bytes / 512 bytes
-I/O size (minimum/optimal): 512 bytes / 512 bytes
-Disklabel type: dos
-Disk identifier: 0x6fcf21f3
-
-Device                               Boot  Start     End Sectors  Size Id Type
-2016-05-27-raspbian-jessie-lite.img1        8192  137215  129024   63M  c W95 FAT32 (LBA)
-2016-05-27-raspbian-jessie-lite.img2      137216 2709503 2572288  1.2G 83 Linux
-\end{lstlisting}
-\FloatBarrier
-
-The image contains two partitions. The first one of starting at sector 8192 and
-the other partition starting at sector 137216. The partitions is of type FAT32
-and Linux and have sizes 63M and 1.2G. This indicates that the first partition
-is most likely a boot partition and the second partition is a traditional file
-system. Actually, it is a linux root filesystem (i.e. /).
-
-%We see that the boot and root partitions starts at sector 8192 and 137216 respectivly.
-%We also notice that each sector is 512 bytes.
-
-%On newer systems, we can mount the device easier using "losetup --show -f -P IMAGE"
-
-%Mount root partition:
-
-To browser and alter the files in the image, it is possible to mount the partitions.
-
-Lets first mount the root partition. This is done by first creating a new folder
-that we will call root which will be located in our working directory. After this,
-we mount the partition starting at sector 137216. To provide this offset information
-to mount, we need to find the offset in bytes. From the fdisk command we could also
-see that each sector is 512 bytes. Thus, we multiply the sector size and the sector
-start to get the offset in bytes.
-
-\begin{lstlisting}[]
-$ export ROOTDIR="${WORKDIR}/root"
-$ mkdir -p ${ROOTDIR}
-# mount -o loop,offset=$((137216*512)) ${IMAGE}.img ${ROOTDIR}
-\end{lstlisting}
-\FloatBarrier
-
-After this, we can also mount the boot partition inside the newly mounted
-root filesystem. This is useful because that partition will be mounted
-this exact place when a \ac{Raspi} starts up with a memory card containing
-this image. It is therefore the natural place to mount it for later purposes.
-
-Mount boot partition:
-\begin{lstlisting}[]
-# mount -o loop,offset=$((8192*512)) ${IMAGE}.img ${ROOTDIR}/boot
-\end{lstlisting}
-\FloatBarrier
-
-We can now change all the files in the disk image as desired.
-
-\subsection{Configuring OS files and scripts}
-
-The \ac{Raspi}s should be setup to be as similar as possible. One of those
-things that is prefered to be different on the devices is their hostname.
-This helps distinguish them from each other. One solution to this in our
-approach would be to uniquely change the hostname in each memory card.
-This is however not desired because that would either require modifying
-the the customized Raspbian lite image before writing the content to the
-memory card or to manually change it in the \ac{Raspi}s after the image has
-been written to a meomory card.
-Instead, we decided to register the ethernet MAC addresses of all the \ac{Raspi}s
-in our testbed. Those had to be used to put them in a domain name anyway.
-
-Below is a part of the file where we keep track of the MAC addresses and assign
-hostnames. This file will be available online and copied to the Raspbian lite
-image in a later step under the listed filename. For different \ac{Raspi}s
-the MAC addresses has to be changed. The MAC address of a network card can be found
-using the command "ifconfig" or "ip addr".
-
-% MAC and Hostname file
-\Suppressnumber\begin{lstlisting}[]
-<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/rasp\_config/nodes.csv}@>
-<@\textcolor{gray}{
----------------------------------------------------------------}
-\Reactivatenumber @>
-# Ethernet MAC    Hostname
-b8:27:eb:5b:da:20 rasp00
-b8:27:eb:7b:c3:91 rasp01
-b8:27:eb:54:9c:64 rasp02
-b8:27:eb:95:bd:11 rasp03
-\end{lstlisting}
-\FloatBarrier
-
-Provided that each \ac{Raspi} will have knowledge of all other \ac{Raspi}s in
-the testbed, it still needs to know which name to give itself.
-We do this using a small Bash script:
-
-% Set hostname
-\Suppressnumber\begin{lstlisting}[]
-<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/rasp\_config/set\_hostname}@>
-<@\textcolor{gray}{
----------------------------------------------------------------}
-\Reactivatenumber @>
-#!/usr/bin/env bash
-
-script_path="$(dirname $(realpath $0))"
-mac=$(cat /sys/class/net/eth0/address)
-hostname=$(grep $mac ${script_path}/nodes.csv | cut -f2 -d' ')
-
-# Assign hostname found in nodes.csv
-if [ ! -z $hostname ]; then
-    echo $hostname > /etc/hostname
-    hostname $hostname
-fi
-\end{lstlisting}
-\FloatBarrier
-
-Line 1 tells the system to interpret the script using Bash. Line 3 gets the
-path of the script itself. Line 4 gets the MAC address. This script will be
-located in a \ac{Raspi} and thus return the MAC address of itself when called.
-Line 4 searches line by line for this mac address.
-Line 8-11 assigns the hostname found in "nodes.csv". If the MAC did not exists,
-then it will keep the default hostname of the system.
-
-We have packed the files and uploaded them to a webserver. These can be
-retrieved with wget and unziped into the Raspbian lite image that
-we are customizing:
-
-% Get the files
-\begin{lstlisting}[]
-$ wget http://kom.aau.dk/project/TuneSCode/raspi/rasp_config.zip
-# unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
-\end{lstlisting}
-\FloatBarrier
-
-"nodes.csv" can be changed using a text editor. For vim, this could be done
-the following way:
-\begin{lstlisting}[]
-# vim ${ROOTDIR}/home/pi/rasp_config/nodes.csv
-\end{lstlisting}
-\FloatBarrier
-
-Finally, to actually make the \ac{Raspi}s change hostname, we have to make
-each \ac{Raspi} call the above script when it starts up.
-Do this by inserting the line below in "\$\{ROOTDIR\}/etc/rc.local".
-The file
-can be opened with your favorite text editor.
-
-\begin{lstlisting}[]
-bash /home/pi/rasp_config/set_hostname"
-\end{lstlisting}
-\FloatBarrier
-
-%This can be done by inserting a call to the script
-%set\_hostname in rc.local before it exits.
-%
-%Call set\_hostname script at startup. We insert a line of code to call script in rc.local just after the initial comments (i.e. lines starting with \#).
-%\begin{lstlisting}[]
-%# line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
-%# sed -i "${line_number}c bash /home/pi/rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
-%\end{lstlisting}
-%\FloatBarrier
-%$ line="bash /home/pi/.rasp_config/set_hostname"
-%# awk -v text="$line" '!/^#/ && !p {print text; p=1} 1' ${ROOTDIR}/etc/rc.local > <@ \Suppressnumber @>
-%    ${ROOTDIR}/etc/rc.local <@ \Reactivatenumber @>
-
-All other files could be updated as well.
-
-\subsection{Installation and Updating the image}
-
-It may be desired to pre-install some programs in the image before it is
-written to all the memory cards that goes into the \ac{Raspi}s.
-This can be done from any linux x86 machine using QEMU Chroot (change root).
-\url{https://wiki.debian.org/QemuUserEmulation}
-%\url{https://wiki.archlinux.org/index.php/Raspberry_Pi}
-
-Due to the \ac{ARM} processor that \ac{Raspi}s are using, it is required to
-install some additional software:
-%Because \ac{Raspi}s are eqipped with an \ac{ARM} processor 
-%%it is not as
-%straightforward as performing the task for two linux systems of the same
-%architecture.
-
-% CHROOT to OS image
-\begin{lstlisting}[]
-# apt-get install binfmt-support qemu qemu-user-static
-# update-binfmts --display qemu-arm
-qemu-arm (enabled):
-     package = qemu-user-static
-        type = magic
-      offset = 0
-       magic = \x7fELF\x01\x01\x01\x00\x00\x00\x00\x00\x00\x00\x00\x00\x02\x00\x28\x00
-        mask = \xff\xff\xff\xff\xff\xff\xff\x00\xff\xff\xff\xff\xff\xff\xff\xff\xfe\xff\xff\xff
- interpreter = /usr/bin/qemu-arm-static
-    detector = 
-\end{lstlisting}
-\FloatBarrier
-% This was neccessary on arch
-%# update-binfmts --importdir /var/lib/binfmts/ --import
-
-Make sure the second command writes "enabled" as the output above. If that 
-is not the case, then try enabling it:
-
-\begin{lstlisting}[]
-# update-binfmts --enable qemu-arm
-\end{lstlisting}
-\FloatBarrier
-
-Provided that qemu-arm is enabled, we should now be able to change root (chroot)
-into our Raspbian lite image. Change root is a method i linux that enables
-the root (/) to be changed. Thus, enabling a linux installation within a
-linux installation.
-
-There are a few commands to be performed before we can change root.
-First, to get internet access from within the Raspbian lite image it is needed
-to copy our resolv.conf into the filesystem. Line 1 steps into Raspbian lite's
-root filesystem. Then line 2 copies resolv.conf.
-
-% CHROOT to OS image
-\begin{lstlisting}[]
-# cd $ROOTDIR
-# cp /etc/resolv.conf etc/resolv.conf
-\end{lstlisting}
-\FloatBarrier
-
-Now, because of the ARM architecture, it is also required to copy
-/usr/bin/qemu-arm-static into the image before we can continue:
-
-% CHROOT to OS image
-\begin{lstlisting}[]
-# cp /usr/bin/qemu-arm-static usr/bin
-\end{lstlisting}
-\FloatBarrier
-
-The final preparation before chaning root is to populate the directories proc,
-sys, and dev:
-
-% CHROOT to OS image
-\begin{lstlisting}[]
-# mount -t proc proc proc/
-# mount --rbind /sys sys/
-# mount --rbind /dev dev/
-\end{lstlisting}
-\FloatBarrier
-
-Finally, the filesystem is ready for us to change root. This can be done with
-"proot". It may be required to install proot:
-
-% CHROOT to OS image
-\begin{lstlisting}[]
-# proot -q qemu-arm-static -S ${ROOTDIR}
-\end{lstlisting}
-\FloatBarrier
-
-Most available online material uses the more known chroot command as written in
-the code block below. This did not work correctly in our machines, but we show
-it as an alternative in case proot may not work on other systems.
-
-% CHROOT to OS image
-\begin{lstlisting}[]
-# chroot ${ROOTDIR} /usr/bin/qemu-arm-static /bin/bash    (ALTERNATIVE TO proot)
-\end{lstlisting}
-\FloatBarrier
-
-If everything went well, we should now be standing in the Raspbian lite filesystem
-under its root. Optionally, we can change the prompt title to indicate that we
-are chrooted:
-
-% Optionally, we may create a unique prompt to indicate we have changed root
-\begin{lstlisting}[]
-# export PS1="(chroot) $PS1"
-\end{lstlisting}
-\FloatBarrier
-
-The Raspbian lite system should now be possible to use as if it had been booted
-in a \ac{Raspi}. The only difference is that the laptop that we are using is
-significantly faster than a \ac{Raspi}. Thus enabling us to for example update,
-upgrade, and install software packages:
-
-% Update system
-\begin{lstlisting}[]
-# apt-get update
-# apt-get upgrade
-\end{lstlisting}
-\FloatBarrier
-
-Lets install some useful applications:
-% Install packages
-\begin{lstlisting}[]
-# apt-get install vim git screen
-\end{lstlisting}
-\FloatBarrier
-
-All the changes that are made here will exists in all \ac{Raspi}s when the
-image is written to a memory card.
-
-\subsection{Installation an overlaying filesystem}
-
-Our goal was to enable the users of the testbed to change however the
-\ac{Raspi} are configured while still being able to revert those changes easily.
-
-We do this by storing a users work in the \ac{Raspi}s in \ac{RAM}. Thus a
-\ac{Raspi}, when a \ac{Raspi} is rebooted, it will forget all changes.
-
-A way to do this is using stacked filesystem. Stacking filesystem enables
-a filesystem to overlay another filesystem. Whenever a file is accessed,
-the upper filesystem will forward the request to the lower filesystem in
-case it does not have it itself. If it has it, it will simpy return the file.
-
-This idea can be used in our setup to mount the root filesystem (i.e. Raspbian
-lite) in the \ac{Raspi}s duing startup as read-only. Thus, the files will not
-be changable. Some programs needs to change files and the testbed admin might
-want to change configurations. To enable this, it is possible to
-overlay a filesystem that is mounted in \ac{RAM} as read/writable on top of
-the regular root. Thus, reading a file may return a file from the lower filesytem,
-but if it is stored, it will be saved in the upper filesystem. Accessing this file
-again will return the stored file from the upper layer.
-
-%We do this using an overlay filesystem. The idea is to let the \ac{Raspi}s
-%mount their root filesystem as 
-%
-%We do this using an overlay filesystem (overlayfs).
-%Overlayfs enables a filesystem to be stacked on top of another filesystem. Thus,
-%if the \ac{Raspi}s mount their root filesystem (/) as read-onlyif we mount our root (/) filesystem as 
-%
-%
-%Overlayfs enables filesystems
-%to be stacked on top of each other. We will be using this to make a lower
-%filesystem and an upper filesystem. The lower filesystem will be our
-%traditional filesystem and the upper filesystem will be mounted in tmpfs
-%(i.e. mounted in \ac{RAM}).
-%
-%Thus, when a file is requsted from stacked filesystem, it will first attempt
-%to fetch the file in the upper filesystem if it does not exists there, it will
-%request it from the lower filessytem.
-
-Assuming that you are still chrooted into the Raspbian lite filesystem, we
-can setup the overlay filesystem (overlayfs).
-
-There already exists implementations overlaying the root filesystem. We will
-use an existing implementation
-available at github: \url{https://github.com/chesty/overlayroot}.
-
-We installed git in a previous step, so lets clone the repository. The below
-code stores it in /tmp which is really mounted in \ac{RAM}. Thus, the files
-will disappear when the machine is rebooted.
-
-% Get files
-\begin{lstlisting}[]
-# OVERLAYROOTDIR="/tmp/overlayroot"
-# git clone https://github.com/chesty/overlayroot.git $OVERLAYROOTDIR
-\end{lstlisting}
-\FloatBarrier
-
-To enable the overlaying filesystem it is required to generate an initial \ac{RAM}
-file system (initramfs). Initramfs is an initial filesystem that gets loaded into
-\ac{RAM} during the startup process of a linux machine to prepare the real
-filesystem.
-
-For this purpose, we need BuxyBox:
-
-% Install required packages
-\begin{lstlisting}[]
-# apt-get install busybox
-\end{lstlisting}
-\FloatBarrier
-
-Add and activate the overlaying filesystem, we need to add the scripts and tell initramfs
-to load the overlaying filesytem:
-
-% Setup initramfs
-\begin{lstlisting}[]
-# cp ${OVERLAYROOTDIR}/hooks-overlay /etc/initramfs-tools/hooks/
-# cp ${OVERLAYROOTDIR}/init-bottom-overlay /etc/initramfs-tools/scripts/init-bottom/
-# echo "overlay" > /etc/initramfs-tools/modules
-\end{lstlisting}
-\FloatBarrier
-
-Raspbian lite uses a "u-boot" to boot, so it should be made aware of the
-initramfs that we will generate.
-
-% Tell uboot to load initramfs
-\begin{lstlisting}[]
-# echo "initramfs init.gz" > /boot/config.txt
-\end{lstlisting}
-\FloatBarrier
-
-Finally, lets generate the image. This is done using "mkinitramfs", that will
-by default look for the kernel modules of the current system. Remember we are
-chrooted, so we need to specify the correct kernel modules to look for. These
-can be found in "/lib/modules".
-
-% Create an initramfs
-\begin{lstlisting}[]
-# ls /lib/modules/
-\end{lstlisting}
-\FloatBarrier
-
-For \ac{Raspi} 1, our kernel modules was "4.4.11+". The other modules in /lib/modules
-is for \ac{Raspi} 2.
-
-Thus, to run mkinitramfs, type in the correct kernel version:
-
-% Create an initramfs
-\begin{lstlisting}[]
-# mkinitramfs -o /boot/init.gz -k 4.4.11+
-\end{lstlisting}
-\FloatBarrier
-
-This should generate a new initial \ac{RAM} filesystem that will overlay a \ac{RAM} filesystem.
-
-\subsection{Write image}
-
-The final step is to write the image to all the memory cards before they can
-be plugged in the \ac{Raspi}s. This is done by first leaving the chrooted filesystem
-and unmounting all the directories we mounted:
-
-% Exit chroot, umount, and write to memory card
-\begin{lstlisting}[]
-# exit
-# cd ..
-# umount --recursive ${ROOTDIR}
-# losetup -d WHICH_NUMBE.img
-\end{lstlisting}
-\FloatBarrier
-
-If successfully unmounted, you can insert a memory card in your machine. In our
-system, this memory card was available under /dev/mmcblk0, but this may be
-different on different machines. For internal memory card readers, it will
-probably be named /dev/mmcblkX where X is some number and if the memory card
-reader is connected through \ac{USB}, then it is likely called /dev/sdX.
-Make sure to write to the correct device as everything will be overwritten!
-
-Below is a few commands that may help you to deduce which device is correct:
-
-\begin{lstlisting}[]
-# lsblk
-# df -h
-\end{lstlisting}
-\FloatBarrier
-
-For us, the device was /dev/mmcblk0, so we write the image to that device:
-\begin{lstlisting}[]
-# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M
-\end{lstlisting}
-\FloatBarrier
-
-\section{Cross-compilation: From PC to Raspberry Pi}
-
-%\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
+WRITE INTRO OF WHY WE WANT TO CROSS COMPILE. E.G. 1) WE DO NOT HAVE MONITORS
+CONNECTED TO THE RASPIS, 2) A PC IS SIGNIFICANTLY FASTER AND FAR BETTER EQUIPPED (RAM, CPU, HARDDRIVE), 3) MORE CONVINIENT TO DO EVERYTHING IN ONE PC AND DISTRIBUTE IT TO THE RASPIS AFTERWARDS. MORE?
 
@@
 
-\subsection{Long running jobs over SSH (PUT THIS SECTION SOMEWHERE ELSE)}
-
-Problem when you logout, then applications will terminate. SCREEN is the answer.
-
-EXAMPLE
-
-\texttt{hello\_world} returns immediately. This is not always the case.
-Sometimes it is desired to run simulations that should run for days. 
-A software package called \texttt{screen} can be used for this purpose.
-Simply run ...
-
 \subsection{Kodo python}
@@
 execute a script function by calling "fab install:feh"
+
+\subsection{Long running jobs over SSH (PUT THIS SECTION SOMEWHERE ELSE)}
+
+Problem when you logout, then applications will terminate. SCREEN is the answer.
+
+EXAMPLE
+
+\texttt{hello\_world} returns immediately. This is not always the case.
+Sometimes it is desired to run simulations that should run for days. 
+A software package called \texttt{screen} can be used for this purpose.
+Simply run ...

### 2016-06-05 schemes.tex
proofreading. Added info on Budget and density for TSNC

@@
 In this section, we present a description of the considered coding schemes
-measured with our the \ac{Raspi} testbed. We introduce a definition
+measured with the \ac{Raspi} testbed. We introduce a definition
 for the primitive coding operations, e.g. encoding, decoding and recoding
@@
 better processing speeds, particularly relevant for the \ac{Raspi}.
-Finally, we include a review of the
+Finally, we include a review of the \todot{this sentence is incomplete}
 
@@
 \ac{RLNC} is an example of intra-session \ac{NC}. Here, data symbols from a
-single flow are combined with each other. In this type of network coding,
-all the original data packets $P_j, j \in [1,g]$, each of $B$ bytes, are used
-to create coded packets. In the following subsections, we describe the
-basic functionalities of \ac{RLNC}.
+single flow are combined with each other. In this type of network coding, all
+the original data packets $P_j, j \in [1,g]$, and each of $B$ bytes, are used to
+create coded packets. In the following subsections, we describe the basic
+functionalities of \ac{RLNC}.
 
@@
 multiplied by a coding coefficient from $GF(q)$. The coding coefficients
-are picked uniformly at random from the \ac{GF} by the encoder. To
+are chosen uniformly at random from the \ac{GF} by the encoder. To
 perform the multiplication of a packet by a coding coefficient, the
@@
 amount of overhead is included in every coded packet given that we
-need to provide some signalling needed for decoding. The coding
+need to provide some signaling needed for decoding. The coding
 coefficients overhead amount for packet $i$, $|v_i|$, can be quantified
@@
 efficient Gaussian elimination techniques \cite{fragouli2006network}.
-On real applications, decoding is performed on-the-fly, e.g. the pivots are
+On real applications, decoding is performed on-the-fly, e.g., the pivots are
 computed as packets are progressively received, in order to minimize the
@@
 %
-This procedure is carried by all the recoders in a given network, therefore
+This procedure is carried by all the recoders in a given network therefore
 allowing any decoder to compute the original data after Gaussian elimination,
@@
 
-In \ac{SRLNC}, instead of considering all the packets to create a coded
-packet as in \ac{RLNC}, for this coding scheme an encoder sets more
-coding coefficients to zero when generating a coded packet with the purpose
-of reducing the overall processing. Decoding is the same as in \ac{RLNC}, but
-given that the coding matrices are now sparse, we will have less operations
-performed in the decoding process. Recoding, although theoreticaly possible,
-is omitted in practical systems since it is too complex to keep packets sparse
-after recoding [\textbf{reference}]. In what follows, we
-describe the coding scheme with a basic method to produce sparse coded
-packets and later we indicate a second one, giving reference to their
-implementation performance.
+In \ac{SRLNC}, instead of considering all the packets to create a coded packet
+as in \ac{RLNC}, an encoder sets more coding coefficients to zero when
+generating a coded packet with the purpose of reducing the overall processing.
+Decoding is the same as in \ac{RLNC}, but given that the coding matrices are now
+sparse, we will have less operations performed in the decoding process.
+Recoding, although theoretically possible, is omitted in practical systems since
+it is too complex to keep packets sparse after recoding
+[\textbf{reference}]\todot{add ref}. In what follows, we describe the coding
+scheme with a basic method to produce sparse coded packets and later we indicate
+a second one, giving reference to their implementation performance.
 
@@
 coefficient to not be zero, since we want to ensure a coding coefficient
-is generate for any random trial where $\mathbb{B}_j = 1$. Therefore, in our
+is generated for any random trial where $\mathbb{B}_j = 1$. Therefore, in our
 implementation of \ac{SRLNC} we exclude the zero element and then pick
@@
 
+The difference between $B$ and $g$ is equal to the losses in the channel and the
+losses due to linear dependencies. Therefore, in a lossless channel, the budget
+is
+\begin{equation}\label{eq:budget}
+    B(g,d)=\sum^{g-1}_{i=0}\frac{1}{P(i,g,d)},
+\end{equation}
+
+where $P(i,n,d)$ is the probability of receiving an innovative coded packet
+after receiving $i$ \ac{l.i.} packets with a coding density $d$. In our implementations, we considered the the upper bound for the innovation probability from \cite{feizi2014tunable}, given as
+\begin{equation}
+    P(i,g,d)\geq 1-(1-d)^{n-i}
+\end{equation}
+
 Provided a desired budget $B$ and the \ac{dof} of the decoder, an encoder
@@
 generation size. Still, we have an implementation that limits the amount of
-feedback to be sent from the decoder in [\textbf{reference}].
+feedback to be sent from the decoder in [\textbf{reference}].\todot{@Chres this reference is missing}
 
-The transmissions made between feedback packets are called the density
-regions since the same estimated density is used for encoding sparse
-packets. Once new feedback is received, an encoder recalculates the coding
-density for the new region until the next feedback packet is received.
-Before the coding density can be estimated, it is essential that the
-encoder has a good estimate of the decoder \ac{dof}, but also the remainder
-of the total budget. The feedback scheme based on the rank reports of
-\eqref{eq:feedback_dofs} roughly splits the remaining coding regions in
-two halves in every. In other words, the first half is the region where
-the encoder currently operates. Once an encoder finishes with this region,
-it proceeds with second half where again it splits this into to two region
-and so on until it finishes on transmitting the whole generation. This is
-also the case for the budget that is split equally among the two new
-regions. The very last region will be assigned the full remainder of
-the total budget and the coding density will not vary.
+The transmissions made between feedback packets are called the density regions
+since the same estimated density is used for encoding sparse packets. Once new
+feedback is received, an encoder recalculates the coding density for the new
+region until the next feedback packet is received. Before the coding density can
+be estimated, it is essential that the encoder has a good estimate of the
+decoder \ac{dof}, but also the remainder of the total budget. To calculate the
+density, we use bisection to estimate a fixed density for the density region
+that satisfies the budget for the $k$-th density region:
+\begin{equation}
+B(s(k-1),r(k),g,d) = \sum^{r(k)}_{i=r(k-1)} \frac{1}{P(i,g,d)} = \sum^{r(k)}_{i=r(k-1)} \frac{1}{1-(1-d)^{g-i}} = \frac{B}{2^k}, k\in [1,...).
+\end{equation}
+%
+% Where the budget is half of the remaining budget for all the density regions
+% except the last one, to which it is assigned the remaining of the budget.
+The feedback scheme based on the rank reports of \eqref{eq:feedback_dofs}
+roughly splits the remaining coding regions in two halves. In other
+words, the first half is the region where the encoder currently operates. Once
+an encoder finishes with this region, it proceeds with second half where again
+it splits this into to two region and so on until it finishes on transmitting
+the whole generation. This is also the case for the budget that is split equally
+among the two new regions. The very last region will be assigned the full
+remainder of the total budget and the coding density will not vary.
 

### 2016-06-05 testbed.tex

--- 2016-06-05 testbed.tex
@@
 \FloatBarrier
-
-\subsection{Kodo python}
-
-\subsection{fabric}
-
-% Exit chroot, umount, and write to memory card
-\begin{lstlisting}[]
-from fabric.api import run, env, task
-# Python Fabric script to run commands on multiple hosts through ssh
-#
-# Run script as 'fab <task>', where <task> is one of the scripts functions
-# marked as a tesk. The task marked as 'default' will be run if <task> is not
-# specified
-
-env.hosts = ['rasp00.domain.com','rasp01.domain.com','rasp02.domain.com']
-env.user = 'root'
-env.password = 'sdn'
-
-@task
-def install(program):
-    """
-    Install a program
-    program: program name
-    """
-    result = run('apt-get install -y {}'.format(program), quiet=True)
-
-@task
-def copy_to_rasp(filename):
-    put(...)
-
-\end{lstlisting}
-\FloatBarrier
-
-execute a script function by calling "fab install:feh"
-
-\section{Cross-compilation: From PC to Raspberry Pi}
-
-%\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
-
-\subsection{Install toolchain on PC}
-
-Besides the previous description (\textbf{Include compiling Kodo from the
-RasPi from the scratch}), the testbed administrator can compile Kodo in its
-personal workstation and transfer the generated binaries directly to
-a path in the \ac{Raspi}. To achieve this, we get a toolchain that
-contains the binaries for the \texttt{raspberry-gxx49-arm-g++} compiler
-for the \ac{Raspi}. Therefore, we strongly recommend any testbed
-administrator to do the following procedure. In what follows, we provide
-the instructions considering that the NFS server uses the \texttt{\$HOME}
-directory as the working directory. However, the administrator may choose
-some other working directory of its preference if desired.
-
-\begin{enumerate}
-
-\item Create toolchain directory:
-\begin{lstlisting}[]
-$ TOOLCHAINDIR="${HOME}/toolchains"
-$ mkdir -p $TOOLCHAINDIR
-$ cd $TOOLCHAINDIR
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-\item Download the \ac{Raspi} toolchain for 64-bit Linux from.
-A more recent \ac{Raspi} toolchain may be available at
-\texttt{http://buildbot.steinwurf.dk/toolchains/linux/}:
-
-\begin{lstlisting}[]
-$ TOOLCHAIN="raspberry-gxx49-arm"
-$ wget http://kom.aau.dk/project/TuneSCode/raspi/${TOOLCHAIN}.zip
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-\item Extract the downloaded file:
-%locally in the NFS server. After
-%this operation, there should be a new directory for the toolchain
-%in the server. \\
-\begin{lstlisting}[]
-$ unzip ${TOOLCHAIN}.zip
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-\item (Optional) Delete zip file:
-%locally in the NFS server. After
-%this operation, there should be a new directory for the toolchain
-%in the server. \\
-\begin{lstlisting}[]
-$ rm ${TOOLCHAIN}.zip
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-\item We can now verify that the ARM cross compiler is working:
-
-\begin{lstlisting}[]
-$ ${TOOLCHAINDIR}/${TOOLCHAIN}/bin/${TOOLCHAIN}-g++ --version
-raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
-Copyright (C) 2014 Free Software Foundation, Inc.
-This is free software; see the source for copying conditions.  There is NO
-warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-%\begin{lstlisting}[]
-%$ echo "${TOOLCHAINDIR}/${TOOLCHAIN}/bin/${TOOLCHAIN}-g++"
-%/home/<USER>/toolchains/raspberry-gxx49-arm/bin/raspberry-gxx49-arm-g++
-%\end{lstlisting}
-%\FloatBarrier
-%\vspace{-5mm}
-
-%    The ARM cross compilers should now be located in
-
-\item Make toolchain binaries available systemwide. Instead of calling
-the ARM cross compiler using its full path, we can make it accessible
-from the command shell systemwide. One way to do this is by adding the 
-toolchain binaries directory to the Linux environment variable \texttt{PATH}
-when the \ac{OS} starts up:
-
-%\item Add toolchain binaries to \texttt{PATH}. Instead specifying the full
-%path to the toolchain binaries we can instead tell the operation system
-%where to search for it. This makes the toolchain binaries available
-%systemwide.
-
-\begin{lstlisting}[]
-$ echo PATH=\"\$PATH:${TOOLCHAINDIR}/${TOOLCHAIN}/bin\" >> ${HOME}/.profile
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-%$ printf 'PATH="%s/%s/bin"\n' "${TOOLCHAINDIR}" "${TOOLCHAIN}" >> ${HOME}/.profile
-
-%\item Add the \texttt{bin} folder of the toolchain to the \texttt{PATH}
-%Linux environment variable of the server. This will help the server OS
-%to recognize the location of the compiler command, which will be needed
-%later. To do so, edit the \texttt{\$HOME/.profile} to add in a newline:
-%\texttt{PATH="\$PATH:\$HOME/raspberry-gxx49-arm/bin"}. Save the
-%\texttt{\$HOME/.profile}. \\
-
-\texttt{.profile} should now contain the line we inserted. There may be more
-code in you file.
-% MAC and Hostname file
-\Suppressnumber\begin{lstlisting}[]
-<@\textcolor{gray}{\$HOME/.profile}@>
-<@\textcolor{gray}{
----------------------------------------------------------------}
-\Reactivatenumber @>
-PATH="$PATH:/home/<USERNAME>/toolchains/raspberry-gxx49-arm/bin"
-\end{lstlisting}
-\FloatBarrier
-
-\item Update \texttt{PATH}. Source \texttt{.profile} to make the changes
-take effect in your system:
-\begin{lstlisting}[]
-$ source ${HOME}/.profile
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-\item ARM cross compiler should now be available systemwide:
-
-\begin{lstlisting}[]
-$ raspberry-gxx49-arm-g++ --version
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-%\item Restart the server session in order for the changes made in the
-%previous step take effect. To verify this, open a new terminal and type:
-%\texttt{raspberry-gxx49-arm-g++ --version}. A correct binary installation
-%should return an output similar to:
-%
-%\texttt{raspberry-gxx49-arm-g++ (crosstool-NG 1.21.0) 4.9.3 20150311 (prerelease)
-%Copyright (C) 2014 Free Software Foundation, Inc.
-%This is free software; see the source for copying conditions.  There is NO
-%warranty; not even for MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.} \\
-
-\end{enumerate}
-
-\subsection{Cross compile example}
-
-Create a directory to hold our code:
-\begin{lstlisting}[]
-$ CODEDIR="${HOME}/code"
-$ mkdir -p ${CODEDIR}
-$ cd ${CODEDIR}
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-Create a \texttt{hello\_world.cpp} using your favorite text editor:
-
-\Suppressnumber\begin{lstlisting}[]
-<@\textcolor{gray}{\${CODEDIR}/hello\_world.cpp}@>
-<@\textcolor{gray}{
----------------------------------------------------------------}
-\Reactivatenumber @>
-#include <iostream>
-
-int main()
-{
-    std::cout << "Hello World!" << std::endl;
-    return 0;
-}
-\end{lstlisting}
-\FloatBarrier
-
-Save \texttt{hello\_world.cpp} and compile it for \ac{Raspi}:
-
-\begin{lstlisting}[]
-$ raspberry-gxx49-arm-g++ hello_world.cpp -o hello_world
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-Lets copy the executable file to a \ac{Raspi} and test it. We will use \ac{SCP}
-to copy the executable to one of the \ac{Raspi}s.
-
-Default username is "pi" and password is "raspberry"
-
-\begin{lstlisting}[]
-$ scp main pi:<RASP_IP>:~/
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-If you do not know the \ac{IP} address of a \ac{Raspi} in your network, you can
-connect a monitor to it and run the following command after you have logged in:
-\begin{lstlisting}[]
-pi@rasp01:~ $ ifconfig
-eth0      Link encap:Ethernet  HWaddr b8:27:eb:72:77:54  
-          inet addr:192.168.87.107  Bcast:192.168.87.255  Mask:255.255.255.0
-          inet6 addr: fe80::e0a5:38f3:6f82:bc79/64 Scope:Link
-          UP BROADCAST RUNNING MULTICAST  MTU:1500  Metric:1
-          RX packets:1537 errors:0 dropped:0 overruns:0 frame:0
-          TX packets:445 errors:0 dropped:0 overruns:0 carrier:0
-          collisions:0 txqueuelen:1000 
-          RX bytes:259117 (253.0 KiB)  TX bytes:52551 (51.3 KiB)
-
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-After the executable has been copied to a \ac{Raspi}. Then, \ac{SSH} to it:
-
-\begin{lstlisting}[]
-$ ssh pi:<RASP_IP>
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-We can list the directory content after we have logged into the \ac{Raspi} and
-see that \texttt{hello\_world} is there:
-
-\begin{lstlisting}[]
-pi@rasp07:~ $ ls
-hello_world  rasp_config
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-Now, simply execute the \texttt{hello\_world}:
-
-\begin{lstlisting}[]
-pi@rasp07:~ $ ./hello_world
-Hello World!
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-\subsection{Long running jobs over SSH (PUT THIS SECTION SOMEWHERE ELSE)}
-
-Problem when you logout, then applications will terminate. SCREEN is the answer.
-
-EXAMPLE
-
-\texttt{hello\_world} returns immediately. This is not always the case.
-Sometimes it is desired to run simulations that should run for days. 
-A software package called \texttt{screen} can be used for this purpose.
-Simply run ...
-
-\subsection{Cross compile Kodo}
-
-\begin{enumerate}
-
-\item Clone the Kodo repository in the server by executing: \\
-\texttt{git clone git://github.com/steinwurf/kodo.git} in \texttt{\$HOME}.
-\textbf{Change the repo to kodo-rlnc or kodo-cpp since just raw kodo is going
-to be depreceated soon} \\
-
-\item Navigate to the repository and configure \texttt{waf} by typing:
-\texttt{python config.py} and select the 16th ``make specification'' file
-for the \ac{Raspi}, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
-presented by the file.
-
-This command configures \texttt{waf} to use the proper compiler and its
-required flags to generate the binaries for the \ac{Raspi}. If the
-configuration was correct, the output will indicate:
-\texttt{'configure' finished successfully (X.XXXs)}, where \texttt{X.XXX}
-is total time in seconds for configuring the project in the server. \\
-
-\item Execute \texttt{python waf build}. If the build process was
-successful, the generated binaries for the \ac{Raspi} should be located
-in \texttt{build/cxx\_raspberry\_gxx49\_arm} in the Kodo repository.
-\textbf{Indicate how the binary files should look like}.
-
-Once this procedure is made, the testbed administrator can relocate the
-generated binary files to the \ac{Raspi}s through the network as desired
-by using the \texttt{scp} command during the configuration step.
-
-\end{enumerate}
-
-\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation}
-
-You can check the build status of Kodo, Fifi and other relevant projects
-through their respective repository master branch on our buildbot page
-\cite{steinwurf2016buildbot}. Our buildbot displays the status of the builds
-for Raspbian 8 and GCC 4.9 for the ARM architecture which is the relevant one
-for the \ac{Raspi}. At the link, you can check build status and build
-statistics. Also, documentation about Kodo basics with a tutorial is available
-at \cite{kododocs}.

### 2016-06-05 measurements.tex
Plot renaming
Results structure done

@@
         \caption[]%
-        {{\small Goodput vs. Generation size for $GF(2)$}}    
+        {{\small Goodput vs. Generation size for $q = 2$}}    
         \label{fig:enc_good_rasp1_gen_gf2}
@@
         \caption[]%
-        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
+        {{\small Goodput vs. Generation size for $q = 2^8$}}    
         \label{fig:enc_good_rasp1_gen_gf256}
@@
         \caption[]%
-        {{\small Goodput vs. Packet size for $GF(2)$ and $g=16$}}    
+        {{\small Goodput vs. Packet size for $q = 2,\ g=16$}}    
         \label{fig:enc_good_rasp1_packet_gf2}
@@
         \caption[]%
-        {{\small Goodput vs. Packet size for $GF(2^8)$ and $g=16$}}    
+        {{\small Goodput vs. Packet size for $q = 2^8,\ g=16$}}    
         \label{fig:enc_good_rasp1_packet_gf256}
@@
         \caption[]%
-        {{\small Goodput vs. Generation size for $GF(2)$}}    
+        {{\small Goodput vs. Generation size for $q = 2$}}    
         \label{fig:enc_good_rasp2_gen_gf2}
@@
         \caption[]%
-        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
+        {{\small Goodput vs. Generation size for $q = 2^8$}}    
         \label{fig:enc_good_rasp2_gen_gf256}
@@
         \caption[]%
-        {{\small Goodput vs. Packet size for $GF(2)$ and $g=16$}}    
+        {{\small Goodput vs. Packet size for $q = 2,\ g=16$}}    
         \label{fig:enc_good_rasp2_packet_gf2}
@@
         \caption[]%
-        {{\small Goodput vs. Packet size for $GF(2^8)$ and $g=16$}}    
+        {{\small Goodput vs. Packet size for $q = 2^8,\ g=16$}}    
         \label{fig:enc_good_rasp2_packet_gf256}
@@
 Fig. \ref{fig:dec_good_rasp1} shows the results of the decoder goodput
-measurements for the \ac{Raspi} 1. and \ref{fig:dec_good_rasp2} does
+measurements for the \ac{Raspi} 1 and Fig. \ref{fig:dec_good_rasp2} does
 the proper for \ac{Raspi} 2.
@@
         \caption[]%
-        {{\small Goodput vs. Generation size for $GF(2)$}}    
+        {{\small Goodput vs. Generation size for $q = 2$}}    
         \label{fig:dec_good_rasp1_gen_gf2}
@@
         \caption[]%
-        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
+        {{\small Goodput vs. Generation size for $q = 2^8$}}    
         \label{fig:dec_good_rasp1_gen_gf256}
@@
         \caption[]%
-        {{\small Goodput vs. Packet size for $GF(2)$ and $g=16$}}    
+        {{\small Goodput vs. Packet size for $q = 2,\ g=16$}}    
         \label{fig:dec_good_rasp1_packet_gf2}
@@
         \caption[]%
-        {{\small Goodput vs. Packet size for $GF(2^8)$ and $g=16$}}    
+        {{\small Goodput vs. Packet size for $q = 2^8,\ g=16$}}    
         \label{fig:dec_good_rasp1_packet_gf256}
@@
     \caption[]
-    {\small Encoder goodput measurements for the \ac{Raspi} 1} 
+    {\small Decoder goodput measurements for the \ac{Raspi} 1} 
     \label{fig:dec_good_rasp1}
@@
         \caption[]%
-        {{\small Goodput vs. Generation size for $GF(2)$}}    
+        {{\small Goodput vs. Generation size for $q = 2$}}    
         \label{fig:dec_good_rasp2_gen_gf2}
@@
         \caption[]%
-        {{\small Goodput vs. Generation size for $GF(2^8)$}}    
+        {{\small Goodput vs. Generation size for $q = 2^8$}}    
         \label{fig:dec_good_rasp2_gen_gf256}
@@
         \caption[]%
-        {{\small Goodput vs. Packet size for $GF(2)$ and $g=16$}}    
+        {{\small Goodput vs. Packet size for $q = 2,\ g=16$}}    
         \label{fig:dec_good_rasp2_packet_gf2}
@@
         \caption[]%
-        {{\small Goodput vs. Packet size for $GF(2^8)$ and $g=16$}}    
+        {{\small Goodput vs. Packet size for $q = 2^8,\ g=16$}}    
         \label{fig:dec_good_rasp2_packet_gf256}
@@
     \caption[]
-    {\small Encoder goodput measurements for the \ac{Raspi} 2} 
+    {\small Decoder goodput measurements for the \ac{Raspi} 2} 
     \label{fig:dec_good_rasp2}
@@
 \subsection{Average Power}
-Short section intro
+With the energy measurement setup described in Section \ref{sec:energy_metrics_methods},
+we compute the metrics described there. We first proceed with the average
+power consumption of the \ac{Raspi} 1 in Fig. \ref{fig:current_rasp1} and
+the \ac{Raspi} 2 in Fig. \ref{fig:current_rasp2}.
 
-Raspberry One
-\begin{figure}[ht!]
+\begin{figure*}
     \centering
-\includegraphics[width=0.7\textwidth]{images/current_vs_sec_raspberry_change_gen_from_-10sec_to_500sec.eps}
-\caption{Current measurements for the \ac{Raspi} 1}
-\label{current_rasp2}
-\end{figure}
+    \begin{subfigure}[b]{0.475\textwidth}
+        \centering
+        \includegraphics[width=1.15\textwidth]{images/current_vs_sec_raspberry_change_gen_from_-10sec_to_500sec.eps}
+        \caption[]%
+        {{\small Current for the \ac{Raspi} 1}}    
+        \label{fig:current_rasp1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.475\textwidth}  
+        \centering 
+        \includegraphics[width=1.15\textwidth]{images/current_vs_sec_raspberry2_change_gen_from_-10sec_to_500sec.eps}
+        \caption[]%
+        {{\small Current for the \ac{Raspi} 2}}    
+        \label{fig:current_rasp2}
+    \end{subfigure}
 
-Raspberry Two
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.7\textwidth]{images/current_vs_sec_raspberry2_change_gen_from_-10sec_to_500sec.eps}
-\caption{Current measurements for the \ac{Raspi} 2}
-\label{current_rasp2}
-\end{figure}
+    \caption[]
+    {\small Current consumption for each \ac{Raspi} model} 
+    \label{fig:current_rasp}
+\end{figure*}
+
+Average current description. Include a table mentioning the current values
+and the resulting power values.
 
 \subsection{Energy per bit}
+With power and goodput measurements, we compute the energy per bit of
+the previously mentioned cases in the same fashion as before.
+
+\subsubsection{Encoding}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.475\textwidth}
+        \centering
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_Binary_encoder_1600.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Generation size for $q = 2$}}    
+        \label{fig:enc_ene_rasp1_gen_gf2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.475\textwidth}  
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_Binary8_encoder_1600.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Generation size for $q = 2^8$}}    
+        \label{fig:enc_ene_rasp1_gen_gf256}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_Binary_encoder_128.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Packet size for $q=2,\ g=128$}}    
+        \label{fig:enc_ene_rasp1_packet_gf2}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_Binary8_encoder_128.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Packet size for $q=2^8,\ g=128$}}    
+        \label{fig:enc_ene_rasp1_packet_gf256}
+    \end{subfigure}
+    \caption[]
+    {\small Encoder energy measurements for the \ac{Raspi} 1} 
+    \label{fig:enc_ene_rasp1}
+\end{figure*}
+
+Raspi 2 encoding
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.475\textwidth}
+        \centering
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_v2_Binary_encoder_1600.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Generation size for $q = 2$}}    
+        \label{fig:enc_ene_rasp2_gen_gf2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.475\textwidth}  
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_encoder_1600.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Generation size for $q = 2^8$}}    
+        \label{fig:enc_ene_rasp2_gen_gf256}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_encoder_128.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Packet size for $q=2,\ g=128$}}    
+        \label{fig:enc_ene_rasp2_packet_gf2}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_encoder_128.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Packet size for $q=2^8,\ g=128$}}    
+        \label{fig:enc_ene_rasp2_packet_gf256}
+    \end{subfigure}
+    \caption[]
+    {\small Encoder energy measurements for the \ac{Raspi} 2} 
+    \label{fig:enc_ene_rasp2}
+\end{figure*}
+
+\subsubsection{Decoding}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.475\textwidth}
+        \centering
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_Binary_decoder_1600.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Generation size for $q = 2$}}    
+        \label{fig:dec_ene_rasp1_gen_gf2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.475\textwidth}  
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_Binary8_decoder_1600.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Generation size for $q = 2^8$}}    
+        \label{fig:dec_ene_rasp1_gen_gf256}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_Binary_decoder_128.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Packet size for $q=2,\ g=128$}}    
+        \label{fig:dec_ene_rasp1_packet_gf2}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_Binary8_decoder_128.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Packet size for $q=2^8,\ g=128$}}    
+        \label{fig:dec_ene_rasp1_packet_gf256}
+    \end{subfigure}
+    \caption[]
+    {\small Decoder energy measurements for the \ac{Raspi} 1} 
+    \label{fig:dec_ene_rasp1}
+\end{figure*}
+
+Raspi 2 decoding
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.475\textwidth}
+        \centering
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_v2_Binary_decoder_1600.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Generation size for $q = 2$}}    
+        \label{fig:dec_ene_rasp2_gen_gf2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.475\textwidth}  
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_decoder_1600.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Generation size for $q = 2^8$}}    
+        \label{fig:dec_ene_rasp2_gen_gf256}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_decoder_128.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Packet size for $q=2,\ g=128$}}    
+        \label{fig:dec_ene_rasp2_packet_gf2}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}[b]{0.475\textwidth}   
+        \centering 
+        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_decoder_128.eps}
+        \caption[]%
+        {{\small Energy per bit vs. Packet size for $q=2^8,\ g=128$}}    
+        \label{fig:dec_ene_rasp2_packet_gf256}
+    \end{subfigure}
+    \caption[]
+    {\small Decoder energy measurements for the \ac{Raspi} 2} 
+    \label{fig:dec_ene_rasp2}
+\end{figure*}
 

### 2016-06-05 metrics.tex
Results structure done

@@
 \subsection{Energetic Expenditure}
+\label{sec:energy_metrics_methods}
 In large-scale networks where several \ac{Raspi}s might be deployed,

### 2016-06-05 testbed.tex
fixed testbed intro

@@
 
-This section will present a testbed of thirty \ac{Raspi}s.
+%This section will present a testbed of thirty \ac{Raspi}s and a \ac{PC}
+The testbed consists of thirty \ac{Raspi}s that will be setup and controlled
+by a testbed administrator from a \ac{PC}.
 %Twenty \ac{Raspi} 1 model B revision 2 and ten \ac{Raspi} 2 model B V1.1.
-They are all equipped with a memory card and are connected to the
+The \ac{Raspi}s are each equipped with a memory card and connected to the
 university network by wire using their ethernet interface (eth0).
 
-To easily discover the \ac{Raspi}s within the university network, they have all
-been assigned a unique name under a common domain.
-This eliminates the need to remember their individual \ac{IP}s.
+To easily discover the \ac{Raspi}s within the university network,
+they have all been assigned a unique name under a common domain.
+This eliminates the need to remember their individual \ac{IP} addresses.
 
-A sketch of the testbed is depicted in figure~\ref{fig:testbed_setup}.
+A sketch of the testbed is depicted in Figure~\ref{fig:testbed_setup}.
 We have two types of \ac{Raspi}s in our setup.
-Table \ref{tab:rasp_naming} shows the naming convention.
+Table~\ref{tab:rasp_naming} shows the naming convention.
 
@@
     Rasp00 - Rasp19 & Raspberry Pi 1 model B rev. 2 \\ \hline
-    Rasp100 - Rasp109 & Rasperry Pi 2 model B V1.1 \\ \hline
+    Rasp20 - Rasp29 & Rasperry Pi 2 model B V1.1 \\ \hline
   \end{tabular}
@@
 
-Accessing them is easily done using \ac{SSH}.
-To address them within the university network,
-The \ac{Raspi}s
+%Accessing them is easily done using \ac{SSH}.
+%To address them within the university network,
+%The \ac{Raspi}s
 
-The \ac{Raspi}s are all equipped with an ethernet interface (eth0) and
-connected by wire to the university's \ac{LAN}. The university network
-administration was provided
-the \ac{MAC} addresses of the ethernet interfaces to automatically assign
-the devices the desired \ac{IP} addresses as shown in the figure. In a personal
-\ac{LAN}, another option could be to manually provide the devices with static
-\ac{IP}s.
+%The \ac{Raspi}s are all equipped with an ethernet interface (eth0) and
+%connected by wire to the university's \ac{LAN}. The university network
+%administration was provided
+%the \ac{MAC} addresses of the ethernet interfaces to automatically assign
+%the devices the desired \ac{IP} addresses as shown in the figure. In a personal
+%\ac{LAN}, another option could be to manually provide the devices with static
+%\ac{IP}s.
 
-This section will be used to present a \ac{Raspi} testbed and the steps to
-install and configure its devices.
+%This section will be used to present a \ac{Raspi} testbed and the steps to
+%install and configure its devices.
 
-The testbed is depicted in figure~\ref{fig:testbed_setup}. It consists of twenty
-Raspberry Pi 1 model B rev 2 (Rasp01 to Rasp20) and
-ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).
+%The testbed is depicted in figure~\ref{fig:testbed_setup}. It consists of twenty
+%Raspberry Pi 1 model B rev 2 (Rasp01 to Rasp20) and
+%ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).
 
-The goal is to configure all the \ac{Raspi}s identically with the same software
-and configurations. There are however a few differences between them that we
-need to take into account. E.g. hostname and network addresses.
+The testbed should be usable by students to perform simulations and
+measurements as part of their semester projects. It is therefore desired
+that the \ac{Raspi}s are configured identically, but still allows the
+students to alter the configurations.
 
-The testbed will be used by students that might need to change how the
-devices are work either temporary or permanently. We will illustrate how this
-can be accomplished using an overlaying filesystem.
+When working on a testbed, it is not always desired to make persistant
+changes to the devices. We also present how the concept of stacked
+filesystems can be used to enable the means of both persistant and
+temporary storage.
 
-Finally, it should be possible to store data that are generated from
-simulations on the memory cards that are in the individual \ac{Raspi}.
+%It is therefore
+%mandatory that the \ac{Raspi}s are easily configurable but also
+%desired to
+
+%The testbed should be usable by students that should be able to configure
+%the \ac{Raspi}'s as desired. It is therefore
+
+%The testbed will be used by students that might need to change how the
+%devices are work either temporary or permanently. We will illustrate how this
+%can be accomplished using an overlaying filesystem.
+
+%The goal is to configure all the \ac{Raspi}s identically with the same software
+%and configurations. There are however a few differences between them that we
+%need to take into account. E.g. hostname and network addresses.
+
+%Finally, it should be possible to store data that are generated from
+%simulations on the memory cards that are in the individual \ac{Raspi}.
 %We using a overlaying filesystem that
@@
 
-The \ac{Raspi}s are all equipped with an ethernet interface (eth0) and
-connected by wire to the university's \ac{LAN}. The university network
-administration was provided
-the \ac{MAC} addresses of the ethernet interfaces to automatically assign
-the devices the desired \ac{IP} addresses as shown in the figure. In a personal
-\ac{LAN}, another option could be to manually provide the devices with static
-\ac{IP}s.
+%The \ac{Raspi}s are all equipped with an ethernet interface (eth0) and
+%connected by wire to the university's \ac{LAN}. The university network
+%administration was provided
+%the \ac{MAC} addresses of the ethernet interfaces to automatically assign
+%the devices the desired \ac{IP} addresses as shown in the figure. In a personal
+%\ac{LAN}, another option could be to manually provide the devices with static
+%\ac{IP}s.
 %that are
@@
 
-We use standard usb power adapters to power the \ac{Raspi}s.
+%We use standard usb power adapters to power the \ac{Raspi}s.
 
@@
 $ cd ${WORKDIR}
-$ wget http://downloads.raspberrypi.org/raspbian_lite/images/raspbian_lite-2016-05-31/${IMAGE}.zip
+$ wget http://kom.aau.dk/project/TuneSCode/raspi/${IMAGE}.zip
 $ unzip ${IMAGE}.zip
@@
 \FloatBarrier
+
+A more recent version of Raspbian lite may be available on 
+\url{http://downloads.raspberrypi.org/raspbian_lite/images}.
 

### 2016-06-05 testbed.tex
More fixes to testbed intro

@@
 To get started, we first need to install an \ac{OS} on the
-Raspberry Pis. We will use Raspbian linux~\cite{raspbian}
+\ac{Raspi}s. We will use Raspbian linux~\cite{raspbian}
 
-We will use a desktop that has linux installed to download,
-configure, and write the image to the memory cards.
+We will be using a \ac{PC} running a Debian-based linux distribution
+to setup a customized Raspbian linux image that can be written to
+a memory card and work in any \ac{Raspi} version 1 or 2.
+%We will use a desktop that has linux installed to download,
+%configure, and write the image to the memory cards.
 %We have decided to use a linux desktop machine to create a
@@
 
-We have decided to go with Raspbian linux~\cite{raspbian} and
-to install it on memory cards.
+%We have decided to go with Raspbian linux~\cite{raspbian} and
+%to install it on memory cards.
 
@@
 
-There exists a number of ways to setup a testbed
+%There exists a number of ways to setup a testbed
+%
+%with multiple devices. We
+%have decided on a very simple approach of simply instal
 
-with multiple devices. We
-have decided on a very simple approach of simply instal
+%-
+%- Download image (wget)
+%- Update/Modify image (chroot)
+%- Burn image
+%- Bang! linux is running
+%-
 
--
-- Download image (wget)
-- Update/Modify image (chroot)
-- Burn image
-- Bang! linux is running
--
+%Open a terminal, and then...
 
-Open a terminal, and then...
+\textbf{hashmark (\#) means to perform operation as root, dollar (\$) means
+to perform operation as user}
 
-hashmark (\#) means to perform operation as root, dollar (\$) means to perform operation as user
-
-The first thing we need to do is to download the linux installation file.
-For Raspbian, this is available at \url{http://downloads.raspberrypi.org}.
+%The first thing we need to do is to download the linux installation file.
+%For Raspbian, this is available at \url{http://downloads.raspberrypi.org}.
 
@@
 The difference between the two is that Raspbian contains a pre-installed desktop
-environment, and Raspbian lite is by default only accessable through a shell. 
-They will both also be remotely accessible using \ac{SSH}.
+environment, and Raspbian lite is by default only accessible through a 
+command shell. 
+Both Raspbian and Raspbian lite will both by default be remotely
+accessible using \ac{SSH}. \ac{SSH} provides the means to remotely
+connect to another machine through a command shell. In fact it is the successor
+of \ac{Telnet} that has been designed with network security in mind.
 
 Our testbed does not have monitors so we will install Raspbian lite.
-A desktop environment can always be installed manually in case that will be
-desired sometime in the future.
+A desktop environment can be installed using Raspbian's package manager
+(apt-get) in case a desktop environment will be desired sometime in the future.
 
-Below is a procedure of how we setup the \ac{Raspi}s in our testbed. We
-have decided a simple setup where each \ac{Raspi} is equipped with a
+Below is the procedure we did to setup the \ac{Raspi}s in our testbed. We
+have performed a simple setup where each \ac{Raspi} is equipped with a
 memory card that contains a slightly customized Raspbian lite image with
@@
 
-The reason this can be done easily is because the official Raspbian lite image
-that we will download simply conntains a complete linux installation that are
-packaged in an image rather than written to a harddrive, memory card, or usb
-pen.
+%The reason this can be done easily is because the official Raspbian lite image
+%that we will download simply conntains a complete linux installation that are
+%packaged in an image rather than written to a harddrive, memory card, or usb
+%pen.
 
-The overall steps to customize the official Raspbian lite image are listed below:
+The overall procedure to customize the official Raspbian lite image
+are:
 \begin{enumerate}

### 2016-06-06 cross_compilation.tex
worked on cross compiling

@@
 
-WRITE INTRO OF WHY WE WANT TO CROSS COMPILE. E.G. 1) WE DO NOT HAVE MONITORS
-CONNECTED TO THE RASPIS, 2) A PC IS SIGNIFICANTLY FASTER AND FAR BETTER EQUIPPED (RAM, CPU, HARDDRIVE), 3) MORE CONVINIENT TO DO EVERYTHING IN ONE PC AND DISTRIBUTE IT TO THE RASPIS AFTERWARDS. MORE?
+Modern \ac{PC}s are significantly better equipped than the \ac{Raspi}s that in
+contrasts to \ac{PC}s target a far more affortable and smaller module size. This
+means that it may be preferred or even mandatory to perform some computational
+expensive tasks in a \ac{PC} rather than in \ac{Raspi}s.
+Example of tasks that are quite computational expensive is to compile software
+packages and large libraries.
+Another reason to use a \ac{PC} may be the hardware limitations of \ac{Raspi}s
+in terms of e.g. memory and disk space. Some software packages might simply be
+too memory demanding to be compiled in a \ac{Raspi}.
+Thus, this section will present how to setup a toolchain in a \ac{PC} that can
+be used to cross compile C++ code to the ARM architecture that the \ac{Raspi}s.
+The toolchain is mandatory on most consumer \ac{PC}s due to the different
+processor architecture.
+
+Furthermore, we will cover how to cross compile a simple C++ example and
+Kodo-cpp as well as how the binaries can be copied from a \ac{PC} to a
+\ac{Raspi} and executed.
+There exists bindings to Kodo in various programming language. We will present
+how to also run a Kodo-python application in a \ac{Raspi}.
+
+%WRITE INTRO OF WHY WE WANT TO CROSS COMPILE. E.G. 1) WE DO NOT HAVE MONITORS
+%CONNECTED TO THE RASPIS, 2) A PC IS SIGNIFICANTLY FASTER AND FAR BETTER EQUIPPED (RAM, CPU, HARDDRIVE), 3) MORE CONVINIENT TO DO EVERYTHING IN ONE PC AND DISTRIBUTE IT TO THE RASPIS AFTERWARDS. MORE?
 
@@
 
-Besides the previous description (\textbf{Include compiling Kodo from the
-RasPi from the scratch}), the testbed administrator can compile Kodo in its
-personal workstation and transfer the generated binaries directly to
-a path in the \ac{Raspi}. To achieve this, we get a toolchain that
-contains the binaries for the \texttt{raspberry-gxx49-arm-g++} compiler
-for the \ac{Raspi}. Therefore, we strongly recommend any testbed
-administrator to do the following procedure. In what follows, we provide
-the instructions considering that the NFS server uses the \texttt{\$HOME}
-directory as the working directory. However, the administrator may choose
-some other working directory of its preference if desired.
+%Besides the previous description (\textbf{Include compiling Kodo from the
+%RasPi from the scratch}), the testbed administrator can compile Kodo in its
+%personal workstation and transfer the generated binaries directly to
+%a path in the \ac{Raspi}. To achieve this, we get a toolchain that
+%contains the binaries for the \texttt{raspberry-gxx49-arm-g++} compiler
+%for the \ac{Raspi}. Therefore, we strongly recommend any testbed
+%administrator to do the following procedure. In what follows, we provide
+%the instructions considering that the NFS server uses the \texttt{\$HOME}
+%directory as the working directory. However, the administrator may choose
+%some other working directory of its preference if desired.
 
@@
 
-Create a directory to hold our code:
+The following example will provide a very basic example of 1) how to cross compile
+a \texttt{hello\_world} c++ example to the \ac{Raspi}'s ARM architecture
+and 2) how to copy and execute the binary in a \ac{Raspi} using \ac{SCP} and \ac{SSH}.
+
+Lets create a directory to hold our code:
 \begin{lstlisting}[]
@@
 
-Create a \texttt{hello\_world.cpp} using your favorite text editor:
+Create the file \texttt{hello\_world.cpp} with the following content using your
+favorite text editor:
 
@@
 
-Lets copy the executable file to a \ac{Raspi} and test it. We will use \ac{SCP}
-to copy the executable to one of the \ac{Raspi}s.
+This should produce a binary \texttt{hello\_world}. Copy it to a \ac{Raspi}
+and test it. We will use \ac{SCP} to copy the binary file to one of the \ac{Raspi}s.
 
-Default username is "pi" and password is "raspberry"
+The default username for our Raspbian lite distribution is "pi" and password is "raspberry"
 
@@
 
-Now, simply execute the \texttt{hello\_world}:
+Now, simply execute the \texttt{hello\_world} to confirm that cross compiling
+\texttt{hello\_world} worked properly:
 
@@
 
-WRITE SOME SMALL INTRO AND MENTION HOW TO REQUEST A KODO LICENSE
+Kodo is a C++11 library for \ac{NC}. There exists a number of bindings for
+Kodo to other popular programming languages. This procedure will go through
+how to setup Kodo-cpp to cross compile to \ac{Raspi}. Kodo-cpp provides a
+simple interface to the underlying C++11 code that exists in the libraries
+Kodo-core and Kodo-rlnc.
+
+In order to use Kodo, it is required to obtain a research- and
+education-friendly license.
+A license can be obtained from \url{http://steinwurf.com/license.html}. It is
+free for research and educational purposes.
 

### 2016-06-06 cross_compilation.tex
Finished kodo-cpp

@@
 
+A more detailed procedure of setting up Kodo-cpp than provided below is available at
+\url{http://docs.steinwurf.com/kodo/kodo-cpp/index.html}
+
 \begin{enumerate}
 
-\item Create a directory to hold our code:
+\item Start by creating a directory to hold our code:
 \begin{lstlisting}[]
@@
 
-\item Clone the Kodo repository and change directory into the repository: \\
+\item Clone the Kodo repository and change directory into the repository:
 \begin{lstlisting}[]
@@
 
-\item SHARED and/or STATIC libraries
-\item COPY TO RASPI
-\item RUN EXECUTABLE encode\_decode\_simple
+\item Make shared library:
+\begin{lstlisting}[]
+$ python waf install --install_shared_libs --install_path="./shared_test"
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\item Copy shared library to a \ac{Raspi}'s home directory (Alternatively, Kodo can also generate static libraries):
+\begin{lstlisting}[]
+$ scp -r shared_test/include shared_test/libkodoc.so pi@<RASP_IP>:~/
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\item Copy a binary using Kodo shared library to the \ac{Raspi}'s home directory:
+\begin{lstlisting}[]
+$ scp -r shared_test/encode_decode_simple pi@<RASP_IP>:~/
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\item Execute binary:
+\begin{lstlisting}[]
+$ ssh pi@<RASP_IP> ./encode_decode_simple
+Data decoded correctly
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Cross compiling Kodo applications works provided that above command
+returned "Data decoded correctly".
 

### 2016-06-06 measurements.tex
Describing TSNC in the results

@@
 function of the packet size for $GF(2)$ and $GF(2^8)$ respectively. In this
-case the gneation size was set to $g = 16$ packets.
+case the generation size was set to $g = 16$ packets.
 
+Similarly, Fig. \ref{fig:enc_good_rasp2} shows the same set of
+measurements for the \ac{Raspi} 2. Hence, Figs. \ref{fig:enc_good_rasp2_gen_gf2}
+and \ref{fig:enc_good_rasp2_gen_gf256} present goodput as function of the
+generation size  and Figs. \ref{fig:enc_good_rasp2_packet_gf2} and 
+\ref{fig:enc_good_rasp2_packet_gf256} as a function of the packet size for the
+same cases mentioned previously. Therefore, we will proceed to make the
+results analysis with \ac{Raspi} 1 and indicate which similarities or
+differences occur for the \ac{Raspi} 2 and when do they occur.
+%
 \begin{figure*}
@@
 \end{figure*}
+%
+As it can seen in the from: Figs. \ref{fig:enc_good_rasp1_gen_gf2},
+\ref{fig:enc_good_rasp1_gen_gf256}, \ref{fig:enc_good_rasp2_gen_gf2} and
+\ref{fig:enc_good_rasp2_gen_gf256}; which indicate the goodput dependency
+on the generation size, the encoding goodput gets reduced as the generation
+size increases, regardless of the \ac{Raspi} model observed. The reason
+is that the encoding operation processing is $\mathcal{O}(g)$ because
+it is required to create $g$ coding coefficients and do $g$ multiplications
+for each packet. This makes the goodput to scale as the inverse of the
+generation size.
 
-Similarly, Fig. \ref{fig:enc_good_rasp2} shows the same set of
-measurements for the \ac{Raspi} 2. Hence, Figs. \ref{fig:enc_good_rasp2_gen_gf2}
-and \ref{fig:enc_good_rasp2_gen_gf256} present goodput as function of the
-generation size  and Figs. \ref{fig:enc_good_rasp2_packet_gf2} and 
-\ref{fig:enc_good_rasp2_packet_gf256} as a function of the packet size for the
-same cases mentioned previously.
+In the sets of figures shown in Figs.~\ref{fig:enc_good_rasp1} and
+\ref{fig:enc_good_rasp2}, it can be observed that the goodput for $GF(2)$
+is higher than for $GF(2^8)$ but still around the same order of magnitud.
+This difference is explained by noticing that \ac{GF} arithmetics in the
+binary field are simply XOR or AND operations. These operations are
+implemented efficiently by most of the architectures nowday and are
+tailored to be fast in principle. However, the operations in $GF(2^8)$
+are more complex given that the finite field arithmetics have to be
+performed with lookup tables which at the end reduces the computing
+speed giving a lower goodput when compared with the binary field.
 
+In \ref{fig:enc_good_rasp1_gen_gf2}, \ref{fig:enc_good_rasp1_gen_gf256},
+\ref{fig:enc_good_rasp2_gen_gf2} and \ref{fig:enc_good_rasp2_gen_gf256};
+it can be seen the goodput trends of 5 codes as a function of
+the generation size: \ac{RLNC}, \ac{SRLNC} with $d = [0.02,\ 0.1]$
+and \ac{TSNC} with two parameters that we mention. The first of them,
+$steps$, is the number of density changes in the system, if any.
+The number of changes is equal to the number of regions minus 1, making
+$steps = \#regions - 1$ and $dep = e$. With these definitions, we first
+evaluate \ac{TSNC} with no changes, e.g. $steps=0$ and the two amounts
+for dependent packets mentioned earlier. In this way the budget is
+either $g + 8$ or $g + 16$. The goal with setting first \ac{TSNC} with
+these values is to observe first the sole effect of the budget in the code
+since $steps = 0$ implies no density changes during the whole process.
+%
 \begin{figure*}

### 2016-06-06 cross_compilation.tex

@@
 
-\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation}
+\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation (WHAT IS THE PURPOSE OF THIS SUBSECTION?)}
 
@@
 \subsection{Kodo python}
+
+Often when simplicity and fast prototyping is of higher importance than speed
+it is often desired to use a scripting language rather than the often faster
+compiled language. Kodo-python provides roughly similar bindings to the
+underlying C++11 implementation of Kodo as Kodo-cpp does. This means that
+python calls to Kodo-python are actually executed in the underlying C++11
+compilied code.
+
+Parsing calls and variables between Python and C++ compiled code is
+not free, but this small introduced overhead may in many cases be worth
+it to take advantage of Pythons and other scripting languages many
+benefits.
+
+Below is a short procedure to use Kodo-python in a \ac{Raspi}.
+
+One advantage of Python compared to Kodo-cpp is that only the Kodo-python
+library needs to be cross compiled. The python scripts using the Kodo
+library needs not to be cross compiled but simply copied to the same
+directory as .
+
+Kodo-python is available at \url{https://github.com/steinwurf/kodo-python}.
+
+\begin{lstlisting}[]
+$ apt-get update
+$ apt-get install python build-essential libpython-dev python-dev
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+% IN ARCH LINUX, MOD_PYTHON NEEDS TO BE INSTALLED
+
+Create a directory to hold our code:
+\begin{lstlisting}[]
+$ CODEDIR="${HOME}/code"
+$ mkdir -p ${CODEDIR}
+$ cd ${CODEDIR}
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\begin{lstlisting}[]
+$ git clone git@github.com:steinwurf/kodo-python.git 
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\begin{lstlisting}[]
+$ cd kodo-python
+$ python2.7 waf configure --cxx_mkspec=cxx_raspberry_gxx49_arm
+$ python waf build
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+KODO-PYTHON IS NOT WORKING!! WAITING FOR HELP ON STEINWURF DEV.
 
@@
 env.hosts = ['rasp00.domain.com','rasp01.domain.com','rasp02.domain.com']
-env.user = 'root'
-env.password = 'sdn'
+env.user = 'pi'
+env.password = 'raspberry'
 
@@
 
-\subsection{Long running jobs over SSH (PUT THIS SECTION SOMEWHERE ELSE)}
+\subsection{Long running jobs using SSH}
 
-Problem when you logout, then applications will terminate. SCREEN is the answer.
+There may be times when it is desired to start a simulation that will
+run for days. For that purpose, it may not be desired to keep
+a \ac{SSH} connection open to the \ac{Raspi} risking that the connection
+will be interrupted and thus result in the \ac{Raspi} terminating
+the running simulation.
 
-EXAMPLE
+There exists a few methods to avoid this risk of simulations terminating
+unexpectedly. One method is to run a program within a \texttt{screen} session.
 
-\texttt{hello\_world} returns immediately. This is not always the case.
-Sometimes it is desired to run simulations that should run for days. 
-A software package called \texttt{screen} can be used for this purpose.
-Simply run ...
+\texttt{screen} enables a user to attach and detach the session as it is
+desired. Programs within the screen session just keeps running.
+
+The following procedure will present how to use SSH to
+\begin{enumerate}
+    \item login to a \ac{Raspi}
+    \item open a screen session
+    \item execute a command
+    \item detach from the screen session
+    \item terminate SSH connection
+    \item login to the \ac{Raspi} again
+    \item attach to screen session to see the program still running
+\end{enumerate}
+
+Start by establishing SSH connection to a \ac{Raspi} and open a screen session:
+\begin{lstlisting}[]
+$ SSH pi@<RASP_IP>
+$ screen
+Screen version 4.02.01 (GNU) 28-Apr-14
+...
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+Press space or return to to clear the shell.
+
+At this stage, we are in a screen session. Now execute a program that never ends:
+\begin{lstlisting}[]
+$ top
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Now that \texttt{top} is running, press Ctrl+a Crtl+d to detach from
+the \texttt{screen} session.
+
+Terminate the SSH connection and login again:
+\begin{lstlisting}[]
+$ exit
+$ SSH pi@<RASP_IP>
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Now that we are logged in to the \ac{Raspi} again, lets see if a
+\texttt{screen} session is still running:
+\begin{lstlisting}[]
+$ screen -list
+There is a screen on:
+	1668.pts-0.rasp09	(06/06/16 04:02:15)	(Detached)
+1 Socket in /var/run/screen/S-pi.
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+It can be seen that our session is still running and that we are
+currently not attached. Lets attach to the session:
+\begin{lstlisting}[]
+$ screen -r 1668.pts-0.rasp09
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+After attaching again, \texttt{top} should still be running. \texttt{screen}
+has a few more useful functionalities that is outside the scope of this
+paper.
+
+To terminate the \texttt{screen} session. First, terminate \texttt{top}
+by pressing 'q', and then type 'exit' two times to first exit the
+\texttt{screen} session and then terminate the \ac{SSH} connection:
+
+%Problem when you logout, then applications will terminate. SCREEN is the answer.
+
+%\texttt{hello\_world} returns immediately. This is not always the case.
+%Sometimes it is desired to run simulations that should run for days. 
+%A software package called \texttt{screen} can be used for this purpose.
+%Simply run ...

### 2016-06-06 cross_compilation.tex
finished fabric

@@
 
-SHORT INTRO. EXPLAIN A FEW USECASES FOR FABRIC. E.G. REBOOT, INSTALL PACKAGE, RUN SCRIPT ON MULTIPLE RASPIS. COPY FILES TO/FROM PC AND MULTIPLE RASPIS
+Controlling multiple devices using \ac{SSH} from a single \ac{PC}
+often leads to a lot of repetitive work. E.g.
+
+\begin{itemize}
+    \item rebooting a set of devices
+    \item installing applications in multiple devices
+    \item copy files to/from multiple devices
+    %\item run a script in multiple devices
+\end{itemize}
+
+\texttt{Fabric} provides a python library to ease the task of working
+with multiple devices from a single \ac{PC}. The code below provides
+a small script that can perform the few items above:
+
+%SHORT INTRO. EXPLAIN A FEW USECASES FOR FABRIC. E.G. REBOOT, INSTALL PACKAGE, RUN SCRIPT ON MULTIPLE RASPIS. COPY FILES TO/FROM PC AND MULTIPLE RASPIS
 
 % Exit chroot, umount, and write to memory card
-\begin{lstlisting}[]
+\Suppressnumber\begin{lstlisting}[]
+<@\textcolor{gray}{\$CODEDIR/fabfile.py}@>
+<@\textcolor{gray}{
+-------------------------------------------}
+\Reactivatenumber @>
 from fabric.api import run, env, task
@@
 @task
+def reboot():
+    """ Reboot device """
+    sudo('reboot', quiet=True)
+
+@task
 def install(program):
@@
     """
-    result = run('apt-get install -y {}'.format(program), quiet=True)
+    result = sudo('apt-get install -y {}'.format(program), quiet=True)
+    print(result)
 
 @task
-def copy_to_rasp(filename):
-    put(...)
+def push(src,dst):
+    """
+    Copy file to device
+    src: source file path
+    dst: destination file path
+    """
+    put(src, dst)
 
@@
 
-execute a script function by calling "fab install:feh"
+The script functions can be called from the command shell in the following
+manner. Notice how fab automatically searches the directory for a file 
+named 'fabfile.py' and how fab is called with function name and arguments
+'fab <FUNCTION>:arg1,arg2,...:
+\begin{lstlisting}[]
+$ fab reboot
+$ fab install:tmux
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\begin{lstlisting}[]
+$ fab reboot
+$ fab install:tmux
+$ fab push:"${CODEDIR}/hello_world",'~/'
+[192.168.87.107] Executing task 'push'
+[192.168.87.107] put: /home/<USER>/code/hello_world -> /home/pi/hello_world
+
+Done.
+Disconnecting from 192.168.87.107... done.
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+%execute a script function by calling "fab install:feh"
 

### 2016-06-06 schemes.tex

@@
 beginning of the transmission process and also to control the decoding
-delay. For \ac{TSNC}, we define the budget, $B \geq g$, to be a target
+delay. For \ac{TSNC}, we define the budget, $b \geq g$, to be a target
 number of coded packets a transmitter wants to send to a receiver
-for decoding a generation of $g$ packets.
+for decoding a generation of $g$ packets. In some scenarios, we may set
+$e$ defined as the excess of \ac{l.d.} packets sent from the encoder.
+This helps to also define the budget as $b = g + e$.
 
-The difference between $B$ and $g$ is equal to the losses in the channel and the
+The difference between $b$ and $g$ is equal to the losses in the channel and the
 losses due to linear dependencies. Therefore, in a lossless channel, the budget
@@
 \begin{equation}\label{eq:budget}
-    B(g,d)=\sum^{g-1}_{i=0}\frac{1}{P(i,g,d)},
+    b(g,d)=\sum^{g-1}_{i=0}\frac{1}{P(i,g,d)}
 \end{equation}
 
-where $P(i,n,d)$ is the probability of receiving an innovative coded packet
+where $P(i,g,d)$ is the probability of receiving an innovative coded packet
 after receiving $i$ \ac{l.i.} packets with a coding density $d$. In our implementations, we considered the the upper bound for the innovation probability from \cite{feizi2014tunable}, given as
 \begin{equation}
-    P(i,g,d)\geq 1-(1-d)^{n-i}
+    P(i,g,d)\geq 1-(1-d)^{g-i}
 \end{equation}
 
-Provided a desired budget $B$ and the \ac{dof} of the decoder, an encoder
+Provided a desired budget $b$ and the \ac{dof} of the decoder, an encoder
 can estimate the required coding density for the packets to not exceed the
@@
 feedback is received, an encoder recalculates the coding density for the new
-region until the next feedback packet is received. Before the coding density can
+region until the next feedback packet is received. before the coding density can
 be estimated, it is essential that the encoder has a good estimate of the
@@
 \begin{equation}
-B(s(k-1),r(k),g,d) = \sum^{r(k)}_{i=r(k-1)} \frac{1}{P(i,g,d)} = \sum^{r(k)}_{i=r(k-1)} \frac{1}{1-(1-d)^{g-i}} = \frac{B}{2^k}, k\in [1,...).
+b(s(k-1),r(k),g,d) = \sum^{r(k)}_{i=r(k-1)} \frac{1}{P(i,g,d)} = \sum^{r(k)}_{i=r(k-1)} \frac{1}{1-(1-d)^{g-i}} = \frac{b}{2^k}, k\in [1,...).
 \end{equation}

### 2016-06-06 raspi_journal.tex
Ready for now..
Update Simon and Juan figures
Extracting the figures from the pdf does not look good
testbed and cross compilation
Setting goodput plots
Results structure done
Added abstract

@@
 \newcommand\floor[1]{\left\lfloor#1\right\rfloor}
+
+\newcommand{\todot}[1]{%
+  \textcolor{red}{TODO: #1}
+}
 
@@
 
+% *** ALGORITHM PACKAGE ***
 \usepackage[]{algorithm2e}
+
+% *** PDF PACKAGE *** ..to extract a page from a PDF with multiple pages.
+\usepackage{pdfpages}
 
@@
 % Authors, for metadata in PDF
-\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Simon Wunderlich, Daniel Lucani and Frank Fitzek}
-
+\AuthorNames{Nestor Hernandez, Chres W. Soerensen, Juan Cabrera, Simon Wunderlich, Daniel E. Lucani and Frank H. P. Fitzek}  
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
@@
 % Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{Due to the recurrent nature }
+\abstract{Deploying a large-scale and configurable testbed for
+  networking and storage can be challenging, not only due to the
+  inherent costs of the hardware, but due to maintenance challenges
+  and ability to replicate results consistently. The latter requires
+  not only the devices to run the same operating system (OS), but also
+  have exactly the same configurations and software packages. This
+  paper presents the design, step-by-step setup, and configuration of
+  an inexpensive testbed using Raspberry Pi devices for networking
+  (wireless or wired) and storage applications, although the
+  architecture can be used for other applciations that require
+  replicable results.  Specifically, we provide an in-depth
+  performance evaluation for network coding, a new paradigm in
+  networking and storage, and demonstrating the processing
+  capabilities and energy behaviour of various code constructions and
+  algorithms over different Raspberry Pi models. Our results show that
+  processing speeds of more than 80 Mbps and 800 Mbps are attainable
+  for a wide array of configurations are attainable for the Raspberry
+  Pi Model 1 and 2, respectively, and that processing energy for
+  network coding is below 1 nJ/bit in a large regime and even an order
+  of magnitude lower for some algorithms.}
 
@@
 
+\section{Cross-compilation: From PC to Raspberry Pi}
+\input{cross_compilation}
+
 \section{Coding Schemes}
@@
 
-\section{Analyzed Metrics}
+\section{Metrics and Measurement Methodology}
 \input{metrics}

### 2016-06-06 measurements.tex
Results description for generation size done

@@
 Similarly, Fig. \ref{fig:enc_good_rasp2} shows the same set of
-measurements for the \ac{Raspi} 2. Hence, Figs. \ref{fig:enc_good_rasp2_gen_gf2}
-and \ref{fig:enc_good_rasp2_gen_gf256} present goodput as function of the
-generation size  and Figs. \ref{fig:enc_good_rasp2_packet_gf2} and 
-\ref{fig:enc_good_rasp2_packet_gf256} as a function of the packet size for the
-same cases mentioned previously. Therefore, we will proceed to make the
-results analysis with \ac{Raspi} 1 and indicate which similarities or
-differences occur for the \ac{Raspi} 2 and when do they occur.
+measurements for the \ac{Raspi} 2. Hence, Figs.
+\ref{fig:enc_good_rasp2_gen_gf2} and \ref{fig:enc_good_rasp2_gen_gf256}
+present goodput as function of the generation size  and
+Figs. \ref{fig:enc_good_rasp2_packet_gf2} and
+\ref{fig:enc_good_rasp2_packet_gf256} as a function of the packet size
+for the same cases mentioned previously. Therefore, we will proceed
+to make the results analysis with \ac{Raspi} 1 and indicate which
+similarities or differences occur for the \ac{Raspi} 2 and when do
+they occur.
 %
@@
 for dependent packets mentioned earlier. In this way the budget is
-either $g + 8$ or $g + 16$. The goal with setting first \ac{TSNC} with
-these values is to observe first the sole effect of the budget in the code
-since $steps = 0$ implies no density changes during the whole process.
+either $g + 8$ or $g + 16$. This means that we tolerate at most 8 or 16
+packets regardless of the generation. The goal with setting first
+\ac{TSNC} with these values is to observe first the sole effect of the
+budget in the code since $steps = 0$ implies no density changes during
+the whole process.
+
+For the plots in the mentioned figures from the encoder goodput measurements,
+\ac{RLNC} presents the worst performance in terms of goodput and
+\ac{TSNC} with $dep = 16$, the best regardless of the \ac{Raspi} model.
+Given that the processing time depends in the amount of coded packets
+required to create, \ac{RLNC} is the slowest to process since it must
+use all of the $g$ original packets. Later, sparse codes process the data
+at a larger rate since less packets are being mixed when creating a
+coded packet. The caveat of these schemes is that the sparser the code,
+the more probable the ocurrences of \ac{l.d.} packets is. So, basically
+the sparser the codes, then more overhead due to transmissions of \ac{l.d.}
+packets they have since it is more likely to generate the same set of
+packets. Excluding the coding coefficients overhead, the overhead due to
+transmissions of \ac{l.d.} packets can be very high.
+For example, if we consider \ac{TSNC} with $dep=16$ and $g = 16$, the budget
+in this case permits to send up to 32 packets which is $2\times$ the generation
+size for an overhead of $100\%$ excluding the one from the coding
+coefficients. This happens because \ac{TSNC} is allowed to add too much
+redundancy in this case, which permits it to use a very low code density $d$.
+For \ac{RLNC} this is not the case, since the occurrence of \ac{l.d.} coded
+packets is low. Even for $GF(2)$, the average amount of redundancy has proven
+to be 1.6 packets after $g$ have been transmitted.
+
 %

### 2016-06-06 measurements.tex
Some changes in the measurements description and couple of in the abstract

@@
 packets is low. Even for $GF(2)$, the average amount of redundancy has proven
-to be 1.6 packets after $g$ have been transmitted.
-
+to be 1.6 packets after $g$ have been transmitted, much less than the
+cases where sparse codes are employed. Overall, we observe that there is
+a trade-off between goodput and \ac{l.d.} coded packets transmission
+overhead.
 %

### 2016-06-06 raspi_journal.tex
Some changes in the measurements description and couple of in the abstract

@@
   (wireless or wired) and storage applications, although the
-  architecture can be used for other applciations that require
+  architecture can be used for other applications that require
   replicable results.  Specifically, we provide an in-depth
@@
   for a wide array of configurations are attainable for the Raspberry
-  Pi Model 1 and 2, respectively, and that processing energy for
-  network coding is below 1 nJ/bit in a large regime and even an order
+  Pi Model 1 and 2, respectively, and that processing energy per bit for
+  network coding is below 1 nJ in a large regime and even an order
   of magnitude lower for some algorithms.}
@@
   %escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
-  escapeinside={<@}{@>}
+  escapeinside={<@}{@>},
   extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8

### 2016-06-06 conclusions.tex
Reorganizing the document and adding basic conclusions

\label{sec:conclusions}
Given the need for a \ac{Raspi} testbed easy to configure and maintain
for network coding applications where results could be reproducible
in a simple fashion, we provide a testbed description at Aalborg
University with an in-depth performance evaluation for network coding
schemes to indicate the processing capabilities and energy behaviour
for two \ac{Raspi} models both of using their \ac{SIMD} capabilities
and considering a multicore implementation for the \ac{Raspi} 2. Our
findings report that processing speeds of more than X Mbps and Y Mbps are attainable for \textbf{[goodput scenarios]}, respectively, and that
processing energy per bit for network coding is below 1 nJ in a large regime
and even an order of magnitude lower for some algorithms with the same power consumption for \textbf{[goodput scenarios]}. Future work in this area,
will be to evaluate further elaborated codecs, expand the setup and
automation of tasks within the testbed creation, consider other working
topologies and include a description for network connectivity where the
testbed has more autonomy with \ac{IP} address assignment.

### 2016-06-06 measurements.tex
Reorganizing the document and adding basic conclusions

@@
 For the goodput, we separate the results according to their time benchmarks
-as we did in Section \ref{sec:metrics} sicne their consider different
+as we did in Section \ref{sec:metrics} since their consider different
 methodologies. We proceed first with the measurements related to the encoder
@@
 \subsubsection{Encoding}
-
 Fig. \ref{fig:enc_good_rasp1} shows the results of the encoder goodput
@@
 coefficients. This happens because \ac{TSNC} is allowed to add too much
-redundancy in this case, which permits it to use a very low code density $d$.
-For \ac{RLNC} this is not the case, since the occurrence of \ac{l.d.} coded
-packets is low. Even for $GF(2)$, the average amount of redundancy has proven
-to be 1.6 packets after $g$ have been transmitted, much less than the
-cases where sparse codes are employed. Overall, we observe that there is
-a trade-off between goodput and \ac{l.d.} coded packets transmission
-overhead.
+redundancy in this case, which permits it to use a, single in this case,
+very low code density $d$. For \ac{RLNC} this is not the case, since the
+occurrence of \ac{l.d.} coded packets is low. Even for $GF(2)$, the
+average amount of redundancy has proven to be 1.6 packets after $g$ have
+been transmitted, much less than the cases where sparse codes are
+utilized. Overall, we observe that there is a trade-off between goodput
+and \ac{l.d.} coded packets transmission overhead.
+
+For Figs.~\ref{fig:enc_good_rasp1_packet_gf2},
+\ref{fig:enc_good_rasp1_packet_gf256}, \ref{fig:enc_good_rasp2_packet_gf2}
+and \ref{fig:enc_good_rasp2_packet_gf256}; we see the packet
+size effect in the encoding goodput in both \ac{Raspi} models and for
+a fixed generation size. For \ac{TSNC} in this case, we allow for 5 density
+changes during the generation transmission and again consider the same
+budgets as before. In all the cases, we clearly observe that there is an
+optimal packet size to operate with. When reviewing the specifications
+of the \ac{Raspi}, both models use a L1 cache of 16 KiB. Hence, the trends
+in the packet size can be explained as follows: For low packet sizes,
+the data processing does not overload the \ac{CPU} of the \ac{Raspi}, so
+the goodput progressively increases given that we simply process more
+data as the packet size increases. However, after a certain packet size,
+the goodput gets affected since the cache starts to saturate. The packets
+towards the cache needs to have more processing. Also important, the
+\ac{CPU} needs to allocate computational resources to other processes from
+the different tasks running in the \ac{Raspi}. Beyond this critical packet
+size, the \ac{CPU} just queues processing which incurs in larger delay
+reducing the goodput.
+
+If we consider the previous effect when reviewing the trends in the
+mentioned figures,
 %
@@
 \end{figure*}
-
-Figures description
-
+%
 \subsubsection{Decoding}

### 2016-06-06 conclusions.tex
Make some edits in the results and conclusions

@@
 automation of tasks within the testbed creation, consider other working
-topologies and include a description for network connectivity where the
-testbed has more autonomy with \ac{IP} address assignment.
+topologies or packet erasures and include a description for network
+connectivity where the testbed has more autonomy with \ac{IP} address assignment.

### 2016-06-06 measurements.tex
Make some edits in the results and conclusions

@@
 optimal packet size to operate with. When reviewing the specifications
-of the \ac{Raspi}, both models use a L1 cache of 16 KiB. Hence, the trends
+of the \ac{Raspi} 1, it uses a L1 cache of 16 KiB. Hence, the trends
 in the packet size can be explained as follows: For low packet sizes,
@@
 If we consider the previous effect when reviewing the trends in the
-mentioned figures,
+mentioned figures, in all the models we observe that the maximum does not
+come at 16 KiB but at a smaller value depending on the model, field size
+and coding scheme considered. The reason is that given there are various
+tasks from other applications for proper functioning running in the
+\ac{Raspi} at the same time as coding, the cache space is filled also
+with the data from these tasks, thus diminishing the cache space available
+for coding.
+
+For the \ac{Raspi} 1 model, we observe in
+Fig.~\ref{fig:enc_good_rasp1_packet_gf2} that the critical
+packet size for \ac{RLNC} using $GF(2)$ occurs at 1 KiB whereas for the
+sparse codes is close to 4 KiB in the most of the cases for $GF(2)$. This
+difference takes place since the sparse codes are much less complex to
+process than \ac{RLNC}, which turns into less data loading in the
+cache for doing computations. However, for \ac{RLNC} given that it is
+a dense code since $d \to 1$, \ac{RLNC} packets load much more data to
+the cache quite easily making this effect visible for smaller packet sizes.
+Fig.~\ref{fig:enc_good_rasp1_packet_gf256}, although the ideal packet
+size remains the same for \ac{RLNC}, for sparse codes it locates closer to
+8 KiB.
 %

### 2016-06-06 measurements.tex
changes in the called plots

@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_encoder_Binary_1600.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_encoder_Binary_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_encoder_Binary8_1600.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_encoder_Binary8_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_encoder_Binary_16.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_encoder_Binary_16.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_encoder_Binary8_16.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_encoder_Binary8_16.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary_1600.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_v2_encoder_Binary_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary8_1600.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_v2_encoder_Binary8_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary_16.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_v2_encoder_Binary_16.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary8_16.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_v2_encoder_Binary8_16.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_decoder_Binary_1600.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_decoder_Binary_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_decoder_Binary8_1600.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_decoder_Binary8_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_decoder_Binary_16.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_decoder_Binary_16.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_decoder_Binary8_16.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_decoder_Binary8_16.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_decoder_Binary_1600.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_v2_decoder_Binary_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_decoder_Binary8_1600.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_generation_size_Rasp_v2_decoder_Binary8_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_decoder_Binary_16.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_v2_decoder_Binary_16.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_decoder_Binary8_16.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/goodput_vs_symbol_size_Rasp_v2_decoder_Binary8_16.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/current_vs_sec_raspberry_change_gen_from_-10sec_to_500sec.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/current_vs_sec_raspberry_change_gen_from_-10sec_to_500sec.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/current_vs_sec_raspberry2_change_gen_from_-10sec_to_500sec.eps}
+        \includegraphics[width=1.15\textwidth]{images/06_06_2016/current_vs_sec_raspberry2_change_gen_from_-10sec_to_500sec.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_Binary_encoder_1600.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary_encoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_Binary8_encoder_1600.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary8_encoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_Binary_encoder_128.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary_encoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_Binary8_encoder_128.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary8_encoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_v2_Binary_encoder_1600.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary_encoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_encoder_1600.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_encoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_encoder_128.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_encoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_encoder_128.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_encoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_Binary_decoder_1600.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary_decoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_Binary8_decoder_1600.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary8_decoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_Binary_decoder_128.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary_decoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_Binary8_decoder_128.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary8_decoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_v2_Binary_decoder_1600.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary_decoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_decoder_1600.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_decoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_decoder_128.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_decoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/23_07_2015/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_decoder_128.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_decoder_128.eps}
         \caption[]%

### 2016-06-06 raspi_journal.tex
Reorganizing the document and adding basic conclusions
Edit abstract

@@
   processing speeds of more than 80 Mbps and 800 Mbps are attainable
-  for a wide array of configurations are attainable for the Raspberry
-  Pi Model 1 and 2, respectively, and that processing energy per bit for
-  network coding is below 1 nJ in a large regime and even an order
-  of magnitude lower for some algorithms.}
+  for a wide array of configurations for the Raspberry Pi Model 1 and
+  2, respectively, and that processing energy per bit for network
+  coding is below 1 nJ in a large regime and even an order of
+  magnitude lower for some algorithms.}
 
@@
 
-% \section{Topologies}
-% \input{topologies}
-
 \section{Metrics and Measurement Methodology}
@@
 
-\section{Measurements}
+\section{Measurements and Discussion}
 \input{measurements}
+
+\section{Conclusion}
+\input{conclusions}
 
@@
 
-\section{Conclusion}
-\label{sec:conclusions}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
+%\section{Materials and Methods}
 

### 2016-06-06 introduction.tex
Second pass on the introduction

--- 2016-06-04 introduction.tex
@@
-At the beginning, there was darkness and then... bang! \ac{NC}
-\cite{ahlswede2000network} appeared to save us from the evilness
-of routing.
+%!TEX root = raspi_journal.tex
+% At the beginning, there was darkness and then... bang! \ac{NC}
+% \cite{ahlswede2000network} appeared to save us from the evilness
+% of routing.
+%
+% General introduction. Introduction to topic addressed in the journal.
+% Review of the State of the Art. Specify why our approach has benefits
+% and which are they. Indicate contributions.
 
-General introduction. Introduction to topic addressed in the journal.
-Review of the State of the Art. Specify why our approach has benefits
-and which are they. Indicate contributions.
+The emergence of powerful and inexpensive single-board computers
+running full versions of standard operating systems (OS) in the last
+years opens exciting possibilities for researchers. This not only
+allows to seamlessly develop implementations that are compatible with
+higher end devices and allows the reuse stable software from the Open
+Source community. It also enables the deployment and testing of large
+scale (hundreds of devices or more) distributed systems at a fraction
+of the cost necessary in previous years. This paper focuses on
+providing the critical steps and mechanisms followed to deploy, setup,
+and maintain a large-scale testbed based on Raspberry Pi devices of
+different models. We also complement this with an in-depth evaluation
+of the Raspberry Pi as a platform to enable a new paradigm in
+networking and storage known as network coding, which relies on
+processing at intermediate nodes to achieve higher throughput, delay
+and reliability performance than state-of-the-art routing techniques.
 
-Our work is organized as follows: Section \ref{sec:testbed} introduces
-the testbed system, its setup, connectivity, files configuration and
-compilation of the Kodo library. Section \ref{sec:schemes} defines the
-coding schemes employed in our study. Later, in Section \ref{sec:metrics}
-we describe the considered metrics for performance comparison of the
-codes deployed in the \ac{Raspi}. In Section \ref{sec:measurements}, we show
-the measurements in the \ac{Raspi} of the mentioned metrics. Final
-conclusions and future work are reviewed in Section \ref{sec:conclusions}.
+% INTRODUCTION TO NETWORK CODING
+Introduced by Ahlswede et al~\cite{ahlswede2000network}, network
+coding constitutes paradigm shift in the way how researchers and
+industry understand and operate networks, by changing the role of
+intermediate relays in the process of transmission of information.
+Relays are no longer limited to storing and forwarding data, but also
+take part in the coding process, through a process called recoding,
+where the relay generates new linear combinations of incoming coded
+packets without previously decoding the data. Network coding allows
+the increase of throughput, reliability, security and delay
+performance of the networks.
+
+Compared to other broadly used coding schemes, e.g., Gallager's LDPC
+codes~\cite{gallager1962low}, Reed-Solomon
+codes~\cite{reed1960polynomial}, network coding is a technology that
+has been implemented in real systems since the early years of its
+conception. In 2006, Katabi et al~\cite{katabi2006practical} published
+the results of the performance of their protocol COPE when implemented
+in a real wireless system, which relied on minimalistic coding to
+provide interesting gains. In 2008, Pedersen et
+al~\cite{pedersen2008implementation} used commercially available
+Symbian OS enabled mobile phones to implement network coding in a
+\ac{D2D} cooperation application. In 2011, researchers at Aalborg
+University developed KODO~\cite{kodo2011pedersen}, a C++ network
+coding library with open source code for researchers intended to make
+network coding implementations easily available for both, the research
+community and commercial entities.
+CATWOMAN~\cite{hundeboll2012catwoman} is a protocol implemented on top
+of the B.A.T.M.A.N. protocol~\cite{johnson2008simple} for IEEE 802.11
+multi-hop meshed networks using some of the intuition from COPE, but
+deploying it in real systems. It is currently available as open source
+code in the Linux kernel. Many other implementations have been tested
+on real world systems~
+\cite{pahlevani2013playncool,katti2008xors,krigslund2013core,paramanathan2013leanandmean}.
+
+Despite this successful deployment in real systems, many of these
+protocols and contributions have been implemented in separate testbeds
+and the experiences are hard to reproduce.  Given the need for
+reproducibility of past and future results among researchers and the
+need of low-cost and easy-to-deploy testbeds, this paper contribution
+is provide detailed instructions on how to set up a low-cost,
+heterogeneous and scalable testbed consisting of Raspberry Pis
+(Raspis), and by providing detailed measurements of goodput and energy
+consumption of such testbed when performing network coding operations
+with different codecs (such as full RLNC, multicore-enabled RLNC,
+sparse RLNC and tunable sparse RLNC). The heterogeneity of the testbed
+comes from the fact that old, single core, Raspberry Pi 1 model B are
+integrated seamlessly in the described testbed with newer, multicore
+versions, like the Raspberry Pi 2 model B.
+
+Our work is organized as follows. Section~\ref{sec:testbed} introduces the
+testbed system, its setup, connectivity, files configuration and compilation of
+the Kodo library. Section~\ref{sec:schemes} defines the coding schemes employed
+in our study. Later, in Section~\ref{sec:metrics} we describe the considered
+metrics for performance comparison of the codes deployed in the \ac{Raspi}. In
+Section~\ref{sec:measurements}, we show the measurements in the \ac{Raspi} of
+the mentioned metrics. Final conclusions and future work are reviewed in
+Section~\ref{sec:conclusions}.
 

### 2016-06-06 measurements.tex

@@
 the generation size: \ac{RLNC}, \ac{SRLNC} with $d = [0.02,\ 0.1]$
-and \ac{TSNC} with two parameters that we mention. The first of them,
-$steps$, is the number of density changes in the system, if any.
-The number of changes is equal to the number of regions minus 1, making
-$steps = \#regions - 1$ and $dep = e$. With these definitions, we first
-evaluate \ac{TSNC} with no changes, e.g. $steps=0$ and the two amounts
-for dependent packets mentioned earlier. In this way the budget is
-either $g + 8$ or $g + 16$. This means that we tolerate at most 8 or 16
-packets regardless of the generation. The goal with setting first
-\ac{TSNC} with these values is to observe first the sole effect of the
-budget in the code since $steps = 0$ implies no density changes during
-the whole process.
+and \ac{TSNC} with an extra parameter that we mention. We define
+$C$ as the number of density changes in the \ac{TSNC} transmission
+process, if any. The number of changes is $C = \#regions - 1$. With
+this definitions, we first evaluate \ac{TSNC} with no changes, e.g.
+$C = 0$ and the two amounts for dependent packets mentioned earlier.
+This means that we tolerate at most 8 or 16 packets regardless of the
+generation. The goal with setting first \ac{TSNC} with these values is to
+observe first the sole effect of the budget in the code since $C = 0$
+implies no density changes during the whole process.
 
 For the plots in the mentioned figures from the encoder goodput measurements,
-\ac{RLNC} presents the worst performance in terms of goodput and
-\ac{TSNC} with $dep = 16$, the best regardless of the \ac{Raspi} model.
+\ac{RLNC} presents the lowest performance in terms of goodput and
+\ac{TSNC} with $e = 16$, the highest regardless of the \ac{Raspi} model.
 Given that the processing time depends in the amount of coded packets
@@
 the sparser the codes, then more overhead due to transmissions of \ac{l.d.}
-packets they have since it is more likely to generate the same set of
-packets. Excluding the coding coefficients overhead, the overhead due to
-transmissions of \ac{l.d.} packets can be very high.
-For example, if we consider \ac{TSNC} with $dep=16$ and $g = 16$, the budget
-in this case permits to send up to 32 packets which is $2\times$ the generation
-size for an overhead of $100\%$ excluding the one from the coding
-coefficients. This happens because \ac{TSNC} is allowed to add too much
-redundancy in this case, which permits it to use a, single in this case,
-very low code density $d$. For \ac{RLNC} this is not the case, since the
-occurrence of \ac{l.d.} coded packets is low. Even for $GF(2)$, the
-average amount of redundancy has proven to be 1.6 packets after $g$ have
-been transmitted, much less than the cases where sparse codes are
-utilized. Overall, we observe that there is a trade-off between goodput
-and \ac{l.d.} coded packets transmission overhead.
+packets since it is more frequent to generate similar set of packets.
+Excluding the coding coefficients overhead, the overhead due to
+transmissions of \ac{l.d.} packets might be high for the sparse schemes.
+For example, if we consider \ac{TSNC} with $e = 16$ and $g = 16$
+in Fig.~\ref{fig:enc_good_rasp1_gen_gf2}, the budget in this case permits
+to send up to 32 packets which is $2\times$ the generation
+size for an overhead of $100\%$ excluding the overhead from appending
+the coding coefficients. This happens because \ac{TSNC}
+has been allowed to add too much redundancy in this case. Given that $C=0$,
+this permits it to use a single very low code density $d$. For \ac{RLNC},
+this is not the case since the occurrence of \ac{l.d.} coded packets is
+small, because all coding coefficients are used. Even for $GF(2)$, the
+average amount of redundant packets for \ac{RLNC} has proven to be 1.6
+packets after $g$ have been transmitted \textbf{[Include a reference]},
+but less than the cases where sparse codes are utilized. Overall, we
+observe that there is a trade-off between goodput and \ac{l.d.} coded
+packets transmission overhead.
 
@@
 changes during the generation transmission and again consider the same
-budgets as before. In all the cases, we clearly observe that there is an
+budgets as before. In all the cases, we observe that there is an
 optimal packet size to operate with. When reviewing the specifications
 of the \ac{Raspi} 1, it uses a L1 cache of 16 KiB. Hence, the trends
-in the packet size can be explained as follows: For low packet sizes,
-the data processing does not overload the \ac{CPU} of the \ac{Raspi}, so
-the goodput progressively increases given that we simply process more
-data as the packet size increases. However, after a certain packet size,
-the goodput gets affected since the cache starts to saturate. The packets
-towards the cache needs to have more processing. Also important, the
-\ac{CPU} needs to allocate computational resources to other processes from
-the different tasks running in the \ac{Raspi}. Beyond this critical packet
-size, the \ac{CPU} just queues processing which incurs in larger delay
-reducing the goodput.
+in the packet size can be explained in the following way: For low packet
+sizes, the data processing does not overload the \ac{CPU} of the
+\ac{Raspi}, so the goodput progressively increases given that we simply
+process more data as the packet size increases. However, after a certain
+packet size, the goodput gets affected since the cache starts to saturate.
+The packets towards the cache needs to have more processing. Beyond this
+critical packet size, the \ac{CPU} just queues processing which incurs in
+larger delay reducing the goodput.
 
 If we consider the previous effect when reviewing the trends in the
-mentioned figures, in all the models we observe that the maximum does not
-come at 16 KiB but at a smaller value depending on the model, field size
-and coding scheme considered. The reason is that given there are various
+mentioned figures, in all the models we observe that the maximum is not
+at 16 KiB but at a smaller value depending on the model, field size
+and coding scheme considered. The reason is that the \ac{CPU} needs to
+allocate computational resources to other processes from the different tasks
+running in the \ac{Raspi}. Then, given there are various
 tasks from other applications for proper functioning running in the
@@
 with the data from these tasks, thus diminishing the cache space available
-for coding.
+for coding operations.
 
@@
 packet size for \ac{RLNC} using $GF(2)$ occurs at 1 KiB whereas for the
-sparse codes is close to 4 KiB in the most of the cases for $GF(2)$. This
-difference takes place since the sparse codes are much less complex to
+sparse codes is close to 8 KiB in the most of the cases for $GF(2)$. This
+difference takes place since the sparse codes mix less packets their
 process than \ac{RLNC}, which turns into less data loading in the
-cache for doing computations. However, for \ac{RLNC} given that it is
-a dense code since $d \to 1$, \ac{RLNC} packets load much more data to
-the cache quite easily making this effect visible for smaller packet sizes.
+cache for doing computations. For a density of $d = 0.1$, packet size of
+$B = 8$ KiB and $g = 16$ packets, we observe that roughly $\ceil{gd} = 2$
+packets are inserted in the cache when calculating a coded packet with this
+sparse code. Loading this into the cache, stands for 16 KiB which is the
+cache size. A similar effect occurs for the other sparse codes. However, for
+\ac{RLNC} given that it is a dense code since $d \to 1$, \ac{RLNC}
+packets load data from all the $g = 16$ coding coefficients, which accounts
+for the 16 KiB of the cache size. In
 Fig.~\ref{fig:enc_good_rasp1_packet_gf256}, although the ideal packet
-size remains the same for \ac{RLNC}, for sparse codes it locates closer to
-8 KiB.
+size remains the same for \ac{RLNC} and the sparse codes, the final goodput
+is lower due to the field size effect.
 %
@@
 %
+The effects mentioned for the \ac{Raspi} 1 were also observed for
+the \ac{Raspi} 2.
 \subsubsection{Decoding}

### 2016-06-06 measurements.tex
Encoder goodput done

@@
 $C$ as the number of density changes in the \ac{TSNC} transmission
-process, if any. The number of changes is $C = \#regions - 1$. With
-this definitions, we first evaluate \ac{TSNC} with no changes, e.g.
-$C = 0$ and the two amounts for dependent packets mentioned earlier.
-This means that we tolerate at most 8 or 16 packets regardless of the
-generation. The goal with setting first \ac{TSNC} with these values is to
-observe first the sole effect of the budget in the code since $C = 0$
-implies no density changes during the whole process.
+process, if any. The maximum number of possible changes will depend
+on the budget. The larger the budget, the more regions are formed and
+more density changes are possible. We first evaluate \ac{TSNC} with no
+changes, e.g. $C = 0$ and the two amounts for dependent packets mentioned
+earlier. This means that we tolerate at most 8 or 16 packets regardless of
+the generation. The goal with setting first \ac{TSNC} with these values
+is to observe first the sole effect of the budget in the code since
+$C = 0$ implies no density changes during the whole process.
 
@@
 %
+\par
 The effects mentioned for the \ac{Raspi} 1 were also observed for
-the \ac{Raspi} 2.
+the \ac{Raspi} 2 as mentioned previously. Still, the \ac{Raspi} 2 achieves
+roughly $5\times$ to $7\times$ gains in terms of encoding speed when comparing
+the goodputs in Figs.~\ref{fig:enc_good_rasp1} and \ref{fig:enc_good_rasp2},
+given that it has an \ac{ARM} Cortex A7 (v7) \ac{CPU} and twice the \ac{RAM}
+size than the \ac{ARM}1176JZF-S (v6) core of the \ac{Raspi} 1 model.
+
+In Figs.\ref{fig:enc_good_rasp2_packet_gf2} and
+\ref{fig:enc_good_rasp2_packet_gf256}, we observe that the packet size for
+the maximum \ac{RLNC} goodput has shifted towards 8 KiB, indicating that
+the \ac{Raspi} 2 is able to handle $16 \times 8$ KiB $= 128$ KiB. This is
+possible because the \ac{Raspi} 2 has a shared L2 cache of 256 KiB allowing
+to still allocate some space for the data to be processed.
+
 \subsubsection{Decoding}
-
 We perform the same evaluation as before but now we focus on the decoder.

### 2016-06-06 conclusions.tex
Second pass on the conclusions

--- 2016-06-06 conclusions.tex
@@
 \label{sec:conclusions}
-Given the need for a \ac{Raspi} testbed easy to configure and maintain
-for network coding applications where results could be reproducible
-in a simple fashion, we provide a testbed description at Aalborg
-University with an in-depth performance evaluation for network coding
-schemes to indicate the processing capabilities and energy behaviour
-for two \ac{Raspi} models both of using their \ac{SIMD} capabilities
-and considering a multicore implementation for the \ac{Raspi} 2. Our
-findings report that processing speeds of more than X Mbps and Y Mbps are attainable for \textbf{[goodput scenarios]}, respectively, and that
-processing energy per bit for network coding is below 1 nJ in a large regime
-and even an order of magnitude lower for some algorithms with the same power consumption for \textbf{[goodput scenarios]}. Future work in this area,
-will be to evaluate further elaborated codecs, expand the setup and
-automation of tasks within the testbed creation, consider other working
-topologies and include a description for network connectivity where the
-testbed has more autonomy with \ac{IP} address assignment.
+Given the need for low-cost, easy to configure, testbeds that enable
+reproducible results, we provide a in-depth description of Aalborg
+University's \ac{Raspi} testbed and how to guarantee replicable
+results and managing scaling of the system.  We also provide a
+performance evaluation for network coding schemes, focusing on
+processing speed and energy behaviour for two \ac{Raspi} models,
+including algorithms that exploit \ac{SIMD} instructions and multicore
+capabilities of the \ac{Raspi} 2. Our measurements show that
+processing speeds of more than 80 Mbps and 800 Mbps are attainable for
+the \ac{Raspi} model 1 and 2, respectively, for a wide range of
+network coding configurations and maintaining a processing energy
+below 1 nJ/bit (or even an order of magnitude lower) in similar
+configurations. Future work in the use of \ac{Raspi} devices will
+focus on expanding the setup and automation of tasks to run the
+testbed, configure specified network topologies (e.g., with specific
+connectivity or packet loss ratios), reserve the use of these
+sub-networks for running tailored experiments, and opening the use of
+the testbed beyond our team at Aalborg University.

### 2016-06-06 cross_compilation.tex
finished fabric

@@
 
-\subsection{Kodo python}
+%\subsection{Kodo python}
+%
+%Often when simplicity and fast prototyping is of higher importance than speed
+%it is often desired to use a scripting language rather than the often faster
+%compiled language. Kodo-python provides roughly similar bindings to the
+%underlying C++11 implementation of Kodo as Kodo-cpp does. This means that
+%python calls to Kodo-python are actually executed in the underlying C++11
+%compilied code.
+%
+%Parsing calls and variables between Python and C++ compiled code is
+%not free, but this small introduced overhead may in many cases be worth
+%it to take advantage of Pythons and other scripting languages many
+%benefits.
+%
+%Below is a short procedure to use Kodo-python in a \ac{Raspi}.
+%
+%One advantage of Python compared to Kodo-cpp is that only the Kodo-python
+%library needs to be cross compiled. The python scripts using the Kodo
+%library needs not to be cross compiled but simply copied to the same
+%directory as .
+%
+%Kodo-python is available at \url{https://github.com/steinwurf/kodo-python}.
+%
+%
+%
+%\begin{lstlisting}[]
+%$ apt-get update
+%$ apt-get install python build-essential libpython-dev python-dev
+%\end{lstlisting}
+%\FloatBarrier
+%\vspace{-5mm}
+%  % IN ARCH LINUX, MOD_PYTHON NEEDS TO BE INSTALLED
+%
+%
+%Create a directory to hold our code:
+%\begin{lstlisting}[]
+%$ CODEDIR="${HOME}/code"
+%$ mkdir -p ${CODEDIR}
+%$ cd ${CODEDIR}
+%\end{lstlisting}
+%\FloatBarrier
+%\vspace{-5mm}
+%
+%\begin{lstlisting}[]
+%$ git clone git@github.com:steinwurf/kodo-python.git 
+%\end{lstlisting}
+%\FloatBarrier
+%\vspace{-5mm}
+%
+%\begin{lstlisting}[]
+%$ cd kodo-python
+%$ python2.7 waf configure --cxx_mkspec=cxx_raspberry_gxx49_arm
+%$ python waf build
+%\end{lstlisting}
+%\FloatBarrier
+%\vspace{-5mm}
+%
+%KODO-PYTHON IS NOT WORKING!! WAITING FOR HELP ON STEINWURF DEV.
+%
+%WRITE HOW TO RUN A KODO PYTHON SCRIPT IN THE RASPIS
 
-Often when simplicity and fast prototyping is of higher importance than speed
-it is often desired to use a scripting language rather than the often faster
-compiled language. Kodo-python provides roughly similar bindings to the
-underlying C++11 implementation of Kodo as Kodo-cpp does. This means that
-python calls to Kodo-python are actually executed in the underlying C++11
-compilied code.
-
-Parsing calls and variables between Python and C++ compiled code is
-not free, but this small introduced overhead may in many cases be worth
-it to take advantage of Pythons and other scripting languages many
-benefits.
-
-Below is a short procedure to use Kodo-python in a \ac{Raspi}.
-
-One advantage of Python compared to Kodo-cpp is that only the Kodo-python
-library needs to be cross compiled. The python scripts using the Kodo
-library needs not to be cross compiled but simply copied to the same
-directory as .
-
-Kodo-python is available at \url{https://github.com/steinwurf/kodo-python}.
-
-\begin{lstlisting}[]
-$ apt-get update
-$ apt-get install python build-essential libpython-dev python-dev
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-% IN ARCH LINUX, MOD_PYTHON NEEDS TO BE INSTALLED
-
-Create a directory to hold our code:
-\begin{lstlisting}[]
-$ CODEDIR="${HOME}/code"
-$ mkdir -p ${CODEDIR}
-$ cd ${CODEDIR}
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-\begin{lstlisting}[]
-$ git clone git@github.com:steinwurf/kodo-python.git 
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-\begin{lstlisting}[]
-$ cd kodo-python
-$ python2.7 waf configure --cxx_mkspec=cxx_raspberry_gxx49_arm
-$ python waf build
-\end{lstlisting}
-\FloatBarrier
-\vspace{-5mm}
-
-KODO-PYTHON IS NOT WORKING!! WAITING FOR HELP ON STEINWURF DEV.
-
-WRITE HOW TO RUN A KODO PYTHON SCRIPT IN THE RASPIS
-
-\subsection{fabric}
+\subsection{Fabric}
 
@@
 a small script that can perform the few items above:
-
-%SHORT INTRO. EXPLAIN A FEW USECASES FOR FABRIC. E.G. REBOOT, INSTALL PACKAGE, RUN SCRIPT ON MULTIPLE RASPIS. COPY FILES TO/FROM PC AND MULTIPLE RASPIS
 

### 2016-06-06 testbed.tex

@@
 \centering
-\includegraphics[width=0.6\textwidth]{images/testbed_setup2.eps}
+\includegraphics[width=0.85\textwidth]{images/testbed_setup2.eps}
 \caption{Testbed setup}
@@
 
-\textbf{hashmark (\#) means to perform operation as root, dollar (\$) means
-to perform operation as user}
-
 %The first thing we need to do is to download the linux installation file.
@@
 \end{enumerate}
+
+Hashmark (\#) and dollar (\$) will be used throughout the procedure
+to indicate if an operation should be run with root permissions or
+user permissions.
+%\textbf{hashmark (\#) means to perform operation as root, dollar (\$) means
+%to perform operation as user}
 
@@
 $ whoami
-chres
+<USERNAME>
 $ sudo whoami
@@
 
-\subsection{Mount image}
+\subsection{The image}
 
@@
 "fdisk" can be used to display what is inside. Pass the arguments "-u sectors" to
-display the sizes in sectors and "-l" to display partitions and exit.
+display the sizes in sectors and "-l" to display partitions and exit fdisk again.
 
@@
 
-The image contains two partitions. The first one of starting at sector 8192 and
+The image is in total 2709504 sectors (1.3GiB) in size and contains two
+partitions. The first one of starting at sector 8192 and
 the other partition starting at sector 137216. The partitions is of type FAT32
 and Linux and have sizes 63M and 1.2G. This indicates that the first partition
-is most likely a boot partition and the second partition is a traditional file
-system. Actually, it is a linux root filesystem (i.e. /).
+is most likely a boot partition and the second partition is a traditional linux file
+system. Actually, it is the linux root filesystem (i.e. /).
+
+\subsection{(Optional) Resize image}
+1.2G is not very much to hold the root filesystem given that it is desired to
+in later steps alter the files and install more packages. It may therefore be
+neccessary to increase the partition size slightly.
+The following steps will therefore illustrate how image and root filesystem
+can be expanded by one \ac{GB}.
+
+First, expand the image one \ac{GB}:
+\begin{lstlisting}[]
+# dd if=/dev/zero bs=1M count=1024 >> ${IMAGE}.img
+\end{lstlisting}
+\FloatBarrier
+
+Use \texttt{fdisk} to check that the image is now one \ac{GB} bigger:
+\begin{lstlisting}[literate={DOLLAR}{\$}1]
+DOLLAR fdisk -u sectors -l ${IMAGE}.img
+Disk 2016-05-27-raspbian-jessie-lite.img: 2.3 GiB, 2461007872 bytes, 4806656 sectors
+Units: sectors of 1 * 512 = 512 bytes
+Sector size (logical/physical): 512 bytes / 512 bytes
+I/O size (minimum/optimal): 512 bytes / 512 bytes
+Disklabel type: dos
+Disk identifier: 0x6fcf21f3
+
+Device                               Boot  Start     End Sectors  Size Id Type
+2016-05-27-raspbian-jessie-lite.img1        8192  137215  129024   63M  c W95 FAT32 (LBA)
+2016-05-27-raspbian-jessie-lite.img2      137216 2709503 2572288  1.2G 83 Linux
+\end{lstlisting}
+\FloatBarrier
 
@@
 %We also notice that each sector is 512 bytes.
+%On newer systems, we can mount the device easier using "losetup --show -f -P IMAGE"
+%Mount root partition:
 
-%On newer systems, we can mount the device easier using "losetup --show -f -P IMAGE"
-
-%Mount root partition:
+\subsection{Mount image}
 

### 2016-06-06 raspi_journal.tex
Encoder goodput measurements almost done
updated acronyms list

@@
 \newcommand\floor[1]{\left\lfloor#1\right\rfloor}
+\newcommand\ceil[1]{\left\lceil#1\right\rceil}
 
@@
 
-\noindent NC: Network Coding\\
-RLNC: Random Linear Network Coding\\}
+% Use these two commands to get used acronyms
+%used=$(grep -ohR '\\ac{[^}]*' *.tex | cut -f2 -d'{' | sort | uniq)
+%for ac in ${used[@]}; do echo "$(grep -R "acro{${ac}}" acronym.tex)"; done | cut -f2-4 -d'{'
+% Use text editor to replace '}{' --> ': ' and '}' --> '\\'
+
+\noindent ACK: Acknowledgment\\
+AMR: Adaptive Multi-Rate\\
+ARM: Advanced RISC Machine\\
+BLAS: Basic Linear Algebra Subprograms\\
+CPU: Central Processing Unit\\
+CSMA/CA: Carrier Sense Multiple Access with Collision Avoidance\\
+GB: Gigabyte\\
+D2D: Device to Device\\
+DAG: Direct Acyclic Graph\\
+DC: Direct Current\\
+DCF: Distributed Coordination Function\\
+GF: Galois Field\\
+GPU: Graphic Processing Unit\\
+IP: Internet Protocol\\
+IPTV: Internet Protocol TeleVision\\
+LAN: Local Area Network\\
+l.d.: linearly dependent\\
+l.i.: linearly independent\\
+LNC: Linear Network Coding\\
+LOS: Line Of Sight\\
+MAC: Medium Access Control\\
+MIMO: Multiple Input Multiple Output\\
+NC: Network Coding\\
+NLOS: Non Line Of Sight\\
+OSI: Open Systems Interconnect\\
+PC: Personal Computer\\
+PNC: Physical layer Network Coding\\
+QoE: Quality of Experience\\
+RLNC: Random Linear Network Coding\\
+SRLNC: Sparse Random Linear Network Coding\\
+SIMD: Single Instruction Multiple Data\\
+SIMD: Single Instruction Multiple Data\\
+SMP: Symmetric Multiprocessor\\
+SOC: System on Chip\\
+SSE: Streaming SIMD Extensions\\
+TSNC: Tunable Sparse Network Coding\\
+VoIP: Voice over Internet Protocol\\
+WLAN: Wireless Local Area Network\\
+dof: degrees of freedom\\
+IP: Internet Protocol\\
+OS: Operating System\\
+NFS: Network File System\\
+RAM: Random Access Memory\\
+Raspi: Raspberry Pi\\
+SSH: Secure Shell\\
+USB: Universal Serial Bus\\
+SCP: Secure copy\\
+Telnet: Telnet}
 

### 2016-06-06 measurements.tex

@@
 \subsubsection{Decoding}
-We perform the same evaluation as before but now we focus on the decoder.
-Fig. \ref{fig:dec_good_rasp1} shows the results of the decoder goodput
+Similar as the encoding goodput, in this Section, we review decoder
+goodput in terms of performance and configurations.
+Fig.~\ref{fig:dec_good_rasp1} shows the results of the decoder goodput
 measurements for the \ac{Raspi} 1 and Fig. \ref{fig:dec_good_rasp2} does

### 2016-06-06 measurements.tex
Goodput done

@@
 possible because the \ac{Raspi} 2 has a shared L2 cache of 256 KiB allowing
-to still allocate some space for the data to be processed.
+to still allocate some space for the data to be processed while achieving
+a maximum goodputs of 105 MB/s.
 
@@
 
-Description
+In Figs.~\ref{fig:dec_good_rasp1} and \ref{fig:dec_good_rasp2}, we
+observe the same generation and packet size effects reported in the
+encoding case. However, we do observe in
+Figs.~\ref{fig:dec_good_rasp1_gen_gf2}, \ref{fig:dec_good_rasp1_gen_gf256},
+\ref{fig:dec_good_rasp2_gen_gf2} and \ref{fig:dec_good_rasp2_gen_gf256};
+that duplicating the generation size does not reduce by a factor of 4 the
+goodput. In principle, given that Gaussian elimination scales as
+$\mathcal{O}(g^3)$ (and thus the processing time), we would expect that
+the goodput scales as $\mathcal{O}(R_{proc,dec}) = \mathcal{O}(g/g^{3}) =
+\mathcal{O}(g^{-2})$. This would imply that duplicating the generation
+size, should reduce the goodput by a factor of 4, which does not. Instead,
+the goodput it is only reduced by a factor of 2. This is only possible if
+the Gaussian elimination is $\mathcal{O}(g^2)$. A study in
+\textbf{[refence about Achutan's measurements on the Raspi]} indicated
+that this is effectively the case. The reason is that the $g^2$ factor in
+the scaling law for our Gaussian elimination is much higher than the $g^3$
+for $g \geq 512$. \textbf{[Why was the $g^2$ factor greather than the
+$g^3$ factor? Wasn't it due to the amount of of bytes per packet?]}
 
+Another difference with the encoding goodput results in the same figures,
+is that even though the \ac{TSNC} with $e = 16$ packets provides the fastest
+encoding, it does not happen to be the same for the decoding. For this
+very sparse scheme, the decoding is affected by the amount of \ac{l.d.}
+packets generated by, which leads to a higher delay in some cases
+(particularly in $g = [64,\ 128]$). For other generation sizes, the
+performance of sparse codes is similar.
+%
 \begin{figure*}
@@
 \end{figure*}
-
-Description
-
+%
 \subsection{Average Power}
-With the energy measurement setup described in Section \ref{sec:energy_metrics_methods},
-we compute the metrics described there. We first proceed with the average
-power consumption of the \ac{Raspi} 1 in Fig. \ref{fig:current_rasp1} and
-the \ac{Raspi} 2 in Fig. \ref{fig:current_rasp2}.
+With the energy measurement setup described in Section
+\ref{sec:energy_metrics_methods}, we compute the metrics described there.
+We first proceed with the average power consumption of the \ac{Raspi} 1
+in Fig.~\ref{fig:current_rasp1} and the \ac{Raspi} 2 in
+Fig.~\ref{fig:current_rasp2}.
 
@@
         \caption[]%
-        {{\small Current for the \ac{Raspi} 1}}
+        {{\small Current for the \ac{Raspi} 1 model}}
         \label{fig:current_rasp1}
@@
         \caption[]%
-        {{\small Current for the \ac{Raspi} 2}}
+        {{\small Current for the \ac{Raspi} 2 model}}
         \label{fig:current_rasp2}

### 2016-06-06 testbed.tex
finished resizing image

@@
 \FloatBarrier
+\vspace{-5mm}
 
@@
 
-\subsection{(Optional) Resize image}
+\subsection{Resize image}
 1.2G is not very much to hold the root filesystem given that it is desired to
@@
 
-First, expand the image one \ac{GB}:
+First, expand the image one \ac{GB} and wait for data to be completely written
+the disk:
 \begin{lstlisting}[]
-# dd if=/dev/zero bs=1M count=1024 >> ${IMAGE}.img
+# dd if=/dev/zero bs=1M count=1024 >> ${IMAGE}.img && sync
 \end{lstlisting}
 \FloatBarrier
+\vspace{-5mm}
 
@@
 \FloatBarrier
+\vspace{-5mm}
+
+Now, to expand the root filesystem it is required to first remove the Linux partition
+and then add it again one \ac{GB} bigger.
+We use fdisk for the task. The echo's within the parenthesis will function as
+key-presses in \texttt{fdisk} and hence delete last partition, create a new
+primary partition, print new partition table, and write new partition table
+to the image:
+
+\begin{lstlisting}[]
+# (echo d; echo ; echo n; echo p; echo ; echo 137216; echo ; echo p; echo w) | fdisk ${IMAGE}.img
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Make the Raspbian image available as a block device: 
+\begin{lstlisting}[]
+# DEV=$(losetup --show -f -P ${IMAGE}.img); echo $DEV
+/dev/loop0
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+We see that the image is now available as /dev/loop0. Use \texttt{lsblk}
+to view the partitions of our image:
+
+\begin{lstlisting}[]
+# lsblk
+NAME      MAJ:MIN RM  SIZE RO TYPE MOUNTPOINT
+...
+loop0       7:0    0  2.3G  0 loop 
+|-loop0p1 259:2    0   63M  0 loop 
+|-loop0p2 259:3    0  2.2G  0 loop
+...
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Check and resize the root filesystem:
+\begin{lstlisting}[]
+# e2fsck -f ${DEV}p2
+# resize2fs ${DEV}p2
+\end{lstlisting}
+\FloatBarrier
 
@@
 
-To browser and alter the files in the image, it is possible to mount the partitions.
+Browsing and altering the files in the image is easy. Simply mount the partitions.
+%To browser and alter the files in the image, it is possible to mount the partitions.
 
 Lets first mount the root partition. This is done by first creating a new folder
-that we will call root which will be located in our working directory. After this,
-we mount the partition starting at sector 137216. To provide this offset information
-to mount, we need to find the offset in bytes. From the fdisk command we could also
-see that each sector is 512 bytes. Thus, we multiply the sector size and the sector
-start to get the offset in bytes.
+that we will name \texttt{root} which will be located in our working directory.
+After this, simply mount the partitions:
+%After this,
+%we mount the partition starting at sector 137216. To provide this offset information
+%to mount, we need to find the offset in bytes. From the fdisk command we could also
+%see that each sector is 512 bytes. Thus, we multiply the sector size and the sector
+%start to get the offset in bytes.
 
@@
 $ mkdir -p ${ROOTDIR}
-# mount -o loop,offset=$((137216*512)) ${IMAGE}.img ${ROOTDIR}
+# mount ${DEV}p2 ${ROOTDIR}
 \end{lstlisting}
 \FloatBarrier
+\vspace{-5mm}
+%# mount -o loop,offset=$((137216*512)) ${IMAGE}.img ${ROOTDIR}
 
@@
 \begin{lstlisting}[]
-# mount -o loop,offset=$((8192*512)) ${IMAGE}.img ${ROOTDIR}/boot
+# mount ${DEV}p1 ${ROOTDIR}/boot
 \end{lstlisting}
 \FloatBarrier
+\vspace{-5mm}
+%# mount -o loop,offset=$((8192*512)) ${IMAGE}.img ${ROOTDIR}/boot
 
@@
 \FloatBarrier
+\vspace{-5mm}
 % This was neccessary on arch
@@
 \FloatBarrier
+\vspace{-5mm}

### 2016-06-06 schemes.tex

@@
 
-In this section, we present a description of the considered coding schemes
-measured with the \ac{Raspi} testbed. We introduce a definition
-for the primitive coding operations, e.g. encoding, decoding and recoding
-(where applies) for each coding scheme. Later, we address particular schemes
-which are obtained by modifying the basic coding operations that provide
-better processing speeds, particularly relevant for the \ac{Raspi}.
-Finally, we include a review of the \todot{this sentence is incomplete}
+In this section, we present a description of the considered coding
+schemes measured with the \ac{Raspi} testbed. We introduce a
+definition for the primitive coding operations, e.g. encoding,
+decoding and recoding (where it applies) for each coding
+scheme. Later, we address particular schemes which are obtained by
+modifying the basic coding operations that provide better processing
+speeds, which is particularly relevant for the \ac{Raspi}.  Finally,
+we include a review of algorithms for network coding that exploit
+multicore capabilities of the \ac{Raspi} 2.
 
@@
 
-\ac{RLNC} is an example of intra-session \ac{NC}. Here, data symbols from a
-single flow are combined with each other. In this type of network coding, all
-the original data packets $P_j, j \in [1,g]$, and each of $B$ bytes, are used to
-create coded packets. In the following subsections, we describe the basic
-functionalities of \ac{RLNC}.
+\ac{RLNC} is an example of intra-session \ac{NC}, i.e., data symbols
+from a single flow are combined with each other. In this type of
+network coding, all the original data packets $P_j, j \in [1,g]$, each
+of $B$ bytes, are used to create coded packets using random linear
+combinations of the original ones. In the following subsections, we
+describe the basic functionalities of \ac{RLNC}.
 
@@
 
-For indicating a receiver which packets were utilized
+For indicating to a receiver how the packets were combined
 to create a coded one, a simple yet versatile choice is to append
-its coding coefficients as a header of the coded packet. Hence, an
+its coding coefficients as a header in the coded packet. Hence, an
 amount of overhead is included in every coded packet given that we
@@
 |v_i| &= \sum_{j=1}^{g} |v_{ij}| = g \times \lceil \log_{2} (q)
-\rceil ~ [\mathrm{bits}]
+\rceil ~ [\mathrm{bits}].
 \end{align}
@@
 \end{array}
-\right]
+\right].
 \end{align}
@@
 $\textbf{V}$ in the linear system
-$\textbf{C} = \textbf{V} \textbf{P}$, which can achieved using
+$\textbf{C} = \textbf{V} \textbf{P}$, which can be achieved using
 efficient Gaussian elimination techniques \cite{fragouli2006network}.
-On real applications, decoding is performed on-the-fly, e.g., the pivots are
-computed as packets are progressively received, in order to minimize the
-computation delay for each step.
+On real applications, decoding is performed on-the-fly, e.g., the
+pivots are computed as packets are progressively received, in order to
+minimize the computation delay for each step.
 
@@
 coding scheme that permits to \textit{recode} former coded packets at any
-point in the network without inquiring in local decoding processing. In
+point in the network without requiring a local decoding of the data. In
 principle, a recoded packet should be indistinguishable from a coded one.
@@
 \label{eq:recoded_packet}
-R_i = \bigoplus_{j=1}^{g} w_{ij} \otimes C_j  ,\ \forall i \in [1,\ldots)
+R_i = \bigoplus_{j=1}^{g} w_{ij} \otimes C_j  ,\ \forall i \in [1,\ldots).
 \end{align}
@@
 In \eqref{eq:recoded_packet}, $w_{ij}$ is the coding coefficient used
-in the $i$-th recoded packet and assigned to multiply a previously coded
-packet $C_j$. These coding coefficients are again uniformly and randomly chosen
-from $GF(q)$. Still, each of the $w_{ij}$ are not the appended recoding
-coefficients for signalling since the they will only retrieve previously
-coded packets. The analytical expression for the appended coefficients
-after recoding is obtained by calculating recoded packets as function of the
-original packets. Therefore, we define the local coding matrix $\textbf{W}$
-in the same way as it was made for $\textbf{V}$. Thus, the local coding matrix
-can be written as:
+in the $i$-th recoded packet and assigned to multiply a previously
+coded packet $C_j$. These coding coefficients are again uniformly and
+randomly chosen from $GF(q)$. However, these $w_{ij}$'s are not
+appended to the previous coding coefficients.  Instead, the system
+will update the previous coefficients. Due to the linearity of the
+operation, this update reduces to recombining the coding coefficients
+equivalent to each original packet with the weight of the
+$w_{i,j}$.Therefore, we define the local coding matrix $\textbf{W}$ in
+the same way as it was made for $\textbf{V}$. Thus, the local coding
+matrix can be written as:
 %
@@
 \label{eq:appended_coded_coefficients}
-{(\textbf{W} \textbf{V})}_{ij} = \sum_{k=1}^{g} w_{ik} v_{kj}\ ,\ \forall i,j \in [1,g] \times [1,g]
+{(\textbf{W} \textbf{V})}_{ij} = \sum_{k=1}^{g} w_{ik} v_{kj}\ ,\ \forall i,j \in [1,g] \times [1,g].
 \end{align}
 %
-This procedure is carried by all the recoders in a given network therefore
-allowing any decoder to compute the original data after Gaussian elimination,
-regardless of the amount of times where recoding was performed. Similarly
-as with the encoding operation, any decoder that collects a set of
-$g$ \ac{l.i.} recoded packets with their respective coefficients, will
-be able to decode the data as mentioned before in Section \ref{sssec:decoding}.
+This update procedure on the coding coefficients is carried by all the
+recoders in a given network therefore allowing any decoder to compute
+the original data after Gaussian elimination, regardless of the amount
+of times recoding was performed and without incurring in any
+additional overhead cost for signaling. Similar to the encoding
+operation, any decoder that collects a set of $g$ \ac{l.i.} recoded
+packets with their respective coefficients, will be able to decode the
+data as mentioned before in Section \ref{sssec:decoding}.
 
@@
 
-In \ac{SRLNC}, instead of considering all the packets to create a coded packet
-as in \ac{RLNC}, an encoder sets more coding coefficients to zero when
-generating a coded packet with the purpose of reducing the overall processing.
-Decoding is the same as in \ac{RLNC}, but given that the coding matrices are now
-sparse, we will have less operations performed in the decoding process.
-Recoding, although theoretically possible, is omitted in practical systems since
-it is too complex to keep packets sparse after recoding
-[\textbf{reference}]\todot{add ref}. In what follows, we describe the coding
-scheme with a basic method to produce sparse coded packets and later we indicate
-a second one, giving reference to their implementation performance.
+In \ac{SRLNC}, instead of considering all the packets to create a
+coded packet as in \ac{RLNC}, an encoder sets more coding coefficients
+to zero when generating a coded packet with the purpose of reducing
+the overall processing.  Decoding is the same as in \ac{RLNC}, but
+given that the coding matrices are now sparse, we will have less
+operations performed in the decoding process.  Recoding, although
+theoretically possible, is omitted since it requires the use of
+heuristics keep packets sparse after recoding, which is inherently
+sub-optimal. In what follows, we describe the coding scheme with a
+basic method to produce sparse coded packets and later we indicate a
+second one, giving reference to their implementation performance.
 
@@
 %
-From the density definition in \eqref{eq:coding_density}, it can be
+From the density definition in~\eqref{eq:coding_density}, it can be
 observed that $0 \leq d \leq 1$. As $g$ increased, we obtain more
-granularity in the density. Notice that the special case $d = 0$ has no
+granularity in the density. Notice that the special case of  $d = 0$ has no
 practical purpose since it implies just zero padded data. So, a practical
@@
 it can be also observed that the case of $d = 1$ reduces to the \ac{RLNC}
-coding scheme described in Section \ref{ssec:RLNC}.
+coding scheme described in Section~\ref{ssec:RLNC}.
 
@@
 %
-In \eqref{eq:sparse_coded_packet}, we have the requirement for the coding
-coefficient to not be zero, since we want to ensure a coding coefficient
-is generated for any random trial where $\mathbb{B}_j = 1$. Therefore, in our
-implementation of \ac{SRLNC} we exclude the zero element and then pick
-uniformly distributed random elements from $GF(q)-\{ 0 \}$. Also, we have
-specified a dependency on the field size for practical
-density values. In case of employing $GF(2)$, the
-maximum plausible density is restricted up to 0.5 since higher values incur
-in more frequent \ac{l.d.} coded packets \textbf{Include reference here}.
+In~\eqref{eq:sparse_coded_packet}, we have the requirement for the
+coding coefficient to not be zero, since we want to ensure a coding
+coefficient is generated for any random trial, where
+$\mathbb{B}_j = 1$. Therefore, in our implementation of \ac{SRLNC} we
+exclude the zero element and then pick uniformly distributed random
+elements from $GF(q)-\{ 0 \}$. Also, we have specified a dependency on
+the field size for practical density values. In case of employing
+$GF(2)$, the maximum plausible density is restricted up to 0.5 since
+higher values incur in more frequent \ac{l.d.} coded
+packets~\cite{realworld_nc2013}.
 
-Reducing $d$ enables the encoder to decrease the average number of packets
-manipulated to make a coded one. This reduces the complexity of the encoder
-since it needs to mix less packets. Moreover, it also simplifies the decoder
-processing given that less nonzero coding coefficients are required to be
-operated during the Gaussian elimination stage.
+Reducing $d$ enables the encoder to decrease the average number of
+packets manipulated to make a coded one. This reduces the complexity
+of the encoder since it needs to mix less packets. Moreover, it also
+simplifies the decoder processing given that less nonzero coding
+coefficients are required to be operated during the Gaussian
+elimination stage.
 
 The drawback of this scheme is that coded packets from the encoder
-become more \ac{l.d.} on each other as the density is reduced.
-This leads to transmission overhead since another coded packet
-is required to be sent for every reception of a redundant packet.
-Also, particularly with this method, we may still generate a coded packet
-which does not contain any data at all. For example, we might find
-the case where $\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] =
-\mathbf{0}$. In that case, the encoder discards the coded packet
-and tries to generate a new one. This situation occurs more frequently
-as the density is reduced.
+become more \ac{l.d.} on each other as the density is reduced.  This
+leads to transmission overhead since another coded packet is required
+to be sent for every reception of a redundant packet.  Also, this
+method may still generate a coded packet, which does not contain any
+information. For example, we might find the case where
+$\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] = \mathbf{0}$ may
+happen frequently for low densities. In that case, the encoder
+discards the coded packet and tries to generate a new one to avoid the
+negative impact on overall system performance.
 
 \subsubsection{Method 2: Sampling the Amount of Packets to Combine}
-The method described from \eqref{eq:sparse_coded_packet} permits
-to obtain a fast implementation in terms of execution time for
-$d \geq 0.3$ \textbf{Include reference here}. Nevertheless, for $d < 0.3$
+The method described from \eqref{eq:sparse_coded_packet} results
+in a fast implementation in terms of execution time for
+$d \geq 0.3$~\cite{practicalview_tsnc2015}. Nevertheless, for $d < 0.3$
 the implementation becomes slow given that more Bernoulli trials are
@@
 Thus, we introduce a second method that permits a fast implementation
-for low coding densities \textbf{Same reference here}.
+for low coding densities~\cite{practicalview_tsnc2015}.
 
 For this method, we first obtain the amount of packets
-that we will combine to create a coded packet. To do it so, a random
-number $\mathbb{N}$ of the original packets is used to produce a
+that we will combine to create a coded packet. To do so, a random
+number, $\mathbb{N}$, of the original packets is used to produce a
 coded packet. For our case, $\mathbb{N}$ is binomially distributed
@@
 the considered density range in this method, this is not a significant
-modification \textbf{Same reference here}. Then, once the distribution for the
-number of packets to mix has been defined, we sample a value $n$ from
-$\mathbb{N}$ and compute $k = \max(1,n)$. Later, we create a create a
-set $\mathcal{K}$ with cardinality $k$, e.g. $|\mathcal{K}| = k$,
-where the elements in $\mathcal{K}$ are the indexes of the packets that are
-going to be considered for making a coded packet. To compute the indexes
+modification~\cite{practicalview_tsnc2015}. Then, once the
+distribution for the number of packets to mix has been defined, we
+sample a value $n$ from $\mathbb{N}$ and compute $k =
+\max(1,n)$. Later, we create a create a set $\mathcal{K}$ with
+cardinality $k$, e.g. $|\mathcal{K}| = k$, where the elements in
+$\mathcal{K}$ are the indexes of the packets that are going to be
+considered for making a coded packet. To compute the indexes
 of the set $\mathcal{K}$, we do the following algorithm in pseudo-code: \\
@@
 \ \\
-Where in Algorithm~\ref{alg:k_set}, the notation $\mathbb{U}(1,g)$ stands
+In Algorithm~\ref{alg:k_set}, the notation $\mathbb{U}(1,g)$ stands
 for a uniform discrete random variable with limits $1$ and $g$. The
@@
 as degrees of freedom to the dimension of the linear span from the coded
-packets that a decoder has at a given point} increases, e.g. as the
+packets that a decoder has at a given point} increases, e.g., as the
 cardinality of the set of \ac{l.i.} coded packets increases. This enables
@@
 \begin{equation}\label{eq:budget}
-    b(g,d)=\sum^{g-1}_{i=0}\frac{1}{P(i,g,d)}
+    b(g,d)=\sum^{g-1}_{i=0}\frac{1}{P(i,g,d)},
 \end{equation}
-
 where $P(i,g,d)$ is the probability of receiving an innovative coded packet
@@
 generation size. Still, we have an implementation that limits the amount of
-feedback to be sent from the decoder in [\textbf{reference}].\todot{@Chres this reference is missing}
+feedback to be sent from the decoder in~\cite{practicalview_tsnc2015}.
 
-The transmissions made between feedback packets are called the density regions
-since the same estimated density is used for encoding sparse packets. Once new
-feedback is received, an encoder recalculates the coding density for the new
-region until the next feedback packet is received. before the coding density can
-be estimated, it is essential that the encoder has a good estimate of the
-decoder \ac{dof}, but also the remainder of the total budget. To calculate the
-density, we use bisection to estimate a fixed density for the density region
-that satisfies the budget for the $k$-th density region:
+The transmissions made between feedback packets are called the density
+regions since the same estimated density is used for encoding sparse
+packets. Once a new feedback is received, an encoder recalculates the
+coding density for the new region until the next feedback packet is
+received. before the coding density can be estimated, it is essential
+that the encoder has a good estimate of the decoder \ac{dof}, but also
+the remainder of the total budget. To calculate the density, we use
+bisection to estimate a fixed density for the density region that
+satisfies the budget for the $k$-th density region:
 \begin{equation}
@@
 % except the last one, to which it is assigned the remaining of the budget.
-The feedback scheme based on the rank reports of \eqref{eq:feedback_dofs}
-roughly splits the remaining coding regions in two halves. In other
-words, the first half is the region where the encoder currently operates. Once
-an encoder finishes with this region, it proceeds with second half where again
-it splits this into to two region and so on until it finishes on transmitting
-the whole generation. This is also the case for the budget that is split equally
-among the two new regions. The very last region will be assigned the full
-remainder of the total budget and the coding density will not vary.
+The feedback scheme based on the rank reports
+of~\eqref{eq:feedback_dofs} roughly splits the remaining coding
+regions in two halves. In other words, the first half is the region
+where the encoder currently operates. Once an encoder finishes with
+this region, it proceeds with second half where again it splits this
+into to two region and so on until it finishes on transmitting the
+whole generation. This is also the case for the budget that is split
+equally among the two new regions. The very last region will be
+assigned the full remainder of the total budget and the coding density
+will not vary.
 
@@
 
-The arithmetic operations needed to encode and decode data are,
-in general, similar. To encode packets, the encoder needs to perform the
-matrix multiplication $\textbf{C} = \textbf{V} \textbf{P}$. On the other
-hand, decoding the information requires the decoder to find
+The arithmetic operations needed to encode and decode data are, in
+general, similar. To encode packets, the encoder needs to perform the
+matrix multiplication $\textbf{C} = \textbf{V} \textbf{P}$. On the
+other hand, decoding the information requires the decoder to find
 $\textbf{V}^{-1}$ and to perform the matrix multiplication
 $\textbf{P} = \textbf{V}^{-1} \textbf{C}$. In both cases, a matrix
-multiplication is needed. Therefore, to make a practical implementation of
-network coding, it is valuable to find a way to optimize the matrix
-multiplications operations for multicore architectures.
+multiplication is needed. Therefore, to make a practical
+implementation of network coding, it is valuable to find a way to
+optimize the matrix multiplications operations for multicore
+architectures.
 
-When designing multi-threaded algorithms for network coding operations, it is
-possible to implement the decoding by combining the matrix inversion and the
-matrix multiplication, e.g. performing the Gauss-Jordan algorithm over the
-coding matrix $\textbf{V}$ while performing, in parallel, row operations on the
-coded data $\textbf{C}$. For example, in~\cite{5061951} and~\cite{4262451} the
-parallelization of the row operations are optimized for \ac{GPU} and \ac{SMP}
-systems respectively. However, the parallelization of such operations provide
-limited speeds up for small block sizes ($\leq 2048$ bytes). The reason is that
-to operate in a parallel fashion over the same coded packet $C_i$ requires
-strained synchronization.
+When designing multi-threaded algorithms for network coding
+operations, it is possible to implement the decoding by combining the
+matrix inversion and the matrix multiplication, e.g., performing the
+Gauss-Jordan algorithm over the coding matrix $\textbf{V}$ while
+performing, in parallel, row operations on the coded data
+$\textbf{C}$. For example, in~\cite{5061951} and~\cite{4262451} the
+parallelization of the row operations are optimized for \ac{GPU} and
+\ac{SMP} systems respectively. However, the parallelization of such
+operations provide limited speeds up for small block sizes
+($\leq 2048$ bytes). The reason is that to operate in a parallel
+fashion over the same coded packet $C_i$ requires strained
+synchronization.
 

### 2016-06-06 measurements.tex
Average power done. Going for energy

@@
 With the energy measurement setup described in Section
-\ref{sec:energy_metrics_methods}, we compute the metrics described there.
-We first proceed with the average power consumption of the \ac{Raspi} 1
-in Fig.~\ref{fig:current_rasp1} and the \ac{Raspi} 2 in
-Fig.~\ref{fig:current_rasp2}.
+\ref{sec:energy_metrics_methods}, we compute the average power of each
+device from their current consumption across time in
+Figs.~\ref{fig:current_rasp1} and \ref{fig:current_rasp2}. In each
+figure, the eletrical current values are classified into three possible
+currents: Idle, transition and processing. These values are identified by
+our post-processing. Later, the values in red are idle currents, green for
+transitions and blue for processing.
 
+For a given configuration of a coding scheme, device type and its parameters,
+only electrical current processing values are present. In general, we
+associate the current samples from a given configuration with its goodput
+through a timestamp. In this way, we relate goodput and power / energy
+measurements. Once identified the current values, we compute the averages
+for each configuration as described in Section
+\ref{sec:energy_metrics_methods}. In the presented current samples, we observe
+a presence of bursty noise. Nevertheless, by taking the average as described
+in \eqref{eq:avg_current}, we remove this contribution in the average
+processing current.
+%
 \begin{figure*}
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/06_06_2016/current_vs_sec_raspberry_change_gen_from_-10sec_to_500sec.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/current_vs_sec_raspberry_change_gen_from_-10sec_to_500sec.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.15\textwidth]{images/06_06_2016/current_vs_sec_raspberry2_change_gen_from_-10sec_to_500sec.eps}
+        \includegraphics[width=1.1\textwidth]{images/06_06_2016/current_vs_sec_raspberry2_change_gen_from_-10sec_to_500sec.eps}
         \caption[]%
@@
 \end{figure*}
+%
+By reviewing the processing current samples in Figs.~\ref{fig:current_rasp1}
+and \ref{fig:current_rasp2}, we observe that the average processing current
+does not change significantly for each \ac{Raspi} model in all the shown
+configurations. Therefore, we approximate the current consumption
+for the devices and compute the average power as indicated in
+\eqref{eq:avg_power}. The results are shown in
+Table~\ref{tab:average_power_table}.
 
-Average current description. Include a table mentioning the current values
-and the resulting power values.
+\begin{table}[H]
+\center
+\caption{Average power for the \ac{Raspi} models}
+\begin{tabular}{|r|r|r|r|}
 
+\hline
+\ac{Raspi} Model & $I_{idle,avg}$ (A)& $I_{proc,avg}$ (A) & $P_{avg}$ (W) \\
+\hline
+\hline
+    \ac{Raspi} 1 &      0.320        &            0.360    & 0.200\\
+\hline
+    \ac{Raspi} 2 &      0.216        &            0.285    & 0.345\\
+\hline
+\end{tabular}
+\vspace{0.2cm}
+\label{tab:average_power_table}
+\end{table}
+%
+From Table~\ref{tab:average_power_table}, we notice that the power expenditure
+for both models is almost the same. Thus, the energy behaviour is mostly
+dependent on the goodput trends since the power is just an scaling constant.
+%
 \subsection{Energy per bit}
 With power and goodput measurements, we compute the energy per bit of
-the previously mentioned cases in the same fashion as before.
+the previously mentioned cases as described in \eqref{eq:energy_per_bit}.
+The trends of the energy per bit are simply the inverse of the goodput since
+both metrics are related by an inverse law.
 
@@
 (words in the finite field) in height and width. The figures show only
-block sizes of $16 \times 16$ or $32 \times 32$ operands since with bigger
-block sizes, the operands do not fit in L1 cache.
+block sizes of $16 \times 16$, $32 \times 32$, $64 \times 64$ operands
+since with bigger block sizes, the operands do not fit in L1 cache.
 
@@
 \includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_1024.pdf}
-\caption{Encoding and Decoding performance for g = 1024 \cite{wunderlich2015network}}
+\caption{Encoding and Decoding performance for $g = 1024$. Block size: $32 \times 32$. \cite{wunderlich2015network}}
 \label{enc_dec1024}
@@
 
-For $g=$ 1024, the blocked baseline measurements outperforms the non blocked
+For $g= 1024$, the blocked baseline measurements outperforms the non blocked
 variant. This means that making the matrix multiplication algorithm cache
@@
 cores provides a gain of 10 folds compared with traditional non-blocked
-algorithms. With $g$ = 1024, the matrix inversion becomes more expensive
+algorithms. With $g = 1024$, the matrix inversion becomes more expensive
 than at smaller generations sizes. Therefore, the decoding throughput
@@
 \includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_128.pdf}
-\caption{Encoding and Decoding performance for g = 128 \cite{wunderlich2015network}}
+\caption{Encoding and Decoding performance for $g = 128$. Block size: $64 \times 64$ \cite{wunderlich2015network}}
 \label{enc_dec128}
@@
 matrix sizes, the gain when using blocked operations in the baselines is not
-that significant when compared with $g$ = 1024. For the same reason, the matrix
+that significant when compared with $g = 1024$. For the same reason, the matrix
 inversion is less expensive. As a consequence, the decoding throughput is 71\%
@@
 \includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_16.pdf}
-\caption{Encoding and Decoding performance for g = 16 \cite{wunderlich2015network}}
+\caption{Encoding and Decoding performance for $g = 16$. Block size: $16 \times 16$ \cite{wunderlich2015network}}
 \label{enc_dec16}
@@
 
-When $g$ = 16, the gains of blocked operations are negligible compared with
+When $g = 16$, the gains of blocked operations are negligible compared with
 the non-blocked ones. The reason behind this behavior is that all the data

### 2016-06-06 testbed.tex
began persistant storage
first draft of testbed ready

@@
 
-\subsection{Write image}
-
-The final step is to write the image to all the memory cards before they can
-be plugged in the \ac{Raspi}s. This is done by first leaving the chrooted filesystem
-and unmounting all the directories we mounted:
+At this point, it is no longer required to be \texttt{chrooted} and the image
+can be written to a memory card. The following commands exits the \texttt{chrooted}
+environment, unmount all partitions, and detaches the loop device:
 
@@
 # umount --recursive ${ROOTDIR}
-# losetup -d WHICH_NUMBE.img
+# losetup -d ${DEV}.img
 \end{lstlisting}
@@
 
-If successfully unmounted, you can insert a memory card in your machine. In our
-system, this memory card was available under /dev/mmcblk0, but this may be
-different on different machines. For internal memory card readers, it will
-probably be named /dev/mmcblkX where X is some number and if the memory card
-reader is connected through \ac{USB}, then it is likely called /dev/sdX.
-Make sure to write to the correct device as everything will be overwritten!
+\subsection{(Optional) Persistent subdirectories}
 
-Below is a few commands that may help you to deduce which device is correct:
+Provided the stacked filesystem was configured, it may be desired to have
+some directories where files are not flushed upon rebooting the \ac{Raspi}s.
+The following procedure will create an extra partition in the image for
+the \ac{Raspi} users home directory that will be made storage persistent.
+%Provided that a stacked filesystem was configured to make the root
+%filesystem forget chances upon reboots is not always desired.
+
+Expand image according to the desired home directory size. Keep in mind not
+to make the image bigger than the target memory card.
+% Expand image
+\begin{lstlisting}[]
+# dd if=/dev/zero bs=1M count=1024 >> ${IMAGE}.img && sync
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Create home partition after the root partition. Use \texttt{fdisk} to
+find the next available sector in the image. In our case, the new
+partition should start at sector 4806656:
+\begin{lstlisting}[]
+# fdisk -lu ${IMAGE}.img
+Disk 2016-05-27-raspbian-jessie-lite.img: 3.3 GiB, 3534749696 bytes, 6903808 sectors
+Units: sectors of 1 * 512 = 512 bytes
+Sector size (logical/physical): 512 bytes / 512 bytes
+I/O size (minimum/optimal): 512 bytes / 512 bytes
+Disklabel type: dos
+Disk identifier: 0x6fcf21f3
+
+Device                               Boot  Start     End Sectors  Size Id Type
+2016-05-27-raspbian-jessie-lite.img1        8192  137215  129024   63M  c W95 FAT32 (LBA)
+2016-05-27-raspbian-jessie-lite.img2      137216 4806655 4669440  2.2G 83 Linux
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Create new partition:
+
+\begin{lstlisting}[]
+# (echo n; echo p; echo ; echo 4806656; echo ; echo p; echo w) | fdisk ${IMAGE}.img
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Create loopback device: 
+\begin{lstlisting}[]
+# DEV=$(losetup --show -f -P ${IMAGE}.img); echo $DEV
+/dev/loop0
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+Format new partition:
+\begin{lstlisting}[]
+# mkfs.ext4 ${DEV}p3
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+The last thing to remember is to inform Raspbian to mount the home partition
+we created during startup. This can be done by adding an entry in \texttt{fstab}:
+\begin{lstlisting}[]
+# mount ${DEV}p2 ${ROOTDIR}
+# echo "/dev/mmcblk0p3 /home ext4 defaults,noatime 0 2" >> ${ROOTDIR}/etc/fstab
+# umount ${ROOTDIR}
+# losetup -d ${DEV}
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+\subsection{Write image to memory card}
+
+The final step is to write the image to all the memory cards before they can
+be used in the \ac{Raspi}s.
+
+%This is done by first leaving the \texttt{chrooted}
+%filesystem and unmounting all the directories we mounted:
+
+% Exit chroot, umount, and write to memory card
+%\begin{lstlisting}[]
+%# exit
+%# cd ..
+%# umount --recursive ${ROOTDIR}
+%# losetup -d ${DEV}.img
+%\end{lstlisting}
+%\FloatBarrier
+%\vspace{-5mm}
+
+%If successfully unmounted, you can 
+Insert a memory card in your machine. It will be available as
+\texttt{/dev/mmcblkX} or \texttt{/dev/sdX}
+
+%In most systems, this memory card was available under \texttt{/dev/mmcblk0}, but this may be
+%different on different machines. For internal memory card readers, it will
+%probably be named /dev/mmcblkX where X is some number and if the memory card
+%reader is connected through \ac{USB}, then it is likely called /dev/sdX.
+Make absolutely sure to write to the correct device as everything will be 
+overwritten!
+Inserting/Ejecting the memory card a couple of times and using the commands
+below may help deducing the correct device:
+%The commands below may help deduce which device is the correct:
+%Below is a few commands that may help you to deduce which device is correct:
 
@@
 
-For us, the device was /dev/mmcblk0, so we write the image to that device:
+For us, the device was \texttt{/dev/mmcblk0}, so we write the image to that device:
 \begin{lstlisting}[]

### 2016-06-06 measurements.tex
Corrections to format writing

@@
 The authors implemented the algorithm described in
-Section~\ref{sub:implementation-multicore} on the Raspberry Pi 2 Model B,
-which features four ARM Cortex-A7 cores in a Broadcom BCM2836 \ac{SOC}
+Section~\ref{sub:implementation-multicore} on the \ac{Raspi} 2 model,
+which features four ARMv7 cores in a Broadcom BCM2836 \ac{SOC}
 with a 900 MHz clock. Each core has a 32 KiB L1 data cache and 32 KiB
@@
 measured results, including the baseline results, were obtained with
-NEON-enabled code adopted from the Fifi library [\textbf{Fifi reference}].
-The NEON extension provides an 128-bit \ac{SIMD} instruction set to the
-\ac{Raspi} 2. Figures~\ref{enc_dec1024}, \ref{enc_dec128} and
-\ref{enc_dec16} show the encoding and decoding throughput in MiB per
-second for different generation sizes ($g$ = 1024, 128, and 16
-respectively). The throughput is the rate of generating $g$ coded packets,
-divided by the time the encoder took to perform the task. The size of
-each coded packet was fixed to $1536$~bytes since that is the typical
-size of an Ethernet frame. The blocked operations were performed dividing
-the matrices in squared sub-blocks of $16,\ 32\ ,\ 64,\ldots,\ 1024$ operands
-(words in the finite field) in height and width. The figures show only
-block sizes of $16 \times 16$, $32 \times 32$, $64 \times 64$ operands
-since with bigger block sizes, the operands do not fit in L1 cache.
-
-The following test cases were considered:
+NEON-enabled code adapted from the Fifi library [\textbf{Fifi reference}].
+The \ac{Raspi} 2 has a NEON extension instruction set which provides
+an 128-bit \ac{SIMD} instructions that speed the computations.
+Figures~\ref{enc_dec1024}, \ref{enc_dec128} and
+\ref{enc_dec16} show the encoding and decoding goodput in MB per
+second for different generation sizes, $g = [1024, 128, 16]$
+respectively. The size of each coded packet was fixed to $1536$~bytes
+since that is the typical size of an Ethernet frame. The blocked operations
+were performed dividing the matrices in squared sub-blocks of
+$16,\ 32\ ,\ 64,\ldots,\ 1024$ operands (words in the Galois field) in
+height and width. The figures show only block sizes of
+$16 \times 16$, $32 \times 32$, $64 \times 64$ operands since with bigger
+block sizes, the operands do not fit in L1 cache. Several testcases
+are considered and detailed.
 
@@
 \ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder uses
-only one thread. And the difference between the non-blocked and blocked
+only one thread. The difference between the non-blocked and blocked
 encoding schemes is that in the blocked scheme, the matrix multiplications are
@@
 \subsubsection{Encoding blocked}
-The encoding results were performed using the
+The encoding results are obtained using the
 method described in Section~\ref{sub:implementation-multicore}. The time
 recorded includes the dependencies resolving, creation of the \ac{DAG},
-and the task scheduling. In practice, it would suffice to calculate and
+and the taskz scheduling. In practice, it would suffice to calculate and
 store this information only once per generation size.
@@
 the time recorded includes the dependencies resolving, the creation of the
-\ac{DAG} and the task scheduling. However, to decode, these calculations are also made for inverting the matrix of coding coefficients.
+\ac{DAG} and the task scheduling. However, to decode, these calculations
+are also made for inverting the matrix of coding coefficients.
 
@@
 variant. This means that making the matrix multiplication algorithm cache
-efficient brings an increase in throughput by a factor of 2.83. When using the
+efficient brings an increase in goodput by a factor of 2.83. When using the
 algorithm described in Section~\ref{sub:implementation-multicore},
-encoding with four cores is on average 3.7 times faster than with one core.
-Similarly, decoding with four codes is 3.05 times faster, on average, than
+encoding with four cores is on average $3.7\times$ faster than with one core.
+Similarly, decoding with four codes is $3.05\times$ faster, on average, than
 decoding with a single core. Figure~\ref{enc_dec1024} shows that the
 implemented algorithm, by exploiting cache efficiency and only three extra
-cores provides a gain of 10 folds compared with traditional non-blocked
+cores provides a $10\times$ gain compared with traditional non-blocked
 algorithms. With $g = 1024$, the matrix inversion becomes more expensive
-than at smaller generations sizes. Therefore, the decoding throughput
-is 46\% of the encoding throughput.
+than at smaller generations sizes. Therefore, the decoding goodput
+is 46\% of the encoding goodput.
 
@@
 
-For $g$ = 128, the differences between the baselines operations show that a
+For $g = 128$, the differences between the baselines operations show that a
 blocked algorithm is 15\% faster than the non-blocked variant. Encoding with
-four cores is 2.82 times faster than with a single core. Due to the smaller
+four cores is $2.82\times$ faster than with a single core. Due to the smaller
 matrix sizes, the gain when using blocked operations in the baselines is not
 that significant when compared with $g = 1024$. For the same reason, the matrix
-inversion is less expensive. As a consequence, the decoding throughput is 71\%
-of the encoding throughput.
+inversion is less expensive. As a consequence, the decoding goodput is 71\%
+of the encoding goodput.
 
@@
 
-The differences in throughput, for all generation sizes, between the
+The differences in goodput, for all generation sizes, between the
 blocked baseline and the single threaded scheduled measurements are due the
@@
 smaller is the calculated ratio. This means that when the problems are bigger,
-the decoding throughput decreases compared with the encoding throughput.
+the decoding goodput decreases compared with the encoding goodput.
 

### 2016-06-06 measurements.tex
Getting testbed description

@@
 The trends of the energy per bit are simply the inverse of the goodput since
-both metrics are related by an inverse law.
+both metrics are related by an inverse law. As made with the goodput, we
+separate the results descriptions according to the operation carried by the
+\ac{Raspi}: Encoding and decoding. Besides this, we differentiate between
+the models in our study. The energy per bit consumption removes the dependency
+on the amount of packets helping to normalize the results and indicating
+consumption on a fair basis for all the configurations and coding operations
+involved in the study.
 
 \subsubsection{Encoding}
+Figs.~\ref{fig:enc_ene_rasp1} and \ref{fig:enc_ene_rasp2} show the encoding
+energy per bit measurements for the \ac{Raspi} 1 and 2 models, respectively.
 

### 2016-06-06 testbed.tex
testbed

@@
 \begin{lstlisting}[]
-# (echo d; echo ; echo n; echo p; echo ; echo 137216; echo ; echo p; echo w) | fdisk ${IMAGE}.img
+$ (echo d; echo ; echo n; echo p; echo ; echo 137216; echo ; echo p; echo w) | fdisk ${IMAGE}.img
 \end{lstlisting}
@@
 
-Make the Raspbian image available as a block device: 
+Make the Raspbian image available as a block device (notice that the
+command is run as root using sudo): 
 \begin{lstlisting}[]
-# DEV=$(losetup --show -f -P ${IMAGE}.img); echo $DEV
+# export DEV=$(sudo losetup --show -f -P ${IMAGE}.img); echo $DEV
 /dev/loop0
@@
 each \ac{Raspi} call the above script when it starts up.
-Do this by inserting the line below in "\$\{ROOTDIR\}/etc/rc.local".
-The file
-can be opened with your favorite text editor.
+Do this with root permissions by inserting the line before
+\texttt{"exit 0"} using your favorite editor:
+%"\$\{ROOTDIR\}/etc/rc.local" using
+%your favorite text editor..
+%The file
+%can be opened with your favorite text editor.
 
-\begin{lstlisting}[]
-bash /home/pi/rasp_config/set_hostname"
+\Suppressnumber\begin{lstlisting}[]
+<@\textcolor{gray}{\$\{ROOTDIR\}/etc/rc.local}@>
+<@\textcolor{gray}{
+-----------------------------------------------------}
+\Reactivatenumber @>
+...
+bash /home/pi/rasp_config/set_hostname
+...
+exit 0
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# cd $ROOTDIR
+$ cd $ROOTDIR
 # cp /etc/resolv.conf etc/resolv.conf
@@
 # umount --recursive ${ROOTDIR}
-# losetup -d ${DEV}.img
+# losetup -d ${DEV}
 \end{lstlisting}

### 2016-06-07 measurements.tex
Starting to close the energy section

@@
 energy per bit measurements for the \ac{Raspi} 1 and 2 models, respectively.
-
+We now proceed to analyze first the \ac{Raspi} 1 case pointing out proper
+differences with the \ac{Raspi} 2 when applicable.
+%
 \begin{figure*}
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary_encoder_1600.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary_encoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary8_encoder_1600.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary8_encoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary_encoder_128.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary_encoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary8_encoder_128.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary8_encoder_128.eps}
         \caption[]%
@@
 \end{figure*}
+%
+In Figs.~\ref{fig:enc_ene_rasp1_gen_gf2} and \ref{fig:enc_ene_rasp1_gen_gf256},
+we see the dependency of the energy per bit processed on the generation size
+for the \ac{Raspi} 1 model. In these type of plots, incrementing the
+generation size incurs in more processing time per byte sent which leads to
+more processing time per bit sent. For \ac{RLNC}, the energy trends
+scales as the processing time scale which is $\mathcal{O}(g)$. For sparse
+codes, this trend is scaled by the density, thus for sparse we have
+$\mathcal{O}(\ceil{gd})$ which can be appreciated in the same figures. We
+do also notice that using $GF(2)$ is energy-wise efficient on the a
+per-bit basis since less operations are used to perform the \ac{GF}
+arithmetics which reduces the amount of energy spent.
 
-Raspi 2 encoding
-
+In Figs.~\ref{fig:enc_ene_rasp1_packet_gf2} and
+\ref{fig:enc_ene_rasp1_packet_gf256} for the same device. We exhibit the
+relationship between the energy per bit processed on the packet size which
+is the inverse of the goodput vs. the packet size scaling law. We set
+$g = 128$ in this case to observe energy per bit consumption in the regime where the
+processing time is considerable. As we notice again in this case,
+$GF(2)$ presents as the field with the smallest energy per bit consumption
+given that is the one that has least complex operations. The trends
+for the energy can be explained as follows: As the packet size increases,
+we process more coded bits at the same time, which increases the encoding
+speed, until we hit the critical packet size. After this value, we spend
+more time queueing data towards the cache besides the processing, which
+increases the time spent per processed bit and thus the energy.
+%
 \begin{figure*}
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary_encoder_1600.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary_encoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_encoder_1600.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_encoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_encoder_128.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_encoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_encoder_128.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_encoder_128.eps}
         \caption[]%
@@
 \end{figure*}
+%
+In Figs.~\ref{fig:enc_ene_rasp2_gen_gf2}, \ref{fig:enc_ene_rasp2_gen_gf256},
+\ref{fig:enc_ene_rasp2_packet_gf2} and \ref{fig:enc_ene_rasp2_packet_gf256} 
+we show the encoding energy per bit consumption for the \ac{Raspi} 2.
+We clearly see that the effects discussed for the \ac{Raspi} 1 also apply
+as well for the \ac{Raspi} 2. Moreover, given that the average power
+is in the same order, but the \ac{Raspi} 2 is a faster device,
+the energy costs for the \ac{Raspi} 2 are $2\times$ less than the \ac{Raspi} 1
+when referring to variable generation sizes and a fixed packet size.
+Furthermore, these costs are 1 order of magnitude less for the \ac{Raspi} 2
+with respect to the \ac{Raspi} 1 regarding the case of a fixed generation
+size and a variable packet size. This makes the \ac{Raspi} 2 to achieve
+a minimum encoding energy consumpiton per bit processed of 0.2 nJ for the
+binary field in the mentioned regime.
 
 \subsubsection{Decoding}
-
+In Figs.~\ref{fig:dec_ene_rasp1_gen_gf2}, \ref{fig:dec_ene_rasp1_gen_gf256},
+\ref{fig:dec_ene_rasp1_packet_gf2} and \ref{fig:dec_ene_rasp1_packet_gf256} 
+we show the encoding energy per bit consumption for the \ac{Raspi} 1.
+Again, we notice very similar behavior and trends as previously
+reviewed for the encoding energy per bit expenditure. In this case,
+we focus on performance among the coding schemes since the behavior 
+and trends were previously explained for the encoding case.
+%
 \begin{figure*}
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary_decoder_1600.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary_decoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary8_decoder_1600.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary8_decoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary_decoder_128.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary_decoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary8_decoder_128.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary8_decoder_128.eps}
         \caption[]%
@@
 \end{figure*}
-
-Raspi 2 decoding
+%
+Some differences occurs due to nature of decoding. In this situation,
+the reception of \ac{l.d.} coded packets just increases the decoding
+delay, therefore reducing the performance of some coding schemes
+in terms of the energy per bit consumption. For example,
 
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary_decoder_1600.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary_decoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_decoder_1600.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_decoder_1600.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_decoder_128.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_decoder_128.eps}
         \caption[]%
@@
         \centering
-        \includegraphics[width=1.1\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_decoder_128.eps}
+        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_decoder_128.eps}
         \caption[]%

### 2016-06-07 metrics.tex
Average power done. Going for energy

@@
 To get this metric for a given configuration, we simply express the energy
-as the product of the average power by the processing time $T_{proc}$ obtained
-from the goodput measurement for the same configuration. In this way, we can
+as the product of the average power by the processing time $T_{proc} [sec/byte]$
+obtained from the goodput measurement for the same configuration. In this way, we can
 relate the processing time with the goodput, the packet and the generation size
@@
 %
-\begin{align} \label{eq:goodput}
-E_b = P_{avg} T_{proc} = P_{avg} \times \frac{g(8B)}{R_{proc}} ~[\mathrm{Joules}]
+\begin{align} \label{eq:energy_per_bit}
+E_b = P_{avg} T_{proc,bit} = P_{avg} \times \frac{T_{proc}}{8gB} = \frac{P_{avg}}{8R_{proc}} ~[\mathrm{Joules}]
 \end{align}

### 2016-06-07 measurements.tex
Energy per bit done. Results done!

@@
 we focus on performance among the coding schemes since the behavior 
-and trends were previously explained for the encoding case.
+and trends were previously explained for the encoding case. Later,
+we introduce the decoding energy results for the \ac{Raspi} 2 doing
+relevant comparisons with the \ac{Raspi} 1.
 %
@@
 delay, therefore reducing the performance of some coding schemes
-in terms of the energy per bit consumption. For example,
-
+in terms of the energy per bit consumption. For example, we notice
+that using \ac{SRLNC} with $d = 0.02$ outperforms \ac{TSNC} with
+$C = 0$ and $e = 16$, for most of the cases in the variable generation
+size curves and in all the cases of variable packet size curves of
+Fig.~\ref{fig:dec_ene_rasp1}. This is a clear scenario where the decoding
+delay is energy-wise susceptible to the transmissions of \ac{l.d.}
+coded packets. With the \ac{Raspi} 1, decoding energies per processed
+bit of 2 nJ or similar are possible. 
+%
 \begin{figure*}
@@
 \end{figure*}
-
+%
+Finally, in Figs.~\ref{fig:dec_ene_rasp2_gen_gf2},
+\ref{fig:dec_ene_rasp2_gen_gf256}, \ref{fig:dec_ene_rasp2_packet_gf2}
+and \ref{fig:dec_ene_rasp2_packet_gf256}; we introduce the decoding energy
+per bit consumption for the \ac{Raspi} 2. Here, we obtain a reduction
+of an order of magnitude in energy per processed bit due to the speed
+of the \ac{Raspi} 2. For example, it can be seen that for the binary field
+with $g = 16$ packets, we achieve a decoding energy consumption per bit 
+processed close to 0.1 nJ in practical systems.
+%
 \subsection{Multicore Network Coding}
@@
 
-The authors implemented the algorithm described in
+To review the performance of \ac{NC} in a multicore using the \ac{Raspi},
+the authors implemented the algorithm described in
 Section~\ref{sub:implementation-multicore} on the \ac{Raspi} 2 model,

### 2016-06-07 testbed.tex

@@
 
-To download the latest Raspbian lite, we go to the url
-\url{http://downloads.raspberrypi.org/raspbian_lite/images/}.
+The latest Raspbian lite image can be downloaded at~\cite{raspbian}.
+%To download the latest Raspbian lite, we go to the url
+%\url{http://downloads.raspberrypi.org/raspbian_lite/images/}.
 At the time of this writing, the latest bundle was
@@
 
-A more recent version of Raspbian lite may be available on 
-\url{http://downloads.raspberrypi.org/raspbian_lite/images}.
+A more recent version of Raspbian lite may be available at~\cite{raspbian}.
+%\url{http://downloads.raspberrypi.org/raspbian_lite/images}.
 
@@
 \begin{lstlisting}[]
-# dd if=/dev/zero bs=1M count=1024 >> ${IMAGE}.img && sync
+$ dd if=/dev/zero bs=1M count=1024 >> ${IMAGE}.img && sync
 \end{lstlisting}
@@
 $ wget http://kom.aau.dk/project/TuneSCode/raspi/rasp_config.zip
-# unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
+$ unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# vim ${ROOTDIR}/home/pi/rasp_config/nodes.csv
+$ vim ${ROOTDIR}/home/pi/rasp_config/nodes.csv
 \end{lstlisting}
@@
 written to all the memory cards that goes into the \ac{Raspi}s.
-This can be done from any linux x86 machine using QEMU Chroot (change root).
-\url{https://wiki.debian.org/QemuUserEmulation}
+This can be done from any linux x86 machine using QEMU Chroot~\cite{QemuUserEmulation}
+(change root).
+%\url{https://wiki.debian.org/QemuUserEmulation}
 %\url{https://wiki.archlinux.org/index.php/Raspberry_Pi}
@@
 # mount -t proc proc proc/
-# mount --rbind /sys sys/
-# mount --rbind /dev dev/
+# mount --bind /sys sys/
+# mount --bind /dev dev/
+# mount --bind /dev/pts dev/pts
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# apt-get update
-# apt-get upgrade
+(chroot) # apt-get update
+(chroot) # apt-get upgrade
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# apt-get install vim git screen
+(chroot) # apt-get install vim git screen
 \end{lstlisting}
@@
 use an existing implementation
-available at github: \url{https://github.com/chesty/overlayroot}.
+available at github: \cite{overlayroot}.
 
@@
 \begin{lstlisting}[]
-# OVERLAYROOTDIR="/tmp/overlayroot"
-# git clone https://github.com/chesty/overlayroot.git $OVERLAYROOTDIR
+(chroot) # OVERLAYROOTDIR="/tmp/overlayroot"
+(chroot) # git clone https://github.com/chesty/overlayroot.git $OVERLAYROOTDIR
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# apt-get install busybox
+(chroot) # apt-get install busybox
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# cp ${OVERLAYROOTDIR}/hooks-overlay /etc/initramfs-tools/hooks/
-# cp ${OVERLAYROOTDIR}/init-bottom-overlay /etc/initramfs-tools/scripts/init-bottom/
-# echo "overlay" > /etc/initramfs-tools/modules
+(chroot) # cp ${OVERLAYROOTDIR}/hooks-overlay /etc/initramfs-tools/hooks/
+(chroot) # cp ${OVERLAYROOTDIR}/init-bottom-overlay /etc/initramfs-tools/scripts/init-bottom/
+(chroot) # echo "overlay" > /etc/initramfs-tools/modules
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# echo "initramfs init.gz" > /boot/config.txt
+(chroot) # echo "initramfs init.gz" > /boot/config.txt
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# ls /lib/modules/
+(chroot) # ls /lib/modules/
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# mkinitramfs -o /boot/init.gz -k 4.4.11+
+(chroot) # mkinitramfs -o /boot/init.gz -k 4.4.11+
 \end{lstlisting}
@@
 
-This should generate a new initial \ac{RAM} filesystem that will overlay a \ac{RAM} filesystem.
+Although there might be printet a few warnings, this should generate
+a new working \texttt{initramfs} that will put a \ac{RAM} filesystem
+on top of the root filesystem.
 
@@
 \begin{lstlisting}[]
-# exit
+(chroot) # exit
 # cd ..
@@
 \begin{lstlisting}[]
-# fdisk -lu ${IMAGE}.img
+$ fdisk -lu ${IMAGE}.img
 Disk 2016-05-27-raspbian-jessie-lite.img: 3.3 GiB, 3534749696 bytes, 6903808 sectors
@@
 \begin{lstlisting}[]
-# (echo n; echo p; echo ; echo 4806656; echo ; echo p; echo w) | fdisk ${IMAGE}.img
+$ (echo n; echo p; echo ; echo 4806656; echo ; echo p; echo w) | fdisk ${IMAGE}.img
 \end{lstlisting}
@@
 \begin{lstlisting}[]
-# DEV=$(losetup --show -f -P ${IMAGE}.img); echo $DEV
+# export DEV=$(sudo losetup --show -f -P ${IMAGE}.img); echo $DEV
 /dev/loop0
@@
 # mount ${DEV}p2 ${ROOTDIR}
-# echo "/dev/mmcblk0p3 /home ext4 defaults,noatime 0 2" >> ${ROOTDIR}/etc/fstab
-# umount ${ROOTDIR}
+# sudo sh -c "echo '/dev/mmcblk0p3 /home ext4 defaults,noatime 0 2' >> ${ROOTDIR}/etc/fstab"
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+The home folder was originally located in the root filesystem. We should
+therefore copy the content to the new home partition:
+\begin{lstlisting}[]
+# mount ${DEV}p3 ${ROOTDIR}/mnt
+# mv ${ROOTDIR}/home/* ${ROOTDIR}/mnt/
+\end{lstlisting}
+\FloatBarrier
+\vspace{-5mm}
+
+That is it. unmount partitions and detach loop device:
+\begin{lstlisting}[]
+# umount --recursive ${ROOTDIR}
 # losetup -d ${DEV}
@@
 
-For us, the device was \texttt{/dev/mmcblk0}, so we write the image to that device:
+For us, the device was \texttt{/dev/mmcblk0}. Write the image to a memory card:
 \begin{lstlisting}[]
-# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M
+# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M && sync
 \end{lstlisting}
@@
 \vspace{-5mm}
+
+The memory card can now be started in a \ac{Raspi}.

### 2016-06-07 cross_compilation.tex
read cross-compilation

@@
 
-Modern \ac{PC}s are significantly better equipped than the \ac{Raspi}s that in
-contrasts to \ac{PC}s target a far more affortable and smaller module size. This
-means that it may be preferred or even mandatory to perform some computational
-expensive tasks in a \ac{PC} rather than in \ac{Raspi}s.
-Example of tasks that are quite computational expensive is to compile software
-packages and large libraries.
-Another reason to use a \ac{PC} may be the hardware limitations of \ac{Raspi}s
-in terms of e.g. memory and disk space. Some software packages might simply be
-too memory demanding to be compiled in a \ac{Raspi}.
-Thus, this section will present how to setup a toolchain in a \ac{PC} that can
-be used to cross compile C++ code to the ARM architecture that the \ac{Raspi}s.
-The toolchain is mandatory on most consumer \ac{PC}s due to the different
-processor architecture.
+Some processing expensive tasks such as compiling code libraries can with
+advantage be performed in a \ac{PC} rather than a \ac{Raspi} to save time.
+This section will present how to setup a toolchain in a \ac{PC} that may
+be used to cross compile C++ code to run in \ac{Raspi}s.
+There will be given an example of compiling a simple C++ application to run
+on \ac{Raspi}, but also how Kodo-cpp can be cross compiled for \ac{Raspi}.
 
-Furthermore, we will cover how to cross compile a simple C++ example and
-Kodo-cpp as well as how the binaries can be copied from a \ac{PC} to a
-\ac{Raspi} and executed.
-There exists bindings to Kodo in various programming language. We will present
-how to also run a Kodo-python application in a \ac{Raspi}.
+%Some tasks can with advantage be performed in \ac{PC} rather than a \ac{Raspi}
+%due to the 
+%
+%Modern \ac{PC}s are significantly better equipped than the \ac{Raspi}s that in
+%contrasts to \ac{PC}s target a far more affortable and smaller module size. This
+%means that it may be preferred or even mandatory to perform some computational
+%expensive tasks in a \ac{PC} rather than in \ac{Raspi}s.
+%Example of tasks that are quite computational expensive is to compile software
+%packages and large libraries.
+%Another reason to use a \ac{PC} may be the hardware limitations of \ac{Raspi}s
+%in terms of e.g. memory and disk space. Some software packages might simply be
+%too memory demanding to be compiled in a \ac{Raspi}.
+%Thus, this section will present how to setup a toolchain in a \ac{PC} that can
+%be used to cross compile C++ code to the ARM architecture that the \ac{Raspi}s.
+%The toolchain is mandatory on most consumer \ac{PC}s due to the different
+%processor architecture.
+%
+%Furthermore, we will cover how to cross compile a simple C++ example and
+%Kodo-cpp as well as how the binaries can be copied from a \ac{PC} to a
+%\ac{Raspi} and executed.
+%There exists bindings to Kodo in various programming language. We will present
+%how to also run a Kodo-python application in a \ac{Raspi}.
 
@@
 
-\subsection{Install toolchain on PC}
+\subsection{Setup toolchain on PC}
 
@@
 
-Kodo is a C++11 library for \ac{NC}. There exists a number of bindings for
-Kodo to other popular programming languages. This procedure will go through
-how to setup Kodo-cpp to cross compile to \ac{Raspi}. Kodo-cpp provides a
-simple interface to the underlying C++11 code that exists in the libraries
-Kodo-core and Kodo-rlnc.
+Kodo is a C++11 network coding library. It is available through bindings in
+a variety of programming languages.
+%There exists a number of bindings for
+%Kodo to other popular programming languages.
+This procedure will present how to configure the Kodo C++ bindings (Kodo-cpp)
+to cross compile applications that can run in \ac{Raspi}. More details are
+provided in the code documentation~\cite{kodocppdoc}.
 
-In order to use Kodo, it is required to obtain a research- and
+%This procedure will go through
+%how to setup Kodo-cpp to cross compile applications that can run in \ac{Raspi}. Kodo-cpp provides a
+%simple interface to the underlying C++11 code that exists in the libraries
+%Kodo-core and Kodo-rlnc.
+
+To use Kodo, it is required to obtain a research- and
 education-friendly license.
-A license can be obtained from \url{http://steinwurf.com/license.html}. It is
-free for research and educational purposes.
+It can be be obtained from~\cite{steinwurflicenselink} and is free
+for research and educational purposes.
 
-A more detailed procedure of setting up Kodo-cpp than provided below is available at
-\url{http://docs.steinwurf.com/kodo/kodo-cpp/index.html}
+%A more detailed procedure of setting up Kodo-cpp than provided below is available at
 
@@
 
-\item Start by creating a directory to hold our code:
+\item Start by creating a directory to hold the code:
 \begin{lstlisting}[]
@@
 
-\item Configure Kodo to build executables for the \ac{ARM} architecture using our toolchain:
+\item Configure Kodo to build executables for the \ac{ARM} architecture using the \ac{Raspi} toolchain:
 \begin{lstlisting}[]
@@
 
-\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation (WHAT IS THE PURPOSE OF THIS SUBSECTION?)}
+\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation \textcolor{red}{(WHAT IS THE PURPOSE OF THIS SUBSECTION?)}}
 
@@
 
-The script functions can be called from the command shell in the following
-manner. Notice how fab automatically searches the directory for a file 
-named 'fabfile.py' and how fab is called with function name and arguments
+The script functions can be called from the shell in the following
+manner. \texttt{Fabric} will automatically search the directory for a file 
+named 'fabfile.py'. The syntax for executing a task and arguments is in the form
 'fab <FUNCTION>:arg1,arg2,...:
@@
 \vspace{-5mm}
+The first function above reboots the \ac{Raspi}s in the lists of hosts, and
+the install function installs a program given by an argument. In the above case,
+\texttt{tmux} is installed.
+%The two functions above reboots the \ac{Raspi}s specified in the list of hosts
+
+Below is a slightly more complicated function call that copies a file from 
+a \ac{PC} to all \ac{Raspi}s in the list of hosts:
 
 \begin{lstlisting}[]
-$ fab reboot
-$ fab install:tmux
 $ fab push:"${CODEDIR}/hello_world",'~/'
@@
 
+\texttt{Fabric} has many other useful functionalities that are useful in
+controlling a bunch of \ac{Raspi}s.
+
 %execute a script function by calling "fab install:feh"
@@
 
-There may be times when it is desired to start a simulation that will
-run for days. For that purpose, it may not be desired to keep
-a \ac{SSH} connection open to the \ac{Raspi} risking that the connection
-will be interrupted and thus result in the \ac{Raspi} terminating
-the running simulation.
+There may be times when a simulation has to run for days in the \ac{Raspi}s.
+For this purpose, it may be inconvenient to keep a \ac{SSH} connection
+open to the \ac{Raspi}s risking that the connection will be interrupted and
+thus leading to the \ac{Raspi} automatically terminating the process.
 
-There exists a few methods to avoid this risk of simulations terminating
-unexpectedly. One method is to run a program within a \texttt{screen} session.
+%There may be times when it is desired to start a simulation that will
+%run for days. For that purpose, it may not be desired to keep
+%a \ac{SSH} connection open to the \ac{Raspi} risking that the connection
+%will be interrupted and thus result in the \ac{Raspi} terminating
+%the running simulation.
 
-\texttt{screen} enables a user to attach and detach the session as it is
-desired. Programs within the screen session just keeps running.
+There exists a few methods to enable the \ac{Raspi}s to continue running
+applications although the connection is terminated either on purpose or
+unexpectedly.
+%There exists a few methods to avoid the risk of simulations terminating
+%unexpectedly.
+One method is to run programs within a \texttt{screen} session.
+\texttt{screen} enables a user to run applications within a \texttt{screen}
+session which never terminates. Users can attach and detach from such a
+session as desired.
+%a session as it is
+%desired. Programs within the screen session just keeps running.
 
-The following procedure will present how to use SSH to
+The following procedure presents how to use \texttt{screen} with \ac{SSH}:
 \begin{enumerate}
@@
 \vspace{-5mm}
-Press space or return to to clear the shell.
+Press space or return to clear the shell.
 
@@
 
-Now that \texttt{top} is running, press Ctrl+a Crtl+d to detach from
+When \texttt{top} is running, press Ctrl+a Crtl+d to detach from
 the \texttt{screen} session.
@@
 
-It can be seen that our session is still running and that we are
-currently not attached. Lets attach to the session:
+It is seen that the session is still running and that no user is currently
+attached to the session. Attach to the session:
 \begin{lstlisting}[]
@@
 After attaching again, \texttt{top} should still be running. \texttt{screen}
-has a few more useful functionalities that is outside the scope of this
+has a few more functionalities that is outside the scope of this
 paper.

### 2016-06-07 cross_compilation.tex
cross-compile update

@@
 a \texttt{hello\_world} c++ example to the \ac{Raspi}'s ARM architecture
-and 2) how to copy and execute the binary in a \ac{Raspi} using \ac{SCP} and \ac{SSH}.
+and 2) how to copy and execute the binary in a \ac{Raspi} using \ac{SCP} and
+\ac{SSH}.
 
@@
 
-\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation \textcolor{red}{(WHAT IS THE PURPOSE OF THIS SUBSECTION?)}}
-
-You can check the build status of Kodo, Fifi and other relevant projects
-through their respective repository master branch on our buildbot page
-\cite{steinwurf2016buildbot}. Our buildbot displays the status of the builds
-for Raspbian 8 and GCC 4.9 for the ARM architecture which is the relevant one
-for the \ac{Raspi}. At the link, you can check build status and build
-statistics. Also, documentation about Kodo basics with a tutorial is available
-at \cite{kododocs}.
+%\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation \textcolor{red}{(WHAT IS THE PURPOSE OF THIS SUBSECTION?)}}
+%
+%You can check the build status of Kodo, Fifi and other relevant projects
+%through their respective repository master branch on our buildbot page
+%\cite{steinwurf2016buildbot}. Our buildbot displays the status of the builds
+%for Raspbian 8 and GCC 4.9 for the ARM architecture which is the relevant one
+%for the \ac{Raspi}. At the link, you can check build status and build
+%statistics. Also, documentation about Kodo basics with a tutorial is available
+%at \cite{kododocs}.
 

### 2016-06-07 introduction.tex
Abstract and Introduction ready

--- 2016-06-04 introduction.tex
@@
-At the beginning, there was darkness and then... bang! \ac{NC}
-\cite{ahlswede2000network} appeared to save us from the evilness
-of routing.
+%!TEX root = raspi_journal.tex
+% At the beginning, there was darkness and then... bang! \ac{NC}
+% \cite{ahlswede2000network} appeared to save us from the evilness
+% of routing.
+%
+% General introduction. Introduction to topic addressed in the journal.
+% Review of the State of the Art. Specify why our approach has benefits
+% and which are they. Indicate contributions.
 
-General introduction. Introduction to topic addressed in the journal.
-Review of the State of the Art. Specify why our approach has benefits
-and which are they. Indicate contributions.
+The emergence of powerful and inexpensive single-board computers
+running full versions of a standard \ac{OS} from many possible in the last
+years opens exciting possibilities for researchers. This not only
+allows to seamlessly develop implementations that are compatible with
+higher end devices and allows the reuse stable software from the Open
+Source community. It also enables the deployment and testing of large
+scale (hundreds of devices or more) distributed systems at a fraction
+of the cost necessary in previous years. This paper focuses on
+providing the critical steps and mechanisms followed to deploy, setup,
+and maintain a large-scale testbed based on Raspberry Pi devices of
+different models. We also complement this with an in-depth evaluation
+of the Raspberry Pi as a platform to enable a new paradigm in
+networking and storage known as \ac{NC}, which relies on
+processing at intermediate nodes to achieve higher throughput, delay
+and reliability performance than state-of-the-art routing techniques.
 
-Our work is organized as follows: Section \ref{sec:testbed} introduces
-the testbed system, its setup, connectivity, files configuration and
-compilation of the Kodo library. Section \ref{sec:schemes} defines the
-coding schemes employed in our study. Later, in Section \ref{sec:metrics}
-we describe the considered metrics for performance comparison of the
-codes deployed in the \ac{Raspi}. In Section \ref{sec:measurements}, we show
-the measurements in the \ac{Raspi} of the mentioned metrics. Final
-conclusions and future work are reviewed in Section \ref{sec:conclusions}.
+% INTRODUCTION TO NETWORK CODING
+Introduced by Ahlswede et al.~\cite{ahlswede2000network}, network
+coding constitutes a paradigm shift in the way how researchers and
+industry understand and operate networks, by changing the role of
+intermediate relays in the process of transmission of information.
+Relays are no longer limited to storing and forwarding data, but also
+take part in the coding process, through a process called recoding,
+where the relay generates new linear combinations of incoming coded
+packets without previously decoding the data. Network coding allows
+the increase of throughput, reliability, security and delay
+performance of the networks.
+
+Compared to other broadly used coding schemes, e.g., Gallager's LDPC
+codes~\cite{gallager1962low} or Reed-Solomon
+codes~\cite{reed1960polynomial}, network coding is a technology that
+has been implemented in real systems since the early years of its
+conception. In 2006, Katabi et al.~\cite{katabi2006practical} published
+the results of the performance of their protocol COPE when implemented
+in a real wireless system, which relied on minimalistic coding to
+provide interesting gains. In 2008, Pedersen et
+al.~\cite{pedersen2008implementation} used commercially available
+Symbian OS enabled mobile phones to implement network coding in a
+\ac{D2D} cooperation-based application. In 2011, researchers at Aalborg
+University developed Kodo~\cite{kodo2011pedersen}, a C++11 network
+coding library with open source code for researchers intended to make
+network coding implementations easily available for both, the research
+community and commercial entities.
+Another case is CATWOMAN~\cite{hundeboll2012catwoman}, a protocol
+implemented on top of the BATMAN protocol~\cite{johnson2008simple} for
+IEEE 802.11 multi-hop meshed networks using some of the intuition from
+COPE, but deploying it in real systems. It is currently available as
+open source code in the Linux kernel. Many other implementations have
+been tested on real world systems~
+\cite{pahlevani2013playncool,katti2008xors,krigslund2013core,paramanathan2013leanandmean}.
+
+Despite this successful deployment in real systems, many of these
+protocols and contributions have been implemented in separate testbeds
+and the experiences are hard to reproduce.  Given the need for
+reproducibility of past and future results among researchers and the
+need of low-cost and easy-to-deploy testbeds, this paper contribution
+is provide detailed instructions on how to set up a low-cost,
+heterogeneous and scalable testbed consisting of Raspberry Pis
+(Raspis), and by providing detailed measurements of goodput and energy
+consumption of such testbed when performing network coding operations
+with different codecs (such as full \ac{RLNC} \cite{ho2006random},
+multicore-enabled \ac{RLNC}, sparse \ac{RLNC} and tunable sparse \ac{RLNC}).
+The heterogeneity of the testbed comes from the fact that old, single core,
+Raspberry Pi 1 model B units are integrated seamlessly in the described
+testbed with newer, multicore versions, like the Raspberry Pi 2 model B.
+Our testbed allows us to obtain a comprehensive set of measurements
+to characterize the goodput and energetic footprint of these devices
+showing that processing speeds of 800 Mbps and energy per bit values
+of 1 nJ or even one order of magnitude less are possible.
+
+Our work is organized as follows. Section~\ref{sec:testbed} introduces the
+testbed system, its setup, files configuration, connectivity and compilation of
+the Kodo library. Section~\ref{sec:schemes} defines the coding schemes employed
+in our study. Later, in Section~\ref{sec:metrics} we describe the considered
+metrics and methodology for performance comparison of the codes deployed in
+the \ac{Raspi}. In Section~\ref{sec:measurements}, we show the measurements in
+the \ac{Raspi} models of the mentioned metrics. Final conclusions and future work
+are reviewed in Section~\ref{sec:conclusions}.
 

### 2016-06-07 raspi_journal.tex
Abstract and Introduction ready

@@
   and ability to replicate results consistently. The latter requires
-  not only the devices to run the same operating system (OS), but also
+  not only the devices to run the same \ac{OS}, but also
   have exactly the same configurations and software packages. This
@@
   performance evaluation for network coding, a new paradigm in
-  networking and storage, and demonstrating the processing
+  networking and storage, and present the processing
   capabilities and energy behaviour of various code constructions and

### 2016-06-07 cross_compilation.tex
Add label for cross_compilation sectio and correct typos

@@
 %\subsection{Kodo cross-compilation: From your PC to the Raspberry Pi}
-
+\label{sec:cross_compilation}
 Some processing expensive tasks such as compiling code libraries can with

### 2016-06-07 introduction.tex
Add label for cross_compilation sectio and correct typos

@@
 Our work is organized as follows. Section~\ref{sec:testbed} introduces the
-testbed system, its setup, files configuration, connectivity and compilation of
-the Kodo library. Section~\ref{sec:schemes} defines the coding schemes employed
-in our study. Later, in Section~\ref{sec:metrics} we describe the considered
-metrics and methodology for performance comparison of the codes deployed in
-the \ac{Raspi}. In Section~\ref{sec:measurements}, we show the measurements in
-the \ac{Raspi} models of the mentioned metrics. Final conclusions and future work
-are reviewed in Section~\ref{sec:conclusions}.
+testbed system, its setup, files configuration and connectivity.
+Section~\ref{sec:cross_compilation} elaborates on the compilation of
+the Kodo library for the \ac{Raspi}. Section~\ref{sec:schemes} defines the
+coding schemes employed in our study. Later, in Section~\ref{sec:metrics}
+we describe the considered metrics and methodology for performance comparison
+of the codes deployed in the \ac{Raspi}. In Section~\ref{sec:measurements}, we
+show the measurements in the \ac{Raspi} models of the mentioned metrics. Final
+conclusions and future work are reviewed in Section~\ref{sec:conclusions}.
 

### 2016-06-07 metrics.tex
Add label for cross_compilation sectio and correct typos

@@
 algorithmic procedures, field operations, hardware processing, multicore
-coordination (where it applies), etc. Moreover, encoding and decoding
-goodput permits to observe if coding is a system-block that limits the
+coordination (where it applies), etc. Moreover, both encoding and decoding
+goodput permit to observe if coding is a system-block that limits the
 end-to-end performance. If a system presents a low goodput, this will
@@
 Furthermore, \ac{Raspi} processors are based in the \ac{ARM} architecture
-which is the same as in mobile devices such as smartphones or tables.
+which is the same as in mobile devices such as smartphones or tablets.
 Thus, the \ac{Raspi} might be used as an experimental tool to get an

### 2016-06-07 testbed.tex
read cross-compilation

@@
 we summarize all the details regarding on setting the connectivity and
-system files for a set of \ac{Raspi}s in a centralized fashion.
-Afterwards, we indicate how to cross-compile the Kodo library in an
-easy way. Finally, we provide further information about Kodo itself in terms
-of testing, other platforms supported and source code documentation
-for further references.
+system files for a set of \ac{Raspi}s in a decentralized fashion.
+Afterwards, we indicate how to cross-compile C++ code and the Kodo
+network coding library in an easy way.
+%Finally, we provide further information about Kodo itself in terms
+%of testing, other platforms supported and source code documentation
+%for further references.
 
@@
 
-When working on a testbed, it is not always desired to make persistant
+When working on a testbed, it is not always desired to make persistent
 changes to the devices. We also present how the concept of stacked
-filesystems can be used to enable the means of both persistant and
+filesystems can be used to enable the means of both persistent and
 temporary storage.
@@
 
-We will be using a \ac{PC} running a Debian-based linux distribution
-to setup a customized Raspbian linux image that can be written to
+We will be using a \ac{PC} running a Debian-based Linux distribution
+to setup a customized Raspbian Linux image that can be written to
 a memory card and work in any \ac{Raspi} version 1 or 2.
@@
 We want to proceed downloading the image with a shell instead of the browser.
-To do this, first open a command window on a linux machine. This guide is
+To do this, first open a command window on a Linux machine. This guide is
 assuming a debian based distribution, but there should only be minor differences
 if you have another package manager. I.e. the application that is used to
-download and install software packages in linux.
+download and install software packages in Linux.
 
@@
 in later steps alter the files and install more packages. It may therefore be
-neccessary to increase the partition size slightly.
+necessary to increase the partition size slightly.
 The following steps will therefore illustrate how image and root filesystem
@@
 and then add it again one \ac{GB} bigger.
-We use fdisk for the task. The echo's within the parenthesis will function as
+We use \texttt{fdisk} for the task. The echo's within the parenthesis
+will function as
 key-presses in \texttt{fdisk} and hence delete last partition, create a new
@@
 The \ac{Raspi}s should be setup to be as similar as possible. One of those
-things that is prefered to be different on the devices is their hostname.
+things that is preferred to be different on the devices is their hostname.
 This helps distinguish them from each other. One solution to this in our
@@
 This is however not desired because that would either require modifying
-the the customized Raspbian lite image before writing the content to the
+the customized Raspbian lite image before writing the content to the
 memory card or to manually change it in the \ac{Raspi}s after the image has
-been written to a meomory card.
+been written to a memory card.
 Instead, we decided to register the ethernet MAC addresses of all the \ac{Raspi}s
@@
 the MAC addresses has to be changed. The MAC address of a network card can be found
-using the command "ifconfig" or "ip addr".
+using the command \texttt{"ifconfig"} or \texttt{"ip addr"}.
 
@@
 Line 4 searches line by line for this mac address.
-Line 8-11 assigns the hostname found in "nodes.csv". If the MAC did not exists,
+Line 8-11 assigns the hostname found in \texttt{"nodes.csv"}. If the MAC did not exists,
 then it will keep the default hostname of the system.
@@
 We have packed the files and uploaded them to a webserver. These can be
-retrieved with wget and unziped into the Raspbian lite image that
+retrieved with \texttt{wget} and unzipped into the Raspbian lite image that
 we are customizing:
@@
 install some additional software:
-%Because \ac{Raspi}s are eqipped with an \ac{ARM} processor 
+%Because \ac{Raspi}s are equipped with an \ac{ARM} processor 
 %%it is not as
-%straightforward as performing the task for two linux systems of the same
+%straightforward as performing the task for two Linux systems of the same
 %architecture.
@@
 
-Assuming that you are still chrooted into the Raspbian lite filesystem, we
+Assuming that you are still \texttt{chrooted} into the Raspbian lite filesystem, we
 can setup the overlay filesystem (overlayfs).
@@
 
-Raspbian lite uses a "u-boot" to boot, so it should be made aware of the
-initramfs that we will generate.
+The bootloader should be made aware of the initramfs that we will generate:
+%Raspbian lite uses "u-boot" to boot, so it should be made aware of the
+%initramfs that we will generate.
 

### 2016-06-07 measurements.tex
References updated

@@
 average amount of redundant packets for \ac{RLNC} has proven to be 1.6
-packets after $g$ have been transmitted \textbf{[Include a reference]},
+packets after $g$ have been transmitted \cite{trullols2011exact,zhao2012notes},
 but less than the cases where sparse codes are utilized. Overall, we
@@
 the Gaussian elimination is $\mathcal{O}(g^2)$. A study in
-\textbf{[refence about Achutan's measurements on the Raspi]} indicated
-that this is effectively the case. The reason is that the $g^2$ factor in
-the scaling law for our Gaussian elimination is much higher than the $g^3$
-for $g \geq 512$. \textbf{[Why was the $g^2$ factor greather than the
-$g^3$ factor? Wasn't it due to the amount of of bytes per packet?]}
+\cite{paramanathan2013leanandmean} for \ac{RLNC} speeds in commercial
+devices indicated that this is effectively the case. The reason is that
+the $g^2$ scaling factor in the scaling law for our Gaussian elimination is much
+higher than the $g^3$ scaling for $g < 512$. Particularly, this factor
+relates to the number of field elements in a packet size as mentioned
+in \cite{paramanathan2013leanandmean}.
 
@@
 measured results, including the baseline results, were obtained with
-NEON-enabled code adapted from the Fifi library [\textbf{Fifi reference}].
+NEON-enabled code adapted from the Fifi library \cite{fifi}.
 The \ac{Raspi} 2 has a NEON extension instruction set which provides

### 2016-06-07 metrics.tex
Fixing typo
Final submission version

@@
 In \eqref{eq:goodput}, $B$ and $g$ are the packet and generation size
-as defined previously and both represented the data to be processed. For
+as defined previously and both represent the data to be processed. For
 goodput measurements, we are concerned in quantifying the processing time
@@
 the processing time required for this processing. In the next subsections, we
-define two time bechmarks available in [\textbf{Chres repos here}].
+define two time bechmarks available in \cite{soerensen2016sparse}.
 The purpose of the benchmarks is to quantify the processing time for
@@
 out its battery. For the energy per bit consumption, it indicates how
-much energy is expended to effectively transmit or receive 1 bit of bit
-considering the encoding or decoding respectively.
+much energy is expended to effectively transmit or receive 1 bit of
+information taking into account the encoding or decoding operations
+respectively.
 

### 2016-06-07 raspi_journal.tex
Final submission version

@@
 % Authors, for the paper (add full first names)
-\Author{N\'estor J.
-Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W.
-S{\o}rensen $^{2,\dagger}$, Juan A.
+\Author{Chres W.
+S{\o}rensen $^{1,\dagger}$, N\'estor J.
+Hern\'andez Marcano $^{1,2,\dagger}$*, Juan A.
 Cabrera G.
 $^{3,4}$, Simon Wunderlich $^{3}$, Daniel E.
-Lucani $^{2,\dagger}$ and Frank H.
+Lucani $^{1,\dagger}$ and Frank H.
 P.
@@
 % Authors, for metadata in PDF
-\AuthorNames{Nestor Hernandez, Chres W. Soerensen, Juan Cabrera, Simon Wunderlich, Daniel E. Lucani and Frank H. P. Fitzek}
+\AuthorNames{Chres W. Soerensen, Nestor J. Hernandez M., Juan Cabrera, Simon Wunderlich, Daniel E. Lucani and Frank H. P. Fitzek}
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
 \address{%
-$^{1}$ \quad Steinwurf ApS. Aalborg, Denmark; nestor@steinwurf.com\\
-$^{2}$ \quad Aalborg University, Department of Electronic Systems. Aalborg, Denmark; \{nh, cws, del\}@es.aau.dk\\
+$^{1}$ \quad Aalborg University, Department of Electronic Systems. Aalborg, Denmark; \{nh, cws, del\}@es.aau.dk\\
+$^{2}$ \quad Steinwurf ApS. Aalborg, Denmark; nestor@steinwurf.com\\
 $^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks. Dresden, Germany; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de\\

### 2016-06-07 testbed.tex
Final submission version

@@
 The testbed consists of thirty \ac{Raspi}s that will be setup and controlled
-by a testbed administrator from a \ac{PC}.
-%Twenty \ac{Raspi} 1 model B revision 2 and ten \ac{Raspi} 2 model B V1.1.
-The \ac{Raspi}s are each equipped with a memory card and connected to the
-university network by wire using their ethernet interface (eth0).
-
-To easily discover the \ac{Raspi}s within the university network,
+by a testbed administrator from a \ac{PC}. The \ac{Raspi}s are each equipped
+with a memory card and connected to the
+university network by wire using their ethernet interface (eth0). To easily
+discover the \ac{Raspi}s within the university network,
 they have all been assigned a unique name under a common domain.
 This eliminates the need to remember their individual \ac{IP} addresses.
-
 A sketch of the testbed is depicted in Figure~\ref{fig:testbed_setup}.
@@
       \textbf{Hostname} & \textbf{Model} \\ \hline
-    Rasp00 - Rasp19 & Raspberry Pi 1 model B rev. 2 \\ \hline
-    Rasp20 - Rasp29 & Rasperry Pi 2 model B V1.1 \\ \hline
+    rasp00 - rasp19 & Raspberry Pi 1 model B rev. 2 \\ \hline
+    rasp20 - rasp29 & Rasperry Pi 2 model B V1.1 \\ \hline
   \end{tabular}
@@
 that the \ac{Raspi}s are configured identically, but still allows the
-students to alter the configurations.
-
-When working on a testbed, it is not always desired to make persistent
+students to alter the configurations. When working on a testbed, it is
+not always desired to make persistent
 changes to the devices. We also present how the concept of stacked
@@
 To get started, we first need to install an \ac{OS} on the
-\ac{Raspi}s. We will use Raspbian linux~\cite{raspbian}
-
-We will be using a \ac{PC} running a Debian-based Linux distribution
+\ac{Raspi}s. We will use Raspbian Linux~\cite{raspbian}. We will be
+using a \ac{PC} running a Debian-based Linux distribution
 to setup a customized Raspbian Linux image that can be written to
@@
 
-Raspbian is made available in two bundles. Raspbian and Raspbian lite.
+Raspbian is made available in two bundles: Raspbian and Raspbian lite.
 The difference between the two is that Raspbian contains a pre-installed desktop
 environment, and Raspbian lite is by default only accessible through a 
-command shell. 
-Both Raspbian and Raspbian lite will both by default be remotely
+command shell. Both Raspbian and Raspbian lite will both by default be remotely
 accessible using \ac{SSH}. \ac{SSH} provides the means to remotely
@@
 (apt-get) in case a desktop environment will be desired sometime in the future.
-
 Below is the procedure we did to setup the \ac{Raspi}s in our testbed. We
@@
     \item Download Raspbian lite
-    \item Alter Raspbian lite. E.g. browse, modify, add, and delete files
+    \item Alter Raspbian lite. e.g. browse, modify, add, and delete files
         in the official Raspbian lite image
-    \item Change root. I.e. change root filesystem into the Raspbian lite
+    \item Change root, i.e. change root filesystem into the Raspbian lite
         image to update and install software packages
@@
 
-Hashmark (\#) and dollar (\$) will be used throughout the procedure
-to indicate if an operation should be run with root permissions or
-user permissions.
+In the following, the hashmark (\#) and dollar (\$) signs will be used
+throughout the procedure to indicate if an operation should be run with
+root permissions or user permissions.
 %\textbf{hashmark (\#) means to perform operation as root, dollar (\$) means
@@
 Notice that the extension has been omitted. This is because the image has been
-packed into a zip file.
-The other variable we declare is a working directory. This is where we will
-download the image to and work on it. In other words, it will be stored in
-/home/<username>/Raspbian
+packed into a zip file. The other variable we declare is a working directory.
+This is where we will download the image to and work on it. In other words, it
+will be stored in \texttt{/home/<username>/Raspbian}
 

### 2016-06-08 schemes.tex
small agreed changes to the multicore section

@@
 
-The idea of the implemented algorithm is to represent each one of the
-sub-block matrix operations: matrix-matrix multiplication,
-matrix-triangle matrix multiplication, triangle-matrix system solving,
-etc; as a base or \textit{kernel} operation that can be optimized
-individually using \ac{SIMD} operations. Each kernel operation, at the
-same time, can be represented as a task with inputs and outputs in memory.
-If an algorithm is formulated conventionally and the data operations on the
-sub-blocks are reordered, then it is possible to resolve data
-dependencies with a \ac{DAG}. For the algorithm, as an example, a dependency
-could be that a sub-block of the matrix in memory cannot be read unless
-a previous writing operation was performed there. When the
-\ac{DAG} is determined, then a scheduler assigns to the available cores the
-execution of the kernel operations that have their dependencies satisfied.
-The benefit of this method is that the synchronization relies only on
-data dependencies and it does not require the insertion of artificial
-synchronization points. Using this technique, the matrix inversion is
-performed using an algorithm based on LU factorization
+The idea of the implemented algorithm is to represent each one of the sub-block
+matrix operations: matrix-matrix multiplication, matrix-triangle matrix
+multiplication, triangle-matrix system solving, etc; as a base or
+\textit{kernel} operation that can be optimized individually using \ac{SIMD}
+operations. Each kernel operation, at the same time, can be represented as a
+task with inputs and outputs in memory that can be assigned to the cores as soon
+as the dependencies are satisfied. The benefit of this method is that the
+synchronization relies only on data dependencies and it does not require the
+insertion of artificial synchronization points. Using this technique, the matrix
+inversion is performed using an algorithm based on LU factorization
 \cite{Dongarra:2011:HPM:2132876.2132885}, and the matrix multiplication is
-performed by making the various matrix-matrix multiplications on the
-sub-blocks.
+performed by making the various matrix-matrix multiplications on the sub-blocks.

### 2016-06-12 debian_usb/write_debian_usb.sh
Remove testbed files

@@ -1,62 +1,0 @@
-#!/usr/bin/env bash
-# A script to download and install debian live cd to a usb pen
-
-echo "change this to arch bootstrap image instead"
-echo "See yaourt install script for how to install from AUR"
-exit 0
-
-dev="$1"  # E.g. /dev/sdb
-IMAGE="debian-live-8.4.0-amd64-standard"
-
-
-# Make sure the script can only be run as root or with sudo
-if [ "$(id -u)" != "0" ]; then
-   echo "This script must be run as root" 1>&2
-   exit 1
-fi
-
-# Check that user specified an input argument
-if [ "$#" != "1" ]; then
-    echo "Please specify device to setup. E.g. /dev/sdb"
-    echo "$0 <device>"
-    exit 1
-fi
-
-# Check if device is a block device
-if [ ! -b $dev ]; then
-    echo "$dev is not a block device"
-    exit 1
-fi
-
-# Make sure that the device is not mounted
-if grep "${dev}" /etc/mtab > /dev/null 2>&1; then
-    echo "Please unmount target device $dev and run the script again"
-fi
-
-# Download live cd image
-#wget http://cdimage.debian.org/debian-cd/current-live/amd64/iso-hybrid/${IMAGE}.iso
-
-echo "Writing ${IMAGE}.iso to $dev"
-#dd if=${IMAGE}.iso of=$dev bs=4M && sync
-
-# Mount image
-loopdevice=$(losetup --show -f -P ${IMAGE}.iso)
-echo "Mounted ${IMAGE}.iso to loop device $loopdevice"
-
-# Mount image to temp directory
-rootdir=$(/bin/mktemp -d)
-mount -o rw ${loopdevice}p1 $rootdir
-echo "Mounted ${loopdevice}p1 to temporary directory $rootdir"
-
-
-
-
-# Unmount root device
-if grep "${rootdir}" /etc/mtab > /dev/null 2>&1; then
-    umount --recursive $rootdir
-fi
-
-# Unmount loopdevice
-if grep "${loopdevice}" /etc/mtab > /dev/null 2>&1; then
-    losetup -d $loopdevice
-fi

### 2016-06-12 upload_rasp_config.sh

@@ -1,5 +1,0 @@
-#!/usr/bin/env bash
-
-zip -r rasp_config rasp_config
-scp rasp_config.zip js3:/afs/ies.auc.dk/project/TuneSCode/public_html/raspi/
-rm rasp_config.zip

### 2016-06-12 raspi_journal.tex
Updating metainfo and paper description
Removing redundant sections

--- 2016-06-07 raspi_journal.tex
@@
 % Full title of the paper (Capitalized)
-\Title{Easy as Pi: A Network Coding Raspberry Pi Testbed}
+\Title{Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in
+the Raspberry Pi Testbed}
 
@@
 % Authors, for metadata in PDF
-\AuthorNames{Nestor Hernandez, Chres W. Soerensen, Juan Cabrera, Simon Wunderlich, Daniel E. Lucani and Frank H. P. Fitzek}
+\AuthorNames{Chres W. Soerensen, Nestor J. Hernandez M., Juan Cabrera, Simon Wunderlich, Daniel E. Lucani and Frank H. P. Fitzek}
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
@@
 
-\section{Testbed Description}
-\input{testbed}
+% \section{Testbed Description}
+% \input{testbed}
 
-\section{Cross-compilation: From PC to Raspberry Pi}
-\input{cross_compilation}
+% \section{Cross-compilation: From PC to Raspberry Pi}
+% \input{cross_compilation}
 

### 2016-06-27 measurements.tex
Rewrittem multicore results based on new measurements

@@
 
-To review the performance of \ac{NC} in a multicore using the \ac{Raspi},
-the authors implemented the algorithm described in
-Section~\ref{sub:implementation-multicore} on the \ac{Raspi} 2 model,
-which features four ARMv7 cores in a Broadcom BCM2836 \ac{SOC}
-with a 900 MHz clock. Each core has a 32 KiB L1 data cache and 32 KiB
-L1 instruction cache. The cores share a 512 KiB L2 cache. All the
-measured results, including the baseline results, were obtained with
-NEON-enabled code adapted from the Fifi library \cite{fifi}.
-The \ac{Raspi} 2 has a NEON extension instruction set which provides
-an 128-bit \ac{SIMD} instructions that speed the computations.
-Figures~\ref{enc_dec1024}, \ref{enc_dec128} and
-\ref{enc_dec16} show the encoding and decoding goodput in MB per
-second for different generation sizes, $g = [1024, 128, 16]$
-respectively. The size of each coded packet was fixed to $1536$~bytes
-since that is the typical size of an Ethernet frame. The blocked operations
-were performed dividing the matrices in squared sub-blocks of
-$16,\ 32\ ,\ 64,\ldots,\ 1024$ operands (words in the Galois field) in
-height and width. The figures show only block sizes of
-$16 \times 16$, $32 \times 32$, $64 \times 64$ operands since with bigger
-block sizes, the operands do not fit in L1 cache. Several testcases
-are considered and detailed.
+To review the performance of \ac{NC} in a multicore architecture using the
+\ac{Raspi}, the authors implemented the algorithm described in
+Section~\ref{sub:implementation-multicore} on the \ac{Raspi} 2 model B, which
+features four ARMv7 cores in a Broadcom BCM2836 \ac{SOC} with a 900 MHz clock.
+Each core has a 32 KiB L1 data cache and 32 KiB L1 instruction cache. The cores
+share a 512 KiB L2 cache. All the measured results, including the baseline
+results, were obtained with NEON-enabled code adapted from the Fifi library
+\cite{fifi}. The \ac{Raspi} 2 has a NEON extension instruction set which
+provides an 128-bit \ac{SIMD} instructions that speed the computations.
+Figures~\ref{enc_dec1024}, \ref{enc_dec128} and \ref{enc_dec16} show the
+encoding and decoding goodput in MB per second for different generation sizes,
+$g = [1024, 128, 16]$ respectively.
+For $g = [128, 16]$, the displayed results are the mean values over 1000 measurements, while for $g=1024$, they are mean values over 100 measurements.
+The size of each coded packet was fixed to
+$1536$~bytes since that is the typical size of an Ethernet frame. The blocked
+operations were performed dividing the matrices in squared sub-blocks of $16,\
+32\ ,\ 64,\ldots,\ 1024$ operands (words in the Galois field) in height and
+width. The figures show only block sizes of $16 \times 16$, and $128 \times 128$
+operands since with bigger block sizes, the operands do not fit in cache.
+Several testcases are considered and detailed.
 
 \subsubsection{Baseline encoding}
-The baseline results involve no recording of the
-\ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder uses
-only one thread. The difference between the non-blocked and blocked
-encoding schemes is that in the blocked scheme, the matrix multiplications are
-performed dividing the matrices in sub-blocks in order to make the algorithm
-cache efficient as described in Section~\ref{sub:implementation-multicore}.
+The baseline results involve no recording of the \ac{DAG} and are performed in a
+\emph{by-the-book} fashion. The encoder uses only one thread. The difference
+between the non-blocked and blocked encoding schemes is that in the blocked
+scheme, the matrix multiplications are performed dividing the matrices in
+sub-blocks in order to make the algorithm cache efficient as described in
+Section~\ref{sub:implementation-multicore}.
 
 \subsubsection{Encoding blocked}
-The encoding results are obtained using the
-method described in Section~\ref{sub:implementation-multicore}. The time
-recorded includes the dependencies resolving, creation of the \ac{DAG},
-and the taskz scheduling. In practice, it would suffice to calculate and
-store this information only once per generation size.
+The encoding results are obtained using the method described in
+Section~\ref{sub:implementation-multicore}. The time recorded includes the
+dependencies resolving, creation of the \ac{DAG}, and the task scheduling. In
+practice, it would suffice to calculate and store this information only once per
+generation size.
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_1024.pdf}
-\caption{Encoding and Decoding performance for $g = 1024$. Block size: $32 \times 32$. \cite{wunderlich2015network}}
+% \includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_1024.pdf}
+\includegraphics[width=0.7\textwidth]{images/GenSize_1024_SymbolSize_1536.eps}
+\caption{Encoding and Decoding performance for $g = 1024$. Block size: $128 \times 128$.}
 \label{enc_dec1024}
@@
 variant. This means that making the matrix multiplication algorithm cache
-efficient brings an increase in goodput by a factor of 2.83. When using the
-algorithm described in Section~\ref{sub:implementation-multicore},
-encoding with four cores is on average $3.7\times$ faster than with one core.
-Similarly, decoding with four codes is $3.05\times$ faster, on average, than
-decoding with a single core. Figure~\ref{enc_dec1024} shows that the
-implemented algorithm, by exploiting cache efficiency and only three extra
-cores provides a $10\times$ gain compared with traditional non-blocked
-algorithms. With $g = 1024$, the matrix inversion becomes more expensive
-than at smaller generations sizes. Therefore, the decoding goodput
-is 46\% of the encoding goodput.
+efficient brings an increase in goodput by a factor of 3.24. When using the
+algorithm described in Section~\ref{sub:implementation-multicore}, encoding with
+four cores is on average $3.9\times$ faster than with one core. Similarly,
+decoding with four codes is $3.9\times$ faster, on average, than decoding with
+a single core. Figure~\ref{enc_dec1024} shows that the implemented algorithm, by
+exploiting cache efficiency and only three extra cores provides a $13\times$
+gain compared with traditional non-blocked algorithms. With $g = 1024$, the
+matrix inversion becomes more expensive than at smaller generations sizes.
+Therefore, the decoding goodput is 58\% of the encoding goodput.
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_128.pdf}
-\caption{Encoding and Decoding performance for $g = 128$. Block size: $64 \times 64$ \cite{wunderlich2015network}}
+\includegraphics[width=0.7\textwidth]{images/GenSize_128_SymbolSize_1536.eps}
+\caption{Encoding and Decoding performance for $g = 128$. Block size: $128 \times 128$}
 \label{enc_dec128}
@@
 For $g = 128$, the differences between the baselines operations show that a
-blocked algorithm is 15\% faster than the non-blocked variant. Encoding with
-four cores is $2.82\times$ faster than with a single core. Due to the smaller
+blocked algorithm is 8\% faster than the non-blocked variant. Encoding with
+four cores is $2.89\times$ faster than with a single core. Due to the smaller
 matrix sizes, the gain when using blocked operations in the baselines is not
 that significant when compared with $g = 1024$. For the same reason, the matrix
-inversion is less expensive. As a consequence, the decoding goodput is 71\%
+inversion is less expensive. As a consequence, the decoding goodput is 46\%
 of the encoding goodput.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_16.pdf}
-\caption{Encoding and Decoding performance for $g = 16$. Block size: $16 \times 16$ \cite{wunderlich2015network}}
+\includegraphics[width=0.7\textwidth]{images/GenSize_16_SymbolSize_1536.eps}
+\caption{Encoding and Decoding performance for $g = 16$. Block size: $16 \times 16$}
 \label{enc_dec16}
@@
 fits in the L1 cache. For the scheduled version, since the problem to solve
-is so small, the gain when using four cores is a factor of 1.68 compared
-with a single core, and 1.01 compared with two cores. Therefore, there
-are no practical benefits in using four cores instead of two.
+is so small, the gain when using four cores is a factor of 2.45 compared
+with a single core, and 1.46 compared with two cores. Therefore, the
+practical benefits in using four cores instead of two are reduced.
 
@@
 effects are negligible for big generation sizes, while considerable for
-small matrices.
+small matrices. For instance, Figure~\ref{enc_dec16} shows that the encoding
+speed when using one core with the described algorithm is 78\% the encoding
+speed without the recording and calculation of the \ac{DAG}.
 
@@
 
-	16   & 1.703     & 0.345    & 4.9 \\
+	16   & 1.495     & 0.169    & 8.8 \\
 \hline
-	32   & 6.573     & 0.914    & 7.2 \\
+	32   & 5.365     & 0.514    & 10.4 \\
 \hline
-	64   & 21.341    & 3.479    & 6.1 \\
+	64   & 20.573    & 2.024    & 10.1 \\
 \hline
-	128  & 82.326    & 17.411   & 4.7 \\
+	128  & 81.357    & 11.755   & 6.9 \\
 \hline
-	256  & 336.398   & 106.861  & 3.1 \\
+	256  & 326.587   & 75.451  & 4.3 \\
 \hline
-	512  & 1548.750  & 659.469  & 2.3 \\
+	512  & 1354.012  & 540.469  & 2.5 \\
 \hline
-	1024 & 6730.380  & 5166.920 & 1.3 \\
+	1024 & 5965.284  & 4373.329 & 1.3 \\
 \hline

### 2016-06-28 conclusions.tex
New abstract and new conclusions

@@
 \label{sec:conclusions}
-Given the need for low-cost, easy to configure, testbeds that enable
-reproducible results, we provide a in-depth description of Aalborg
-University's \ac{Raspi} testbed and how to guarantee replicable
-results and managing scaling of the system.  We also provide a
-performance evaluation for network coding schemes, focusing on
-processing speed and energy behaviour for two \ac{Raspi} models,
-including algorithms that exploit \ac{SIMD} instructions and multicore
-capabilities of the \ac{Raspi} 2. Our measurements show that
-processing speeds of more than 80 Mbps and 800 Mbps are attainable for
-the \ac{Raspi} model 1 and 2, respectively, for a wide range of
-network coding configurations and maintaining a processing energy
-below 1 nJ/bit (or even an order of magnitude lower) in similar
-configurations. Future work in the use of \ac{Raspi} devices will
-focus on expanding the setup and automation of tasks to run the
-testbed, configure specified network topologies (e.g., with specific
-connectivity or packet loss ratios), reserve the use of these
-sub-networks for running tailored experiments, and opening the use of
-the testbed beyond our team at Aalborg University.
+Given the usefulness of the \ac{Raspi} as a low-complex
+processing node in large-scale networks and network coding
+techniques against state-of-the-art routing, we provide
+a performance evaluation of network coding schemes focusing on
+processing speed and energy consumption for two \ac{Raspi} models.
+The evaluation includes algorithms that exploit both \ac{SIMD}
+instructions and multicore capabilities of the \ac{Raspi} 2. Our
+measurements show that processing speeds of more than 80 Mbps and 800
+Mbps are attainable for the \ac{Raspi} model 1 and 2, respectively,
+for a wide range of network coding configurations and maintaining
+a processing energy below 1 nJ/bit (or even an order of magnitude lower)
+in similar configurations. For the use of multithreading, we quantify
+processing gains ranging from 2$\times$ for $g = 16$ to 13$\times$ for
+$g = 1024$ when employing 4 threads each in a different core. Future
+work in the use of \ac{Raspi} devices will focus on considering: (i)
+the performance of the \ac{Raspi} in scenarios with synthetic packet
+losses, (ii) wireless networks where real packet losses can occur
+and (iii) other topologies such as broadcast or
+cooperative scenario to compare with theoretical results in order to
+evaluate the performance of different network codeswith the \ac{Raspi}.

### 2016-06-28 introduction.tex
Removing redundant sections
Some edits

--- 2016-06-07 introduction.tex
@@
 
-Our work is organized as follows. Section~\ref{sec:testbed} introduces the
-testbed system, its setup, files configuration, connectivity and compilation of
-the Kodo library. Section~\ref{sec:schemes} defines the coding schemes employed
-in our study. Later, in Section~\ref{sec:metrics} we describe the considered
-metrics and methodology for performance comparison of the codes deployed in
-the \ac{Raspi}. In Section~\ref{sec:measurements}, we show the measurements in
-the \ac{Raspi} models of the mentioned metrics. Final conclusions and future work
-are reviewed in Section~\ref{sec:conclusions}.
+Our work is organized as follows. Section~\ref{sec:schemes} defines the
+coding schemes employed in our study. Later, in Section~\ref{sec:metrics}
+we describe the considered metrics and methodology for performance comparison
+of the codes deployed in the \ac{Raspi}. In Section~\ref{sec:measurements}, we
+show the measurements in the \ac{Raspi} models of the mentioned metrics
+providing full discussions about the observed operational regimes. Final
+conclusions and future work are reviewed in Section~\ref{sec:conclusions}.
 

### 2016-06-28 schemes.tex
Some edits

@@
 
-The difference between $b$ and $g$ is equal to the losses in the channel and the
-losses due to linear dependencies. Therefore, in a lossless channel, the budget
-is
+The difference between $b$ and $g$ is equal to the losses in the channel
+and the losses due to linear dependencies. Therefore, in a lossless
+channel, the budget is:
 \begin{equation}\label{eq:budget}
@@
 where $P(i,g,d)$ is the probability of receiving an innovative coded packet
-after receiving $i$ \ac{l.i.} packets with a coding density $d$. In our implementations, we considered the the upper bound for the innovation probability from \cite{feizi2014tunable}, given as
+after receiving $i$ \ac{l.i.} packets with a coding density $d$. In our
+implementations, we considered the lower bound for the innovation probability
+from \cite{feizi2014tunable}, given as:
 \begin{equation}
-    P(i,g,d)\geq 1-(1-d)^{g-i}
+    P(i,g,d) \geq 1-(1-d)^{g-i}
 \end{equation}
@@
 \begin{equation}
-b(s(k-1),r(k),g,d) = \sum^{r(k)}_{i=r(k-1)} \frac{1}{P(i,g,d)} = \sum^{r(k)}_{i=r(k-1)} \frac{1}{1-(1-d)^{g-i}} = \frac{b}{2^k}, k\in [1,...).
+b(r(k),r(k+1),g,d) = \sum^{r(k+1)}_{i=r(k)} \frac{1}{P(i,g,d)} = \sum^{r(k+1)}_{i=r(k)} \frac{1}{1-(1-d)^{g-i}} = \frac{b}{2^k},\ k\in [1,\ldots)
 \end{equation}
@@
 The feedback scheme based on the rank reports
-of~\eqref{eq:feedback_dofs} roughly splits the remaining coding
+in~\eqref{eq:feedback_dofs} roughly splits the remaining coding
 regions in two halves. In other words, the first half is the region
@@
 this region, it proceeds with second half where again it splits this
-into to two region and so on until it finishes on transmitting the
+into two new regions and so on, until it finishes the transmission the
 whole generation. This is also the case for the budget that is split
@@
 
-\subsection{Implementation for the Raspberry Pi Multicore Architecture}
+\subsection{Network Coding Implementation for the Raspberry Pi Multicore
+Architecture}
 \label{sub:implementation-multicore}

### 2016-06-28 introduction.tex
Changing introduction...

@@
 
-The emergence of powerful and inexpensive single-board computers
-running full versions of a standard \ac{OS} from many possible in the last
-years opens exciting possibilities for researchers. This not only
-allows to seamlessly develop implementations that are compatible with
-higher end devices and allows the reuse stable software from the Open
-Source community. It also enables the deployment and testing of large
-scale (hundreds of devices or more) distributed systems at a fraction
-of the cost necessary in previous years. This paper focuses on
-providing the critical steps and mechanisms followed to deploy, setup,
-and maintain a large-scale testbed based on Raspberry Pi devices of
-different models. We also complement this with an in-depth evaluation
-of the Raspberry Pi as a platform to enable a new paradigm in
-networking and storage known as \ac{NC}, which relies on
-processing at intermediate nodes to achieve higher throughput, delay
-and reliability performance than state-of-the-art routing techniques.
+% RAW INTRODUCTION: NEED OF DISTRIBUTED NETWORKS AND THE RASPBERRY PI
+Due to the advent of the \ac{IoT}, around 50 million devices
+ranging from sensors to phones are expected to be connected into
+data networks in relatively short period of time \textbf{[REFERENCE]}.
+This massive deployment requires the design and testing of new
+distributed systems that permit to cope with the amount of traffic
+from the proposed services provided by these devices. Therefore,
+development platforms that help to quickly deploy, analyze and
+evaluate this type of settings are highly desirable for research.
+The emergence of a powerful and inexpensive portable computer such
+as the Raspberry Pi running standard \ac{OS} like Linux or even
+Windows allows to achieve this goal since enables the deployment
+of distributed systems at a lower cost than the necessary in
+previous years by using standard protocol. We also complement this
+with an in-depth evaluation of the Raspberry Pi as a platform to
+enable a new paradigm in networking and storage known as \ac{NC},
+which relies on processing at intermediate nodes to achieve
+higher throughput, delay and reliability performance than
+state-of-the-art routing techniques.
 

### 2016-06-28 introduction.tex
Abstract changes

@@
 % RAW INTRODUCTION: NEED OF DISTRIBUTED NETWORKS AND THE RASPBERRY PI
-Due to the advent of the \ac{IoT}, around 50 million devices
-ranging from sensors to phones are expected to be connected into
+Due to the advent of the \ac{IoT}, approximately fifty million devices
+ranging from sensors to phones are expected to be connected through
 data networks in relatively short period of time \textbf{[REFERENCE]}.
@@
 The emergence of a powerful and inexpensive portable computer such
-as the Raspberry Pi running standard \ac{OS} like Linux or even
-Windows allows to achieve this goal since enables the deployment
-of distributed systems at a lower cost than the necessary in
-previous years by using standard protocol. We also complement this
-with an in-depth evaluation of the Raspberry Pi as a platform to
-enable a new paradigm in networking and storage known as \ac{NC},
-which relies on processing at intermediate nodes to achieve
-higher throughput, delay and reliability performance than
-state-of-the-art routing techniques.
+as the Raspberry Pi, running standard \ac{OS} like Linux or Windows,
+allows to achieve this goal since it enables the deployment
+of distributed systems at a low cost. Also, the use of an \ac{OS} that
+has a large user community helps to manage this networks in less time
+\textbf{INCLUDE PRIOR WORK}.
 
 % INTRODUCTION TO NETWORK CODING
-Introduced by Ahlswede et al.~\cite{ahlswede2000network}, network
-coding constitutes a paradigm shift in the way how researchers and
-industry understand and operate networks, by changing the role of
-intermediate relays in the process of transmission of information.
-Relays are no longer limited to storing and forwarding data, but also
-take part in the coding process, through a process called recoding,
-where the relay generates new linear combinations of incoming coded
-packets without previously decoding the data. Network coding allows
-the increase of throughput, reliability, security and delay
-performance of the networks.
+Introduced in~\cite{ahlswede2000network}, \ac{NC}
+constitutes a paradigm shift in the way networks are understood
+by changing how information is sent through them.
+Instead of treating the packets as atomic
+unmodifiable units, packets are seen as algebraic entities in a \ac{GF}
+that can be operated on to create new coded packets. This permits to
+remove the limitation of sending \textit{specific} packets by now sending
+coded packets as \textit{linear equations} of the original ones. This
+change in the way of seeing how the data is represented, brings new
+features that can be exploited. In this way, instead of typically encoding
+and decoding on a hop basis, relaying nodes can take part in the
+coding process without needing to decode. Therefore, a relay can
+\textit{recode} packets, i.e. encode again previously received encoded
+(but not decoded) packets in order to reduce delay and still
+take advantage of the data representation for the next hop.
 
-Compared to other broadly used coding schemes, e.g., Gallager's LDPC
+Compared to other broadly used coding schemes, e.g. \ac{LDPC}
 codes~\cite{gallager1962low} or Reed-Solomon
@@
 has been implemented in real systems since the early years of its
-conception. In 2006, Katabi et al.~\cite{katabi2006practical} published
-the results of the performance of their protocol COPE when implemented
-in a real wireless system, which relied on minimalistic coding to
-provide interesting gains. In 2008, Pedersen et
+conception. Katti et al.~\cite{katti2008xors} showed the
+performance of the COPE protocol for the two-way relay channel
+in a wireless network, which relied on minimalistic coding and obtaining
+gains over a forwarding scheme. Later, Pedersen et
 al.~\cite{pedersen2008implementation} used commercially available
-Symbian OS enabled mobile phones to implement network coding in a
-\ac{D2D} cooperation-based application. In 2011, researchers at Aalborg
+Symbian OS mobile phones to implement network coding in a
+\ac{D2D} cooperation-based application. Furthermore, researchers at Aalborg
 University developed Kodo~\cite{kodo2011pedersen}, a C++11 network
-coding library with open source code for researchers intended to make
-network coding implementations easily available for both, the research
-community and commercial entities.
-Another case is CATWOMAN~\cite{hundeboll2012catwoman}, a protocol
+coding library intended to make network coding functionalities easily
+available for both the research community and commercial entities.
+Based on Kodo is CATWOMAN~\cite{hundeboll2012catwoman}, a protocol
 implemented on top of the BATMAN protocol~\cite{johnson2008simple} for
-IEEE 802.11 multi-hop meshed networks using some of the intuition from
-COPE, but deploying it in real systems. It is currently available as
-open source code in the Linux kernel. Many other implementations have
-been tested on real world systems~
+WiFi multi-hop meshed networks using some of the intuition from
+COPE, but deployed within the X topology with overhearing and
+currently available as open source in the Linux kernel. Many other
+implementations have been tested on real world systems~
 \cite{pahlevani2013playncool,katti2008xors,krigslund2013core,paramanathan2013leanandmean}.
 
-Despite this successful deployment in real systems, many of these
-protocols and contributions have been implemented in separate testbeds
-and the experiences are hard to reproduce.  Given the need for
-reproducibility of past and future results among researchers and the
-need of low-cost and easy-to-deploy testbeds, this paper contribution
-is provide detailed instructions on how to set up a low-cost,
-heterogeneous and scalable testbed consisting of Raspberry Pis
-(Raspis), and by providing detailed measurements of goodput and energy
-consumption of such testbed when performing network coding operations
-with different codecs (such as full \ac{RLNC} \cite{ho2006random},
-multicore-enabled \ac{RLNC}, sparse \ac{RLNC} and tunable sparse \ac{RLNC}).
-The heterogeneity of the testbed comes from the fact that old, single core,
-Raspberry Pi 1 model B units are integrated seamlessly in the described
-testbed with newer, multicore versions, like the Raspberry Pi 2 model B.
-Our testbed allows us to obtain a comprehensive set of measurements
-to characterize the goodput and energetic footprint of these devices
-showing that processing speeds of 800 Mbps and energy per bit values
-of 1 nJ or even one order of magnitude less are possible.
+In this work, we provide detailed measurements of the goodput and energy
+consumption of \ac{Raspi} models 1 and 2, when performing network coding
+operations with different codecs based on \ac{RLNC} \cite{ho2006random}
+such as: full \ac{RLNC}, multicore-enabled \ac{RLNC}, sparse \ac{RLNC}
+and tunable sparse \ac{RLNC}. For this work, we assess the \ac{Raspi}
+performance excluding the channel effect in the processing, meaning that
+we do not consider packet losses or delays in order to have a
+description of the codes in terms of their parameters. To achieve this,
+we perform a measurement campaign with the indicated coding schemes and
+their parameters in our local Raspberry Pi testbed. Our measurements permit
+us to characterize the processing speed (goodput) and energy consumption
+of these devices showing that speeds of 800 Mbps and processing energy per bit
+values of 0.1 nJ are possible.
 
@@
 show the measurements in the \ac{Raspi} models of the mentioned metrics
-providing full discussions about the observed operational regimes. Final
-conclusions and future work are reviewed in Section~\ref{sec:conclusions}.
+providing full discussions about the observed operational regimes and effects.
+Final conclusions and future work are reviewed in
+Section~\ref{sec:conclusions}.
 

### 2016-06-29 introduction.tex
Making corrections..

@@
 % RAW INTRODUCTION: NEED OF DISTRIBUTED NETWORKS AND THE RASPBERRY PI
-Due to the advent of the \ac{IoT}, approximately fifty million devices
+Due to the advent of the \ac{IoT}, approximately fifty billion devices
 ranging from sensors to phones are expected to be connected through
-data networks in relatively short period of time \textbf{[REFERENCE]}.
+data networks in relatively short period of time \cite{cisco2011forecast}.
 This massive deployment requires the design and testing of new
-distributed systems that permit to cope with the amount of traffic
+distributed systems that permit to manage the amount of traffic
 from the proposed services provided by these devices. Therefore,
@@
 The emergence of a powerful and inexpensive portable computer such
-as the Raspberry Pi, running standard \ac{OS} like Linux or Windows,
-allows to achieve this goal since it enables the deployment
-of distributed systems at a low cost. Also, the use of an \ac{OS} that
-has a large user community helps to manage this networks in less time
-\textbf{INCLUDE PRIOR WORK}.
+as the Raspberry Pi, running standard operating systems such as
+Linux or Windows, allows to achieve this goal since it enables the
+deployment of distributed systems in a rapid fashion at a low cost.
+Also, the use of an operating system that has a large user community
+permits to administrative these networks in a flexible, stable and
+supported fashion.
 
@@
 has been implemented in real systems since the early years of its
-conception. Katti et al.~\cite{katti2008xors} showed the
+conception. Authors in~\cite{katti2008xors} showed the
 performance of the COPE protocol for the two-way relay channel
 in a wireless network, which relied on minimalistic coding and obtaining
-gains over a forwarding scheme. Later, Pedersen et
-al.~\cite{pedersen2008implementation} used commercially available
+gains over a forwarding scheme. Later, the work in~\cite{pedersen2008implementation} used commercially available
 Symbian OS mobile phones to implement network coding in a
-\ac{D2D} cooperation-based application. Furthermore, researchers at Aalborg
-University developed Kodo~\cite{kodo2011pedersen}, a C++11 network
-coding library intended to make network coding functionalities easily
-available for both the research community and commercial entities.
-Based on Kodo is CATWOMAN~\cite{hundeboll2012catwoman}, a protocol
-implemented on top of the BATMAN protocol~\cite{johnson2008simple} for
-WiFi multi-hop meshed networks using some of the intuition from
-COPE, but deployed within the X topology with overhearing and
-currently available as open source in the Linux kernel. Many other
-implementations have been tested on real world systems~
-\cite{pahlevani2013playncool,katti2008xors,krigslund2013core,paramanathan2013leanandmean}.
+\ac{D2D} cooperation-based application. Furthermore,
+in~\cite{kodo2011pedersen}, the Kodo library was introduce. Kodo is
+a C++11 network coding library intended to make network coding
+basic functionalities easily available for both the research community
+and commercial entities. Based on Kodo, the CATWOMAN
+protocol~\cite{hundeboll2012catwoman} is implemented on top of the
+BATMAN protocol~\cite{johnson2008simple} for WiFi multi-hop meshed
+networks. It uses some of the intuition from COPE, but it is deployed
+within the X topology with overhearing links. Its source code is available
+as open source in the Linux kernel. Moreover, many other successful
+implementations have been tested on real world systems such as
+found in~\cite{pahlevani2013playncool,krigslund2013core,
+paramanathan2013leanandmean}. For the Raspberry Pi platform, an evaluation
+of the performance of \ac{RLNC} can be found in \cite{paramanathan2014sharing}.
+However, this evaluation focused particularly on observing the achievable
+speeds with \ac{RLNC} \cite{ho2006random} by different configurations of
+the code parameters with a single thread and no hardware acceleration through
+\ac{SIMD}.
 
-In this work, we provide detailed measurements of the goodput and energy
-consumption of \ac{Raspi} models 1 and 2, when performing network coding
-operations with different codecs based on \ac{RLNC} \cite{ho2006random}
-such as: full \ac{RLNC}, multicore-enabled \ac{RLNC}, sparse \ac{RLNC}
-and tunable sparse \ac{RLNC}. For this work, we assess the \ac{Raspi}
-performance excluding the channel effect in the processing, meaning that
-we do not consider packet losses or delays in order to have a
+In this work, we provide detailed measurements of the goodput (processing
+speed) and energy consumption of \ac{Raspi} models 1 and 2, when
+performing network coding operations with different codecs based on \ac{RLNC}
+such as: full dense \ac{RLNC}, multicore-enabled \ac{RLNC}, sparse \ac{RLNC}
+and tunable sparse \ac{RLNC}. For these coding schemes, the encoder and implementations from Kodo now detect and exploit the \ac{SIMD}
+capabilities of the Raspberry Pi. We also assess the \ac{Raspi}
+performance excluding the effect of packet losses or delays in order to have a
 description of the codes in terms of their parameters. To achieve this,
@@
 their parameters in our local Raspberry Pi testbed. Our measurements permit
-us to characterize the processing speed (goodput) and energy consumption
+us to characterize the goodput and energy consumption
 of these devices showing that speeds of 800 Mbps and processing energy per bit
-values of 0.1 nJ are possible.
-
-Our work is organized as follows. Section~\ref{sec:schemes} defines the
+values of 0.1 nJ are possible. Our work is organized as follows.
+Section~\ref{sec:schemes} defines the
 coding schemes employed in our study. Later, in Section~\ref{sec:metrics}

### 2016-06-29 measurements.tex
Rewrittem multicore results based on new measurements
Making corrections..

@@
 Fig. \ref{fig:enc_good_rasp1} shows the results of the encoder goodput
-measurements for the \ac{Raspi} 1. Figs. \ref{fig:enc_good_rasp1_gen_gf2}
+measurements for the \ac{Raspi} 1. Fig. \ref{fig:enc_good_rasp1_gen_gf2}
 and \ref{fig:enc_good_rasp1_gen_gf256} present goodput as function of the
 generation size for $GF(2)$ and $GF(2^8)$ respectively for a packet size
-of $B = 1600$ bytes. Figs. \ref{fig:enc_good_rasp1_packet_gf2} and
+of $B = 1600$ bytes. Fig. \ref{fig:enc_good_rasp1_packet_gf2} and
 \ref{fig:enc_good_rasp1_packet_gf256} present the same metric but now as
@@
 Similarly, Fig. \ref{fig:enc_good_rasp2} shows the same set of
-measurements for the \ac{Raspi} 2. Hence, Figs.
+measurements for the \ac{Raspi} 2. Hence, Fig.
 \ref{fig:enc_good_rasp2_gen_gf2} and \ref{fig:enc_good_rasp2_gen_gf256}
 present goodput as function of the generation size  and
-Figs. \ref{fig:enc_good_rasp2_packet_gf2} and
+Fig. \ref{fig:enc_good_rasp2_packet_gf2} and
 \ref{fig:enc_good_rasp2_packet_gf256} as a function of the packet size
@@
 %
-As it can seen in the from: Figs. \ref{fig:enc_good_rasp1_gen_gf2},
+As it can seen in the from: Fig. \ref{fig:enc_good_rasp1_gen_gf2},
 \ref{fig:enc_good_rasp1_gen_gf256}, \ref{fig:enc_good_rasp2_gen_gf2} and
@@
 
-In the sets of figures shown in Figs.~\ref{fig:enc_good_rasp1} and
+In the sets of figures shown in Fig.~\ref{fig:enc_good_rasp1} and
 \ref{fig:enc_good_rasp2}, it can be observed that the goodput for $GF(2)$
@@
 
-In \ref{fig:enc_good_rasp1_gen_gf2}, \ref{fig:enc_good_rasp1_gen_gf256},
+In Fig.~\ref{fig:enc_good_rasp1_gen_gf2}, \ref{fig:enc_good_rasp1_gen_gf256},
 \ref{fig:enc_good_rasp2_gen_gf2} and \ref{fig:enc_good_rasp2_gen_gf256};
-it can be seen the goodput trends of 5 codes as a function of
+it can be seen the goodput trends of five codes as a function of
 the generation size: \ac{RLNC}, \ac{SRLNC} with $d = [0.02,\ 0.1]$
@@
 
-For Figs.~\ref{fig:enc_good_rasp1_packet_gf2},
+For Fig.~\ref{fig:enc_good_rasp1_packet_gf2},
 \ref{fig:enc_good_rasp1_packet_gf256}, \ref{fig:enc_good_rasp2_packet_gf2}
@@
 size effect in the encoding goodput in both \ac{Raspi} models and for
-a fixed generation size. For \ac{TSNC} in this case, we allow for 5 density
+a fixed generation size. For \ac{TSNC} in this case, we allow for five density
 changes during the generation transmission and again consider the same
@@
 roughly $5\times$ to $7\times$ gains in terms of encoding speed when comparing
-the goodputs in Figs.~\ref{fig:enc_good_rasp1} and \ref{fig:enc_good_rasp2},
+the goodputs in Fig.~\ref{fig:enc_good_rasp1} and \ref{fig:enc_good_rasp2},
 given that it has an \ac{ARM} Cortex A7 (v7) \ac{CPU} and twice the \ac{RAM}
@@
 
-In Figs.\ref{fig:enc_good_rasp2_packet_gf2} and
+In Fig.~\ref{fig:enc_good_rasp2_packet_gf2} and
 \ref{fig:enc_good_rasp2_packet_gf256}, we observe that the packet size for
@@
 
-In Figs.~\ref{fig:dec_good_rasp1} and \ref{fig:dec_good_rasp2}, we
+In Fig.~\ref{fig:dec_good_rasp1} and \ref{fig:dec_good_rasp2}, we
 observe the same generation and packet size effects reported in the
 encoding case. However, we do observe in
-Figs.~\ref{fig:dec_good_rasp1_gen_gf2}, \ref{fig:dec_good_rasp1_gen_gf256},
+Fig.~\ref{fig:dec_good_rasp1_gen_gf2}, \ref{fig:dec_good_rasp1_gen_gf256},
 \ref{fig:dec_good_rasp2_gen_gf2} and \ref{fig:dec_good_rasp2_gen_gf256};
-that duplicating the generation size does not reduce by a factor of 4 the
+that duplicating the generation size does not reduce by a factor of four the
 goodput. In principle, given that Gaussian elimination scales as
@@
 \ref{sec:energy_metrics_methods}, we compute the average power of each
-device from their current consumption across time in
-Figs.~\ref{fig:current_rasp1} and \ref{fig:current_rasp2}. In each
-figure, the eletrical current values are classified into three possible
+device from their elecric current consumption across time in
+Fig.~\ref{fig:current_rasp1} and \ref{fig:current_rasp2}. In each
+figure, the eletric current values are classified into three possible
 currents: Idle, transition and processing. These values are identified by
@@
 through a timestamp. In this way, we relate goodput and power / energy
-measurements. Once identified the current values, we compute the averages
-for each configuration as described in Section
+measurements. Once identified the electric current values, we compute the
+averages for each configuration as described in Section
 \ref{sec:energy_metrics_methods}. In the presented current samples, we observe
@@
         \caption[]%
-        {{\small Current for the \ac{Raspi} 1 model}}
+        {{\small Electric current for the \ac{Raspi} 1 model}}
         \label{fig:current_rasp1}
@@
         \caption[]%
-        {{\small Current for the \ac{Raspi} 2 model}}
+        {{\small Electric current for the \ac{Raspi} 2 model}}
         \label{fig:current_rasp2}
@@
     \caption[]
-    {\small Current consumption for each \ac{Raspi} model}
+    {\small Electric current for each \ac{Raspi} model}
     \label{fig:current_rasp}
@@
 %
-By reviewing the processing current samples in Figs.~\ref{fig:current_rasp1}
+By reviewing the processing current samples in Fig.~\ref{fig:current_rasp1}
 and \ref{fig:current_rasp2}, we observe that the average processing current
 does not change significantly for each \ac{Raspi} model in all the shown
-configurations. Therefore, we approximate the current consumption
+configurations. Therefore, we approximate the electric current consumption
 for the devices and compute the average power as indicated in
@@
 on the amount of packets helping to normalize the results and indicating
-consumption on a fair basis for all the configurations and coding operations
-involved in the study.
+energy consumption on a fair basis for all the configurations and coding
+operations involved in the study.
 
 \subsubsection{Encoding}
-Figs.~\ref{fig:enc_ene_rasp1} and \ref{fig:enc_ene_rasp2} show the encoding
+Fig.~\ref{fig:enc_ene_rasp1} and \ref{fig:enc_ene_rasp2} show the encoding
 energy per bit measurements for the \ac{Raspi} 1 and 2 models, respectively.
@@
 %
-In Figs.~\ref{fig:enc_ene_rasp1_gen_gf2} and \ref{fig:enc_ene_rasp1_gen_gf256},
+In Fig.~\ref{fig:enc_ene_rasp1_gen_gf2} and \ref{fig:enc_ene_rasp1_gen_gf256},
 we see the dependency of the energy per bit processed on the generation size
@@
 
-In Figs.~\ref{fig:enc_ene_rasp1_packet_gf2} and
+In Fig.~\ref{fig:enc_ene_rasp1_packet_gf2} and
 \ref{fig:enc_ene_rasp1_packet_gf256} for the same device. We exhibit the
@@
 %
-In Figs.~\ref{fig:enc_ene_rasp2_gen_gf2}, \ref{fig:enc_ene_rasp2_gen_gf256},
+In Fig.~\ref{fig:enc_ene_rasp2_gen_gf2}, \ref{fig:enc_ene_rasp2_gen_gf256},
 \ref{fig:enc_ene_rasp2_packet_gf2} and \ref{fig:enc_ene_rasp2_packet_gf256}
@@
 \subsubsection{Decoding}
-In Figs.~\ref{fig:dec_ene_rasp1_gen_gf2}, \ref{fig:dec_ene_rasp1_gen_gf256},
+In Fig.~\ref{fig:dec_ene_rasp1_gen_gf2}, \ref{fig:dec_ene_rasp1_gen_gf256},
 \ref{fig:dec_ene_rasp1_packet_gf2} and \ref{fig:dec_ene_rasp1_packet_gf256}
@@
 %
-Finally, in Figs.~\ref{fig:dec_ene_rasp2_gen_gf2},
+Finally, in Fig.~\ref{fig:dec_ene_rasp2_gen_gf2},
 \ref{fig:dec_ene_rasp2_gen_gf256}, \ref{fig:dec_ene_rasp2_packet_gf2}
@@
 provides an 128-bit \ac{SIMD} instructions that speed the computations.
-Figures~\ref{enc_dec1024}, \ref{enc_dec128} and \ref{enc_dec16} show the
+Fig.~\ref{enc_dec1024}, \ref{enc_dec128} and \ref{enc_dec16} show the
 encoding and decoding goodput in MB per second for different generation sizes,
-$g = [1024, 128, 16]$ respectively.
-For $g = [128, 16]$, the displayed results are the mean values over 1000 measurements, while for $g=1024$, they are mean values over 100 measurements.
-The size of each coded packet was fixed to
+$g = [1024, 128, 16]$ respectively. For $g = [128, 16]$, the displayed results
+are the mean values over 1000 measurements, while for $g=1024$, they are mean
+values over 100 measurements. The size of each coded packet was fixed to
 $1536$~bytes since that is the typical size of an Ethernet frame. The blocked
@@
 decoding with four codes is $3.9\times$ faster, on average, than decoding with
-a single core. Figure~\ref{enc_dec1024} shows that the implemented algorithm, by
+a single core. Fig.~\ref{enc_dec1024} shows that the implemented algorithm, by
 exploiting cache efficiency and only three extra cores provides a $13\times$
@@
 effects are negligible for big generation sizes, while considerable for
-small matrices. For instance, Figure~\ref{enc_dec16} shows that the encoding
+small matrices. For instance, Fig.~\ref{enc_dec16} shows that the encoding
 speed when using one core with the described algorithm is 78\% the encoding

### 2016-06-29 metrics.tex
Making corrections..

@@
 \begin{align} \label{eq:goodput}
-R_{proc} = \frac{gB}{T_{proc}} ~ [\mathrm{Bytes/second}]
+R_{proc} = \frac{gB}{T_{proc}} ~ [\mathrm{Byte/second}]
 \end{align}
@@
 is divided in two parts. In the first part, called a \textit{pre-run},
-we quantify the amount of \textit{transmitted} coded packets from an
-encoder (named 1 in Fig. \ref{fig:enc_goodput_benchmark}) required for
+we quantify the amount of \textit{transmitted} coded packets, from
+encoder 1 in Fig. \ref{fig:enc_goodput_benchmark}, required for
 decoding in a single encoder-decoder link with no packet erasures
@@
 In the second part which is the actual \textit{simulation}, a reseted
-encoder (2 in Fig. \ref{fig:enc_goodput_benchmark}) is given the same
+encoder 2 in Fig. \ref{fig:enc_goodput_benchmark} is given the same
 seed as in the pre-run and then we measure the time from which the
@@
 that we want to feed the decoder with the same packets in the same
-order. Later, in the actual simulation, an encoder (2 in Fig.
-\ref{fig:dec_goodput_benchmark}) is given the same packets in the same
-order from the pre-run and then we measure the time from which the
-process start until the decoder finishes to retrieve the original
-packets. Finally, this measurement is saved as the decoder $T_{proc}$
-for this general configuration.
+order. Later, in the actual simulation, a new decoder is given the
+same packets in the same order from the pre-run and then we measure
+the time from which the process starts until the decoder finishes to
+retrieve the original packets. Finally, this measurement is saved as
+the decoder $T_{proc}$ for this general configuration.
 
@@
 out its battery. For the energy per bit consumption, it indicates how
-much energy is expended to effectively transmit or receive 1 bit of
+much energy is expended to effectively transmit or receive one bit of
 information taking into account the encoding or decoding operations
@@
 to estimate the energic expenditure in both of our \ac{Raspi}
-models. The energy measurement setup goal is to quantify the power
+models. The energy measurement setup goal is to quantify the energy
 consumption of the \ac{Raspi} over long periods of processing time to
@@
 the current since the \ac{Raspi} feeds from a fixed input voltage of $5V$
-set by the Agilent device, but its current consumption is variable.
+set by the Agilent device, but its electric current demand is variable.
 Hence, the measured variable is the current consumed by the device for
@@
 \begin{align} \label{eq:avg_current}
-I_{avg} = \frac{1}{N_s}\sum_{k=1}^{N_s} I_{k}  ~[\mathrm{Amperes}]
+I_{avg} = \frac{1}{N_s}\sum_{k=1}^{N_s} I_{k}  ~[\mathrm{Ampere}]
 \end{align}
@@
 \begin{align} \label{eq:avg_power}
-P_{avg} = V_{supply}(I_{proc,avg} - I_{idle,avg}) ~[\mathrm{Watts}]
+P_{avg} = V_{supply}(I_{proc,avg} - I_{idle,avg}) ~[\mathrm{Watt}]
 \end{align}
@@
 To get this metric for a given configuration, we simply express the energy
-as the product of the average power by the processing time $T_{proc} [sec/byte]$
-obtained from the goodput measurement for the same configuration. In this way, we can
-relate the processing time with the goodput, the packet and the generation size
-as shown:
+as the product of the average power by the processing time $T_{proc}
+~[\mathrm{sec/byte}]$ obtained from the goodput measurement for the same
+configuration. In this way, we can relate the processing time with the
+goodput, the packet and the generation size as shown:
 %
 \begin{align} \label{eq:energy_per_bit}
-E_b = P_{avg} T_{proc,bit} = P_{avg} \times \frac{T_{proc}}{8gB} = \frac{P_{avg}}{8R_{proc}} ~[\mathrm{Joules}]
+E_b = P_{avg} T_{proc,bit} = P_{avg} \times \frac{T_{proc}}{8gB} = \frac{P_{avg}}{8R_{proc}} ~[\mathrm{Joule}]
 \end{align}

### 2016-06-30 introduction.tex
Tentative version for submission

@@
 % RAW INTRODUCTION: NEED OF DISTRIBUTED NETWORKS AND THE RASPBERRY PI
-Due to the advent of the \ac{IoT}, approximately fifty billion devices
+Due to the advent of the \ac{IoT}, approximately 50 billion devices
 ranging from sensors to phones are expected to be connected through

### 2016-08-10 schemes.tex
Changing introduction...
minor corrections

@@
 
-In this section, we present a description of the considered coding
-schemes measured with the \ac{Raspi} testbed. We introduce a
+In this section, we present the considered coding schemes that are evaluated
+in the \ac{Raspi} 1 and 2.
+%In this section, we present a description of the considered coding
+%schemes measured with the \ac{Raspi} testbed.
+We introduce a
 definition for the primitive coding operations, e.g. encoding,
@@
 \subsubsection{Encoding}
-In \ac{RLNC}, any coded packet is a linear combination from all
+In \ac{RLNC}, any coded packet is a linear combination of all
 the original packets. For the coding scheme, packets are seen as
@@
 the equivalence  $\textbf{V}$ in its reduced echelon form. The steps
-for reducing the matrix by elementary row operations are carried each time
+for reducing the matrix by elementary row operations are carried out each time
 a \ac{l.i.} packet is received. Once in reduced echelon form, packets
@@
 is able to create new coded packets without needing to decode previously
-received ones from an encoding source. Therefore, \ac{RLNC} is an end-to-end
+received packets from an encoding source. Therefore, \ac{RLNC} is an end-to-end
 coding scheme that permits to \textit{recode} former coded packets at any
@@
 Thus, we define a recoded packet as $R_i$ and consider the coding
-coefficients $w_{i1}, \ldots, w_{ig}$ as the used ones to
+coefficients $w_{i1}, \ldots, w_{ig}$ as used to
 create $R_i$. Later, a recoded packet can be written as:
@@
 the overall processing.  Decoding is the same as in \ac{RLNC}, but
-given that the coding matrices are now sparse, we will have less
-operations performed in the decoding process.  Recoding, although
+given that the coding matrices are now sparse means that there will be less
+operations to perform in the decoding process.  Recoding, although
 theoretically possible, is omitted since it requires the use of
-heuristics keep packets sparse after recoding, which is inherently
-sub-optimal. In what follows, we describe the coding scheme with a
-basic method to produce sparse coded packets and later we indicate a
-second one, giving reference to their implementation performance.
+heuristics to keep packets sparse after recoding, which is inherently
+sub-optimal.
+%In what follows, we describe the coding scheme with a
+%basic method to produce sparse coded packets and later we indicate a
+%second one, giving reference to their implementation performance.
+In what follows, we describe the coding scheme with two
+different methods to produce sparse coded packets.
 
@@
 granularity in the density. Notice that the special case of  $d = 0$ has no
-practical purpose since it implies just zero padded data. So, a practical
-range for the density excludes the zero case, $0 < d \leq 1$. Moreover,
-it can be also observed that the case of $d = 1$ reduces to the \ac{RLNC}
-coding scheme described in Section~\ref{ssec:RLNC}.
+practical purpose since it implies just zero padded data.
+\textcolor{red}{exclude the case d=1 for gf(2) here}
+So, a practical
+range for the density excludes the zero case, $0 < d \leq 1$.
+%Moreover,
+%it can be also observed that the case of $d = 1$ reduces to the \ac{RLNC}
+%coding scheme described in Section~\ref{ssec:RLNC}.
+Moreover, the densities $d=0.5$ in $GF(2)$ and $d=1$ in higher order
+\ac{GF}s is similar to the \ac{RLNC} scheme described in Section~\ref{ssec:RLNC}.
 
@@
 of them, we utilize a set of Bernoulli random variables all with parameter
-$d$ as it success probability, i.e. $\mathbb{B}_j \sim Bernoulli(d)\ ,\ \forall
+$d$ as its success probability, i.e. $\mathbb{B}_j \sim Bernoulli(d)\ ,\ \forall
 j \in [1,g]$. In this way, we can represent a coded packet in \ac{SRLNC} as:
@@
 higher values incur in more frequent \ac{l.d.} coded
-packets~\cite{realworld_nc2013}.
+packets~\cite{realworld_nc2013}.\textcolor{red}{Rather more coding complexity}
 
 Reducing $d$ enables the encoder to decrease the average number of
-packets manipulated to make a coded one. This reduces the complexity
+packets mixed to make a coded one. This reduces the complexity
 of the encoder since it needs to mix less packets. Moreover, it also
@@
 in a fast implementation in terms of execution time for
-$d \geq 0.3$~\cite{practicalview_tsnc2015}. Nevertheless, for $d < 0.3$
-the implementation becomes slow given that more Bernoulli trials are
-required in total for all random variables to generate a coded packet.
-Thus, we introduce a second method that permits a fast implementation
+$d \geq 0.3$~\cite{practicalview_tsnc2015}.
+It is however not able to utilize the full performance potential for
+low densities as the total number of Bernoulli trials remain unchanged
+independently of the density.
+%Nevertheless, for $d < 0.3$
+%the implementation becomes slow given that more Bernoulli trials are
+%required in total for all random variables to generate a coded packet.
+Thus, we introduce a second method that permits a faster implementation
 for low coding densities~\cite{practicalview_tsnc2015}.
@@
     C_i  &= \bigoplus_{m \in \mathcal{K}} v_{im} \otimes P_{m},\ v_{im} \neq 0,\ \forall i \in [1,\ldots)
-    %L \subseteq \{1,\dots,g\}: |L|=k ,\
 \end{align}
-
-% It is often desired to express the coding density as $d=\frac{k}{g}$. We call
-% this notation $k-sparse$ where $k$ is the average number of packets combined to
-% produce a coded packet.
-
-%For low coding density, the encoder might generate a coded packet that consists
-%of no coded packets. I.e. the packet consists of all zeroes
-
-%In \ac{SRLNC}, instead of considering all the packets to create a coded
-%packet like \ac{RLNC} does, here the encoder sets some coding coefficients to
-%zero when creating a new coded packet. This permits to reduce the complexity
-%of both the encoding and decoding operations since the encoder (or decoder)
-%requires less operations to process the data. Therefore, a new code parameter
-%to control the sparsity, the code density $d$, is included to vary the
-%number of non-zero packet that are combined. Here are various approaches to
-%set the density.
-%
-%A first method is to specify the number of zeros in a given
-%generation size and later generate coded packets with this amount. For example:
-%16 zeros in a coding vector of 64 packets where the position of zeros are
-%modified at random for every coded packet generated. Another method is to
-%define an average number of zeros in the coding vector. Therefore, more or
-%less zeros are exactly generated for each coded packet in the process.
-%However, if not carefully made, using a sparse coding scheme might increase
-%the probability of generating \ac{l.d.} packets which incurs both overhead
-%from redundant information and processing delay.
 

### 2016-08-12 metrics.tex
some corrections

@@
 \subsubsection{Encoding Benchmark}
+%Fig. \ref{fig:enc_goodput_benchmark} refers to the benchmark setup
+%made for measuring the encoding processing time of the considered
+%coding schemes given various coding parameters.
 Fig. \ref{fig:enc_goodput_benchmark} refers to the benchmark setup
-made for measuring the encoding processing time. The time benchmark
-is divided in two parts. In the first part, called a \textit{pre-run},
+made for measuring the encoding processing time.
+The time benchmark
+is divided in two parts as a way to exclude the decoding processing
+time from the measurements. In the first part, called a \textit{pre-run},
 we quantify the amount of \textit{transmitted} coded packets, from
 encoder 1 in Fig. \ref{fig:enc_goodput_benchmark}, required for
-decoding in a single encoder-decoder link with no packet erasures
+decoding a generation of packets in a single encoder-decoder link
+with no packet erasures
 for a defined configuration of coding scheme, coding parameters and
 amount of feedback. In the case of \ac{TSNC}, we also record the
-points where a feedback was received from the decoder. The purpose of
-the pre-run is to predict how an encoder should behave with a given
-seed within its random number generator. This part of the benchmark is
-not regarded as a measurement.
+feedback packets received from the decoder. The purpose of
+the pre-run is to observe how an encoder behaves with a given
+seed within its random number generator.
+This part of the benchmark is not measured.
+%This part of the benchmark is not regarded as a measurement.
+%Fig. \ref{fig:enc_goodput_benchmark} refers to the benchmark setup
+%made for measuring the encoding processing time. The time benchmark
+%is divided in two parts. In the first part, called a \textit{pre-run},
+%we quantify the amount of \textit{transmitted} coded packets, from
+%encoder 1 in Fig. \ref{fig:enc_goodput_benchmark}, required for
+%decoding in a single encoder-decoder link with no packet erasures
+%for a defined configuration of coding scheme, coding parameters and
+%amount of feedback. In the case of \ac{TSNC}, we also record the
+%points where a feedback was received from the decoder. The purpose of
+%the pre-run is to predict how an encoder should behave with a given
+%seed within its random number generator. This part of the benchmark is
+%not regarded as a measurement.
 
-In the second part which is the actual \textit{simulation}, a reseted
-encoder 2 in Fig. \ref{fig:enc_goodput_benchmark} is given the same
-seed as in the pre-run and then we measure the time from which the
+The second part is the actual \textit{simulation}. The objective of this
+part is to replicate the pre-run to obtain the encoding speed without
+spending time decoding the packets.
+A reseted encoder 2 in Fig. \ref{fig:enc_goodput_benchmark} is given the
+same seed as in the pre-run and then we measure the time from which the 
 process start until we reach the amount of transmitted packets in the
-pre-run. Then, this measurement is stored as the encoder $T_{proc}$
-for this generic configuration.
+pre-run. The measurement is stored as the encoder $T_{proc}$ for
+this generic configuration. For \ac{TSNC} simulations, the recorded
+feedback packets are injected according to the observations in the pre-run.
+
+%In the second part which is the actual \textit{simulation}, a reseted
+%encoder 2 in Fig. \ref{fig:enc_goodput_benchmark} is given the same
+%seed as in the pre-run and then we measure the time from which the
+%process start until we reach the amount of transmitted packets in the
+%pre-run. Then, this measurement is stored as the encoder $T_{proc}$
+%for this generic configuration.
 
@@
 first calculate the average current in each the idle state $I_{idle,avg}$
-and the processing state $I_{idle,avg}$ for all the available sample for
+and the processing state $I_{proc,avg}$ for all the available sample for
 the given configuration. Regardless of the current type, the average value

### 2016-08-12 schemes.tex
some corrections

@@
 sample a value $n$ from $\mathbb{N}$ and compute $k =
-\max(1,n)$. Later, we create a create a set $\mathcal{K}$ with
+\max(1,n)$. Later, we create a set $\mathcal{K}$ with
 cardinality $k$, e.g. $|\mathcal{K}| = k$, where the elements in
@@
 decoder accomulates more coded packets, the probability that the next
-received coded packet will be \ac{l.d.} increases.
+received coded packet will be \ac{l.d.} increases~\cite{feizi2014tunable}.
+\textcolor{red}{We can cite Feizi2012 here. That is the paper with the markov chain}
 
@@
 coding density for the new region until the next feedback packet is
-received. before the coding density can be estimated, it is essential
-that the encoder has a good estimate of the decoder \ac{dof}, but also
+received. Before the coding density can be estimated, it is essential
+that the encoder has a good estimate of the decoder's \ac{dof}, but also
 the remainder of the total budget. To calculate the density, we use

### 2016-08-14 conclusions.tex
more changes

@@
 cooperative scenario to compare with theoretical results in order to
-evaluate the performance of different network codeswith the \ac{Raspi}.
+evaluate the performance of different network codes with the \ac{Raspi}.

### 2016-08-14 measurements.tex
some corrections
more changes

@@
 
-With the testbed, methodology and setups from the previous sections, we
-proceed to obtain the measurements for the \ac{Raspi} 1 and 2 platforms.
+%With the testbed, methodology and setups from the previous sections, we
+With the methodology and setups from the previous sections, we
+proceed to obtain the measurements for the \ac{Raspi} 1 and 2 devices.
 We consider the following set of parameters for our study:
@@
 for both models is almost the same. Thus, the energy behaviour is mostly
-dependent on the goodput trends since the power is just an scaling constant.
+dependent on the goodput trends since the power is just a scaling constant.
 %
@@
 To review the performance of \ac{NC} in a multicore architecture using the
-\ac{Raspi}, the authors implemented the algorithm described in
+\ac{Raspi}, we implemented the algorithm described in
 Section~\ref{sub:implementation-multicore} on the \ac{Raspi} 2 model B, which
@@
 share a 512 KiB L2 cache. All the measured results, including the baseline
-results, were obtained with NEON-enabled code adapted from the Fifi library
-\cite{fifi}. The \ac{Raspi} 2 has a NEON extension instruction set which
+results, were obtained with
+NEON enabled.
+%NEON-enabled code adapted from the Fifi library \cite{fifi}.
+The \ac{Raspi} 2 has a NEON extension instruction set which
 provides an 128-bit \ac{SIMD} instructions that speed the computations.
-Fig.~\ref{enc_dec1024}, \ref{enc_dec128} and \ref{enc_dec16} show the
+Fig.~\ref{enc_dec1024}, \ref{enc_dec128} and \ref{enc_dec16} shows the
 encoding and decoding goodput in MB per second for different generation sizes,

### 2016-08-14 introduction.tex
Some ideas

@@
 The emergence of a powerful and inexpensive portable computer such
-as the Raspberry Pi, running standard operating systems such as
-Linux or Windows, allows to achieve this goal since it enables the
+as the Raspberry Pi makes this possible by enabling system designers
+to quickly deploy many customizable devices at the same time
+for a low cost.
+
+By running standard operating systems such as
+Linux or Windows, it allows to achieve this goal since it enables the
 deployment of distributed systems in a rapid fashion at a low cost.
@@
 we perform a measurement campaign with the indicated coding schemes and
-their parameters in our local Raspberry Pi testbed. Our measurements permit
+their parameters in the Raspberry Pi platform. Our measurements permit
 us to characterize the goodput and energy consumption

### 2016-08-14 measurements.tex
more corrections

@@
 ,\ 65536,\ 131072]$ bytes with a generation size fixed on $g = [16,\ 128]$
-to see computing load that the \ac{Raspi} present in the low and high
+to see the performance of the \ac{Raspi}s in low and high
 packet size regimes. We considered $B = 1536$ bytes for the optimized
@@
 $d = [0.02,\ 0.1]$. For \ac{TSNC}, we considered excess packets,
-$e = [8,\ 16]$, so that the budget is simply $b = g + e$. In all our
+$e = [8,\ 16]$, so that the budget is $b = g + e$. In all our
 measurement reports, to simplify their review, we first presents the
@@
 measurements for the \ac{Raspi} 1. Fig. \ref{fig:enc_good_rasp1_gen_gf2}
-and \ref{fig:enc_good_rasp1_gen_gf256} present goodput as function of the
+and \ref{fig:enc_good_rasp1_gen_gf256} presents goodput as function of the
 generation size for $GF(2)$ and $GF(2^8)$ respectively for a packet size
@@
 \ref{fig:enc_good_rasp2}, it can be observed that the goodput for $GF(2)$
-is higher than for $GF(2^8)$ but still around the same order of magnitud.
+is higher than for $GF(2^8)$ but still around the same order of magnitude.
 This difference is explained by noticing that \ac{GF} arithmetics in the
 binary field are simply XOR or AND operations. These operations are
-implemented efficiently by most of the architectures nowday and are
+implemented efficiently by most of the architectures nowadays and are
 tailored to be fast in principle. However, the operations in $GF(2^8)$
@@
 \ref{fig:enc_good_rasp2_gen_gf2} and \ref{fig:enc_good_rasp2_gen_gf256};
-it can be seen the goodput trends of five codes as a function of
+it can be seen that the goodput trends of five codes as a function of
 the generation size: \ac{RLNC}, \ac{SRLNC} with $d = [0.02,\ 0.1]$
 and \ac{TSNC} with an extra parameter that we mention. We define
-$C$ as the number of density changes in the \ac{TSNC} transmission
-process, if any. The maximum number of possible changes will depend
-on the budget. The larger the budget, the more regions are formed and
-more density changes are possible. We first evaluate \ac{TSNC} with no
-changes, e.g. $C = 0$ and the two amounts for dependent packets mentioned
-earlier. This means that we tolerate at most 8 or 16 packets regardless of
-the generation. The goal with setting first \ac{TSNC} with these values
-is to observe first the sole effect of the budget in the code since
-$C = 0$ implies no density changes during the whole process.
-
+$C$\fxnote{C is already defined as the set of l.i. coded packets}
+as the number of density regions in the \ac{TSNC} transmission
+process. The maximum number of possible regions depends
+on the generation size. See equation~\eqref{eq:feedback_dofs}.
+The larger the generation, the more density regions may
+be formed and more density changes are possible.
+Throughout this paper, \ac{TSNC} is configured to use the maximum number
+of density regions possible. 
+As there can be at least $C=1$ density region in a transmission, we use
+$C=0$ to indicate the maximum possible density regions. This is
+used for \ac{TSNC} in plots where the generation size is not fixed.
+%In fact, \ac{TSNC} is configured to use the
+%maximum possible density regions in all plots throughout this paper.
+%The larger the generation, the more regions are formed and
+%more density changes are possible.
+%Throughout the section, we evaluate \ac{TSNC} with as many possible
+%density regions that are possible to form during a transmission. This number
+%grows as the generation increases, so we define $C=0$ as the maximum
+%number of possible regions.
+%
+%We first evaluate \ac{TSNC} with no
+%changes, e.g. $C = 0$ and the two amounts for dependent packets mentioned
+%earlier. This means that we tolerate at most 8 or 16\fxnote{dependent packets} packets regardless of
+%the generation. The goal with setting first \ac{TSNC} with these values
+%is to observe first the sole effect of the budget in the code since
+%$C = 0$ implies no density changes during the whole process.
+%
 For the plots in the mentioned figures from the encoder goodput measurements,
@@
 required to create, \ac{RLNC} is the slowest to process since it must
-use all of the $g$ original packets. Later, sparse codes process the data
+use all of the $g$ original packets\fxnote{The encoding process speed depends on the total number of original packets to mix.
+Thus coding density and number of coded packets per generation}.
+Later, sparse codes process the data
 at a larger rate since less packets are being mixed when creating a
@@
 sizes, the data processing does not overload the \ac{CPU} of the
-\ac{Raspi}, so the goodput progressively increases given that we simply
+\ac{Raspi}, so the goodput progressively increases given that we
 process more data as the packet size increases. However, after a certain
@@
 Fig.~\ref{fig:dec_good_rasp1} shows the results of the decoder goodput
-measurements for the \ac{Raspi} 1 and Fig. \ref{fig:dec_good_rasp2} does
-the proper for \ac{Raspi} 2.
+measurements for the \ac{Raspi} 1 and Fig. \ref{fig:dec_good_rasp2} for the \ac{Raspi} 2.
 
@@
 \ref{fig:dec_good_rasp2_gen_gf2} and \ref{fig:dec_good_rasp2_gen_gf256};
-that duplicating the generation size does not reduce by a factor of four the
-goodput. In principle, given that Gaussian elimination scales as
+that duplicating\fxnote{What does duplicating the generation size mean? Did you mean doubling?} the generation size does not reduce the goodput by a
+factor of four. In principle, given that Gaussian elimination scales as
 $\mathcal{O}(g^3)$ (and thus the processing time), we would expect that
-the goodput scales as $\mathcal{O}(R_{proc,dec}) = \mathcal{O}(g/g^{3}) =
-\mathcal{O}(g^{-2})$. This would imply that duplicating the generation
-size, should reduce the goodput by a factor of 4, which does not. Instead,
-the goodput it is only reduced by a factor of 2. This is only possible if
+the goodput to scale as $\mathcal{O}(R_{proc,dec}) = \mathcal{O}(g/g^{3}) =
+\mathcal{O}(g^{-2})$. This would imply that duplicating\fxnote{doubling?} the generation
+size, should reduce the goodput by a factor of four, which is not the case. Instead,
+the goodput is only reduced by a factor of two. This is only possible if
 the Gaussian elimination is $\mathcal{O}(g^2)$. A study in
@@
 devices indicated that this is effectively the case. The reason is that
-the $g^2$ scaling factor in the scaling law for our Gaussian elimination is much
+the $g^2$ scaling factor in the scaling law\fxnote{scaling estimate or scaling expression or something else instead of scaling law} of the Gaussian elimination
+is much
 higher than the $g^3$ scaling for $g < 512$. Particularly, this factor
@@
 Another difference with the encoding goodput results in the same figures,
-is that even though the \ac{TSNC} with $e = 16$ packets provides the fastest
+is that even though \ac{TSNC} with $e = 16$ packets provides the fastest
 encoding, it does not happen to be the same for the decoding. For this
@@
 (particularly in $g = [64,\ 128]$). For other generation sizes, the
-performance of sparse codes is similar.
+performance of sparse codes is similar.\fxnote{This block is incorrect. e=16 is not the fastest encoder nor decoder. e=8 is!}
 %
@@
 the previously mentioned cases as described in \eqref{eq:energy_per_bit}.
-The trends of the energy per bit are simply the inverse of the goodput since
+The trends of the energy per bit are simply\fxnote{The word "simply" should be forbidden} the inverse of the goodput since
 both metrics are related by an inverse law. As made with the goodput, we
@@
 
-To review the performance of \ac{NC} in a multicore architecture using the
-\ac{Raspi}, we implemented the algorithm described in
+To review the performance of \ac{NC} in a multicore architecture,
+%using the \ac{Raspi}
+we implemented the algorithm described in
 Section~\ref{sub:implementation-multicore} on the \ac{Raspi} 2 model B, which
-features four ARMv7 cores in a Broadcom BCM2836 \ac{SOC} with a 900 MHz clock.
+features four ARMv7 cores in a Broadcom BCM2836 \ac{SOC} with a 900 MHz clock.\fxnote{... which features an ARMv7 CPU with four cores in a Broadcom ...}
 Each core has a 32 KiB L1 data cache and 32 KiB L1 instruction cache. The cores

### 2016-08-14 metrics.tex
more corrections

@@
 To extract the average power for a given configuration in our setup, we
-first calculate the average current in each the idle state $I_{idle,avg}$
+first calculate the average current in each\fxnote{each of?} the idle state $I_{idle,avg}$
 and the processing state $I_{proc,avg}$ for all the available sample for
@@
 \subsubsection{Energy per Bit Consumption}
-To get this metric for a given configuration, we simply express the energy
+To get this metric for a given configuration, we express the energy
 as the product of the average power by the processing time $T_{proc}

### 2016-08-15 schemes.tex
more corrections
corrections and density regions estimate script

@@
 the relationship between original and recoded packets. The resulting
-coding matrix is simply the multiplication of matrices $\textbf{W}$ and
+coding matrix is the multiplication of matrices $\textbf{W}$ and
 $\textbf{V}$. Denoting ${(\textbf{W} \textbf{V})}_{ij}$ as the element
@@
 transmission process. The points in the process occur when a decoder
-obtains a given amount of \ac{dof}. In our implementation, we define $r(k),\
-k \in [1, \ldots)$ as the rank $r$ of the decoder\footnote{The rank of
-a decoder is the rank of its coding matrix at a given point in the
-transmissions process.} where a decoder has to send the $k$-th feedback in
+obtains a given amount of \ac{dof}. In our implementation, we define $r(k)$ as the \ac{dof}s of the decoder where it has to send the $k$-th feedback in
 \eqref{eq:feedback_dofs}.
@@
 \begin{equation}\label{eq:feedback_dofs}
-    r(k) = \floor{g\cdot \left[\frac{2^k -1}{2^k}\right]},\ k \in [1,\ldots)
+    r(k) = \floor{g\cdot \left[\frac{2^k -1}{2^k}\right]},\ k \in \Big[1,\ldots,\ceil{log_2(g)}+1\Big]
 \end{equation}

### 2016-08-15 measurements.tex
corrections and density regions estimate script
corrections

@@
 process. The maximum number of possible regions depends
-on the generation size. See equation~\eqref{eq:feedback_dofs}.
+on the generation size. See~\eqref{eq:feedback_dofs}.
 The larger the generation, the more density regions may
@@
 \ref{fig:dec_good_rasp2_gen_gf2} and \ref{fig:dec_good_rasp2_gen_gf256};
-that duplicating\fxnote{What does duplicating the generation size mean? Did you mean doubling?} the generation size does not reduce the goodput by a
+that doubling the generation size does not reduce the goodput by a
 factor of four. In principle, given that Gaussian elimination scales as
@@
 the goodput to scale as $\mathcal{O}(R_{proc,dec}) = \mathcal{O}(g/g^{3}) =
-\mathcal{O}(g^{-2})$. This would imply that duplicating\fxnote{doubling?} the generation
+\mathcal{O}(g^{-2})$. This would imply that doubling the generation
 size, should reduce the goodput by a factor of four, which is not the case. Instead,

### 2016-08-15 metrics.tex
corrections

@@
 To extract the average power for a given configuration in our setup, we
-first calculate the average current in each\fxnote{each of?} the idle state $I_{idle,avg}$
+first calculate the average current in the idle state $I_{idle,avg}$
 and the processing state $I_{proc,avg}$ for all the available sample for

### 2016-08-15 schemes.tex
corrections

@@
 decoder accomulates more coded packets, the probability that the next
-received coded packet will be \ac{l.d.} increases~\cite{feizi2014tunable}.
-\textcolor{red}{We can cite Feizi2012 here. That is the paper with the markov chain}
+received coded packet will be \ac{l.d.} increases~\cite{Feizi2012}.
+%\cite{feizi2014tunable}.
 

### 2016-08-15 measurements.tex
plots from juan
more corrections (removed l.d. and l.i.)

@@
 For all the codes, we use $g = [16,\ 32,\ 64,\ 128,\ 256,\ 512]$
-and $q = [2,\ 2^8]$. For the non-optimized multicore implementations
+and $q = [2,\ 2^8]$. For the single-core implementations
 and cases when the generation size is varied $B = 1600$ bytes.
@@
 $e = [8,\ 16]$, so that the budget is $b = g + e$. In all our
-measurement reports, to simplify their review, we first presents the
+measurement reports, to simplify their review, we first present the
 results for the \ac{Raspi} 1 and later continue with the \ac{Raspi} 2.
@@
 measurements for the \ac{Raspi} 1. Fig. \ref{fig:enc_good_rasp1_gen_gf2}
-and \ref{fig:enc_good_rasp1_gen_gf256} presents goodput as function of the
+and \ref{fig:enc_good_rasp1_gen_gf256} present goodput as function of the
 generation size for $GF(2)$ and $GF(2^8)$ respectively for a packet size
@@
 and \ac{TSNC} with an extra parameter that we mention. We define
-$C$\fxnote{C is already defined as the set of l.i. coded packets}
-as the number of density regions in the \ac{TSNC} transmission
+$C$ as the number of density regions in the \ac{TSNC} transmission
 process. The maximum number of possible regions depends
@@
 \ac{TSNC} with $e = 16$, the highest regardless of the \ac{Raspi} model.
-Given that the processing time depends in the amount of coded packets
+Given that the processing time depends on the amount of coded packets
 required to create, \ac{RLNC} is the slowest to process since it must
-use all of the $g$ original packets\fxnote{The encoding process speed depends on the total number of original packets to mix.
-Thus coding density and number of coded packets per generation}.
+use all of the $g$ original packets
+%\fxnote{The encoding process speed depends on the total number of original packets to mix. Thus coding density and number of coded packets per generation}.
 Later, sparse codes process the data
@@
 coded packet. The caveat of these schemes is that the sparser the code,
-the more probable the ocurrences of \ac{l.d.} packets is. So, basically
-the sparser the codes, then more overhead due to transmissions of \ac{l.d.}
+the more probable the ocurrences of linearly dependent packets is. So, basically
+the sparser the codes, then more overhead due to transmissions of linearly dependent
 packets since it is more frequent to generate similar set of packets.
 Excluding the coding coefficients overhead, the overhead due to
-transmissions of \ac{l.d.} packets might be high for the sparse schemes.
+transmissions of linearly dependent packets might be high for the sparse schemes.
 For example, if we consider \ac{TSNC} with $e = 16$ and $g = 16$
@@
 this permits it to use a single very low code density $d$. For \ac{RLNC},
-this is not the case since the occurrence of \ac{l.d.} coded packets is
+this is not the case since the occurrence of linearly dependent coded packets is
 small, because all coding coefficients are used. Even for $GF(2)$, the
@@
 but less than the cases where sparse codes are utilized. Overall, we
-observe that there is a trade-off between goodput and \ac{l.d.} coded
+observe that there is a trade-off between goodput and linearly dependent coded
 packets transmission overhead.
@@
 devices indicated that this is effectively the case. The reason is that
-the $g^2$ scaling factor in the scaling law\fxnote{scaling estimate or scaling expression or something else instead of scaling law} of the Gaussian elimination
+the $g^2$ scaling factor in the scaling law of the Gaussian elimination
 is much
@@
 encoding, it does not happen to be the same for the decoding. For this
-very sparse scheme, the decoding is affected by the amount of \ac{l.d.}
+very sparse scheme, the decoding is affected by the amount of linearly dependent
 packets generated by, which leads to a higher delay in some cases
 (particularly in $g = [64,\ 128]$). For other generation sizes, the
-performance of sparse codes is similar.\fxnote{This block is incorrect. e=16 is not the fastest encoder nor decoder. e=8 is!}
+performance of sparse codes is similar.
 %
@@
 the previously mentioned cases as described in \eqref{eq:energy_per_bit}.
-The trends of the energy per bit are simply\fxnote{The word "simply" should be forbidden} the inverse of the goodput since
+The trends of the energy per bit are the inverse of the goodput since
 both metrics are related by an inverse law. As made with the goodput, we
@@
 Some differences occurs due to nature of decoding. In this situation,
-the reception of \ac{l.d.} coded packets just increases the decoding
+the reception of linearly dependent coded packets just increases the decoding
 delay, therefore reducing the performance of some coding schemes
@@
 Fig.~\ref{fig:dec_ene_rasp1}. This is a clear scenario where the decoding
-delay is energy-wise susceptible to the transmissions of \ac{l.d.}
+delay is energy-wise susceptible to the transmissions of linearly dependent
 coded packets. With the \ac{Raspi} 1, decoding energies per processed
@@
 Section~\ref{sub:implementation-multicore} on the \ac{Raspi} 2 model B, which
-features four ARMv7 cores in a Broadcom BCM2836 \ac{SOC} with a 900 MHz clock.\fxnote{... which features an ARMv7 CPU with four cores in a Broadcom ...}
+features four ARMv7 cores in a Broadcom BCM2836 \ac{SOC} with a 900 MHz clock.
+%\fxnote{... which features an ARMv7 CPU with four cores in a Broadcom ...}
 Each core has a 32 KiB L1 data cache and 32 KiB L1 instruction cache. The cores
@@
 provides an 128-bit \ac{SIMD} instructions that speed the computations.
-Fig.~\ref{enc_dec1024}, \ref{enc_dec128} and \ref{enc_dec16} shows the
+Fig.~\ref{enc_dec1024}, \ref{enc_dec128} and \ref{enc_dec16} show the
 encoding and decoding goodput in MB per second for different generation sizes,
@@
 % \includegraphics[width=0.7\textwidth]{images/2015-04-18_encoding_decoding_1024.pdf}
-\includegraphics[width=0.7\textwidth]{images/GenSize_1024_SymbolSize_1536.eps}
+%\includegraphics[width=0.7\textwidth]{images/GenSize_1024_SymbolSize_1536.eps}
+\includegraphics[width=0.7\textwidth]{images/GenSize_1024_SymbolSize_1536.pdf}
 \caption{Encoding and Decoding performance for $g = 1024$. Block size: $128 \times 128$.}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{images/GenSize_128_SymbolSize_1536.eps}
+%\includegraphics[width=0.7\textwidth]{images/GenSize_128_SymbolSize_1536.eps}
+\includegraphics[width=0.7\textwidth]{images/GenSize_128_SymbolSize_1536.pdf}
 \caption{Encoding and Decoding performance for $g = 128$. Block size: $128 \times 128$}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{images/GenSize_16_SymbolSize_1536.eps}
+%\includegraphics[width=0.7\textwidth]{images/GenSize_16_SymbolSize_1536.eps}
+\includegraphics[width=0.7\textwidth]{images/GenSize_16_SymbolSize_1536.pdf}
 \caption{Encoding and Decoding performance for $g = 16$. Block size: $16 \times 16$}

### 2016-08-15 metrics.tex
more corrections (removed l.d. and l.i.)

@@
 goodput measurements, we are concerned in quantifying the processing time
-for either encoding or decoding $g$ \ac{l.i.} packets. Thus, $T_{proc}$ is
+for either encoding or decoding $g$ linearly independent packets. Thus, $T_{proc}$ is
 the processing time required for this processing. In the next subsections, we
@@
 goodput benchmarks are carried during the period of time where $I_{proc}$
-occurs. We remark that a simulation is the conveying of $g$ \ac{l.i.} coded
+occurs. We remark that a simulation is the conveying of $g$ linearly independent coded
 packets. Finally, for each configuration, each set of current measurements is

### 2016-08-15 schemes.tex
more corrections (removed l.d. and l.i.)

@@
 number is produced in practice given that a decoder needs only
-$g$ \ac{l.i.} coded packets to decode the batch. Also, in
+$g$ linearly independent coded packets to decode the batch. Also, in
 \eqref{eq:coded_packet}, $v_{ij}$ is the coding coefficient used in the
@@
 \label{sssec:decoding}
-To be able to decode a batch of $g$ packets, a \ac{l.i.} set of $g$
+To be able to decode a batch of $g$ packets, a linearly independent set of $g$
 coded packets, $C_i,\ i \in [1,g]$ is required at a decoder.
@@
 for reducing the matrix by elementary row operations are carried out each time
-a \ac{l.i.} packet is received. Once in reduced echelon form, packets
+a linearly independent packet is received. Once in reduced echelon form, packets
 can be retrieved by doing a substitution starting from the latest
@@
 additional overhead cost for signaling. Similar to the encoding
-operation, any decoder that collects a set of $g$ \ac{l.i.} recoded
+operation, any decoder that collects a set of $g$ linearly independent recoded
 packets with their respective coefficients, will be able to decode the
@@
 $GF(2)$, the maximum plausible density is restricted up to 0.5 since
-higher values incur in more frequent \ac{l.d.} coded
+higher values incur in more frequent linearly dependent coded
 packets~\cite{realworld_nc2013}.\textcolor{red}{Rather more coding complexity}
@@
 The drawback of this scheme is that coded packets from the encoder
-become more \ac{l.d.} on each other as the density is reduced.  This
+become more linearly dependent on each other as the density is reduced.  This
 leads to transmission overhead since another coded packet is required
@@
 decoder accomulates more coded packets, the probability that the next
-received coded packet will be \ac{l.d.} increases~\cite{Feizi2012}.
+received coded packet will be linearly dependent increases~\cite{Feizi2012}.
 %\cite{feizi2014tunable}.
@@
 packets that a decoder has at a given point} increases, e.g., as the
-cardinality of the set of \ac{l.i.} coded packets increases. This enables
+cardinality of the set of linearly independent coded packets increases. This enables
 \ac{TSNC} to significantly reduce the complexity, particularly in the
@@
 for decoding a generation of $g$ packets. In some scenarios, we may set
-$e$ defined as the excess of \ac{l.d.} packets sent from the encoder.
+$e$ defined as the excess of linearly dependent packets sent from the encoder.
 This helps to also define the budget as $b = g + e$.
@@
 where $P(i,g,d)$ is the probability of receiving an innovative coded packet
-after receiving $i$ \ac{l.i.} packets with a coding density $d$. In our
+after receiving $i$ linearly independent packets with a coding density $d$. In our
 implementations, we considered the lower bound for the innovation probability

### 2016-08-15 measurements.tex
more changes

@@
 and cases when the generation size is varied $B = 1600$ bytes.
-We consider a setup where we only vary the packet size,
+We consider another setup where only the packet size varies,
 $B = [64,\ 128,\ 256,\ 512,\ 1024,\ 2048,\ 4096,\ 8192,\ 16384,\ 32768
@@
 to see the performance of the \ac{Raspi}s in low and high
-packet size regimes. We considered $B = 1536$ bytes for the optimized
-multicore implementation. For \ac{SRLNC}, we considered
-$d = [0.02,\ 0.1]$. For \ac{TSNC}, we considered excess packets,
+packet size regimes. The third setup we considered used $B = 1536$ bytes for the optimized
+multicore implementation. 
+%For \ac{SRLNC}, we considered $d = [0.02,\ 0.1]$.
+\ac{SRLNC} was measured with the densities $d = [0.02,\ 0.1]$.
+For \ac{TSNC}, we considered excess packets,
 $e = [8,\ 16]$, so that the budget is $b = g + e$. In all our
@@
 For the goodput, we separate the results according to their time benchmarks
-as we did in Section \ref{sec:metrics} since their consider different
-methodologies. We proceed first with the measurements related to the encoder
+as we did in Section \ref{sec:metrics}.
+%since their consider different methodologies.
+We proceed first with the measurements related to the encoder
 and later review the case of the decoder.
@@
 %
-As it can seen in the from: Fig. \ref{fig:enc_good_rasp1_gen_gf2},
+As it can seen from Fig. \ref{fig:enc_good_rasp1_gen_gf2},
 \ref{fig:enc_good_rasp1_gen_gf256}, \ref{fig:enc_good_rasp2_gen_gf2} and
@@
 it is required to create $g$ coding coefficients and do $g$ multiplications
-for each packet. This makes the goodput to scale as the inverse of the
+for each packet. This makes the goodput scale as the inverse of the
 generation size.
@@
 binary field are simply XOR or AND operations. These operations are
-implemented efficiently by most of the architectures nowadays and are
-tailored to be fast in principle. However, the operations in $GF(2^8)$
+implemented efficiently in nowadays architectures.
+%and are tailored to be fast in principle.
+However, the operations in $GF(2^8)$
 are more complex given that the finite field arithmetics have to be
@@
 process. The maximum number of possible regions depends
-on the generation size. See~\eqref{eq:feedback_dofs}.
+on the generation size~\eqref{eq:feedback_dofs}.
 The larger the generation, the more density regions may
@@
 required to create, \ac{RLNC} is the slowest to process since it must
-use all of the $g$ original packets
+use all of the $g$ original packets.
 %\fxnote{The encoding process speed depends on the total number of original packets to mix. Thus coding density and number of coded packets per generation}.
@@
 the sparser the codes, then more overhead due to transmissions of linearly dependent
-packets since it is more frequent to generate similar set of packets.
+packets.
+%since it is more frequent to generate similar set of packets.
 Excluding the coding coefficients overhead, the overhead due to
@@
 the coding coefficients. This happens because \ac{TSNC}
-has been allowed to add too much redundancy in this case. Given that $C=0$,
-this permits it to use a single very low code density $d$. For \ac{RLNC},
+has been allowed to add too much redundancy in this case.
+%Given that $C=0$, this permits it to use a single very low code density $d$.
+For \ac{RLNC},
 this is not the case since the occurrence of linearly dependent coded packets is
@@
 If we consider the previous effect when reviewing the trends in the
-mentioned figures, in all the models we observe that the maximum is not
+mentioned figures, in all the models, we observe that the maximum coding performance is not
 at 16 KiB but at a smaller value depending on the model, field size
@@
 packet size for \ac{RLNC} using $GF(2)$ occurs at 1 KiB whereas for the
-sparse codes is close to 8 KiB in the most of the cases for $GF(2)$. This
-difference takes place since the sparse codes mix less packets their
-process than \ac{RLNC}, which turns into less data loading in the
+sparse codes is close to 8 KiB in most cases for $GF(2)$. This
+difference takes place since the sparse codes mix less packets
+than \ac{RLNC}, which turns into less data loading in the
 cache for doing computations. For a density of $d = 0.1$, packet size of

### 2016-08-15 schemes.tex
more changes

@@
 practical purpose since it implies just zero padded data.
-\textcolor{red}{exclude the case d=1 for gf(2) here}
+%In $GF(2)$ only, we also eliminate the case of $d = 1$ as it would always
+%produce a coding vector of all ones.
+%In $GF(2)$ only, $d = 1$ causes coding vectors to always be all ones.
+%Furthermore, $d = 1$ in $GF(2)$ leads to coding vectors that are always filled
+%with ones, producing the same coded packet.
+%\textcolor{red}{exclude the case d=1 for gf(2) here}
 So, a practical
 range for the density excludes the zero case, $0 < d \leq 1$.
+%range for the density that we use is $0 < d \leq 1$, and for $GF(2)$ only, $0 < d < 1$.
 %Moreover,
@@
 %coding scheme described in Section~\ref{ssec:RLNC}.
-Moreover, the densities $d=0.5$ in $GF(2)$ and $d=1$ in higher order
-\ac{GF}s is similar to the \ac{RLNC} scheme described in Section~\ref{ssec:RLNC}.
+%
+Furthermore, in $GF(2)$ there is no benefit of using $d > 0.5$ in terms of
+generating linearly independent packets~\cite{realworld_nc2013}. Thus,
+we limit the range to $0 < d \leq 0.5$ in $GF(2)$.
+
+%Moreover, the densities $d=0.5$ in $GF(2)$ and $d=1$ in higher order
+%\ac{GF}s is similar to the \ac{RLNC} scheme described in Section~\ref{ssec:RLNC}.
 

### 2016-08-15 introduction.tex
New introduction almost there

@@
 development platforms that help to quickly deploy, analyze and
-evaluate this type of settings are highly desirable for research.
-The emergence of a powerful and inexpensive portable computer such
-as the Raspberry Pi makes this possible by enabling system designers
-to quickly deploy many customizable devices at the same time
-for a low cost.
+evaluate this type of scenarios are highly desirable for research.
+With the emergence of the \ac{Raspi}, a lrelatively powerful low-cost
+computer with the size of a credit card, these evaluations are becoming
+possible now. This platform has been used as a general purpose hardware
+for \ac{IoT} applications as reported in surveys such as
+\cite{alfuqaha2015iot}. In these applications, the
+\ac{Raspi} might be the sensoring or computing entity (or even both) for
+a required task. To achieve this, it can be extended from being a
+simple computer using self-designed or already available extension modules.
 
-By running standard operating systems such as
-Linux or Windows, it allows to achieve this goal since it enables the
-deployment of distributed systems in a rapid fashion at a low cost.
-Also, the use of an operating system that has a large user community
-permits to administrative these networks in a flexible, stable and
-supported fashion.
+A benefit of using the \ac{Raspi} as development platform is its large
+community of supporters. By running standard operating systems such as
+Linux or Windows, this permits to utilize standard, well tested and
+reliable tools to administrate and maintain these networks in
+a flexible, stable and supported manner which is a major requirement
+to make a scalable deployment. Moreover, by enabling system designers to
+configure and deploy several devices at the same time, possible deployments
+of tens, hundreds or even thousands of Raspberry Pi's would allow to
+analyze representative data patterns of the \ac{IoT}. Different use cases of
+\ac{IoT} applications employing the \ac{Raspi} as a building block can be found
+in the literature. A basic study of the \ac{Raspi} as a possible device
+for sensor applications can be found in \cite{vujovic2014raspberry}.
+Authors in \cite{kruger2015rapid} consider using the \ac{Raspi} as an
+\ac{6LoWPAN} gateway for a set of sensor and mobile devices to an
+\ac{IP} version 6 network. In \cite{mahmoud2016sensorian}, a general
+purpose sensoring platform for \ac{IoT} is presented using the \ac{Raspi}
+as its basic building block.
 

### 2016-08-15 reviewer_reply.txt
review replies

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 
Reviewer 1:
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

Dear reviewer,
Thank you very much for the valuable feedback. We have corrected the indicated typos and several others particularly in section 4. We have also replaced the abbreviations "l.d." and "l.i." to "linearly dependent" and "linearly independent".

FIXME: variable "g" used on page 2 or 3 before it is defined

FIXME: the notation [1,g] (and many other notations) should be changed to
       maybe [1,2,...g]

FIXME: change notation such as $\mathbb{N}$ as this is typically used for positive numbers

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 
Reviewer 2:
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

Dear reviewer,
Thank you very much for the valuable feedback. We have listed your comments below and described what we have changed to hopefully improve the indicated issues.

 - The proposed system is not well described

We have rewritten the parts that indicate a proposed system. All simulations are performed within a single Raspberry Pi. We only replace the traditional power supply with an Agilent to monitor and log the power consumption.

- Finally and in a word, the motivation of this paper is unclear. The main question is “why Raspberry pi in network coding?”. What is the advantage of using Raspberry pi?

We consider the Raspberry Pi 1 and 2 to be good representatives in the field of low budget and internet of things devices in terms of performance and capabilities. The two devices have one and four cores respectively and they support hardware acceleration that is mandatory to reach the full potential of network coding. We have updated the introduction to hopefully elaborate a bit more on why network coding in Raspberry Pi is interesting. Another reason for using the Raspberry Pi is its large user community in contrast to many other low cost devices.

- They only consider q=2 and 28 , however, as it is mentioned in “Chou, Philip A., Yunnan Wu, and Kamal Jain. "Practical network coding." (2003).”, based on security aspect, in practice, wey should consider q=28 and 216. By this assumption, they should show and compare the results with q=216 too.

We have made a reference to two papers by Achuthan et al. ("Lean and Mean" and "Sharing the Pi" that include measurements for both q=2^8 and q=2^16 that indicates a performance degradation of approximately 10x). We also ran some simulations ourself that indicated similar performance gab between the two field types.
The reason that we do not consider q=2^16 is that nobody uses it today. q=2^8 is the standard today and q=2 is beneficial in terms of performance in low performance devices. For security purposes, there exists better ways than using q=2^16.

FIXME: Did we include achuthans papers?
FIXME: Should we argue somewhere the performance of 2^16 and argue why we use the two fields q=2 and q=2^16?

- The list of references neglects some of the most relevant papers. Moreover, the authors have cited to their previous papers (i.e., [6,7,8,10,11,12,13,17,21,27,30])!!! It seems they want to increase citation of their papers!

We link to our prior work as this paper is mostly based on those papers. We have removed reference 10 and 30 and added a few more citations to related work done by others.

FIXME: Did we remove reference 10 and 30?

- The presentation of the paper is not very good. The authors did not care very much about the structure, the language (i.e., page 2 line 42 “Furthermore, in [7], the Kodo library was introduce.” Should be introduced….)

We have corrected the topys mentioned and several others throughout the paper.

FIXME: Did you correct the sentence "... the Kodo library was introduce"?

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 
Reviewer 3:
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

Dear reviewer,
Thank you very much for the valuable feedback. We have corrected the typos as suggested and changed the figures in section 4.4 to show the goodput instead of the throughput.

### 2016-08-15 metrics.tex
review replies

@@
 sensor applications where devices are positioned for measurement retrieval
-without any supervision for large periods fo time.
+without any supervision for large periods of time.
 

### 2016-08-15 schemes.tex
removed fixme

@@
 higher values incur in more frequent linearly dependent coded
-packets~\cite{realworld_nc2013}.\textcolor{red}{Rather more coding complexity}
+packets~\cite{realworld_nc2013} accompanied by higher coding complexity.
+%\textcolor{red}{Rather more coding complexity}
 

### 2016-08-16 measurements.tex
more corrections

@@
 when referring to variable generation sizes and a fixed packet size.
-Furthermore, these costs are 1 order of magnitude less for the \ac{Raspi} 2
+Furthermore, these costs are one order of magnitude less for the \ac{Raspi} 2
 with respect to the \ac{Raspi} 1 regarding the case of a fixed generation
-size and a variable packet size. This makes the \ac{Raspi} 2 to achieve
+size and a variable packet size. This makes the \ac{Raspi} 2 achieve
 a minimum encoding energy consumpiton per bit processed of 0.2 nJ for the
@@
 %
-Some differences occurs due to nature of decoding. In this situation,
+Some differences occurs due to the nature of decoding. In this situation,
 the reception of linearly dependent coded packets just increases the decoding

### 2016-08-16 introduction.tex
Advances in the introduction description

@@
 purpose sensoring platform for \ac{IoT} is presented using the \ac{Raspi}
-as its basic building block.
+as its basic building block. Other interesting \ac{IoT} use cases
+are the works presented in \cite{wirz2015enabling,alletto2016indoor}. In the first
+of these works, many \ac{Raspi}s are used as controllable smart devices
+with network connectivity that may ubiquously interact with different users,
+each represented by a mobile device through a smartphone application.
+The second work considers \ac{Raspi}s as a data processing unit
+for disseminating artwork content in smart museums.
 

### 2016-08-16 schemes.tex

@@
 from a single flow are combined with each other. In this type of
-network coding, all the original data packets $P_j, j \in [1,g]$, each
+%network coding, all the original data packets $P_j, j \in [1,g]$, each
+network coding, $g$ original data packets $P_j, j \in [1,g]$, each
 of $B$ bytes, are used to create coded packets using random linear

### 2016-08-16 reviewer_reply.txt
I do not remember what I did
Removing some remainings

@@
 
-FIXME: variable "g" used on page 2 or 3 before it is defined
+FIXME: Nestor, what do you think about the way I defined "g" on page 3? I believe "g" is first used on page 3 now. Not page 2 anymore as the reviewer stated?
 
@@
 
-We have corrected the topys mentioned and several others throughout the paper.
-
-FIXME: Did you correct the sentence "... the Kodo library was introduce"?
+We have corrected all the mentioned and other found typos by proof-reading the manuscript.
 
@@
 Dear reviewer,
-Thank you very much for the valuable feedback. We have corrected the typos as suggested and changed the figures in section 4.4 to show the goodput instead of the throughput.
+Thank you very much for your valuable feedback. We have corrected all the mentioned and other found
+typos as suggested by proof-reading the manuscript and changed the figures in section 4.4 to show the goodput instead of the throughput by properly labelling the axis and verifying that the shown
+data is correct.

### 2016-08-16 reviewer_reply.txt
The remaining work

@@
 Dear reviewer,
-Thank you very much for the valuable feedback.
-We have corrected the indicated typos and several others particularly in section 4.
-We have also replaced the abbreviations "l.d." and "l.i." to "linearly dependent" and "linearly independent".
+Thank you very much for your valuable feedback. We have corrected all the indicated and other
+found typos by proof-reading the manuscript. We have also replaced the abbreviations "l.d." and
+"l.i." to "linearly dependent" and "linearly independent" as suggested to enhance clarity in the 
+notation.
 
@@
 
+Nestor: Where is this exactly right now? I cannot see it :(
+
 FIXME: the notation [1,g] (and many other notations) should be changed to
        maybe [1,2,...g]
+Nestor: Can you make this modification while I advance in the intro?
 
 FIXME: change notation such as $\mathbb{N}$ as this is typically used for positive numbers
+Nestor: Can you make this modification while I advance in the intro?
 
@@
 
+Nestor: Which were these papers? These numbers have changed already
+
 - The presentation of the paper is not very good.

### 2016-08-16 schemes.tex
changed some [1,g] to [1,2,...,g]

@@
 %network coding, all the original data packets $P_j, j \in [1,g]$, each
-network coding, $g$ original data packets $P_j, j \in [1,g]$, each
+network coding, $g$ original data packets $P_j, j \in [1,2,\ldots,g]$, each
 of $B$ bytes, are used to create coded packets using random linear
@@
 To be able to decode a batch of $g$ packets, a linearly independent set of $g$
-coded packets, $C_i,\ i \in [1,g]$ is required at a decoder.
+coded packets, $C_i,\ i \in [1,2,\ldots,g]$ is required at a decoder.
 Once this set has been collected for a decoder,
@@
 node. Finally, the appended coefficients for $R_i$ are
-${(\textbf{W} \textbf{V})}_{ik}$ with $k \in [1,g]$. By doing some
+${(\textbf{W} \textbf{V})}_{ik}$ with $k \in [1,2,\ldots,g]$. By doing some
 algebra, each ${(\textbf{W} \textbf{V})}_{ij}$ term can be verified to be
@@
 refer to this fixed ratio as the average coding density $d$. Thus, for any
-coded packet $C_i$ with coding coefficients $v_{ij},\ j \in [1,g]$, its
+coded packet $C_i$ with coding coefficients $v_{ij},\ j \in [1,2,\ldots,g]$, its
 coding density is defined as follows:
@@
 $d$ as its success probability, i.e. $\mathbb{B}_j \sim Bernoulli(d)\ ,\ \forall
-j \in [1,g]$. In this way, we can represent a coded packet in \ac{SRLNC} as:
+j \in [1,2,\ldots,g]$. In this way, we can represent a coded packet in \ac{SRLNC} as:
 %

### 2016-08-16 reviewer_reply.txt
removed half a fixme
New introduction

@@
 "l.i." to "linearly dependent" and "linearly independent" as suggested to enhance clarity in the 
-notation.
-
-FIXME: Nestor, what do you think about the way I defined "g" on page 3? I believe "g" is first used on page 3 now. Not page 2 anymore as the reviewer stated?
-
-Nestor: Where is this exactly right now? I cannot see it :(
+notation. Regarding the definition of "g", We have defined the parameter "g" as the total number of original packets to be encoded.
 
@@
 Dear reviewer,
-Thank you very much for the valuable feedback. We have listed your comments below and described what we have changed to hopefully improve the indicated issues.
+Thank you very much for your valuable feedback. We have listed your comments below and described what we have changed to hopefully improve the indicated issues.
 
@@
 
-We have rewritten the parts that indicate a proposed system.
-All simulations are performed within a single Raspberry Pi.
-We only replace the traditional power supply with an Agilent to monitor and log the power consumption.
+We have rewritten the parts that indicate a proposed system. All our measurements are performed within a single Raspberry Pi. We only replace the traditional power supply with an Agilent Power
+Supply device to monitor and log the power consumption.
 
@@
 
-We consider the Raspberry Pi 1 and 2 to be good representatives in the field of low budget and internet of things devices in terms of performance and capabilities.
-The two devices have one and four cores respectively and they support hardware acceleration that is mandatory to reach the full potential of network coding.
-We have updated the introduction to hopefully elaborate a bit more on why network coding in Raspberry Pi is interesting.
+We consider that the Raspberry Pi models 1 and 2 are good representatives of a low-cost computer
+considered as IoT devices in terms of performance and capabilities. We now elaborate on this idea in the introduction by providing various use cases of IoT + Raspi. At the end of the description of
+the use cases of IoT + Raspi, we specifically mention that despite this advances, data is still
+being conveyed in a conventional way that will hit a performance roof with new services demands. This is why we motivate about network coding since it is proven its utility in the area of meshed
+networks where IoT deployments occur.
 Another reason for using the Raspberry Pi is its large user community in contrast to many other low cost devices.
+This allows a system developer to use standard tools and / or based on either Windows or Linux, reducing the development time.
+Finally, the Raspberry Pi models 1 and 2, have one and four cores respectively and they support hardware acceleration through the NEON instruction set in ARM that is mandatory to reach the full potential of network coding where we have included the proper details.
+We have updated the introduction to hopefully elaborate on all these subjects to show why using network coding in Raspberry Pi is interesting.
 
@@
 
-We have made a reference to two papers by Achuthan et al.
-("Lean and Mean" and "Sharing the Pi" that include measurements for both q=2^8 and q=2^16 that indicates a performance degradation of approximately 10x).
-We also ran some simulations ourself that indicated similar performance gab between the two field types.
-The reason that we do not consider q=2^16 is that nobody uses it today.
-q=2^8 is the standard today and q=2 is beneficial in terms of performance in low performance devices.
-For security purposes, there exists better ways than using q=2^16.
-
-FIXME: Did we include achuthans papers?
-FIXME: Should we argue somewhere the performance of 2^16 and argue why we use the two fields q=2 and q=2^16?
+We have made a reference to two papers by Achuthan et al. ("Lean and Mean" and "Sharing the Pi").
+These two references include measurements for both q=2^8 and q=2^16 and indicate a performance degradation of approximately 10x.
+The underlying reason is that using Galois fields higher than 2^8 provide no perceivable benefit in terms of the decoding probability while increasing in complexity.
+At the end, this turns disastrous for the code.
+We also ran a few measurements ourself that
+indicated similar performance gab between the two field types.
+Another reason to not consider q=2^16 is that it is not a standard field size.
+q=2^8 is the standard today and q=2 is beneficial in terms of performance in low-computing power devices.
+For security purposes, there exists even better ways than using q=2^16.
 

### 2016-08-16 introduction.tex
Removing some remainings
New introduction

--- 2016-08-15 introduction.tex
@@
 purpose sensoring platform for \ac{IoT} is presented using the \ac{Raspi}
-as its basic building block.
+as its basic building block. Various interesting \ac{IoT} use cases
+are the works presented in \cite{wirz2015enabling,alletto2016indoor,
+jalali2016fog,ueyama2014exploiting}. In \cite{wirz2015enabling}, many
+\ac{Raspi}s are used as controllable smart devices
+with network connectivity that may ubiquously interact with different users,
+each represented by a mobile device through a smartphone application.
+The study in \cite{alletto2016indoor} considers \ac{Raspi}s as a data
+processing unit for disseminating artwork content in smart museums.
+An \ac{IoT} setting where the \ac{Raspi} is employed as a nano-server
+in distributed storage and computing can be found in \cite{jalali2016fog}.
+Finally, in \cite{ueyama2014exploiting}, the authors present
+the \ac{Raspi} as the processing entity of an unmanned aereal
+vehicle application to increase the resilience of a wireless sensor networks.
+However, even though all these advances in the \ac{IoT} area regarding
+the exploitation of the \ac{Raspi} capabilities, the application data
+is forwarded using former conventional routing methods which may
+not satisfy the need of a distributed network for \ac{IoT}
+applications as mentioned earlier
 
 % INTRODUCTION TO NETWORK CODING
-Introduced in~\cite{ahlswede2000network}, \ac{NC}
-constitutes a paradigm shift in the way networks are understood
-by changing how information is sent through them.
+In this context, introduced in~\cite{ahlswede2000network}, \ac{NC}
+constitutes a paradigm shift in the way data networks are understood
+by changing how information is sent through them and stored at the end devices.
 Instead of treating the packets as atomic
@@
 (but not decoded) packets in order to reduce delay and still
-take advantage of the data representation for the next hop.
+take advantage of the data representation for the next hop. This new type
+of coding across the network is proven to achieve the multicast
+capacity \cite{ahlswede2000network,koetter2003algebraic}.
 
-Compared to other broadly used coding schemes, e.g. \ac{LDPC}
+Compared to other broadly used coding schemes, such as \ac{LDPC}
 codes~\cite{gallager1962low} or Reed-Solomon
@@
 \ac{D2D} cooperation-based application. Furthermore,
-in~\cite{kodo2011pedersen}, the Kodo library was introduce. Kodo is
+in~\cite{kodo2011pedersen}, the Kodo library was introduced. Kodo is
 a C++11 network coding library intended to make network coding
@@
 found in~\cite{pahlevani2013playncool,krigslund2013core,
-paramanathan2013leanandmean}. For the Raspberry Pi platform, an evaluation
-of the performance of \ac{RLNC} can be found in \cite{paramanathan2014sharing}.
+paramanathan2013leanandmean,seferoglu2011i2nc}. For the Raspberry Pi device, an evaluation
+of the performance of a decentralized network code for distributed systems, \ac{RLNC},
+\cite{ho2006random}, can be found in \cite{paramanathan2014sharing}.
 However, this evaluation focused particularly on observing the achievable
-speeds with \ac{RLNC} \cite{ho2006random} by different configurations of
-the code parameters with a single thread and no hardware acceleration through
-\ac{SIMD}.
+speeds only for \ac{RLNC} with different configurations of
+the code parameters. In this previous work, a relevant practical aspect that
+was not evaluated was the use of hardware acceleration through \ac{SIMD} or
+the multi-core capabilities of more advanced \ac{Raspi} models. These features are
+becoming more frequent in new processors to largely increase their computational
+power for the upcoming demand. In this sense, the Raspberry Pi posses an \ac{ARM}
+architecture that could be multi-core as mentioned and also exploits the \ac{SIMD}
+feature with the optimized NEON instruction set, but still to the best of our knowledge
+there has been no documentation in the literature about these capabilities.
 
-In this work, we provide detailed measurements of the goodput (processing
+Therefore, in this work we provide detailed measurements of the goodput (processing
 speed) and energy consumption of \ac{Raspi} models 1 and 2, when
 performing network coding operations with different codecs based on \ac{RLNC}
-such as: full dense \ac{RLNC}, multicore-enabled \ac{RLNC}, sparse \ac{RLNC}
-and tunable sparse \ac{RLNC}. For these coding schemes, the encoder and implementations from Kodo now detect and exploit the \ac{SIMD}
-capabilities of the Raspberry Pi. We also assess the \ac{Raspi}
-performance excluding the effect of packet losses or delays in order to have a
-description of the codes in terms of their parameters. To achieve this,
-we perform a measurement campaign with the indicated coding schemes and
-their parameters in the Raspberry Pi platform. Our measurements permit
-us to characterize the goodput and energy consumption
-of these devices showing that speeds of 800 Mbps and processing energy per bit
-values of 0.1 nJ are possible. Our work is organized as follows.
+such as: full dense \ac{RLNC}, multi-core enabled \ac{RLNC}, sparse \ac{RLNC}
+and tunable sparse \ac{RLNC}. For these coding schemes, the encoder and decoder
+implementations from Kodo are able to detect and make use of the \ac{SIMD}
+through the NEON instruction set of the Raspberry Pi by recognizing the \ac{ARM}
+architecture with its multicore capabilities. We assess
+the \ac{Raspi} performance excluding the effect of packet losses or delays in
+order to have a description of the processing and energy consumption for only the
+codes in terms of their parameters. To achieve this, we perform a measurement
+campaign with the indicated coding schemes and their parameters in various models
+of a Raspberry Pi device. Our measurements permit us to characterize the mentioned
+metrics of these devices showing that processing peeds of 800 Mbps and processing
+energy per bit values of 0.1 nJ are possible. Our work is organized as follows.
 Section~\ref{sec:schemes} defines the

### 2016-08-16 reviewer_reply.txt
Corrected version. Update review reply. Update readme.rst

@@
 Dear reviewer,
-Thank you very much for your valuable feedback. We have corrected all the indicated and other
-found typos by proof-reading the manuscript. We have also replaced the abbreviations "l.d." and
-"l.i." to "linearly dependent" and "linearly independent" as suggested to enhance clarity in the 
-notation. Regarding the definition of "g", We have defined the parameter "g" as the total number of original packets to be encoded.
+Thank you very much for your valuable feedback. We have listed your comments below and described
+our corrections to hopefully solve the indicated issues.
 
-FIXME: the notation [1,g] (and many other notations) should be changed to
-       maybe [1,2,...g]
-Nestor: Can you make this modification while I advance in the intro?
+- We have corrected all the indicated and other found typos by proof-reading the manuscript. We
+have also replaced the abbreviations "l.d." and "l.i." to "linearly dependent" and "linearly
+independent" as suggested to enhance clarity in the notation.
 
-FIXME: change notation such as $\mathbb{N}$ as this is typically used for positive numbers
-Nestor: Can you make this modification while I advance in the intro?
+- Regarding the definition of "g", We have defined the parameter "g" as the total number of
+original packets to be encoded once at beginning of Section 2.
+
+- For the notation [1,g] to denote the set of integer number between 1 and "g", we have modified
+all its appearances to [1,2,...,g] to indicate the integer nature of this set in a more standard
+fashion. Also, in our
+definitions the notation
+
+- For the notation $\mathbb{N}$ for the random number of packets to be combined in SRLNC, we have
+modified all its appearances to $\mathbb{M}$ to avoid any confusion with the notation for the set of
+positive numbers.
 
@@
 Dear reviewer,
-Thank you very much for your valuable feedback. We have listed your comments below and described what we have changed to hopefully improve the indicated issues.
+Thank you very much for your valuable feedback. We have listed your comments below and described
+our corrections or observations to hopefully solve the indicated issues.
 
@@
 
-We have rewritten the parts that indicate a proposed system. All our measurements are performed within a single Raspberry Pi. We only replace the traditional power supply with an Agilent Power
+We have rewritten the parts that indicate a proposed system. All our measurements are performed
+within a single Raspberry Pi. We only replace the traditional power supply with an Agilent Power
 Supply device to monitor and log the power consumption.
 
-- Finally and in a word, the motivation of this paper is unclear. The main question is “why Raspberry pi in network coding?”. What is the advantage of using Raspberry pi?
+- Finally and in a word, the motivation of this paper is unclear. The main question is "why
+Raspberry pi in network coding?". What is the advantage of using Raspberry pi?
 
 We consider that the Raspberry Pi models 1 and 2 are good representatives of a low-cost computer
-considered as IoT devices in terms of performance and capabilities. We now elaborate on this idea in the introduction by providing various use cases of IoT + Raspi. At the end of the description of
+considered as IoT devices in terms of performance and capabilities. We now elaborate on this idea
+in the introduction by providing various use cases of IoT + Raspi. At the end of the description of
 the use cases of IoT + Raspi, we specifically mention that despite this advances, data is still
-being conveyed in a conventional way that will hit a performance roof with new services demands. This is why we motivate about network coding since it is proven its utility in the area of meshed
-networks where IoT deployments occur.
-Another reason for using the Raspberry Pi is its large user community in contrast to many other low cost devices.
-This allows a system developer to use standard tools and / or based on either Windows or Linux, reducing the development time.
-Finally, the Raspberry Pi models 1 and 2, have one and four cores respectively and they support hardware acceleration through the NEON instruction set in ARM that is mandatory to reach the full potential of network coding where we have included the proper details.
-We have updated the introduction to hopefully elaborate on all these subjects to show why using network coding in Raspberry Pi is interesting.
+being conveyed in a conventional way that will hit a performance roof with new services demands.
+This is why we motivate about network coding, e.g. since the usefulness of network coding has been
+verified in the area of meshed networks in prior works. Meshed networks will be the scenario where
+upcoming IoT deployments will mostly occur.
 
-- They only consider q=2 and 28 , however, as it is mentioned in “Chou, Philip A., Yunnan Wu, and Kamal Jain.
-"Practical network coding." (2003).”, based on security aspect, in practice, wey should consider q=28 and 216.
-By this assumption, they should show and compare the results with q=216 too.
+Another two important reasons for using the Raspberry Pi are: First, its large user community in
+contrast to many other low-cost devices. This allows a system developer to use standard tools
+and / or based on either Windows or Linux, reducing the development time. Second, the Raspberry
+Pi models 1 and 2, have one and four cores respectively and they support hardware acceleration
+through the NEON instruction set in ARM that is mandatory to reach the full potential of network
+coding where we have included the proper details. We have updated the introduction to elaborate
+on all these subjects to show why using network coding in Raspberry Pi is interesting.
 
-We have made a reference to two papers by Achuthan et al. ("Lean and Mean" and "Sharing the Pi").
-These two references include measurements for both q=2^8 and q=2^16 and indicate a performance degradation of approximately 10x.
-The underlying reason is that using Galois fields higher than 2^8 provide no perceivable benefit in terms of the decoding probability while increasing in complexity.
-At the end, this turns disastrous for the code.
-We also ran a few measurements ourself that
-indicated similar performance gab between the two field types.
-Another reason to not consider q=2^16 is that it is not a standard field size.
-q=2^8 is the standard today and q=2 is beneficial in terms of performance in low-computing power devices.
-For security purposes, there exists even better ways than using q=2^16.
+- They only consider q=2 and 28 , however, as it is mentioned in "Chou, Philip A., Yunnan Wu, and
+Kamal Jain. "Practical network coding." (2003).", based on security aspect, in practice, wey
+should consider q=28 and 216. By this assumption, they should show and compare the results with
+q=216 too.
 
-- The list of references neglects some of the most relevant papers.
-Moreover, the authors have cited to their previous papers (i.e., [6,7,8,10,11,12,13,17,21,27,30])!!!
-It seems they want to increase citation of their papers!
+We have made a reference to two papers by Achuthan et al. (i.e. "Lean and Mean" [23] and "Sharing
+the Pi" [25]). These two references include measurements for both q=2^8 and q=2^16 and indicate
+a performance degradation of approximately 10X for going from q=2^8 to q=2^16. The underlying
+reason is that using Galois fields higher than 2^8 provide no perceivable benefit in terms of the
+decoding probability while increasing in complexity and processing overhead due to the coding
+coefficients. At the end, this significantly reduces the performance of the code. To verify this,
+we also ran a few measurements ourself that indicated a similar performance gap between the two
+field types. Another reason to not consider q=2^16 is that it is not a standard field size. q=2^8
+is the standard today (comparable with Reed-Solomon codes for example) and q=2 is beneficial in
+terms of performance in low-computing power devices. Finally, for security purposes, there exists
+much secure ways than only using q=2^16.
 
-We link to our prior work as this paper is mostly based on those papers. We have removed reference 10 and 30 and added a few more citations to related work done by others.
+- The list of references neglects some of the most relevant papers. Moreover, the authors have
+cited to their previous papers (i.e., [6,7,8,10,11,12,13,17,21,27,30])!!! It seems they want to
+increase citation of their papers!
 
-FIXME: Did we remove reference 10 and 30?
+We have updated the list of references to provide a richer balance in the State-of-the-Art,
+relevant baseline references and our prior work.
 
-Nestor: Which were these papers? These numbers have changed already
+We now have included several references to previous State-of-the-Art and references related
+to use cases for IoT employing the Raspberry Pi [1-9]. Also we have included missing
+references and grouped them with the baseline of network coding [10-16,26].
 
-- The presentation of the paper is not very good.
-The authors did not care very much about the structure, the language (i.e., page 2 line 42 “Furthermore, in [7], the Kodo library was introduce.” Should be introduced….)
+We link to our prior work as this paper evaluation is based on research lines started
+in those papers. These prior works report our findings in the area of network coding for
+wireless mesh networks and network coding for the Raspberry Pi. To be more specific: Theoretical
+gains and practical implementations of network coding for wireless
+meshed networks are reported in [17,19,21,22]. The Kodo library, our basic building block for the coding operations is [18]. Basic measurements + observed effects of Random
+Linear Network Coding for commercial devices are found in [23]. A initial study of RLNC for
+the Raspberry Pi is available in [25]. Finally, our work with Sparse and Tunable Sparse Network
+Coding is described in [28-31].
+
+At the end, our references consist of less than 27% of the references in the study. We hope
+that this solves the raised issue.
+
+- The presentation of the paper is not very good. The authors did not care very much about the
+structure, the language (i.e., page 2 line 42 "Furthermore, in [7], the Kodo library was
+introduce." Should be introduced....)
 
@@
 Thank you very much for your valuable feedback. We have corrected all the mentioned and other found
-typos as suggested by proof-reading the manuscript and changed the figures in section 4.4 to show the goodput instead of the throughput by properly labelling the axis and verifying that the shown
+typos as suggested by proof-reading the manuscript and changed the figures in section 4.4 to show
+the goodput instead of the throughput by properly labelling the axis and verifying that the shown
 data is correct.

### 2016-08-16 introduction.tex
Corrected version. Update review reply. Update readme.rst

@@
 codes~\cite{reed1960polynomial}, network coding is a technology that
-has been implemented in real systems since the early years of its
-conception. Authors in~\cite{katti2008xors} showed the
-performance of the COPE protocol for the two-way relay channel
+has been studied and implemented in real systems since the early years of
+its conception. A decentralized network code that has been proven
+to achieve the multicast capacity with very high probability is
+\ac{RLNC} \cite{ho2006random}. Later, a work observing the
+benefits of employing \ac{RLNC} in meshed networks is the MORE protocol
+addressed in \cite{chachulski2007more}. Shortly afterwards, authors
+in~\cite{katti2008xors} showed the performance of an implementation
+of the COPE protocol for the two-way relay channel
 in a wireless network, which relied on minimalistic coding and obtaining
-gains over a forwarding scheme. Later, the work in~\cite{pedersen2008implementation} used commercially available
+gains over a forwarding scheme. Later, the work
+in~\cite{pedersen2008implementation} used commercially available
 Symbian OS mobile phones to implement network coding in a
@@
 found in~\cite{pahlevani2013playncool,krigslund2013core,
-paramanathan2013leanandmean,seferoglu2011i2nc}. For the Raspberry Pi device, an evaluation
-of the performance of a decentralized network code for distributed systems, \ac{RLNC},
-\cite{ho2006random}, can be found in \cite{paramanathan2014sharing}.
+paramanathan2013leanandmean,seferoglu2011i2nc}. For the Raspberry Pi device, an
+evaluation of \ac{RLNC} can be found in \cite{paramanathan2014sharing}.
 However, this evaluation focused particularly on observing the achievable

### 2016-08-16 schemes.tex
Corrected version. Update review reply. Update readme.rst

@@
 %network coding, all the original data packets $P_j, j \in [1,g]$, each
-network coding, $g$ original data packets $P_j, j \in [1,2,\ldots,g]$, each
+network coding, $g$ original data packets also called a generation
+\cite{chou2003practical}, $P_j, j \in [1,2,\ldots,g]$, each
 of $B$ bytes, are used to create coded packets using random linear
@@
 \begin{align} \label{eq:coded_packet}
-C_i  &= \bigoplus_{j=1}^{g} v_{ij} \otimes P_j ,\ \forall i \in [1,\ldots)
+C_i  &= \bigoplus_{j=1}^{g} v_{ij} \otimes P_j ,\ \forall i \in [1,2,\ldots)
 \end{align}
@@
 \label{eq:appended_coded_coefficients}
-{(\textbf{W} \textbf{V})}_{ij} = \sum_{k=1}^{g} w_{ik} v_{kj}\ ,\ \forall i,j \in [1,g] \times [1,g].
+{(\textbf{W} \textbf{V})}_{ij} = \sum_{k=1}^{g} w_{ik} v_{kj}\ ,\ \forall i,j \in [1,2,\ldots,g] \times [1,2,\ldots,g].
 \end{align}
@@
 that we will combine to create a coded packet. To do so, a random
-number, $\mathbb{N}$, of the original packets is used to produce a
-coded packet. For our case, $\mathbb{N}$ is binomially distributed
+number, $\mathbb{M}$, of the original packets is used to produce a
+coded packet. For our case, $\mathbb{M}$ is binomially distributed
 with parameters $g$ for the number of trials and $d$ for its success
-probability, e.g. $\mathbb{N} \sim Binomial(g,d)$. However,
+probability, e.g. $\mathbb{M} \sim Binomial(g,d)$. However,
 when sampling from this distribution, the case
-$\mathbb{N} = 0$ occurs with a non-zero probability. In order to handle
+$\mathbb{M} = 0$ occurs with a non-zero probability. In order to handle
 this special case, our implementation considers
-$\mathbb{K} = \max(1,\mathbb{N})$ as the final amount of packets to be
+$\mathbb{K} = \max(1,\mathbb{M})$ as the final amount of packets to be
 mixed together. In this way, we always ensure that at least one packet is
@@
 The only caveat is that the case of $\mathbb{K} = 1$ occurs slightly
-more often than $\mathbb{N} = 1$ in the original distribution, but for
+more often than $\mathbb{M} = 1$ in the original distribution, but for
 the considered density range in this method, this is not a significant
@@
 distribution for the number of packets to mix has been defined, we
-sample a value $n$ from $\mathbb{N}$ and compute $k =
-\max(1,n)$. Later, we create a set $\mathcal{K}$ with
+sample a value $m$ from $\mathbb{M}$ and compute $k =
+\max(1,m)$. Later, we create a set $\mathcal{K}$ with
 cardinality $k$, e.g. $|\mathcal{K}| = k$, where the elements in
@@
 is filled with non-repeated elements taken uniformly at random from
-$[1,\ldots,g]$. Finally, once the set of indexes has been defined, a coded
-packet using \ac{SRLNC} can be written as shown in
+the continuous interval $[1,\ldots,g]$. Finally, once the set of indexes has been
+defined, a coded packet using \ac{SRLNC} can be written as shown in
 \eqref{eq:sparse_coded_packet2}:
@@
 \begin{equation}\label{eq:feedback_dofs}
-    r(k) = \floor{g\cdot \left[\frac{2^k -1}{2^k}\right]},\ k \in \Big[1,\ldots,\ceil{log_2(g)}+1\Big]
+    r(k) = \floor{g\cdot \left[\frac{2^k -1}{2^k}\right]},\ k \in \Big[1, 2, \ldots,\ceil{log_2(g)}+1\Big]
 \end{equation}

### 2016-08-16 reviewer_reply.txt
Update reviewer 3 comments

@@
 Dear reviewer,
-Thank you very much for your valuable feedback. We have corrected all the mentioned and other found
-typos as suggested by proof-reading the manuscript and changed the figures in section 4.4 to show
-the goodput instead of the throughput by properly labelling the axis and verifying that the shown
-data is correct.
+Thank you very much for your valuable feedback.
+We have listed your comments below and described our corrections or observations to
+hopefully solve the indicated issues.
+
+- The setting is limited to a network without intermediate nodes and without packet loss
+We considered this scenario to measure the code performance on device basis. For example, adding
+the effect of packet losses would not permit to estimate the energy consumption on a given device
+since there is energy wasted on possibly lost packets in a given setting.
+
+- Usually RLNC is not a practical scheme due to its high storage cost at the intermediate
+nodes when the number of packets is large.
+For RLNC the amount of collected packets needed to decode would be similar to any other erasure
+code the only difference is that they are coded and some overhead due to the coding coefficients
+must be hold. Still, in the study we open the possibility to reduce the complexity by using sparse
+codes.
+
+- Regarding typos:
+We have corrected all the mentioned and other found typos as suggested by proof-reading the
+manuscript and changed the figures in section 4.4 to show the goodput instead of the throughput by
+properly labelling the axis and verifying that the shown data is correct.

### 2016-09-29 introduction.tex
Uncommited changes?

@@
 evaluate this type of scenarios are highly desirable for research.
-With the emergence of the \ac{Raspi}, a lrelatively powerful low-cost
+With the emergence of the \ac{Raspi}, a relatively powerful low-cost
 computer with the size of a credit card, these evaluations are becoming
@@
 not satisfy the need of a distributed network for \ac{IoT}
-applications as mentioned earlier
+applications as mentioned earlier.
 
@@
 was not evaluated was the use of hardware acceleration through \ac{SIMD} or
-the multi-core capabilities of more advanced \ac{Raspi} models. These features are
+the multicore capabilities of more advanced \ac{Raspi} models. These features are
 becoming more frequent in new processors to largely increase their computational
 power for the upcoming demand. In this sense, the Raspberry Pi posses an \ac{ARM}
-architecture that could be multi-core as mentioned and also exploits the \ac{SIMD}
+architecture that could be multicore as mentioned and also exploits the \ac{SIMD}
 feature with the optimized NEON instruction set, but still to the best of our knowledge
@@
 performing network coding operations with different codecs based on \ac{RLNC}
-such as: full dense \ac{RLNC}, multi-core enabled \ac{RLNC}, sparse \ac{RLNC}
+such as: full dense \ac{RLNC}, multicore enabled \ac{RLNC}, sparse \ac{RLNC}
 and tunable sparse \ac{RLNC}. For these coding schemes, the encoder and decoder

### 2016-09-29 schemes.tex
Uncommited changes?

@@
 \eqref{eq:coding_matrix}, from top to bottom. The purpose is to obtain
-the equivalence  $\textbf{V}$ in its reduced echelon form. The steps
+the equivalence of $\textbf{V}$ in its reduced echelon form. The steps
 for reducing the matrix by elementary row operations are carried out each time
@@
 equivalent to each original packet with the weight of the
-$w_{i,j}$.Therefore, we define the local coding matrix $\textbf{W}$ in
+$w_{ij}$.Therefore, we define the local coding matrix $\textbf{W}$ in
 the same way as it was made for $\textbf{V}$. Thus, the local coding
@@
 information. For example, we might find the case where
-$\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] = \mathbf{0}$ may
-happen frequently for low densities. In that case, the encoder
+$\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] = \mathbf{0}$ to occur
+frequently for low densities. In that case, the encoder
 discards the coded packet and tries to generate a new one to avoid the
@@
 Therefore, in \ac{TSNC}, a simple procedure for controlling this probability
-is to gradually increase the coding density as the \ac{dof}\footnote{We refer
+is to gradually increase the coding density as the \ac{dof} \footnote{We refer
 as degrees of freedom to the dimension of the linear span from the coded

### 2016-09-30 introduction.tex
fix typo

@@
 of a Raspberry Pi device. Our measurements permit us to characterize the mentioned
-metrics of these devices showing that processing peeds of 800 Mbps and processing
+metrics of these devices showing that processing speeds of 800 Mbps and processing
 energy per bit values of 0.1 nJ are possible. Our work is organized as follows.
